---
title: "Cosy analysis"
author: "Louise Bernard"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
output:
  bookdown::pdf_document2:
    number_sections: true
    keep_tex: true
  bookdown::html_document2:
    number_sections: true
header-includes:
  - \usepackage{float}
  - \usepackage{booktabs}
  - \usepackage{lscape}
  - \usepackage{mathtools}
  - \usepackage{amsmath}
  - \newcommand{\blandscape}{\begin{landscape}}
  - \newcommand{\elandscape}{\end{landscape}}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include=FALSE, warning  = FALSE, fig.pos = "H", out.extra = "")

# Run on a subsample of the data for faster processing
random_subsample <- FALSE

# Function to check if a package is installed, and if not, install it
install_if_needed <- function(package) {
  if (!require(package, character.only = TRUE)) {
    install.packages(package, dependencies = TRUE)
    library(package, character.only = TRUE)
  }
}

# List of packages to load
packages <- c(
  "knitr", "kableExtra", "did", "fixest", "data.table", "lubridate", 
  "dplyr", "ggplot2", "RColorBrewer", "tidyr", "scales", 
  "forcats", "viridis",  "stringr", "stargazer", "panelView", "readxl", "HonestDiD"
)

# Load (and install if needed) each package
lapply(packages, install_if_needed)

# Create folders without warning message
dir.create("../graphs", showWarnings = FALSE)
dir.create("../data", showWarnings = FALSE)
dir.create("../data/scratch", showWarnings = FALSE)
dir.create("../data/output", showWarnings = FALSE)
dir.create("../data/input", showWarnings = FALSE)
dir.create("../tables", showWarnings = FALSE)

# set dictionary
setFixest_dict(c(total_consumption = "Consumption in kWh per period", 
                 daily_consumption = "Consumption in kWh per day",
                 consumption_hh = "Half Hourly Consumption in kWh",
                 share_consumption = "Share of daily consumption",
                 weekly_consumption = "Gas Consumption per Week in kWh",
                 cosy_contract_active = "Cosy Contract Active",
                 daily_avg_heating_degree = "HDD",
                 avg_heating_degree = "HDD",
                 settlement_week = "Week",
                 date = "Day", 
                 hashed_mpan = "Household", 
                 tariff_gsp_group_id = "GSP", 
                 rate_period = "Rate period",
                 is_variable = "Variable Tariff",
                 energy_efficiency = "Energy Efficiency",
                 estimated_annual_consumption = "EAC",
                 eac_mwh = "EAC in mWh",
                 is_hp_installed = "Is HP Installed",
                 predicted_is_installed = "Is HP Installed",
                 elec_consumption = "Monthly Electricity Consumption (kWh)",
                 gas_consumption = "Monthly Gas Consumption (kWh)",
                 month_date = "Month",
                 is_winter = "Winter",
                 previous_is_variable = "Prev Is Variable",
                 epc_letter = "EPC",
                 predicted_heatloss_watts = "Heatloss (W)",
                 total_floor_area = "Floor Area (m sq)",
                 urban = "Urban",
                 floor_area = "Floor area",
                 property_value = "Property value",
                 account_id = "Household",
                 ev_charging = "EV Charging",
                 has_ev = "EV User"))


# Custom colors from the provided image 
flexible_color <- "#4C515C"  # Replace with the exact hex code for Flexible
cosy_color <- "#5F8ED9"      # Replace with the exact hex code for Cosy

# Define main functions
# Function to format numbers
format_number <- function(number) {
  return(format(round(number), big.mark = ",", scientific = FALSE))
}

# Function to format numbers with four decimal places
format_decimal <- function(number, decimals = 4) {
  return(format(round(number, decimals), nsmall = decimals, big.mark = ",", scientific = FALSE))
}


# Register the pre-treatment average fit statistic
fitstat_register("pre_avg", function(x) {
  
  # Extract the formula
  formula <- x$fml_all$linear
  
  # Extract the outcome variable from the formula
  outcome_variable <- all.vars(formula)[1]
  
  # Extract the call object and evaluate the data argument
  call_object <- x$call
  data_expr <- call_object$data
  data <- eval(data_expr)
  
  # Get the logical vector of observations used in the model
  obs_used <- obs(x)
  
  # Subset the original dataset using this logical vector
  data_used <- data[obs_used, ]
  
  # Ensure the outcome variable is treated as a column name
  outcome_values <- data_used[[outcome_variable]]
  
  # Create pre-avg for non-HP installed group
  pre_avg <- mean(outcome_values[data_used$cosy_contract_active == 0], na.rm = TRUE)
  
  # Format the pre-avg
  formatted_pre_avg <- format_decimal(pre_avg)
  
  return(formatted_pre_avg)
}, "Half Hourly Consumption")



# Add number of time periods
fitstat_register("t_obs", function(x) {
  
  # time variable
  t_var <- x$fixef_vars[3]
  
  # nbr of unique val for t var
  t_obs <- x$fixef_sizes[t_var]
  
  return(format_number(t_obs))
}, "Number of Time Periods")

CleanPreAverage <- function(file_path) {
  
  # Read the generated LaTeX file
  file_content <- readLines(file_path)
  
  # Find the lines with the pre-treatment average and remove them
  if (length(grep("Half Hourly Consumption", file_content))==1) {
    pre_avg_line_index <- grep("Half Hourly Consumption", file_content)
  } else {
    pre_avg_line_index <- grep("Half Hourly Consumption", file_content)[2]
  }
  
  pre_avg_lines <- file_content[pre_avg_line_index:(pre_avg_line_index)]
  file_content <- file_content[-c(pre_avg_line_index, pre_avg_line_index)]
  
  # Find the position just after the coefficients
  coeff_end_index <- grep("Fixed-effects", file_content) -2
  
  # Insert the pre-treatment average row after the coefficients
  file_content <- append(file_content, pre_avg_lines, after = coeff_end_index)
  file_content <- append(file_content, "\\emph{Pre-Treatment Average}\\\\", after = coeff_end_index)
  
  # Add a \midrule after the pre-treatment average
  file_content <- append(file_content, "\\midrule", after = coeff_end_index)
  
  # Modify the label for "Size of the 'effective' sample" to "Number of Households"
  sample_line <- grep("Size of the 'effective' sample", file_content)
  file_content[sample_line] <- gsub("Size of the 'effective' sample", "Number of Households", file_content[sample_line])
  
  # Write the modified content back to the LaTeX file
  writeLines(file_content, file_path)
}


```


# Data Preparation

## Merging consumption and customers info datasets

```{r load-data}

if(!file.exists("../data/scratch/aggregated_data.RDS")) {
  
  # agreement data
  # run queries/Cosy - agreement data
  agreements <- fread("../data/input/Cosy_-_agreement_data_2024_07_24.csv") %>%
    filter(product_display_name == "Cosy Octopus") %>%
    arrange(hashed_mpan, agreement_valid_from) %>%
    mutate(
      from = as.Date(agreement_valid_from),
      to = as.Date(agreement_valid_to)
    ) %>%
    select(hashed_mpan, from, to) %>%
    group_by(hashed_mpan) %>%
    summarise(
      periods = list(data.frame(from, to)),
      first_adoption = min(from),  # Get the earliest agreement date for 'adoption'
      first_week = format(min(from), "%Y-%U"),  # Format the first adoption date as year-week
      .groups = 'drop'
    )
  
  # files are created using 
  # queries/cosy - cosy electricity readings
  # queries/cosy - cosy electricity reading part 2 which I ran for different years seperately
  aggregated_data <- rbind(fread("../data/input/cosy_-_cosy_electricity_reading_part_2_2024_07_26.csv"),
                           fread("../data/input/cosy_-_cosy_electricity_reading_part_2_2024_07_26 (1).csv"),
                           fread("../data/input/cosy_-_cosy_electricity_reading_part_2_2024_07_26 (2).csv")) %>%
    rename(total_consumption = total_read_value,
           consumption_hh = mean_read_value) %>%
    mutate(date = as.Date(settlement_date)) %>% 
    filter(!is.na(date))     %>%
    select(-c(settlement_date))
  
  # Function to check if a date falls within any period
  check_active_contract <- function(date, periods) {
    any(sapply(1:nrow(periods[[1]]), function(i) date >= periods[[1]][i, "from"] && (date <= periods[[1]][i, "to"] | is.na(periods[[1]][i, "to"]))))
  }
  
  # Add indicator without heavy merging
  consumption_with_indicator <- aggregated_data %>%
    rowwise() %>%
    mutate(
      cosy_contract_active = {
        periods <- agreements$periods[agreements$hashed_mpan == hashed_mpan]
        if (length(periods) == 0) 0 else as.integer(check_active_contract(date, periods))
      }
    ) %>%
    ungroup()
  
  # join with the earliest adoption date
  aggregated_data <- consumption_with_indicator %>%
    inner_join(agreements %>% select(-periods))
  
  # add overall
  aggregated_data <- rbind(
    aggregated_data, 
    aggregated_data %>% 
      group_by(account_id, hashed_mpan, date, cosy_contract_active, first_adoption, first_week) %>%
      summarise(total_consumption = sum(total_consumption)) %>%
      mutate(rate_period = "Overall",
             consumption_hh = total_consumption/48)) %>%
    mutate(rate_period = factor(rate_period, levels = c("Morning Cosy",
                                                        "Afternoon Cosy",
                                                        "Peak Rate",
                                                        "Other", 
                                                        "Overall")), 
           weeks_since_cosy = floor(as.numeric(difftime(date, first_adoption, units = "weeks")))) 
  
  # Remove the ~ 50 mpans with 2 account id
  duplicate_mpan <- aggregated_data %>%
    select(account_id, hashed_mpan) %>%    # Selecting the necessary columns
    distinct() %>%                         # Removing completely identical rows
    count(hashed_mpan) %>%                 # Count occurrences of each hashed_mpan
    filter(n > 1) %>%                      # Keep only those with more than one occurrence
    left_join(aggregated_data %>% group_by(account_id, hashed_mpan) %>% summarise(min_date = min(date), max_date = max(date)), by = "hashed_mpan") %>%
    arrange(hashed_mpan, account_id)       # Arrange for better visibility
  
  # add customers characteristics
  # from queries/cosy - cosy details
  cosy_cosy_details_2024_06_25 <- fread("../data/input/cosy_-_cosy_details_2024_06_25.csv") %>%
    distinct()
  
  # Remove moan associated with two accounts !
  merged_data <- aggregated_data %>%
    filter(!hashed_mpan %in% duplicate_mpan$hashed_mpan) %>%
    inner_join(cosy_cosy_details_2024_06_25)
  
  # add weather
  # queries/cosy analysis - weather
  weather <- fread("../data/input/Cosy Analysis Weather Mar 26 daily.csv") %>% 
    rename_with(.cols = starts_with("weekly"), 
                .fn = ~ sub("^weekly", "daily", .)) %>%
    mutate(date_day=as.Date(date_day, format = "%Y-%m-%d")) %>%
    rename(date = date_day)
  
  aggregated_data <- merged_data %>%
    left_join(weather, by =c("gsp_group_id", "date"))
  
  
  Prev_contract <- fread("../data/input/Cosy_-_agreement_data_2024_07_24.csv") %>%
    arrange(hashed_mpan, as.Date(agreement_valid_from)) %>%
    group_by(hashed_mpan) %>%
    mutate(
      previous_contract = lag(product_display_name),
      previous_is_variable = lag(is_variable),
      previous_is_charged_half_hourly = lag(is_charged_half_hourly),
      is_cosy = product_display_name == "Cosy Octopus"
    ) %>%
    filter(is_cosy) %>%
    slice_head(n=1)
  
  
  aggregated_data <- aggregated_data %>%
    mutate(epc_letter = case_when(
      energy_efficiency >= 91 ~ "A",
      energy_efficiency >= 81 & energy_efficiency <= 90 ~ "B",
      energy_efficiency >= 69 & energy_efficiency <= 80 ~ "C",
      energy_efficiency >= 55 & energy_efficiency <= 68 ~ "D",
      energy_efficiency >= 39 & energy_efficiency <= 54 ~ "E",
      energy_efficiency >= 21 & energy_efficiency <= 38 ~ "F",
      energy_efficiency <= 20 ~ "G",
      TRUE ~ NA_character_
    ),
    eac_mwh = estimated_annual_consumption/1000) %>%
    left_join(Prev_contract)
  
  
  saveRDS(aggregated_data, "../data/scratch/aggregated_data.RDS")
  
  rm(weather, adoption, consumption_with_indicator, agreements)
} else {
  aggregated_data <- readRDS("../data/scratch/aggregated_data.RDS") 
}

# Run on a subsample of the data for faster processing
if (random_subsample) {
  set.seed(123)
  sampled_accounts <- sample(unique(aggregated_data$account_id), 1000)
  aggregated_data <- aggregated_data %>% 
    filter(account_id %in% sampled_accounts)
  gc()
}


```

## Rates Graphs 

### Figure 2: Cosy Rate by Period

```{r plotcosyrate}
# Load the prices
rates <- fread("../data/input/cosy_-_rate_analysis_2024_07_15.csv")  %>%
  mutate(valid_from = as.Date(valid_from),
         valid_to = as.Date(valid_to),
         valid_from = ifelse(is.na(valid_from), as.Date("2022-12-13"), valid_from),
         valid_to = ifelse(is.na(valid_to), as.Date("2024-07-15"), valid_to),
         valid_from = as.Date(valid_from),
         valid_to = as.Date(valid_to)
  ) %>%
  filter(!(valid_from == as.Date("2022-12-13") & valid_to == as.Date("2023-03-31")), !valid_from == "2024-06-30") 

# Add the typical marginal price as a reference column
marginal_price <- rates %>%
  filter(rate_start_at == "INTERVAL '07:00:00' HOUR TO SECOND") %>%
  distinct(tariff_gsp_group_id, valid_from, unit_rate) %>%
  rename(typical_marginal_price=unit_rate)

# Merge typical marginal price back into the full dataset
rates <- rates %>%
  left_join(marginal_price) %>%
  mutate(share_of_typical = unit_rate / typical_marginal_price * 100)

plot_selection <- rates %>%
  filter(tariff_gsp_group_name == "North Western",valid_from == "2022-12-13") 

# Get the unique valid_from date
unique_valid_from <- unique(plot_selection$valid_from)

# Create a sequence of times for the single day in 1-minute intervals
times <- seq(from = as.POSIXct(paste(unique_valid_from, "00:00:00")), 
             to = as.POSIXct(paste(unique_valid_from, "23:59:00")), by = "1 min")

# Initialize rates with NA and group
rate_data <- data.frame(
  time = times,
  rate = NA,
  group = "Cosy"
)

# Function to convert INTERVAL strings to times and apply the rates
apply_rates <- function(data, rates) {
  for (i in 1:nrow(data)) {
    start_time <- as.POSIXct(paste(unique_valid_from, substr(data$rate_start_at[i], 11, 18)), format="%Y-%m-%d %H:%M:%S")
    end_time <- as.POSIXct(paste(unique_valid_from, substr(data$rate_end_at[i], 11, 18)), format="%Y-%m-%d %H:%M:%S")
    if (start_time > end_time) {
      # Handle cases where the interval crosses midnight
      rates$rate[rates$time >= start_time | rates$time < end_time] <- data$unit_rate[i]
    } else {
      rates$rate[rates$time >= start_time & rates$time < end_time] <- data$unit_rate[i]
    }
  }
  return(rates)
}

# Apply the rates using the most recent period
rate_data <- apply_rates(plot_selection, rate_data)

# Create a data frame for Flexible Octopus with a constant rate
flexible_octopus <- data.frame(
  time = times,
  rate = plot_selection[plot_selection$rate_start_at == "INTERVAL '07:00:00' HOUR TO SECOND",]$unit_rate,
  group = "Typical Marginal Price"
)

# Combine both data frames
combined_rates <- rbind(rate_data, flexible_octopus)

# Define the specific rate values for y-axis breaks
rate_values <- sort(unique(plot_selection$unit_rate))

# Define the time periods for shading
shaded_times <- data.frame(
  xmin = as.POSIXct(paste(unique_valid_from, c("04:00:00", "13:00:00", "16:00:00")), format="%Y-%m-%d %H:%M:%S"),
  xmax = as.POSIXct(paste(unique_valid_from, c("07:00:00", "16:00:00", "19:00:00")), format="%Y-%m-%d %H:%M:%S"),
  fill = c("red", "red", "lightblue")
)

# Calculate the typical marginal price (you can adjust this based on your data)
typical_marginal_price <- mean(combined_rates %>% filter(group == "Typical Marginal Price") %>% pull(rate), na.rm = TRUE)

# Add a new column for the share of the typical marginal price
combined_rates <- combined_rates %>%
  mutate(share_of_typical = rate / typical_marginal_price * 100)

# Plot the line chart with Flexible Octopus in dashed line and specific y-axis breaks
# Assuming unique_valid_from is the date used in your 'time' sequence
ggplot(combined_rates, aes(x = time, y = rate, color = group, linetype = group)) +
  geom_rect(data = shaded_times, aes(xmin = xmin, xmax = xmax, ymin = -Inf, ymax = Inf, fill = fill),
            inherit.aes = FALSE, alpha = 0.2) +
  geom_line(size = 1) +
  labs(x = "Time of Day",
       y = "Rate (p/kWh)",
       color = "Tariff") +
  scale_x_datetime(date_labels = "%H:%M", 
                   date_breaks = "2 hour", 
                   limits = c(as.POSIXct(min(combined_rates$time)), 
                              as.POSIXct(max(combined_rates$time)- hours(1)))) +  # Set x-axis limits with correct date
  scale_y_continuous(
    name = "Rate (p/kWh)",
    breaks = rate_values,
    labels = scales::label_number(accuracy = 0.01),  # Format y-axis with 2 decimal places
    sec.axis = sec_axis(~ . / typical_marginal_price, 
                        name = "Share of Typical Marginal Price (%)", 
                        labels = scales::percent_format(accuracy = 1))
  ) +
  theme_minimal() + 
  theme(legend.position = "bottom") +
  scale_color_manual(values = c("Cosy" = cosy_color, "Typical Marginal Price" = flexible_color)) +
  scale_linetype_manual(values = c("Cosy" = "solid", "Typical Marginal Price" = "dashed")) +
  scale_fill_identity() +
  guides(linetype = "none")

ggsave("../graphs/Cosy Tariff.png", width = 10, height = 4, dpi = 300)

```

```{r}
# Load the prices
rates <- fread("../data/input/cosy_-_rate_analysis_2024_07_15.csv")  %>%
  mutate(valid_from = as.Date(valid_from),
         valid_to = as.Date(valid_to),
         valid_from = ifelse(is.na(valid_from), as.Date("2022-12-13"), valid_from),
         valid_to = ifelse(is.na(valid_to), as.Date("2024-07-15"), valid_to),
         valid_from = as.Date(valid_from),
         valid_to = as.Date(valid_to)
  ) %>%
  filter(!(valid_from == as.Date("2022-12-13") & valid_to == as.Date("2023-03-31")), !valid_from == "2024-06-30") 

# Add the typical marginal price as a reference column
marginal_price <- rates %>%
  filter(rate_start_at == "INTERVAL '07:00:00' HOUR TO SECOND") %>%
  distinct(tariff_gsp_group_id, valid_from, unit_rate) %>%
  rename(typical_marginal_price=unit_rate)

# Merge typical marginal price back into the full dataset
rates <- rates %>%
  left_join(marginal_price) %>%
  mutate(share_of_typical = unit_rate / typical_marginal_price * 100)

plot_selection <- rates %>%
  filter(tariff_gsp_group_name == "North Western",valid_from == "2024-03-31") 

# Get the unique valid_from date
unique_valid_from <- unique(plot_selection$valid_from)

# Create a sequence of times for the single day in half-hour intervals
times <- seq(from = as.POSIXct(paste(unique_valid_from, "00:00:00")), 
             to = as.POSIXct(paste(unique_valid_from, "23:30:00")), by = "30 min")

# Initialize rates with NA and group
rate_data <- data.frame(
  time = times,
  rate = NA,
  group = "Cosy"
)

# Function to convert INTERVAL strings to times and apply the rates
apply_rates <- function(data, rates) {
  for (i in 1:nrow(data)) {
    start_time <- as.POSIXct(paste(unique_valid_from, substr(data$rate_start_at[i], 11, 18)), format="%Y-%m-%d %H:%M:%S")
    end_time <- as.POSIXct(paste(unique_valid_from, substr(data$rate_end_at[i], 11, 18)), format="%Y-%m-%d %H:%M:%S")
    if (start_time > end_time) {
      # Handle cases where the interval crosses midnight
      rates$rate[rates$time >= start_time | rates$time < end_time] <- data$unit_rate[i]
    } else {
      rates$rate[rates$time >= start_time & rates$time < end_time] <- data$unit_rate[i]
    }
  }
  return(rates)
}

# Apply the rates using the most recent period
rate_data <- apply_rates(plot_selection, rate_data)

# Create a data frame for Flexible Octopus with a constant rate
flexible_octopus <- data.frame(
  time = times,
  rate = plot_selection[plot_selection$rate_start_at == "INTERVAL '07:00:00' HOUR TO SECOND",]$unit_rate,
  group = "Typical Marginal Price"
)

# Combine both data frames
combined_rates <- rbind(rate_data, flexible_octopus)

# Define the specific rate values for y-axis breaks
rate_values <- sort(unique(plot_selection$unit_rate))

# Define the time periods for shading
shaded_times <- data.frame(
  xmin = as.POSIXct(paste(unique_valid_from, c("04:00:00", "13:00:00", "16:00:00")), format="%Y-%m-%d %H:%M:%S"),
  xmax = as.POSIXct(paste(unique_valid_from, c("07:00:00", "16:00:00", "19:00:00")), format="%Y-%m-%d %H:%M:%S"),
  fill = c("lightblue", "lightblue", "red")
)

# Calculate the typical marginal price (you can adjust this based on your data)
typical_marginal_price <- mean(combined_rates %>% filter(group == "Typical Marginal Price") %>% pull(rate), na.rm = TRUE)

# Add a new column for the share of the typical marginal price
combined_rates <- combined_rates %>%
  mutate(share_of_typical = rate / typical_marginal_price * 100)

# Plot the line chart with Flexible Octopus in dashed line and specific y-axis breaks
ggplot(combined_rates, aes(x = time, y = rate, color = group, linetype = group)) +
  geom_rect(data = shaded_times, aes(xmin = xmin, xmax = xmax, ymin = -Inf, ymax = Inf, fill = fill),
            inherit.aes = FALSE, alpha = 0.2) +
  geom_line(size = 1) +
  labs(x = "Time of Day",
       y = "Rate (p/kWh)",
       color = "Tariff") +
  scale_x_datetime(date_labels = "%H:%M", date_breaks = "2 hour") +
  scale_y_continuous(
    name = "Rate (p/kWh)",
    breaks = rate_values,
    labels = scales::label_number(accuracy = 0.01),  # Format y-axis with 2 decimal places
    sec.axis = sec_axis(~ . / typical_marginal_price, 
                        name = "Share of Typical Marginal Price (%)", 
                        labels = scales::percent_format(accuracy = 1))
  ) +
  theme_minimal() + 
  theme(legend.position = "bottom") +
  scale_color_manual(values = c("Cosy" = cosy_color, "Typical Marginal Price" = flexible_color)) +
  scale_linetype_manual(values = c("Cosy" = "solid", "Typical Marginal Price" = "dashed")) +
  scale_fill_identity() +
  guides(linetype = "none")


```

### Figure A.16: Rates by Rate Period and GSP Group as of 01 June 2024

```{r rategsp}
# Create rate_period indicator
rates <- rates %>%
  mutate(rate_period = case_when(
    rate_start_at == "INTERVAL '04:00:00' HOUR TO SECOND" ~ "Morning \n & Afternoon Cosy",
    rate_start_at == "INTERVAL '07:00:00' HOUR TO SECOND" ~ "Other \n ( ~ Typical Marginal Price)",
    rate_start_at == "INTERVAL '13:00:00' HOUR TO SECOND" ~ "Morning \n & Afternoon Cosy",
    rate_start_at == "INTERVAL '16:00:00' HOUR TO SECOND" ~ "Peak Rate",
    rate_start_at == "INTERVAL '19:00:00' HOUR TO SECOND" ~ "Other \n ( ~ Typical Marginal Price)",
    TRUE ~ "Other"
  ),
  rate_period = factor(rate_period, levels = c("Morning \n & Afternoon Cosy","Other \n ( ~ Typical Marginal Price)", "Peak Rate")))

# Get the number of unique GSP group names
num_gsp_groups <- length(unique(rates$tariff_gsp_group_name))

# Define a color palette using RColorBrewer and colorRampPalette to generate more colors if needed
palette <- colorRampPalette(brewer.pal(12, "Set3"))(num_gsp_groups)

# Add the typical marginal price as a reference column
rates_selection <- rates %>%
  filter(valid_from == "2024-03-31") 


# Part 1: Bar graph showing all the rates by rate_period and GSP group name
ggplot(rates_selection, aes(x = rate_period, y = unit_rate, fill = tariff_gsp_group_name)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(x = "Rate Period",
       y = "Rate (p/kWh)",
       fill = "GSP Group") +
  scale_y_continuous(
    name = "Rate (p/kWh)",
    labels = scales::label_number(accuracy = 0.01),  # Format y-axis with 2 decimal places
    sec.axis = sec_axis(~ . / typical_marginal_price, 
                        name = "Share of Typical Marginal Price (%)", 
                        labels = scales::percent_format(accuracy = 1))
  ) +
  theme_minimal() +
  scale_fill_manual(values = palette) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggsave("../graphs/Rates_by_Rate_Period_and_GSP_Group.png", width = 10, height = 6, dpi = 300)

```

### Figure A.17: Rates Over Time


```{r rate-by-periods}

# Get the global min and max unit_rate
global_min_rate <- min(rates$unit_rate, na.rm = TRUE)
global_max_rate <- max(rates$unit_rate, na.rm = TRUE)

# Part 2: Line graphs showing the change in rates over time for each rate_period, grouped by region
rates_long <- rates %>%
  group_by(tariff_gsp_group_name, rate_period) %>%
  arrange(valid_from)

# Create annotations data frame
annotations <- rates_long %>%
  group_by(rate_period) %>%
  summarise(
    valid_from = as.Date("2023-01-01"),
    share_of_typical = median(share_of_typical, na.rm = TRUE),
    unit_rate = median(unit_rate, na.rm = TRUE),
    tariff_gsp_group_name = unique(tariff_gsp_group_name)
  )

ggplot(rates_long, aes(x = valid_from, y = unit_rate, color = tariff_gsp_group_name, group = interaction(tariff_gsp_group_name, rate_period))) +
  geom_line(size = 1) +
  labs(
    x = "Date",
    y = "Rate (p/kWh)",
    color = "GSP Group") +
  theme_minimal() +
  scale_color_manual(values = palette) +
  ylim(global_min_rate, global_max_rate) +
  geom_text(data = annotations, aes(label = rate_period), vjust = 0.8, hjust = 0, color = "grey")


ggsave("../graphs/Rate_Changes_by_Period.png", width = 12, height = 8, dpi = 300)

```


### Figure A.18: Rates as Share of Typical Marginal Price Over Time

```{r margprice}
# Aggregate the data by rate_period and valid_from to get the average for all GSP groups
rates_avg <- rates %>%
  group_by(rate_period, valid_from) %>%
  summarise(
    avg_unit_rate = mean(unit_rate, na.rm = TRUE),
    avg_share_of_typical = mean(share_of_typical, na.rm = TRUE)
  )

# Create annotations data frame
annotations <- rates_avg %>%
  group_by(rate_period) %>%
  summarise(
    valid_from = as.Date("2023-01-01"),
    avg_unit_rate = median(avg_unit_rate, na.rm = TRUE),
    avg_share_of_typical = median(avg_share_of_typical, na.rm = TRUE)
  )

# Define specific y-axis breaks for share of typical marginal price
share_breaks <- seq(0, 160, 20)

# Define a palette of blue colors
blue_palette <- scales::brewer_pal(palette = "Blues")(length(unique(rates_avg$rate_period)))

# Plot average share of typical marginal price over time
ggplot(rates_avg, aes(x = valid_from, y = avg_share_of_typical, color = rate_period, group = rate_period)) +
  geom_line(size = 1) +
  labs(
    x = "Date",
    y = "Average Share of Typical Marginal Price (%)",
    color = "Rate Period"
  ) +
  theme_minimal() +
  scale_color_manual(values = blue_palette) +
  scale_y_continuous(
    name = "Average Share of Typical Marginal Price (%)",
    breaks = share_breaks,
    labels = scales::percent_format(accuracy = 0.1, scale = 1)
  ) + 
  theme(legend.position = "bottom") +
  geom_text(data = annotations, aes(label = rate_period), vjust = 1.2, hjust = 0, color = "grey")


ggsave("../graphs/Average_Share_of_Typical_Marginal_Price_by_Period.png", width = 12, height = 8, dpi = 300)

```

## Summary Statistics Tables and Graphs {#sec:sumstats}

```{r prevcontractanalysis, eval=TRUE}
Next_contract <- fread("../data/input/Cosy_-_agreement_data_2024_07_24.csv") %>%
  arrange(hashed_mpan, desc(as.Date(agreement_valid_from))) %>%
  group_by(hashed_mpan) %>%
  mutate(na_flag = ifelse(is.na(agreement_valid_to), 1, 0),
         na_cumsum = cumsum(na_flag)) %>%
  filter(na_cumsum == 1) %>%
  select(-na_flag, -na_cumsum) %>%
  ungroup()%>%
  group_by(hashed_mpan) %>%
  slice(1) %>%
  mutate(is_variable = ifelse(product_display_name %in% 
                                c("Co-op Flexible",
                                  "Flexible Avro",
                                  "Flexible Octopus",
                                  "Flexible Octopus Smart Pay as You Go",
                                  "Loyal Flexible Octopus Smart Pay as You Go"), FALSE, is_variable)) %>%
  group_by(is_charged_half_hourly) %>%
  tally() %>%
  ungroup() %>%
  mutate(share_is_variable = n/sum(n))

# Contract before cosy
first_cosy_contracts <- fread("../data/input/Cosy_-_agreement_data_2024_07_24.csv") %>%
  arrange(hashed_mpan, as.Date(agreement_valid_from)) %>%
  group_by(hashed_mpan) %>%
  mutate(
    previous_contract = lag(product_display_name),
    previous_is_variable = lag(is_variable),
    previous_is_charged_hh = lag(is_charged_half_hourly),
    is_cosy = product_display_name == "Cosy Octopus"
  ) %>%
  filter(is_cosy) %>%
  slice_head(n = 1) %>%
  mutate(previous_is_variable = ifelse(previous_contract %in% 
                                         c("Co-op Flexible",
                                           "Flexible Avro",
                                           "Flexible Octopus",
                                           "Flexible Octopus Smart Pay as You Go",
                                           "Loyal Flexible Octopus Smart Pay as You Go"), 
                                       FALSE, 
                                       previous_is_variable)) %>%
  filter(!is.na(previous_is_variable)) %>%
  group_by(previous_is_charged_hh) %>%
  tally() %>%
  mutate(share = 100*n/sum(n)) %>%
  arrange(share)
```

### Figure 3: Weekly Adoption of the Cosy tariff

```{r adoption}

# Prepare the data
weekly_adoptions <- aggregated_data %>%
  ungroup() %>%
  select(hashed_mpan, first_adoption) %>%
  distinct() %>%
  mutate(first_week = floor_date(first_adoption, "week")) %>%
  group_by(first_week) %>%
  summarise(adoptions = n())

# Define the date for the announcement
announcement_date <- as.Date("2023-08-31")

# Choose a color from the Brewer palette for the text annotation
text_color <- brewer.pal(n = 3, name = "Set1")[1]

# Create the plot with the vertical line and adjusted annotation
ggplot(weekly_adoptions, aes(x = first_week, y = adoptions)) +
  geom_line(color = cosy_color) +  # Line plot for trends with a color from the Brewer palette
  geom_point(color = cosy_color) +  # Points to highlight individual data with the same color
  geom_vline(xintercept = as.numeric(announcement_date), linetype = "dashed", color = text_color) +  # Vertical line for the announcement
  annotate("text", x = announcement_date - weeks(1), y = 150,
           label = "Announcement:\nBoiler Upgrade Scheme\nincrease to £7,500", hjust = 1, color = text_color) +  # Annotate the vertical line
  labs(
    x = "Week",
    y = "Customers switching to Cosy"
  ) +
  scale_x_date(
    labels = scales::date_format("%b %y"),  # Formatting months and years
    date_breaks = "1 month"  # Adjust this based on your data density
  ) +
  theme_minimal() +
  theme(
    legend.position="none",
    axis.text.x = element_text(angle = 45, hjust = 1)  # Improve readability by rotating labels
  )

# Save the plot
ggsave("../graphs/weekly_adoptions.png", width = 16, height = 8, units = "cm")

```

```{r cosy-retention}
# Analyze contracts
contract_analysis_all <-fread("../data/input/Cosy_-_agreement_data_2024_07_24.csv") 

contract_analysis <- contract_analysis_all %>%
  inner_join(aggregated_data %>% distinct(account_id, hashed_mpan)) %>%
  filter(product_display_name == "Cosy Octopus") %>%
  arrange(account_id, hashed_mpan, agreement_valid_from) %>%
  mutate(
    from = as.Date(agreement_valid_from),
    to = as.Date(agreement_valid_to)
  ) %>%
  select(account_id, hashed_mpan, from, to) %>%
  group_by(account_id) %>%
  summarise(
    num_contracts = n(),  # Count number of contracts per customer
    ongoing = sum(is.na(to)),  # Count how many contracts are ongoing
    ended = sum(!is.na(to))  # Count how many contracts have ended
  ) %>%
  mutate(
    category = case_when(
      num_contracts == 1 & ongoing == 1 ~ "Stayed on Cosy (ongoing)",
      num_contracts == 1 & ended == 1 ~ "Tried then switched",
      num_contracts > 1 ~ "Multiple contracts",
      TRUE ~ "Other"  # Catch-all for any other cases
    )
  )

# Count each category
category_counts <- contract_analysis %>%
  count(category)

print(category_counts)

```


## Availability of smart meter data

### Figure A.19: Smart Meter Data Availability for Cosy Adopters

```{r panelview, eval= FALSE}

if (!file.exists("../graphs/data_availability.png")) {
  plot_panel <- panelview(consumption_hh ~ cosy_contract_active + daily_avg_heating_degree, 
                          data = aggregated_data %>% filter(rate_period=="Overall", !is.na(date), !is.na(hashed_mpan)) %>% select(consumption_hh, hashed_mpan, date, cosy_contract_active, daily_avg_heating_degree) %>% distinct(), index = c("hashed_mpan","date"), 
                          xlab = "Time", ylab = "hashed_mpan", by.timing = TRUE, 
                          pre.post = TRUE, gridOff = TRUE, axis.lab.gap = c(100),
                          main = "Smart Meter Data Availability",
                          background = "white",
                          color = c(flexible_color, cosy_color, "white"),
                          legend.labs = c("Before Cosy", "After Cosy", "No smart meter data"), 
                          collapse.history = "TRUE")
  ggsave("../graphs/data_availability.png", 
         width = 16, height = 8, units = "cm")
}

```


## External Validity Tables 



```{r early-vs-late}

# start date
start_date <- aggregated_data %>% ungroup() %>% summarise(date=min(first_adoption, na.rm = TRUE))
start_date <- start_date$date

# Found the previous contract before adopting cosy
Prev_contract <- fread("../data/input/Cosy_-_agreement_data_2024_07_24.csv") %>%
  arrange(hashed_mpan, as.Date(agreement_valid_from)) %>%
  group_by(hashed_mpan) %>%
  mutate(
    previous_contract = lag(product_display_name),
    previous_is_variable = lag(is_variable),
    previous_is_charged_half_hourly = lag(is_charged_half_hourly),
    is_cosy = product_display_name == "Cosy Octopus"
  ) %>%
  filter(is_cosy) %>%
  slice_head(n=1)

# Create a hashed_mpan dataset
first_adoption <- aggregated_data %>%
  left_join(Prev_contract) %>%
  ungroup() %>%
  select(hashed_mpan, tariff_gsp_group_id, first_adoption, urbanity, previous_is_charged_half_hourly,
         floor_area, eac_mwh, property_value, energy_efficiency, estimated_annual_consumption) %>%
  distinct() %>%
  mutate(adoption_week =  round(as.numeric(difftime(floor_date(first_adoption, "week"), start_date, units = "weeks"))),
         urban = case_when(
           urbanity %in% c('Large Urban Areas', 'Smaller Urban Areas') ~ 1,
           urbanity %in% c('Accessible Settlements', 'Sparse/Remote Villages/Dwellings', 'Accessible Villages/Dwellings', 'Sparse/Remote Settlements') ~ 0,
           TRUE ~ NA
         ))

# early adoptors table
m_adopters <- feols(adoption_week ~ i(urban, ref=0) + log(floor_area) + log(property_value) + log(energy_efficiency) + log(estimated_annual_consumption) + previous_is_charged_half_hourly, data = first_adoption, se = "hetero")

etable(m_adopters)

# Extract coefficients and standard errors
coefs <- coeftable(m_adopters) %>%
  data.frame() %>%
  tibble::rownames_to_column("term") %>%
  filter(term != "(Intercept)") %>%
  mutate(term = case_when(term == "i(factor_var = urban, ref = 0)" ~ "Urban",
                          term == "log(floor_area)" ~ "Log Floor Area",
                          term == "log(property_value)" ~ "Log Property Value",
                          term == "log(energy_efficiency)" ~ "Log Energy Efficiency",
                          term == "log(estimated_annual_consumption)" ~ "Log Estimated Consumption",
                          term == "previous_is_touTRUE" ~ "Previous Contract Is ToU",
                          TRUE ~ term),
         lower_ci = Estimate - 1.96 * `Std..Error`,
         upper_ci = Estimate + 1.96 * `Std..Error`
  ) %>%
  arrange(Estimate)


# Add a note below the graph
note <- "Note: The dependent variable is adoption week (0 for the first week adopters up to 65 for the later). \n Early adopters are more urban, have higher electricity consumption and more energy efficient homes. \n Data: Domus dataset and OE energy."

```





```{r pop-weighted-msoas1, eval= FALSE}
# Function to calculate weighted standard deviation
weighted_sd <- function(x, w) {
  sum_w <- sum(w, na.rm = TRUE)
  mean_w <- sum(w * x, na.rm = TRUE) / sum_w
  sqrt(sum(w * (x - mean_w)^2, na.rm = TRUE) / sum_w)
}

# Function to perform weighted t-test
weighted_t_test <- function(x, w, y, v) {
  n_x <- sum(w, na.rm = TRUE)
  n_y <- sum(v, na.rm = TRUE)
  mean_x <- sum(w * x, na.rm = TRUE) / n_x
  mean_y <- sum(v * y, na.rm = TRUE) / n_y
  var_x <- sum(w * (x - mean_x)^2, na.rm = TRUE) / n_x
  var_y <- sum(v * (y - mean_y)^2, na.rm = TRUE) / n_y
  t_stat <- (mean_x - mean_y) / sqrt(var_x / n_x + var_y / n_y)
  df <- (var_x / n_x + var_y / n_y)^2 / ((var_x / n_x)^2 / (n_x - 1) + (var_y / n_y)^2 / (n_y - 1))
  p_value <- 2 * pt(-abs(t_stat), df)
  return(p_value)
}

# Function to summarize and test
summarize_and_test <- function(data, var_name, weight_name) {
  # Calculate weighted means, standard deviations, and non-missing observation counts for each treatment group
  summary_stats <- data %>%
    group_by(treated) %>%
    summarise(
      N = sum(!is.na(.data[[var_name]])), # Count non-missing observations
      Weighted_Mean = weighted.mean(.data[[var_name]], .data[[weight_name]], na.rm = TRUE),
      SD = weighted_sd(.data[[var_name]], .data[[weight_name]]),
      .groups = 'drop'
    ) %>%
    pivot_wider(names_from = treated, values_from = c("N", "Weighted_Mean", "SD"), names_sep = " ")
  
  # Prepare for weighted t-test by separating data and weights
  data1 <- filter(data, treated == 1)[[var_name]]
  weights1 <- filter(data, treated == 1)[[weight_name]]
  data2 <- filter(data, treated == 0)[[var_name]]
  weights2 <- filter(data, treated == 0)[[weight_name]]
  
  # Check if both groups have sufficient data for weighted t-test
  if (length(unique(data1)) > 1 && length(unique(data2)) > 1 && length(data1) > 1 && length(data2) > 1) {
    p_value <- weighted_t_test(data1, weights1, data2, weights2)
  } else {
    p_value <- NA_real_ # Insufficient data or variability
  }
  
  # Combine results
  tibble(Variable = var_name) %>%
    bind_cols(summary_stats) %>%
    mutate(`P Value` = p_value)
}

# Read and process each dataset
# https://www.ons.gov.uk/peoplepopulationandcommunity/populationandmigration/populationestimates/datasets/middlesuperoutputareamidyearpopulationestimates

population2022 <- read_excel("../data/input/sapemsoasyoatablefinal.xlsx", sheet = "Mid-2022 MSOA 2021", skip = 3)

cosy_hp_details <- fread("../data/input/cosy_-_cosy_details_2024_07_24.csv") %>%
  inner_join(aggregated_data %>% select(hashed_mpan) %>% distinct()) %>%
  select(hashed_mpan, postcode) %>%
  distinct() %>%
  group_by(postcode) %>%
  tally() %>%
  filter(!postcode == "")
# https://www.data.gov.uk/dataset/c2235117-cbfd-480d-8fc7-b564bd0f4d58/output-area-2021-to-lsoas-to-msoas-to-lep-to-lad-dec-2022-best-fit-lookup-in-en-v2
postcode_msoa <- fread("../data/input/PCD_OA21_LSOA21_MSOA21_LAD_AUG23_UK_LU.csv") %>%
  left_join(cosy_hp_details, by = c("pcds" = "postcode")) %>%
  mutate(n = ifelse(is.na(n), 0, 1)) %>%
  select(msoa21cd, n) %>%
  group_by(msoa21cd) %>%
  summarise(treated = sum(n))
# https://www.ons.gov.uk/peoplepopulationandcommunity/personalandhouseholdfinances/incomeandwealth/bulletins/smallareamodelbasedincomeestimates/financialyearending2020
income <- readxl::read_excel("../data/input/saiefy1920finalqaddownload280923.xlsx", sheet = "Total annual income", skip = 4) %>%
  select(`MSOA code`, `Total annual income (£)`) %>%
  distinct() 

# Load and preprocess the property_prices data
# https://www.ons.gov.uk/peoplepopulationandcommunity/housing/datasets/hpssadataset3meanhousepricebymsoaquarterlyrollingyear
property_prices <- read_excel("../data/input/HPSSA Dataset 3 - Mean price paid by MSOA.xls", 
                              sheet = "1a", skip = 4) %>%
  select(`MSOA code`, `Year ending Mar 2023`) %>%
  rename(msoa21cd = `MSOA code`, `Property price (£)` = `Year ending Mar 2023`)

# customs dataset from https://www.ons.gov.uk/datasets/create
hh_size <- fread("../data/input/custom-filtered-2024-07-03T10_58_30Z.csv") %>%
  group_by(`Middle layer Super Output Areas Code`) %>%
  mutate(sum_obs = sum(Observation), weight = Observation / sum_obs) %>%
  summarise(`Average HH Size` = sum(weight * `Household size (9 categories) Code`))

hh_deprivaton <- fread("../data/input/custom-filtered-2024-07-03T10_43_12Z.csv") %>%
  group_by(`Middle layer Super Output Areas Code`) %>%
  mutate(sum_obs = sum(Observation), `HH Not Deprived in Any Dim. (%)` = 100 * Observation / sum_obs) %>%
  filter(`Household deprivation (6 categories) Code` == 1)

avg_age <- fread("../data/input/custom-filtered-2024-07-03T11_15_15Z.csv") %>%
  group_by(`Middle layer Super Output Areas Code`) %>%
  mutate(sum_obs = sum(Observation), weight = Observation / sum_obs) %>%
  summarise(`Average Age` = sum(weight * `Age (101 categories) Code`))

education <- fread("../data/input/custom-filtered-2024-07-03T11_22_39Z.csv") %>%
  group_by(`Middle layer Super Output Areas Code`) %>%
  mutate(sum_obs = sum(Observation), `Share Level 4 Qualifications (%)` = 100 * Observation / sum_obs) %>%
  filter(`Highest level of qualification (7 categories) Code` == 4)

# Merge all datasets by `MSOA code` or `Middle layer Super Output Areas Code`
merged_data <- postcode_msoa %>%
  inner_join(income, by = c("msoa21cd"="MSOA code")) %>%
  inner_join(property_prices,by = c("msoa21cd")) %>%
  inner_join(hh_size, by = c("msoa21cd" = "Middle layer Super Output Areas Code")) %>%
  inner_join(hh_deprivaton, by = c("msoa21cd" = "Middle layer Super Output Areas Code")) %>%
  inner_join(avg_age, by = c("msoa21cd" = "Middle layer Super Output Areas Code")) %>%
  inner_join(education, by = c("msoa21cd" = "Middle layer Super Output Areas Code")) %>%
  inner_join(population2022 %>% select(`MSOA 2021 Code`, Total), by = c("msoa21cd" = "MSOA 2021 Code")) %>%
  mutate(country = substr(msoa21cd, 1, 1),
         treated = as.numeric(treated > 0)) %>%
  filter(!msoa21cd == "", country %in% c("E", "W"))

# List of variables of interest
variables <- c(
  "Total annual income (£)",
  "Property price (£)",
  "Average HH Size",
  "HH Not Deprived in Any Dim. (%)",
  "Average Age",
  "Share Level 4 Qualifications (%)"
)

# Applying the function across all variables
results <- purrr::map_dfr(variables, ~summarize_and_test(merged_data, .x, "Total")) %>%
  as.data.frame()

# Format the counts with thousand separators
results <- results %>%
  mutate(`N 1` = format(`N 1`, big.mark = ",", scientific = FALSE),
         `N 0` = format(`N 0`, big.mark = ",", scientific = FALSE))

# Adjust the format of the table for LaTeX output
formatted_results <- results %>%
  select(Variable, `Weighted_Mean 1`, `SD 1`, `Weighted_Mean 0`, `SD 0`, `P Value`) %>%
  rename(
    `Weighted Mean Treated` = `Weighted_Mean 1`,
    `SD Treated` = `SD 1`,
    `Weighted Mean Others` = `Weighted_Mean 0`,
    `SD Others` = `SD 0`
  ) %>%
  mutate(
    `Weighted Mean Treated` = paste0(format(round(`Weighted Mean Treated`, 2), big.mark = ",", nsmall = 2), " (", format(round(`SD Treated`, 2), big.mark = ",", nsmall = 2), ")"),
    `Weighted Mean Others` = paste0(format(round(`Weighted Mean Others`, 2), big.mark = ",", nsmall = 2), " (", format(round(`SD Others`, 2), big.mark = ",", nsmall = 2), ")"),
    `P Value` = format(round(`P Value`, 2), nsmall = 2)
  ) %>%
  select(Variable, `Weighted Mean Treated`, `Weighted Mean Others`)

# Add the N values to the column names
colnames(formatted_results)[2] <- paste0("MSOAs with Cosy Adopters (N = ", results$`N 1`[1], ")")
colnames(formatted_results)[3] <- paste0("Other MSOAs (N = ", results$`N 0`[1], ")")

# Create the LaTeX table using stargazer
stargazer(formatted_results, type = "latex", summary = FALSE, 
          title = "External Validity by Area for \textit{Cosy} Adopters",
          rownames = FALSE,
          digits = 2,
          label = "tab:msoa-stats-cosy",
          out = "../tables/balance_table_cosy.tex")

# Read the content of the generated LaTeX table
latex_table <- readLines("../tables/balance_table_cosy.tex")

# Insert custom headers with multicolumn
header_row <- " & \\multicolumn{2}{c}{Weighted Mean} \\\\"
position <- grep("\\\\begin\\{tabular\\}", latex_table) + 1
latex_table <- append(latex_table, header_row, after = position)

# Replace the first and last instances of \hline \\[-1.8ex] with \hline \hline \\[-1.8ex]
hline_ex_lines <- grep("\\hline" , latex_table)
if (length(hline_ex_lines) >= 2) {
  latex_table[hline_ex_lines[1]] <- gsub("\\hline", "\\hline\\hline", latex_table[hline_ex_lines[1]], fixed = TRUE)
  latex_table[hline_ex_lines[length(hline_ex_lines)]] <- gsub("\\hline", "\\hline\\hline", latex_table[hline_ex_lines[length(hline_ex_lines)]], fixed = TRUE)
}

# Write the modified LaTeX table to a new file
writeLines(latex_table, "../tables/balance_table_cosy.tex")
```





```{r pop-weighted-msoas, eval= FALSE}

# Function to summarize and test
summarize_and_test <- function(data, var_name, weight_name) {
  # Calculate weighted means, standard deviations, and non-missing observation counts for each treatment group
  summary_stats <- data %>%
    group_by(treated) %>%
    summarise(
      N = sum(!is.na(.data[[var_name]])), # Count non-missing observations
      Weighted_Mean = weighted.mean(.data[[var_name]], .data[[weight_name]], na.rm = TRUE),
      SD = weighted_sd(.data[[var_name]], .data[[weight_name]]),
      .groups = 'drop'
    ) %>%
    pivot_wider(names_from = treated, values_from = c("N", "Weighted_Mean", "SD"), names_sep = " ")
  
  # Prepare for weighted t-test by separating data and weights
  data1 <- filter(data, treated == 1)[[var_name]]
  weights1 <- filter(data, treated == 1)[[weight_name]]
  data2 <- filter(data, treated == 0)[[var_name]]
  weights2 <- filter(data, treated == 0)[[weight_name]]
  
  # Check if both groups have sufficient data for weighted t-test
  if (length(unique(data1)) > 1 && length(unique(data2)) > 1 && length(data1) > 1 && length(data2) > 1) {
    p_value <- weighted_t_test(data1, weights1, data2, weights2)
  } else {
    p_value <- NA_real_ # Insufficient data or variability
  }
  
  # Combine results
  tibble(Variable = var_name) %>%
    bind_cols(summary_stats) %>%
    mutate(`P Value` = p_value)
}


# Load and preprocess the cosy_hp_details data
population2022 <- read_excel("../data/input/sapemsoasyoatablefinal.xlsx", sheet = "Mid-2022 MSOA 2021", skip = 3)

cosy_hp_details <- fread("../data/input/cosy_-_cosy_details_2024_07_24.csv") %>%
  inner_join(aggregated_data %>% select(hashed_mpan) %>% distinct(), by = "hashed_mpan") %>%
  select(hashed_mpan, postcode, property_value) %>%
  distinct() %>%
  group_by(postcode) %>%
  summarise(property_value = mean(property_value, na.rm = TRUE)) %>%
  filter(postcode != "")

# Load and preprocess the postcode_msoa data
postcode_msoa <- fread("../data/input/PCD_OA21_LSOA21_MSOA21_LAD_AUG23_UK_LU.csv") %>%
  left_join(cosy_hp_details, by = c("pcds" = "postcode")) %>%
  mutate(treated = ifelse(is.na(property_value), 0, 1)) %>%
  select(msoa21cd, treated, property_value)

# Load and preprocess the property_prices data
property_prices <- read_excel("../data/input/HPSSA Dataset 3 - Mean price paid by MSOA.xls", 
                              sheet = "1a", skip = 4) %>%
  select(`MSOA code`, `Year ending Mar 2023`) %>%
  rename(msoa21cd = `MSOA code`, year_ending_mar_2023 = `Year ending Mar 2023`)

# Merge all datasets
merged_data <- postcode_msoa %>%
  inner_join(property_prices, by = "msoa21cd") %>%
  mutate(country = substr(msoa21cd, 1, 1)) %>%
  filter(msoa21cd != "", country %in% c("E", "W"))

# Create combined data frame for plotting
treated_1 <- merged_data %>%
  filter(treated == 1) %>%
  select(property_value = year_ending_mar_2023) %>%
  mutate(group = "MSOAs with Cosy Customers")

treated_0 <- merged_data %>%
  filter(treated == 0) %>%
  select(property_value = year_ending_mar_2023) %>%
  mutate(group = "MSOAs without Cosy Customers")

property_value_data <- merged_data %>%
  filter(!is.na(property_value)) %>%
  select(property_value) %>%
  mutate(group = "Cosy Customers")

combined_data <- bind_rows(
  treated_1,
  treated_0,
  property_value_data
)

# Trim outliers by removing values outside the 1st and 99th percentiles
trimmed_combined_data <- combined_data %>%
  group_by(group) %>%
  filter(property_value > quantile(property_value, 0.01) & property_value < quantile(property_value, 0.99))

# Calculate means for each group
means <- trimmed_combined_data %>%
  group_by(group) %>%
  summarise(mean_value = mean(property_value, na.rm = TRUE))

ggplot(trimmed_combined_data, aes(x = property_value, color = group, fill = group)) +
  geom_density(alpha = 0.5, aes(y = ..scaled..)) +
  geom_vline(data = means, aes(xintercept = mean_value, color = group), linetype = "dashed") +
  scale_color_manual(values = c("skyblue", "lightgreen", "orange")) +
  scale_fill_manual(values = c("skyblue", "lightgreen", "orange")) +
  scale_x_continuous(labels = dollar_format(prefix = "£", suffix = "k", scale = 1e-3, big.mark = ",")) +
  labs(
    title = "Density Plot of Property Prices",
    x = "Property Value",
    y = "Density",
    color = NULL,  # Remove the legend title for color
    fill = NULL    # Remove the legend title for fill
  ) +
  theme_classic() +
  theme(legend.position = "bottom")


ggsave("../graphs/average_property_price.png", width = 12, height = 8, dpi = 300)


```


# Empirical Analysis {#sec:results}

## TWFE Heterogeneity Analysis

### Table A.9: Cosy Adoption on Electricity Consumption Controlling for EV Charging

```{r ev}
# ev half hours 
# Read the CSV file
ev_charging <- fread("../data/input/cosy_-_ev_detection_2024_07_04.csv") %>%
  mutate(ev_charging = 1,
         date = as.Date(interval_start),
         interval_start = as.POSIXct(interval_start, format="%Y-%m-%d %H:%M:%S"),
         hour = as.integer(format(interval_start, "%H")),
         rate_period = case_when(
           hour >= 4 & hour < 7 ~ "Morning Cosy",
           hour >= 13 & hour < 16 ~ "Afternoon Cosy",
           hour >= 16 & hour < 19 ~ "Peak Rate",
           TRUE ~ "Other"
         )
  )

# Aggregate at the account id, mpan, date and rate period level
ev_charging_agg <- rbind(ev_charging %>%
                           group_by(account_id,  hashed_mpan, date, rate_period) %>%
                           tally(),
                         ev_charging %>%
                           group_by(account_id,  hashed_mpan, date) %>%
                           tally() %>% 
                           mutate(rate_period="Overall")) %>%
  rename(ev_charging=n)

# EV users details
ev_users <- ev_charging %>%
  group_by(account_id) %>%
  summarise(is_ev_detected= min(as.Date(interval_start)))

# Update hp_installed with the new ev_charging values using case_when
aggregated_data <- aggregated_data %>%
  left_join(ev_charging_agg) %>%
  mutate(ev_charging = ifelse(is.na(ev_charging), 0, ev_charging),
         ev_charging = case_when(
           rate_period == "Overall" ~ ev_charging / 48,
           rate_period == "Other" ~ ev_charging / 30,
           TRUE ~ ev_charging / 6
         ),
         rate_period = factor(rate_period, levels = c("Morning Cosy",
                                                      "Afternoon Cosy",
                                                      "Peak Rate",
                                                      "Other", 
                                                      "Overall"))) %>%
  left_join(ev_users) %>%
  mutate(has_ev = as.numeric(is_ev_detected <= date),
         has_ev = ifelse(is.na(has_ev), 0, has_ev)) %>%
  distinct(account_id, date, rate_period, .keep_all=TRUE)

# Fit the model
m1c <- feols(consumption_hh ~ i(cosy_contract_active, ref=0) + has_ev + i(cosy_contract_active, has_ev, ref=0) | 
               daily_avg_heating_degree + account_id + date, 
             data = aggregated_data, 
             cluster = ~account_id, 
             split = ~ rate_period)

etable( m1c, cluster = ~ account_id + date)

# Generate the initial LaTeX table
etable(m1c, tex = TRUE, title = "Cosy Adoption on Electricity Consumption Controlling for EV Charging", 
       fitstat = ~ N + g + pre_avg + t_obs + r2, 
       file = "../tables/did_ev.tex", replace = TRUE, label = "tab:hp-did-ev")
CleanPreAverage("../tables/did_ev.tex")
```

###  Table 3: Cosy Adoption on Probability of Charging EV by Period

```{r}


# Identify the period with the highest EV charging for each mpan and date
ev_charging_max <- ev_charging %>%
  group_by(account_id, hashed_mpan, date, rate_period) %>%
  summarise(ev_charging = sum(ev_charging, na.rm = TRUE)) %>%
  group_by(account_id, hashed_mpan, date) %>%
  filter(ev_charging == max(ev_charging)) %>%
  mutate(highest_ev_charging = 1) %>%
  ungroup()

ev_charging_max <- ev_charging_max %>%
  left_join(aggregated_data %>% select(account_id, hashed_mpan, date, cosy_contract_active) %>% distinct()) 

# Create dummy variables for rate periods
ev_charging_max <- ev_charging_max %>%
  mutate(
    Morning_Cosy = ifelse(rate_period == "Morning Cosy", 1, 0),
    Afternoon_Cosy = ifelse(rate_period == "Afternoon Cosy", 1, 0),
    Peak_Rate = ifelse(rate_period == "Peak Rate", 1, 0),
    Other = ifelse(rate_period == "Other", 1, 0)
  )

# Run the fixed effects models
m_charging1 <- feols(Morning_Cosy ~ i(cosy_contract_active) | account_id + date, data = ev_charging_max, cluster = ~ account_id)
m_charging2 <- feols(Afternoon_Cosy ~ i(cosy_contract_active) | account_id + date, data = ev_charging_max, cluster = ~ account_id)
m_charging3 <- feols(Peak_Rate ~ i(cosy_contract_active) | account_id + date, data = ev_charging_max, cluster = ~ account_id)
m_charging4 <- feols(Other ~ i(cosy_contract_active) | account_id + date, data = ev_charging_max, cluster = ~ account_id)


# Generate the LaTeX table with the dependent variable named "Charging EV"
etable(m_charging1, m_charging2, m_charging3, m_charging4, 
       tex = TRUE, 
       title = "Cosy Adoption on Probability of Charging EV by Period", 
       headers = c("Morning Cosy", "Afternoon Cosy", "Peak Rate", "Other"),
       fitstat = ~ N + g + pre_avg + r2, 
       file = "../tables/ev_charging.tex", 
       replace = TRUE, 
       label = "tab:ev-charging",
       dict = c(Morning_Cosy = "Charging EV", 
                Afternoon_Cosy = "Charging EV", 
                Peak_Rate = "Charging EV", 
                Other = "Charging EV"))

file_path <- "../tables/ev_charging.tex"

# Read the generated LaTeX file
file_content <- readLines(file_path)

# Find the lines with the pre-treatment average and remove them
if (length(grep("Charging EV", file_content))==1) {
  pre_avg_line_index <- grep("Charging EV", file_content)
} else {
  pre_avg_line_index <- grep("Charging EV", file_content)[2]
}

pre_avg_lines <- file_content[pre_avg_line_index:(pre_avg_line_index)]
file_content <- file_content[-c(pre_avg_line_index, pre_avg_line_index)]

# Find the position just after the coefficients
coeff_end_index <- grep("Fixed-effects", file_content) -2

# Insert the pre-treatment average row after the coefficients
file_content <- append(file_content, pre_avg_lines, after = coeff_end_index)
file_content <- append(file_content, "\\emph{Pre-Treatment Average}\\\\", after = coeff_end_index)

# Add a \midrule after the pre-treatment average
file_content <- append(file_content, "\\midrule", after = coeff_end_index)

# Modify the label for "Size of the 'effective' sample" to "Number of Households"
sample_line <- grep("Size of the 'effective' sample", file_content)
file_content[sample_line] <- gsub("Size of the 'effective' sample", "Number of Households", file_content[sample_line])

# Modify the name of the dependent in pre-treatment averages
var_line <- grep("Half Hourly Consumption", file_content)
file_content[sample_line] <- gsub("Half Hourly Consumption", "Charging EV", file_content[var_line])

# Add note
note <- "\\floatfoot{\\justifying \\footnotesize \\upshape \\textbf{Note:} We show the results of four OLS models where the dependent variable is whether a charging event occurred in the period of interest – morning \\textit{Cosy} 4am-7am (column 1), afternoon \\textit{Cosy} 1pm-4pm (column 2), peak 4pm-7pm (column 3), and all other hours of the day (column 4). The sample is 127,789 charging events among 1,743 \\textit{Cosy} adopters for whom we detect evidence of EV charging. Where a charging events stretches across multiple periods, we attribute it to the period that comprises the \\textit{majority} of the event (in minutes). We see that among these EV owning \\textit{Cosy} adopters, \\textit{Cosy} adoption is associated with more charging the off-peak period and less in the peak and other periods.}"

file_content <- append(file_content, note, after = grep("\\centering", file_content)-1)

# Write the modified content back to the LaTeX file
writeLines(file_content, file_path)



```

### Table A.10: Impact of Cosy for Leavers


```{r }
# Function to create the ggplot for each period
create_ggplot <- function(period_data, period_name) {
  # Extract coefficients, standard errors, and event time
  coefficients <- period_data$att.egt   # Convert to daily values
  standard_errors <- period_data$se.egt   # Convert to daily values
  event_time <- period_data$egt
  
  # Create a data frame for plotting
  plot_data <- data.frame(
    event_time = event_time,
    coefficient = coefficients,
    lower_ci = coefficients - 1.96 * standard_errors,
    upper_ci = coefficients + 1.96 * standard_errors,
    period = ifelse(event_time < 0, "No", "Yes")
  )
  
  # Reverse the color order
  plot_data$period <- factor(plot_data$period, levels = c("Yes", "No"))
  
  # Create the ggplot
  p <- ggplot(plot_data, aes(x = event_time, y = coefficient, color = period)) +
    geom_point() +
    geom_line() +
    geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, , alpha = 0.6) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
    scale_color_manual(
      name = "Has Adopted Cosy", 
      labels = c("No" = "No", "Yes" = "Yes"),
      values = c("No" = flexible_color, "Yes" = cosy_color)  # Custom colors
    ) +
    # scale_x_continuous(breaks = seq(-50, 50, 10)) +
    labs(
      x = "Weeks since adoption",
      y = "Dynamic ATT for Half Hourly Consumption im kWh"
    ) +
    theme_minimal()
  
  return(p)
}

# Identify the cases where cosy_contract_active switches from 1 to 0
aggregated_data <- aggregated_data %>%
  mutate(leavers = (account_id %in% contract_analysis[!contract_analysis$category == "Stayed on Cosy (ongoing)",]$account_id))

# Identify when they leave
leave_date <- aggregated_data  %>%
  filter(leavers == 1) %>%
  mutate(no_active_contract = as.numeric(cosy_contract_active==0 & date >= first_adoption)) %>% 
  ungroup() %>%
  group_by(account_id) %>%
  filter(no_active_contract==1) %>%
  summarise(leave_date = min(date))

# Create weeks since leaving
start_date <- min(leave_date$date)

# Create the data for CS
leavers_did <- aggregated_data %>%
  inner_join(leave_date) %>%
  ungroup() %>%
  mutate(
    # Calculate the difference in weeks from the start_date
    week = as.numeric(difftime(date, start_date, units = "weeks")) %/% 1 + 1,
    # Assuming you have a way to determine 'firstweek', adjust similarly if needed
    firstweek = as.numeric(difftime(leave_date, start_date, units = "weeks")) %/% 1 + 1) %>%
  group_by(hashed_mpan, firstweek, week, rate_period) %>%
  summarise(consumption_hh = mean(consumption_hh)) %>%
  mutate(
    id = as.numeric(hashed_mpan),
    firstweek = as.numeric(firstweek),
    week = as.numeric(week)
  )

m_leavers <- feols(consumption_hh ~ i(cosy_contract_active, ref=0) + i(cosy_contract_active, leavers, ref=0, ref2=0)  | daily_avg_heating_degree + account_id + date, 
                   data = aggregated_data, 
                   cluster = ~account_id, 
                   split = ~ rate_period)

etable(m_leavers, tex=TRUE, title = "Impact of Cosy for Leavers",
       fitstat = ~ N + g + pre_avg +t_obs + r2, file = "../tables/did_leavers.tex", replace = TRUE, label="tab:did-leavers")
CleanPreAverage("../tables/did_leavers.tex")

leavers_ev <- aggregated_data %>%
  distinct(account_id, leavers) %>%
  left_join(ev_users) %>%
  mutate(has_ev = (!is.na(is_ev_detected)))


# Group by leavers and has_ev, then count
grouped_data <- leavers_ev %>%
  group_by(leavers, has_ev) %>%
  summarise(count = n()) %>%
  ungroup() %>%
  group_by(leavers) %>%
  mutate(proportion = count / sum(count))

# Plot the bar plot
ggplot(grouped_data, aes(x = as.factor(leavers), y = proportion, fill = as.factor(has_ev))) +
  geom_bar(stat = "identity", position = "stack") +
  scale_fill_manual(values = c("skyblue", "orange"), labels = c("No EV", "Has EV")) +
  scale_y_continuous(labels = scales::percent) +
  labs(x = "Leavers", y = "Proportion", fill = "EV Status") +
  theme_minimal() +
  theme(legend.position = "bottom")

ggsave(filename= "../graphs/leavers_ev.png",width = 10, height = 8, dpi = 300)



#% 0.1731 in survey
```



### Table A.11: Impact of Cosy by LCTs Ownership

```{r smartsurvey}

survey_responses <- fread("../data/input/cosy_-_smart_tariff_survey_2024_09_12.csv")

# Step 1: Clean and split 'all_lcts' column without modifying original data
cleaned_lcts <- survey_responses$all_lcts %>%
  str_remove_all("[\\[\\]\"]") %>%
  str_split(",")

# Step 2: Find unique values across all rows
unique_values <- cleaned_lcts %>%
  unlist() %>%
  str_trim() %>%
  unique()

# Step 3: Create new columns for each unique value
for (val in unique_values) {
  # Add column with 1 if the value is present in the row, 0 otherwise, without changing original df
  survey_responses[[val]] <- sapply(cleaned_lcts, function(x) ifelse(val %in% x, 1, 0))
}

survey_responses <- survey_responses %>%
  mutate(`Has EV` = as.numeric(!has_ev == ""),
         `Has EV Charger` = as.numeric(!has_charger_ev=="")) %>%
  select(-c(has_ev, has_charger_ev, charging_method))

# View the resulting dataframe
summary(survey_responses)

df <- aggregated_data %>%
  select(account_id, consumption_hh, cosy_contract_active, date, daily_avg_heating_degree, rate_period) %>%
  inner_join(survey_responses %>% 
               rename(`Has Solar PV` = `Solar panels or other microgeneration`)) %>%
  filter(account_id %in% unique(survey_responses$account_id))


# Run the regression model
m1_filtered <- feols(consumption_hh ~ i(cosy_contract_active, ref=0) |
                       account_id + date + daily_avg_heating_degree,
                     data = df,
                     split = ~ rate_period,
                     cluster = ~account_id)
tempreg <- feols(consumption_hh ~ i(cosy_contract_active) +
                   i(cosy_contract_active, `Home battery`, ref=0) +
                   i(cosy_contract_active, `Has Solar PV`, ref=0) +
                   i(cosy_contract_active, `Has EV`, ref=0) |
                   account_id + date + daily_avg_heating_degree,
                 data = df,
                 split = ~ rate_period,
                 cluster = ~account_id)
etable(m1_filtered)

etable(tempreg, tex=TRUE, title = "Impact of Cosy by LCTs Ownership",
       fitstat = ~ N + g + pre_avg +t_obs + r2, file = "../tables/did_lcts.tex", replace = TRUE, label="tab:did-lcts")

CleanPreAverage("../tables/did_lcts.tex")

```

```{r graphslctscombi}

# Step 2: Create combinations of EV, Solar, and Battery and count the occurrences
survey_responses_filtered <- survey_responses %>%
  filter(account_id %in% unique(aggregated_data$account_id)) 

lct_matrix <-survey_responses_filtered %>%
  group_by(`Has EV`, `Solar panels or other microgeneration`, `Home battery`) %>%
  summarise(count = n()) %>%
  ungroup() %>%
  mutate(share = count / sum(count))

# Step 3: Create readable labels for combinations
lct_matrix_wide <- lct_matrix %>%
  mutate(
    # Combine only the values that exist, ignoring any empty or missing LCTs
    Combination = trimws(paste(
      ifelse(`Has EV` == 1, "EV", ""),
      ifelse(`Home battery` == 1, "Battery", ""),
      ifelse(`Solar panels or other microgeneration` == 1, "Solar", "")
    )),
    # Remove any trailing/leading spaces and '+' when no tech is present
    Combination = gsub("\\s+", " + ", Combination),  # Ensures proper spacing
    Combination = gsub("^\\s*\\+\\s*", "", Combination),  # Removes leading '+'
    Combination = gsub("\\s*\\+\\s*$", "", Combination),  # Removes trailing '+'
    # If nothing is in the combination, label it as "No other LCT"
    Combination = ifelse(Combination == "", "No other LCT", Combination)
  ) %>%
  arrange(desc(share))

# Step 4: Create a bar plot with ColorBrewer and no borders
ggplot(lct_matrix_wide, aes(x = reorder(Combination, -share), y = share, fill = Combination)) +
  geom_bar(stat = "identity") +  # No border around bars
  coord_flip() +  # Flip coordinates for easier reading
  scale_fill_brewer(palette = "Set3") +  # Use ColorBrewer scheme
  scale_y_continuous(labels = scales::percent_format()) +
  labs(
    x = " ",
    y = paste0("Proportion of Sample (%) [N=", dim(survey_responses_filtered)[1], ']')
  ) +
  theme_minimal() +
  theme(
    legend.position = "none")  # Remove legend

ggsave("../graphs/lct_combinaison.png",
       width = 16, height = 8, units = "cm")


# Step 1: Calculate the share of each LCT
lct_summary <- survey_responses_filtered %>%
  summarise(
    `Home battery (%)` = mean(`Home battery`) * 100,
    `Solar PV (%)` = mean(`Solar panels or other microgeneration`) * 100,
    `EV (%)` = mean(`Has EV`) * 100
  ) %>%
  pivot_longer(cols = everything(), names_to = "LCT", values_to = "Share")

```



### Pre-trends checks

```{r honestdid, eval=FALSE}


honest_did <- function(es,
                       e          = 0,
                       type       = c("smoothness", "relative_magnitude"),
                       gridPoints = 100,
                       ...) {
  
  type <- match.arg(type)
  
  # Make sure that user is passing in an event study
  if (es$type != "dynamic") {
    stop("need to pass in an event study")
  }
  
  # Check if used universal base period and warn otherwise
  if (es$DIDparams$base_period != "universal") {
    stop("Use a universal base period for honest_did")
  }
  
  # Recover influence function for event study estimates
  es_inf_func <- es$inf.function$dynamic.inf.func.e
  
  # Recover variance-covariance matrix
  n <- nrow(es_inf_func)
  V <- t(es_inf_func) %*% es_inf_func / n / n
  
  # Check time vector is consecutive with referencePeriod = -1
  referencePeriod <- -1
  consecutivePre  <- !all(diff(es$egt[es$egt <= referencePeriod]) == 1)
  consecutivePost <- !all(diff(es$egt[es$egt >= referencePeriod]) == 1)
  if ( consecutivePre | consecutivePost ) {
    msg <- "honest_did expects a time vector with consecutive time periods;"
    msg <- paste(msg, "please re-code your event study and interpret the results accordingly.", sep="\n")
    stop(msg)
  }
  
  # Remove the coefficient normalized to zero
  hasReference <- any(es$egt == referencePeriod)
  if ( hasReference ) {
    referencePeriodIndex <- which(es$egt == referencePeriod)
    V    <- V[-referencePeriodIndex,-referencePeriodIndex]
    beta <- es$att.egt[-referencePeriodIndex]
  } else {
    beta <- es$att.egt
  }
  
  nperiods <- nrow(V)
  npre     <- sum(1*(es$egt < referencePeriod))
  npost    <- nperiods - npre
  if ( !hasReference & (min(c(npost, npre)) <= 0) ) {
    if ( npost <= 0 ) {
      msg <- "not enough post-periods"
    } else {
      msg <- "not enough pre-periods"
    }
    msg <- paste0(msg, " (check your time vector; note honest_did takes -1 as the reference period)")
    stop(msg)
  }
  
  baseVec1 <- basisVector(index=(e+1),size=npost)
  orig_ci  <- constructOriginalCS(betahat        = beta,
                                  sigma          = V,
                                  numPrePeriods  = npre,
                                  numPostPeriods = npost,
                                  l_vec          = baseVec1)
  
  if (type=="relative_magnitude") {
    robust_ci <- createSensitivityResults_relativeMagnitudes(betahat        = beta,
                                                             sigma          = V,
                                                             numPrePeriods  = npre,
                                                             numPostPeriods = npost,
                                                             l_vec          = baseVec1,
                                                             gridPoints     = gridPoints,
                                                             ...)
    
  } else if (type == "smoothness") {
    robust_ci <- createSensitivityResults(betahat        = beta,
                                          sigma          = V,
                                          numPrePeriods  = npre,
                                          numPostPeriods = npost,
                                          l_vec          = baseVec1,
                                          ...)
  }
  
  return(list(robust_ci=robust_ci, orig_ci=orig_ci, type=type))
}

# start date
start_date <- aggregated_data %>% ungroup() %>% select(date) %>% distinct() %>% summarise(date = min(date))
start_date <- start_date$date

# Adjust your existing code to calculate 'week' and 'firstweek' as the number of weeks from the start_date
did_data <- aggregated_data %>%
  ungroup() %>%
  filter(rate_period == "Overall") %>%
  mutate(
    # Calculate the difference in weeks from the start_date
    week = as.numeric(difftime(date, start_date, units = "weeks")) %/% 1 + 1,
    # Assuming you have a way to determine 'firstweek', adjust similarly if needed
    firstweek = as.numeric(difftime(first_adoption, start_date, units = "weeks")) %/% 1 + 1) %>%
  group_by(hashed_mpan, firstweek, week) %>%
  summarise(consumption_hh = mean(consumption_hh)) %>%
  mutate(
    id = as.numeric(hashed_mpan),
    firstweek = as.numeric(firstweek),
    week = as.numeric(week)
  )

est_cs <- att_gt(yname = "consumption_hh",
                 tname = "week",
                 idname = "id",
                 gname = "firstweek",
                 data = did_data,
                 clustervars = "id",
                 control_group=c("notyettreated"),
                 base_period = "universal",
                 allow_unbalanced_panel = TRUE,
                 print_details = FALSE)

es <- did::aggte(est_cs, type = "dynamic",
                 min_e = -49, max_e = 49, na.rm = TRUE)

#Run sensitivity analysis for relative magnitudes
sensitivity_results <- honest_did(es, e=0,type="relative_magnitude",Mbarvec=seq(from = 0.5, to = 2, by = 0.5))

HonestDiD::createSensitivityPlot_relativeMagnitudes(sensitivity_results$robust_ci,
                                                    sensitivity_results$orig_ci)

ggsave("../graphs/sensitivity_results.png")

```

### Figure 11: Impact of Cosy by Outside Temperature


```{r base-reg}
# Fit the model
m1 <- feols(consumption_hh ~ i(cosy_contract_active, ref=0)  | 
              daily_avg_heating_degree, 
            data = aggregated_data, 
            cluster = ~account_id, 
            split = ~ rate_period)

m1_cold <- feols(consumption_hh ~ i(cosy_contract_active, ref=0)  | 
                   daily_avg_air_temperature_celsius , 
                 data = aggregated_data %>% filter(daily_avg_air_temperature_celsius <0), 
                 cluster = ~account_id, 
                 split = ~ rate_period)
m2_cold <- feols(consumption_hh ~ i(cosy_contract_active, ref=0)  | 
                   daily_avg_air_temperature_celsius , 
                 data = aggregated_data %>% filter(daily_avg_air_temperature_celsius >= 0, 
                                                   daily_avg_air_temperature_celsius < 5), 
                 cluster = ~account_id, 
                 split = ~ rate_period)
m3_cold <- feols(consumption_hh ~ i(cosy_contract_active, ref=0)  | 
                   daily_avg_air_temperature_celsius, 
                 data = aggregated_data %>% filter(daily_avg_air_temperature_celsius >= 5, 
                                                   daily_avg_air_temperature_celsius < 10), 
                 cluster = ~account_id, 
                 split = ~ rate_period)
m4_cold <- feols(consumption_hh ~ i(cosy_contract_active, ref=0)  | 
                   daily_avg_air_temperature_celsius , 
                 data = aggregated_data %>% filter(daily_avg_air_temperature_celsius >= 10), 
                 cluster = ~account_id, 
                 split = ~ rate_period)

# Extract coefficients and standard errors
coefs <- rbind(
  coeftable(m1_cold) %>%
    data.frame() %>%
    mutate(model = "< 0°C"),
  coeftable(m2_cold) %>%
    data.frame() %>%
    mutate(model = "0-5°C"),
  coeftable(m3_cold) %>%
    data.frame() %>%
    mutate(model = "5-10°C"),
  coeftable(m4_cold) %>%
    data.frame() %>%
    mutate(model = ">10°C")) %>%
  mutate(lower_ci = Estimate - 1.96 * `Std..Error`,
         upper_ci = Estimate + 1.96 * `Std..Error`,
         `Average Daily Temperature` = factor(model, levels = c("< 0°C",
                                                                "0-5°C",
                                                                "5-10°C",
                                                                ">10°C")),
         rate_period = factor(sample, levels = c("Morning Cosy",
                                                 "Afternoon Cosy",
                                                 "Peak Rate",
                                                 "Other", 
                                                 "Overall")))


# Define colors with increasing darkness
colors <- c("< 0°C" = "#AFCBE3",  # Lightest blue
            "0-5°C" = "#8AAFD4",  # Slightly darker
            "5-10°C" = "#6694C6", # Medium blue
            ">10°C" = "#466CA8")  # Darkest blue

# Create the ggplot
ggplot(coefs %>% filter(rate_period != "Overall"), aes(x = `Average Daily Temperature`, 
                                                       y = Estimate, fill = `Average Daily Temperature`)) +
  geom_col() +  # Use geom_col for pre-computed y values
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, alpha = 0.6, color = "black") + 
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
  scale_y_continuous(name = "Estimate (kWh)") +  # Set y-axis label
  scale_fill_manual(values = colors) +  # Assign colors with increasing darkness
  labs(fill = "Average Daily Temperature") +  # Remove x-axis label, keep legend title
  theme_minimal() +  # Apply minimal theme
  facet_wrap(~ rate_period, scales = "free_y", ncol = 2) +  # Facet with 2 columns and free y-axis scales
  theme(
    axis.title.x = element_blank(),  # Remove x-axis title
    axis.text.x = element_blank(),   # Remove x-axis text
    axis.ticks.x = element_blank(),  # Remove x-axis ticks
    legend.position = "bottom"       # Place legend at the bottom
  )
```

```{r temperature-analysis}

# Unique periods 
periods <- unique(aggregated_data$rate_period)

# Round degrees Celsius 
aggregated_data <- aggregated_data %>% 
  mutate(temp_degree = factor(
    case_when(
      daily_avg_air_temperature_celsius < 0 ~ 0,
      daily_avg_air_temperature_celsius < 25 ~ round(daily_avg_air_temperature_celsius),
      TRUE ~ 25
    )
  ))


# Run the regression model
tempreg <- feols(consumption_hh ~ i(cosy_contract_active, temp_degree, ref=0) |
                   temp_degree,
                 data = aggregated_data,
                 split = ~ rate_period,
                 cluster = ~account_id)

# Loop through each model in tempreg to create plots
for (i in 1:length(tempreg)) {
  
  # Find model
  val <- tempreg[[i]]$model_info$sample$value
  j <- which(sapply(1:length(m1), function(j) m1[[j]]$model_info$sample$value) == val)
  
  # Extract coefficients and standard errors
  coefs <- coeftable(tempreg[[i]]) %>%
    data.frame() %>%
    tibble::rownames_to_column("term") %>%
    as_tibble() %>%
    separate(term, into = c("cosy_contract_active", "remove1", "daily_avg_air_temperature_celsius", "remove2"), sep = "::") %>%
    mutate(daily_avg_air_temperature_celsius = as.numeric(daily_avg_air_temperature_celsius),
           lower_ci = Estimate - 1.96 * `Std..Error`,
           upper_ci = Estimate + 1.96 * `Std..Error`
    ) %>%
    mutate(`/% ATE` = Estimate / abs(m1[[j]]$coefficients) * 100,     
           lower_ci_ATE = `/% ATE` - 1.96 * (`Std..Error` / abs(m1[[j]]$coefficients) * 100),
           upper_ci_ATE = `/% ATE` + 1.96 * (`Std..Error` / abs(m1[[j]]$coefficients) * 100)
    )
  
  # Create the ggplot
  ggplot(coefs, aes(x = daily_avg_air_temperature_celsius, y = Estimate)) +
    geom_point(color = cosy_color) +  # Use your desired color
    geom_line(color = cosy_color) +   # Use your desired color
    geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, alpha = 0.6, color = cosy_color) +  # Use your desired color
    geom_hline(yintercept = m1[[j]]$coefficients, linetype = "dashed", alpha = 0.6, color = cosy_color) +  # Add horizontal line at 100% ATE
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
    scale_y_continuous(
      name = "Estimate (kWh)", 
      sec.axis = sec_axis(~ ./m1[[j]]$coefficients, name = "% of ATE", labels = scales::percent_format())
    ) +
    labs(
      x = "Average Temperature in Degrees",
    ) +
    theme_minimal()
  
  # Print the plot
  ggsave(paste0("../graphs/cosy_temperature_", tolower(gsub(" ", "_", val)), ".png"),
         width = 16, height = 8, units = "cm")
}


# Remove the overall model if it exists
all_coefs <- coeftable(tempreg) %>%
  inner_join(coeftable(m1) %>% select(sample, Estimate) %>% rename(average = Estimate)) %>%
  data.frame() %>%
  filter(sample != "Overall") %>%
  separate(coefficient, into = c("cosy_contract_active", "remove1", "daily_avg_air_temperature_celsius", "remove2"), sep = "::") %>%
  mutate(daily_avg_air_temperature_celsius = as.numeric(daily_avg_air_temperature_celsius),
         lower_ci = Estimate - 1.96 * `Std..Error`,
         upper_ci = Estimate + 1.96 * `Std..Error`
  ) %>%
  mutate(`/% ATE` = Estimate / abs(average) * 100,     
         lower_ci_ATE = `/% ATE` - 1.96 * (`Std..Error` / average * 100),
         upper_ci_ATE = `/% ATE` + 1.96 * (`Std..Error` / average * 100)
  ) %>%
  mutate(sample = factor(sample, levels = c("Morning Cosy",
                                            "Afternoon Cosy",
                                            "Peak Rate",
                                            "Other", 
                                            "Overall")))

# Create the ggplot
ggplot(all_coefs, aes(x = daily_avg_air_temperature_celsius, y = Estimate)) +
  geom_point(color = cosy_color) +  # Use your desired color
  geom_line(color = cosy_color) +   # Use your desired color
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, alpha = 0.6, color = cosy_color) +  # Use your desired color
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
  geom_hline(aes(yintercept = average), linetype = "dashed", alpha = 0.6, color = cosy_color) +  # Add horizontal line for the average
  scale_y_continuous(
    name = "Estimate (kWh)"  ) +
  labs(
    x = "Average Temperature in Degrees (°C)",
  ) +
  theme_minimal() +
  facet_wrap(~sample)

# Print the plot
ggsave("../graphs/cosy_temperature_all.png", width = 16, height = 8, units = "cm")

rm(m_heatloss, coefs, coefs_total, m2a, tempreg)
gc()
```

### Installer FE [not included in the paper]

```{r installer-fe}


# Unique periods 
periods <- unique(aggregated_data$rate_period)

# Installer FE
installers <- fread("../data/input/cosy_-_hp_engineers_2025_03_17.csv")


# Run the regression model
tempreg <- feols(consumption_hh ~ i(cosy_contract_active, hp_engineer, ref=0) |
                    daily_avg_heating_degree + account_id + date,
                 data = aggregated_data %>% inner_join(installers %>%
                                                         filter(!is.na(hp_engineer))),
                 split = ~ rate_period,
                 cluster = ~account_id)

# Loop through each model in tempreg to create plots
for (i in 1:length(tempreg)) {
  
  # Find model
  val <- tempreg[[i]]$model_info$sample$value
  j <- which(sapply(1:length(m1), function(j) m1[[j]]$model_info$sample$value) == val)
  
  # Extract coefficients and standard errors
  coefs <- coeftable(tempreg[[i]]) %>%
    data.frame() %>%
    tibble::rownames_to_column("term") %>%
    as_tibble() %>%
    separate(term, into = c("cosy_contract_active", "remove1", "daily_avg_air_temperature_celsius", "remove2"), sep = "::") %>%
    mutate(daily_avg_air_temperature_celsius = as.numeric(daily_avg_air_temperature_celsius),
           lower_ci = Estimate - 1.96 * `Std..Error`,
           upper_ci = Estimate + 1.96 * `Std..Error`
    ) %>%
    mutate(`/% ATE` = Estimate / abs(m1[[j]]$coefficients) * 100,     
           lower_ci_ATE = `/% ATE` - 1.96 * (`Std..Error` / abs(m1[[j]]$coefficients) * 100),
           upper_ci_ATE = `/% ATE` + 1.96 * (`Std..Error` / abs(m1[[j]]$coefficients) * 100)
    )
  
  # Create the ggplot
  ggplot(coefs, aes(x = daily_avg_air_temperature_celsius, y = Estimate)) +
    geom_point(color = cosy_color) +  # Use your desired color
    geom_line(color = cosy_color) +   # Use your desired color
    geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, alpha = 0.6, color = cosy_color) +  # Use your desired color
    geom_hline(yintercept = m1[[j]]$coefficients, linetype = "dashed", alpha = 0.6, color = cosy_color) +  # Add horizontal line at 100% ATE
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
    scale_y_continuous(
      name = "Estimate (kWh)", 
      sec.axis = sec_axis(~ ./m1[[j]]$coefficients, name = "% of ATE", labels = scales::percent_format())
    ) +
    labs(
      x = "Average Temperature in Degrees",
    ) +
    theme_minimal()
  
  # Print the plot
  ggsave(paste0("../graphs/cosy_temperature_", tolower(gsub(" ", "_", val)), ".png"),
         width = 16, height = 8, units = "cm")
}


# Remove the overall model if it exists
all_coefs <- coeftable(tempreg) %>%
  inner_join(coeftable(m1) %>% select(sample, Estimate) %>% rename(average = Estimate)) %>%
  data.frame() %>%
  filter(sample != "Overall") %>%
  separate(coefficient, into = c("cosy_contract_active", "remove1", "daily_avg_air_temperature_celsius", "remove2"), sep = "::") %>%
  mutate(daily_avg_air_temperature_celsius = as.numeric(daily_avg_air_temperature_celsius),
         lower_ci = Estimate - 1.96 * `Std..Error`,
         upper_ci = Estimate + 1.96 * `Std..Error`
  ) %>%
  mutate(`/% ATE` = Estimate / abs(average) * 100,     
         lower_ci_ATE = `/% ATE` - 1.96 * (`Std..Error` / average * 100),
         upper_ci_ATE = `/% ATE` + 1.96 * (`Std..Error` / average * 100)
  ) %>%
  mutate(sample = factor(sample, levels = c("Morning Cosy",
                                            "Afternoon Cosy",
                                            "Peak Rate",
                                            "Other", 
                                            "Overall")))

# Create the ggplot
ggplot(all_coefs, aes(x = daily_avg_air_temperature_celsius, y = Estimate)) +
  geom_point(color = cosy_color) +  # Use your desired color
  geom_line(color = cosy_color) +   # Use your desired color
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, alpha = 0.6, color = cosy_color) +  # Use your desired color
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
  geom_hline(aes(yintercept = average), linetype = "dashed", alpha = 0.6, color = cosy_color) +  # Add horizontal line for the average
  scale_y_continuous(
    name = "Estimate (kWh)"  ) +
  labs(
    x = "Average Temperature in Degrees (°C)",
  ) +
  theme_minimal() +
  facet_wrap(~sample)

# Print the plot
ggsave("../graphs/cosy_temperature_all.png", width = 16, height = 8, units = "cm")

rm(m_heatloss, coefs, coefs_total, m2a, tempreg)
gc()
```

## Moderators

### Table A.12: Cosy Adoption by Previous Tariff Type

```{r prev-tariff-tex}

# Register the pre-treatment average fit statistic
fitstat_register("pre_avg_tou", function(x) {
  
  # Extract the formula
  formula <- x$fml_all$linear
  
  # Extract the outcome variable from the formula
  outcome_variable <- all.vars(formula)[1]
  
  # Extract the call object and evaluate the data argument
  call_object <- x$call
  data_expr <- call_object$data
  data <- eval(data_expr)
  
  # Get the logical vector of observations used in the model
  obs_used <- obs(x)
  
  # Subset the original dataset using this logical vector
  data_used <- data[obs_used, ]
  
  # Ensure the outcome variable is treated as a column name
  outcome_values <- data_used[[outcome_variable]]
  
  # Create pre-avg for non-HP installed group
  pre_avg <- mean(outcome_values[data_used$previous_is_charged_half_hourly == 1 & data_used$date < data_used$first_adoption], na.rm = TRUE)
  
  # Format the pre-avg
  formatted_pre_avg <- format_decimal(pre_avg)
  
  return(formatted_pre_avg)
}, "Half Hourly Consumption ToU")


# Register the pre-treatment average fit statistic
fitstat_register("pre_avg_nontou", function(x) {
  
  # Extract the formula
  formula <- x$fml_all$linear
  
  # Extract the outcome variable from the formula
  outcome_variable <- all.vars(formula)[1]
  
  # Extract the call object and evaluate the data argument
  call_object <- x$call
  data_expr <- call_object$data
  data <- eval(data_expr)
  
  # Get the logical vector of observations used in the model
  obs_used <- obs(x)
  
  # Subset the original dataset using this logical vector
  data_used <- data[obs_used, ]
  
  # Ensure the outcome variable is treated as a column name
  outcome_values <- data_used[[outcome_variable]]
  
  # Create pre-avg for non-HP installed group
  pre_avg <- mean(outcome_values[data_used$previous_is_charged_half_hourly == 0 & data_used$date < data_used$first_adoption], na.rm = TRUE)
  
  # Format the pre-avg
  formatted_pre_avg <- format_decimal(pre_avg)
  
  return(formatted_pre_avg)
}, "Half Hourly Consumption Non-ToU")


m3 <- feols(consumption_hh ~ i(cosy_contract_active) +  i(cosy_contract_active, previous_is_charged_half_hourly, ref=0) | 
              daily_avg_heating_degree + account_id + date, 
            data = aggregated_data, 
            cluster = ~account_id,
            split = ~ rate_period)

etable(m3, tex = TRUE, title = "Cosy Adoption by Previous Tariff Type",
       label = "tab:prevrav",
       fitstat = ~ N + g + pre_avg_nontou + pre_avg_tou +t_obs + r2,
       dict = c(previous_is_charged_half_hourly = "Prev is ToU"),
       file = "../tables/did_prevar.tex", replace = TRUE)

# Read the generated LaTeX file
file_content <- readLines("../tables/did_prevar.tex")

# Find the lines with the pre-treatment average and remove them
pre_avg_line_index <- grep("Half Hourly Consumption", file_content)[2]
pre_avg_line_index2 <- grep("Half Hourly Consumption", file_content)[3]
pre_avg_lines <- file_content[pre_avg_line_index:(pre_avg_line_index2)]
file_content <- file_content[-c(pre_avg_line_index, pre_avg_line_index2)]

# Find the position just after the coefficients
coeff_end_index <- grep("Cosy Contract Active", file_content)[2] + 2
if (length(coeff_end_index) > 1) {
  coeff_end_index <- coeff_end_index[-1]
}

# Insert the pre-treatment average row after the coefficients
file_content <- append(file_content, pre_avg_lines, after = coeff_end_index)

file_content <- append(file_content,"\\emph{Pre-Treatment Average}\\", after = coeff_end_index)

# Add a \midrule after the pre-treatment average
file_content <- append(file_content, "\\midrule", after = coeff_end_index+3)

# Write the modified content back to the LaTeX file
writeLines(file_content, "../tables/did_prevar.tex")  

```



### Figure A.29: Impact of Cosy Adoption by EAC on Consumption and Figure A.30: Impact of Cosy Adoption by EAC on Share of Consumption

```{r eac, eval=FALSE}
rm(m2a)

# Create unique breaks for eac_mwh
breaks <- unique(quantile(aggregated_data[!is.na(aggregated_data$eac_mwh),]$eac_mwh, probs = seq(0, 1, by = 0.1)))

# Create pretty labels for the categories
labels <- sapply(1:(length(breaks)-1), function(i) paste0(round(breaks[i]), "MWh to ", round(breaks[i+1]), "MWh"))

# Create the categories for eac_mwh
aggregated_data <- aggregated_data %>%
  mutate(eac_mwh_category = cut(eac_mwh, 
                                breaks = breaks, 
                                include.lowest = TRUE,
                                labels = labels))

# Run the regression models
tempreg_total <- feols(consumption_hh ~ i(cosy_contract_active, eac_mwh_category, ref =0) 
                       | date +  account_id + daily_avg_heating_degree,
                       data = aggregated_data %>% filter(!is.na(eac_mwh)),
                       split = ~ rate_period,
                       cluster = ~account_id)

tempreg_share <- feols(share_consumption ~ i(cosy_contract_active, eac_mwh_category, ref =0) 
                       | date +  account_id + daily_avg_heating_degree,
                       data = aggregated_data %>% 
                         filter(!is.na(eac_mwh), !rate_period=="Overall") %>%
                         group_by(account_id, date) %>%
                         mutate(share_consumption = total_consumption/sum(total_consumption)),
                       split = ~ rate_period,
                       cluster = ~account_id)

# share
m1_share <- feols(share_consumption ~ i(cosy_contract_active) | daily_avg_heating_degree + account_id + date, 
                  data = aggregated_data %>% 
                    filter(!is.na(eac_mwh), !rate_period=="Overall") %>%
                    group_by(account_id, date) %>%
                    mutate(share_consumption = total_consumption/sum(total_consumption)), 
                  cluster = ~account_id, 
                  split = ~ rate_period)

for (i in 1:5) {
  
  # Find model
  val <- tempreg_total[[i]]$model_info$sample$value
  j <- which(sapply(1:5, function(j) m1[[j]]$model_info$sample$value) == val)
  
  # Extract coefficients and standard errors for total_consumption
  coefs_total <- coeftable(tempreg_total[i]) %>%
    data.frame() %>%
    separate(coefficient, into = c("cosy_contract_active", "remove1", "EAC MWh Category", "remove2"), sep = "::") %>%
    mutate(lower_ci = Estimate - 1.96 * `Std..Error`,
           upper_ci = Estimate + 1.96 * `Std..Error`,
           outcome = "Total Consumption") %>%
    mutate(`EAC MWh Category` = factor(`EAC MWh Category`, levels = labels))
  if (i<5) {
    # Extract coefficients and standard errors for share_consumption
    coefs_share <- coeftable(tempreg_share[i]) %>%
      data.frame() %>%
      separate(coefficient, into = c("cosy_contract_active", "remove1", "EAC MWh Category", "remove2"), sep = "::") %>%
      mutate(lower_ci = Estimate - 1.96 * `Std..Error`,
             upper_ci = Estimate + 1.96 * `Std..Error`,
             outcome = "Share Consumption") %>%
      mutate(`EAC MWh Category` = factor(`EAC MWh Category`, levels = labels))
  }
  # Choose a color palette that can handle more than 9 categories
  brewer_colors <- scales::hue_pal()(length(unique(coefs_share$`EAC MWh Category`)))
  
  # Create the ggplot
  ggplot(coefs_total, aes(x = `EAC MWh Category`, y = Estimate , fill = `EAC MWh Category`)) +
    geom_bar(stat = "identity", show.legend = FALSE) +
    geom_errorbar(aes(ymin = lower_ci , ymax = upper_ci), width = 0.2, color = "grey") +
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
    geom_hline(yintercept = m1[[j]]$coefficients, linetype = "dashed", color = cosy_color, alpha=0.6) +  # Add horizontal line at ATE
    scale_fill_brewer(palette = "Spectral") +  # Use the chosen palette
    labs(
      x = "EAC MWh Decile",
    ) +
    scale_y_continuous(
      name = "Estimate (kWh)", 
      sec.axis = sec_axis(~ ./m1[[j]]$coefficients, name = "% of ATE", labels = scales::percent_format())
    ) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),  # Tilt x-axis labels for better readability
      legend.position = "none"  # Remove legend
    )
  
  # Print the plot
  ggsave(paste0("../graphs/eac_", val %>% tolower() %>% str_replace(" ", "_"), ".png"),
         width = 16, height = 8, units = "cm")
  
  if (i<5) {
    # Create the ggplot
    ggplot(coefs_share, aes(x = `EAC MWh Category`, y = Estimate, fill = `EAC MWh Category`)) +
      geom_bar(stat = "identity", show.legend = FALSE) +
      geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, color = "grey") +
      geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
      geom_hline(yintercept = m1_share[[i]]$coefficients, linetype = "dashed", color = cosy_color, alpha=0.6) +  # Add horizontal line at ATE
      scale_fill_brewer(palette = "Spectral") +  # Use the chosen palette
      labs(
        x = "EAC MWh Decile",
      ) +
      scale_y_continuous(
        name = "% of Daily Consumption",
        labels = scales::percent_format(),
        sec.axis = sec_axis(~ ./m1_share[[i]]$coefficients, name = "% of ATE", labels = scales::percent_format())
      ) +
      theme_minimal() +
      theme(
        axis.text.x = element_text(angle = 45, hjust = 1),  # Tilt x-axis labels for better readability
        legend.position = "none"  # Remove legend
      )
    
    # Print the plot
    ggsave(paste0("../graphs/eac_share_", tempreg_total[[i]]$model_info$sample$value %>% tolower() %>% str_replace(" ", "_"), ".png"),
           width = 16, height = 8, units = "cm")
  }
}


# Extract coefficients and standard errors for each model and convert to % of ATE
extract_and_combine_coefs <- function(tempreg_model, m1_model, labels) {
  all_coefs <- data.frame()
  
  for (i in 1:length(tempreg_model)) {
    val <- tempreg_model[[i]]$model_info$sample$value
    j <- which(sapply(1:length(m1_model), function(j) m1_model[[j]]$model_info$sample$value) == val)
    
    coefs <- coeftable(tempreg_model[[i]]) %>%
      data.frame() %>%
      tibble::rownames_to_column("term") %>%
      as_tibble() %>%
      separate(term, into = c("cosy_contract_active", "remove1", "EAC_MWh_Category", "remove2"), sep = "::") %>%
      mutate(
        average = m1_model[[j]]$coefficients,
        EAC_MWh_Category = factor(EAC_MWh_Category, levels = labels),
        lower_ci = Estimate - 1.96 * Std..Error,
        upper_ci = Estimate + 1.96 * Std..Error,
        `%_ATE` = Estimate / abs(m1_model[[j]]$coefficients) * 100,
        lower_ci_ATE = `%_ATE` - 1.96 * (Std..Error / m1_model[[j]]$coefficients * 100),
        upper_ci_ATE = `%_ATE` + 1.96 * (Std..Error / m1_model[[j]]$coefficients * 100),
        outcome = ifelse(grepl("share", deparse(substitute(tempreg_model))), "Share Consumption", "Total Consumption"),
        period = factor(val, levels = c("Morning Cosy",
                                        "Afternoon Cosy",
                                        "Peak Rate",
                                        "Other", 
                                        "Overall")))
    
    all_coefs <- bind_rows(all_coefs, coefs)
  }
  
  return(all_coefs)
}

# Combine all coefficients
all_coefs_total <- extract_and_combine_coefs(tempreg_total, m1, labels)
all_coefs_share <- extract_and_combine_coefs(tempreg_share, m1_share, labels)
all_coefs <- bind_rows(all_coefs_total, all_coefs_share)

# Create the combined ggplot using facet_wrap
ggplot(all_coefs_share %>% filter(period!="Overall"), aes(x = EAC_MWh_Category, y = Estimate, fill = EAC_MWh_Category)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, color = "grey") +
  geom_hline(aes(yintercept = average), linetype = "dashed", alpha = 0.6, color = cosy_color) +  # Add horizontal line for the average
  scale_fill_brewer(palette = "Spectral") +  # Use the chosen palette
  labs(
    x = "EAC MWh Decile",
  ) +
  scale_y_continuous(
    name = "Estimate (kWh)", 
    labels = scales::percent_format()
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Tilt x-axis labels for better readability
    legend.position = "none"  # Remove legend
  ) +
  facet_wrap(~ period)

# Save the combined plot
ggsave("../graphs/eac_share_combined.png", device = "png", width = 16, height = 12, dpi = 300)


# Create the combined ggplot using facet_wrap
ggplot(all_coefs_total %>% filter(period!="Overall"), aes(x = EAC_MWh_Category, y = Estimate, fill = EAC_MWh_Category)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, color = "grey") +
  geom_hline(aes(yintercept = average), linetype = "dashed", alpha = 0.6, color = cosy_color) +  # Add horizontal line for the average
  scale_fill_brewer(palette = "Spectral") +  # Use the chosen palette
  labs(
    x = "EAC MWh Decile",
  ) +
  scale_y_continuous(
    name = "Estimate (kWh)", 
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Tilt x-axis labels for better readability
    legend.position = "none"  # Remove legend
  ) +
  facet_wrap(~ period)

# Save the combined plot
ggsave("../graphs/eac_combined.png", device = "png", width = 16, height = 12, dpi = 300)

# List all objects in the environment
all_objects <- ls()

# Specify the objects you want to keep
keep_objects <- c("aggregated_data", "m1", "m1_share", "cosy_color", "flexible_color")

# Remove all objects except the ones you want to keep
rm(list = setdiff(all_objects, keep_objects))

# Verify the remaining objects
ls()
gc()

```


### Figure A.28: Impact of Cosy Adoption by EPC Score on Consumption


```{r epc-plot}
m2a <- feols(consumption_hh ~ i(cosy_contract_active, epc_letter, ref=0)  | 
               daily_avg_heating_degree + date + account_id,
             data = aggregated_data, 
             split = ~ rate_period,
             cluster = ~account_id)

# share
m1_share <- feols(share_consumption ~ i(cosy_contract_active) | daily_avg_heating_degree + account_id + date, 
                  data = aggregated_data %>% 
                    filter(!is.na(epc_letter), !rate_period=="Overall") %>%
                    group_by(account_id, date) %>%
                    mutate(share_consumption = total_consumption/sum(total_consumption)), 
                  cluster = ~account_id, 
                  split = ~ rate_period)

# Define colors to match the Energy Efficiency Rating chart
rating_colors <- c(
  "A" = "#00CC00",  # Green
  "B" = "#66FF33",  # Light Green
  "C" = "#FFFF00",  # Yellow
  "D" = "#FF9900",  # Orange
  "E" = "#FF6600",  # Dark Orange
  "F" = "#FF0000",  # Red
  "G" = "#990000"   # Dark Red
)

for (i in 1:5) {
  # Find model
  val <- m2a[[i]]$model_info$sample$value
  j <- which(sapply(1:5, function(j) m1[[j]]$model_info$sample$value) == val)
  
  # Extract coefficients and standard errors
  coefs <- coeftable(m2a[[i]]) %>%
    data.frame() %>%
    tibble::rownames_to_column("term") %>%
    separate(term, into = c("cosy_contract_active", "remove1", "EPC letter", "remove2"), sep = "::") %>%
    mutate(lower_ci = Estimate - 1.96 * `Std..Error`,
           upper_ci = Estimate + 1.96 * `Std..Error`
    )
  # Assuming coefs is your data frame and rating_colors is your color vector
  coefs <- coefs %>%
    mutate(EPC_label_position = max(Estimate) * 0.1)  # Position for EPC labels on the right
  
  # Create the ggplot
  ggplot(coefs, aes(y = rev(factor(`EPC letter`)), x = Estimate, fill = factor(`EPC letter`))) +
    geom_bar(stat = "identity", show.legend = FALSE) +
    geom_errorbar(aes(xmin = lower_ci, xmax = upper_ci), width = 0.2, color = "grey") +
    geom_vline(xintercept = 0, linetype = "dashed", color = "black") +  # Add vertical line at x = 0
    geom_vline(xintercept = m1[[j]]$coefficients, linetype = "dashed", color = cosy_color, alpha=0.6) +  # Add vertical line at ATE
    geom_text(aes(x = EPC_label_position, label = `EPC letter`), hjust = 0, color = "white") +  # Add EPC letters on the right
    scale_fill_manual(values = rating_colors, name = "EPC Letter") +  # Use the defined colors+
    labs(
      x = "Average Half Hourly Consumption",
      y = "EPC Letter"
    ) +
    theme_minimal() +
    theme(
      axis.text.y = element_blank(),  # Hide original y-axis text
      axis.ticks.y = element_blank(),  # Hide original y-axis ticks
      axis.text.y.right = element_text(hjust = 0.5),  # Center the text on the right-hand side
      axis.title.y.right = element_text(margin = margin(l = 10)),  # Add margin to right y-axis title
      legend.position = "none"  # Remove legendx
    )
  
  
  # Print the plot
  ggsave(paste0("../graphs/epc_", val %>% tolower() %>% str_replace(" ", "_"), ".png"),
         width = 16, height = 8, units = "cm")
}

# Assuming m2a is your model list, m1 contains the ATE values, and rating_colors is your color vector
all_coefs <- data.frame()

for (i in 1:5) {
  # Find model
  val <- m2a[[i]]$model_info$sample$value
  j <- which(sapply(1:5, function(j) m1[[j]]$model_info$sample$value) == val)
  
  # Extract coefficients and standard errors
  coefs <- coeftable(m2a[[i]]) %>%
    data.frame() %>%
    tibble::rownames_to_column("term") %>%
    separate(term, into = c("cosy_contract_active", "remove1", "EPC_letter", "remove2"), sep = "::") %>%
    mutate(
      average = m1[[j]]$coefficients,
      lower_ci = Estimate - 1.96 * Std..Error,
      upper_ci = Estimate + 1.96 * Std..Error,
      `%_ATE` = Estimate / abs(m1[[j]]$coefficients) * 100,
      lower_ci_ATE = lower_ci / abs(m1[[j]]$coefficients) * 100,
      upper_ci_ATE = upper_ci / abs(m1[[j]]$coefficients) * 100,
      period = val
    )
  
  # Combine all coefficients
  all_coefs <- bind_rows(all_coefs, coefs)
}

# Assuming coefs is your data frame and rating_colors is your color vector
all_coefs <- all_coefs %>%
  mutate(EPC_label_position = max(`Estimate`) * 0.1)  # Position for EPC labels on the right

# Create the ggplot
ggplot(all_coefs %>% filter(period!="Overall"), aes(y = factor(EPC_letter, levels = rev(unique(EPC_letter))), x = Estimate, fill = factor(EPC_letter))) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  geom_errorbar(aes(xmin = lower_ci, xmax = upper_ci), width = 0.2, color="grey") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black") +  # Add vertical line at x = 0
  geom_vline(aes(xintercept = average), linetype = "dashed", color = cosy_color, alpha = 0.6) +  # Add vertical line at average ATE
  geom_text(aes(x = EPC_label_position, label = EPC_letter), color = "black") +  # Add EPC letters on the right
  scale_fill_manual(values = rating_colors, name = "EPC Letter") +  # Use the defined colors
  labs(
    x = "Estimate (kWh)",
    y = "EPC Letter"
  ) +
  theme_minimal() +
  theme(
    axis.text.y = element_blank(),  # Hide original y-axis text
    axis.ticks.y = element_blank(),  # Hide original y-axis ticks
    axis.text.y.right = element_text(hjust = 0.5),  # Center the text on the right-hand side
    axis.title.y.right = element_text(margin = margin(l = 10)),  # Add margin to right y-axis title
    legend.position = "none"  # Remove legend
  ) +
  facet_wrap(~ period, scales = "free_y")

# Print the plot
ggsave("../graphs/cosy_epc_combined.png", width = 16, height = 8, units = "cm")

rm(m2a)
```

### Figure A.33: Impact of Cosy Adoption by Heat Loss on Consumption and Figure A.34: Impact of Cosy Adoption by Heat Loss on Share of Consumption

```{r heatloss}

# Create unique breaks for predicted_heatloss_watts
breaks <- unique(quantile(aggregated_data[!is.na(aggregated_data$predicted_heatloss_watts),]$predicted_heatloss_watts/1000, probs = seq(0, 1, by = 0.1)))

# Create pretty labels for the categories
labels <- sapply(1:(length(breaks)-1), function(i) paste0(round(breaks[i], 1), " kW to ", round(breaks[i+1], 1), " kW"))

# Create the categories for predicted_heatloss_watts
aggregated_data <- aggregated_data %>%
  mutate(predicted_heatloss_watts_category = cut(predicted_heatloss_watts/1000, 
                                                 breaks = breaks, 
                                                 include.lowest = TRUE,
                                                 labels = labels))


m_heatloss <- feols(consumption_hh ~ i(cosy_contract_active, predicted_heatloss_watts_category, ref =0) 
                    | date +  account_id + daily_avg_heating_degree,
                    data = aggregated_data %>% filter(!is.na(predicted_heatloss_watts_category)),
                    split = ~ rate_period,
                    cluster = ~account_id)

for (i in 1:5) {
  
  # Find model
  val <- m_heatloss[[i]]$model_info$sample$value
  j <- which(sapply(1:5, function(j) m1[[j]]$model_info$sample$value) == val)
  
  # Extract coefficients and standard errors for total_consumption
  coefs_total <- coeftable(m_heatloss[i]) %>%
    data.frame() %>%
    separate(coefficient, into = c("cosy_contract_active", "remove1", "Heatloss MW Category", "remove2"), sep = "::") %>%
    mutate(lower_ci = Estimate - 1.96 * `Std..Error`,
           upper_ci = Estimate + 1.96 * `Std..Error`,
           outcome = "Total Consumption") %>%
    mutate(`Heatloss MW Category` = factor(`Heatloss MW Category`, levels = labels))
  
  # Define the shades of reds
  red_palette <- c("#FF9999", "#FF8080", "#FF6666", "#FF4D4D", "#FF3333", "#FF1A1A", "#FF0000", "#E60000", "#CC0000", "#B20000")
  
  # Create the ggplot
  ggplot(coefs_total, aes(x = `Heatloss MW Category`, y = Estimate, fill = `Heatloss MW Category`)) +
    geom_bar(stat = "identity", show.legend = FALSE) +
    geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, color = "grey") +
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
    geom_hline(yintercept = m1[[j]]$coefficients, linetype = "dashed", color = cosy_color, alpha = 0.6) +  # Add horizontal line at ATE
    scale_fill_manual(values = red_palette) +
    labs(
      x = "Heatloss MW Decile",
    ) +
    scale_y_continuous(
      name = "Estimate (kWh)", 
      sec.axis = sec_axis(~ ./m1[[j]]$coefficients, name = "% of ATE", labels = scales::percent_format())
      
    ) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),  # Tilt x-axis labels for better readability
      legend.position = "none"  # Remove legend
    )
  
  # Print the plot
  ggsave(paste0("../graphs/heatloss_", val %>% tolower() %>% str_replace(" ", "_"), ".png"),
         width = 16, height = 8, units = "cm")
  
}


m_heatloss2 <- feols(share_consumption ~ i(cosy_contract_active, predicted_heatloss_watts_category, ref =0)
                     | date +  account_id + daily_avg_heating_degree,
                     data = aggregated_data %>% 
                       filter(!is.na(predicted_heatloss_watts_category), !rate_period=="Overall") %>%
                       group_by(account_id, date) %>%
                       mutate(share_consumption = total_consumption/sum(total_consumption)),
                     split = ~ rate_period,
                     cluster = ~account_id)

for (i in 1:4) {
  
  # Find model
  val <- m_heatloss2[[i]]$model_info$sample$value
  j <- which(sapply(1:4, function(j) m1_share[[j]]$model_info$sample$value) == val)
  
  # Extract coefficients and standard errors for total_consumption
  coefs_total <- coeftable(m_heatloss2[i]) %>%
    data.frame() %>%
    separate(coefficient, into = c("cosy_contract_active", "remove1", "Heatloss MW Category", "remove2"), sep = "::") %>%
    mutate(lower_ci = Estimate - 1.96 * `Std..Error`,
           upper_ci = Estimate + 1.96 * `Std..Error`,
           outcome = "Total Consumption") %>%
    mutate(`Heatloss MW Category` = factor(`Heatloss MW Category`, levels = labels))
  
  # Define the shades of reds
  red_palette <- c("#FF9999", "#FF8080", "#FF6666", "#FF4D4D", "#FF3333", "#FF1A1A", "#FF0000", "#E60000", "#CC0000", "#B20000")
  
  # Create the ggplot
  ggplot(coefs_total, aes(x = `Heatloss MW Category`, y = Estimate, fill = `Heatloss MW Category`)) +
    geom_bar(stat = "identity", show.legend = FALSE) +
    geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, color = "grey") +
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
    geom_hline(yintercept = m1_share[[j]]$coefficients, linetype = "dashed", color = cosy_color, alpha = 0.6) +  # Add horizontal line at ATE
    scale_fill_manual(values = red_palette) +
    labs(
      x = "Heatloss MW Decile",
    ) +
    scale_y_continuous(
      name = "% of Daily Consumption",
      labels = scales::percent_format(),
      sec.axis = sec_axis(~ ./m1_share[[j]]$coefficients, name = "% of ATE", labels = scales::percent_format())
    ) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),  # Tilt x-axis labels for better readability
      legend.position = "none"  # Remove legend
    )
  
  # Print the plot
  ggsave(paste0("../graphs/share_heatloss_", val %>% tolower() %>% str_replace(" ", "_"), ".png"),
         width = 16, height = 8, units = "cm")
  
}


# Extract coefficients and standard errors for each model and convert to % of ATE
extract_and_combine_coefs <- function(tempreg_model, m1_model, labels) {
  all_coefs <- data.frame()
  
  for (i in 1:length(tempreg_model)) {
    val <- tempreg_model[[i]]$model_info$sample$value
    j <- which(sapply(1:length(m1_model), function(j) m1_model[[j]]$model_info$sample$value) == val)
    
    coefs <- coeftable(tempreg_model[[i]]) %>%
      data.frame() %>%
      tibble::rownames_to_column("term") %>%
      as_tibble() %>%
      separate(term, into = c("cosy_contract_active", "remove1", "EAC_MWh_Category", "remove2"), sep = "::") %>%
      mutate(
        average = m1_model[[j]]$coefficients,
        EAC_MWh_Category = factor(EAC_MWh_Category, levels = labels),
        lower_ci = Estimate - 1.96 * Std..Error,
        upper_ci = Estimate + 1.96 * Std..Error,
        `%_ATE` = Estimate / abs(m1_model[[j]]$coefficients) * 100,
        lower_ci_ATE = `%_ATE` - 1.96 * (Std..Error / m1_model[[j]]$coefficients * 100),
        upper_ci_ATE = `%_ATE` + 1.96 * (Std..Error / m1_model[[j]]$coefficients * 100),
        outcome = ifelse(grepl("share", deparse(substitute(tempreg_model))), "Share Consumption", "Total Consumption"),
        period = factor(val, levels = c("Morning Cosy",
                                        "Afternoon Cosy",
                                        "Peak Rate",
                                        "Other", 
                                        "Overall")))
    
    all_coefs <- bind_rows(all_coefs, coefs)
  }
  
  return(all_coefs)
}


# Combine all coefficients
all_coefs_total <- extract_and_combine_coefs(m_heatloss, m1, labels)
all_coefs_share <- extract_and_combine_coefs(m_heatloss2, m1_share, labels)
all_coefs <- bind_rows(all_coefs_total, all_coefs_share)

# Create the combined ggplot using facet_wrap
ggplot(all_coefs_share %>% filter(period!="Overall"), aes(x = EAC_MWh_Category, y = Estimate, fill = EAC_MWh_Category)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, color = "grey") +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
  geom_hline(aes(yintercept = average), linetype = "dashed", color = cosy_color, alpha = 0.6) +  # Add horizontal line at ATE
  scale_fill_manual(values = red_palette) +
  labs(
    x = "Heatloss MW Decile",
  ) +
  scale_y_continuous(
    name = "% of Daily Consumption",
    labels = scales::percent_format(),
  ) +  
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Tilt x-axis labels for better readability
    legend.position = "none"  # Remove legend
  ) +
  facet_wrap(~ period)

# Save the combined plot
ggsave("../graphs/heatloss_share_combined.png", device = "png", width = 16, height = 12, dpi = 300)


# Create the combined ggplot using facet_wrap
ggplot(all_coefs_total %>% filter(period!="Overall"), aes(x = EAC_MWh_Category, y = Estimate, fill = EAC_MWh_Category)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, color = "grey") +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
  geom_hline(aes(yintercept = average), linetype = "dashed", color = cosy_color, alpha = 0.6) +  # Add horizontal line at ATE
  scale_fill_manual(values = red_palette) +
  labs(
    x = "Heatloss MW Decile",
  ) +
  scale_y_continuous(
    name = "Estimate (kWh)"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Tilt x-axis labels for better readability
    legend.position = "none"  # Remove legend
  ) +
  facet_wrap(~ period)

# Save the combined plot
ggsave("../graphs/heatloss_combined.png", device = "png", width = 16, height = 12, dpi = 300)




# List all objects in the environment
all_objects <- ls()

# Specify the objects you want to keep
keep_objects <- c("aggregated_data", "m1", "m1_share", "cosy_color", "flexible_color", "CleanPreAverage", "format_decimal", "format_number")

# Remove all objects except the ones you want to keep
rm(list = setdiff(all_objects, keep_objects))



```

### Figure A.31: Impact of Cosy Adoption by Floor Area on Consumption and Figure A.32: Impact of Cosy Adoption by Floor Area on Share of Consumptio

```{r floor-area}

gc()

# Create unique breaks for total_floor_area
breaks <- unique(quantile(aggregated_data[!is.na(aggregated_data$total_floor_area),]$total_floor_area, probs = seq(0, 1, by = 0.1)))

# Create pretty labels for the categories
labels <- sapply(1:(length(breaks)-1), function(i) paste0(round(breaks[i], 0), " to ", round(breaks[i+1], 0), " m sq."))

# Create the categories for total_floor_area
aggregated_data <- aggregated_data %>%
  mutate(total_floor_area_category = cut(total_floor_area, 
                                         breaks = breaks, 
                                         include.lowest = TRUE,
                                         labels = labels))


m_floor <- feols(consumption_hh ~ i(cosy_contract_active, total_floor_area_category, ref =0) 
                 | date +  account_id + daily_avg_heating_degree,
                 data = aggregated_data %>% filter(!is.na(total_floor_area_category)),
                 split = ~ rate_period,
                 cluster = ~account_id)

for (i in 1:5) {
  
  # Find model
  val <- m_floor[[i]]$model_info$sample$value
  j <- which(sapply(1:5, function(j) m1[[j]]$model_info$sample$value) == val)
  
  # Extract coefficients and standard errors for total_consumption
  coefs_total <- coeftable(m_floor[i]) %>%
    data.frame() %>%
    separate(coefficient, into = c("cosy_contract_active", "remove1", "Floor Area", "remove2"), sep = "::") %>%
    mutate(lower_ci = Estimate - 1.96 * `Std..Error`,
           upper_ci = Estimate + 1.96 * `Std..Error`,
           outcome = "Total Consumption") %>%
    mutate(`Floor Area` = factor(`Floor Area`, levels = labels))
  
  # Define the shades of reds
  red_palette <- c("#FF9999", "#FF8080", "#FF6666", "#FF4D4D", "#FF3333", "#FF1A1A", "#FF0000", "#E60000", "#CC0000", "#B20000")
  
  # Create the ggplot
  ggplot(coefs_total, aes(x = `Floor Area`, y = Estimate, fill = `Floor Area`)) +
    geom_bar(stat = "identity", show.legend = FALSE) +
    geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, color = "grey") +
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
    geom_hline(yintercept = m1[[j]]$coefficients, linetype = "dashed", color = cosy_color, alpha = 0.6) +  # Add horizontal line at ATE
    scale_fill_manual(values = red_palette) +
    labs(
      x = "Floor Area Decile",
      y = "Half Hourly Consumption in kWh"
    ) +
    scale_y_continuous(
      name = "Estimate (kWh)", 
    ) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),  # Tilt x-axis labels for better readability
      legend.position = "none"  # Remove legend
    )
  
  # Print the plot
  ggsave(paste0("../graphs/floor_area_", val %>% tolower() %>% str_replace(" ", "_"), ".png"),
         width = 16, height = 8, units = "cm")
  
}


m_floor_share <- feols(share_consumption ~ i(cosy_contract_active, total_floor_area_category, ref =0)
                       | date +  account_id + daily_avg_heating_degree,
                       data = aggregated_data %>% 
                         filter(!is.na(total_floor_area_category), !rate_period=="Overall") %>%
                         group_by(account_id, date) %>%
                         mutate(share_consumption = total_consumption/sum(total_consumption)),
                       split = ~ rate_period,
                       cluster = ~account_id)

for (i in 1:4) {
  
  # Find model
  val <- m_floor_share[[i]]$model_info$sample$value
  j <- which(sapply(1:4, function(j) m1_share[[j]]$model_info$sample$value) == val)
  
  # Extract coefficients and standard errors for total_consumption
  coefs_total <- coeftable(m_floor_share[i]) %>%
    data.frame() %>%
    separate(coefficient, into = c("cosy_contract_active", "remove1", "Floor Area", "remove2"), sep = "::") %>%
    mutate(lower_ci = Estimate - 1.96 * `Std..Error`,
           upper_ci = Estimate + 1.96 * `Std..Error`,
           outcome = "Total Consumption") %>%
    mutate(`Floor Area` = factor(`Floor Area`, levels = labels))
  
  # Define the shades of reds
  red_palette <- c("#FF9999", "#FF8080", "#FF6666", "#FF4D4D", "#FF3333", "#FF1A1A", "#FF0000", "#E60000", "#CC0000", "#B20000")
  
  # Create the ggplot
  ggplot(coefs_total, aes(x = `Floor Area`, y = Estimate, fill = `Floor Area`)) +
    geom_bar(stat = "identity", show.legend = FALSE) +
    geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, color = "grey") +
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
    geom_hline(yintercept = m1_share[[j]]$coefficients, linetype = "dashed", color = cosy_color, alpha = 0.6) +  # Add horizontal line at ATE
    scale_fill_manual(values = red_palette) +
    labs(
      x = "Floor Area Decile",
      y = "Half Hourly Consumption in kWh"
    ) +
    scale_y_continuous(
      name = "% of Daily Consumption",
      labels = scales::percent_format(),
      sec.axis = sec_axis(~ ./m1_share[[j]]$coefficients, name = "% of ATE", labels = scales::percent_format())
    ) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),  # Tilt x-axis labels for better readability
      legend.position = "none"  # Remove legend
    )
  
  # Print the plot
  ggsave(paste0("../graphs/share_floor_area_", val %>% tolower() %>% str_replace(" ", "_"), ".png"),
         width = 16, height = 8, units = "cm")
  
}

# Initialize an empty data frame to store all coefficients
all_coefs <- data.frame()

# Extract coefficients for total consumption
for (i in 1:5) {
  val <- m_floor[[i]]$model_info$sample$value
  j <- which(sapply(1:5, function(j) m1[[j]]$model_info$sample$value) == val)
  
  coefs_total <- coeftable(m_floor[[i]]) %>%
    data.frame() %>%
    tibble::rownames_to_column("term") %>%
    separate(term, into = c("cosy_contract_active", "remove1", "Floor_Area", "remove2"), sep = "::") %>%
    mutate(
      average = m1[[j]]$coefficients,
      lower_ci = Estimate - 1.96 * `Std..Error`,
      upper_ci = Estimate + 1.96 * `Std..Error`,
      `%_ATE` = Estimate / abs(m1[[j]]$coefficients) * 100,
      lower_ci_ATE = lower_ci / abs(m1[[j]]$coefficients) * 100,
      upper_ci_ATE = upper_ci / abs(m1[[j]]$coefficients) * 100,
      outcome = "Total Consumption",
      `Floor_Area` = factor(`Floor_Area`, levels = labels),
      period = factor(val, levels = c("Morning Cosy",
                                      "Afternoon Cosy",
                                      "Peak Rate",
                                      "Other", 
                                      "Overall")))
  
  all_coefs <- bind_rows(all_coefs, coefs_total)
}

# Extract coefficients for share consumption
for (i in 1:4) {
  val <- m_floor_share[[i]]$model_info$sample$value
  j <- which(sapply(1:4, function(j) m1_share[[j]]$model_info$sample$value) == val)
  
  coefs_share <- coeftable(m_floor_share[[i]]) %>%
    data.frame() %>%
    tibble::rownames_to_column("term") %>%
    separate(term, into = c("cosy_contract_active", "remove1", "Floor_Area", "remove2"), sep = "::") %>%
    mutate(
      average = m1_share[[j]]$coefficients,
      lower_ci = Estimate - 1.96 * `Std..Error`,
      upper_ci = Estimate + 1.96 * `Std..Error`,
      `%_ATE` = Estimate / abs(m1_share[[j]]$coefficients) * 100,
      lower_ci_ATE = lower_ci / abs(m1_share[[j]]$coefficients) * 100,
      upper_ci_ATE = upper_ci / abs(m1_share[[j]]$coefficients) * 100,
      period = val,
      outcome = "Share Consumption",
      `Floor_Area` = factor(`Floor_Area`, levels = labels),
      period = factor(val, levels = c("Morning Cosy",
                                      "Afternoon Cosy",
                                      "Peak Rate",
                                      "Other", 
                                      "Overall")))
  
  all_coefs <- bind_rows(all_coefs, coefs_share)
}

# Define the shades of reds
red_palette <- c("#FF9999", "#FF8080", "#FF6666", "#FF4D4D", "#FF3333", "#FF1A1A", "#FF0000", "#E60000", "#CC0000", "#B20000")

# Create the combined ggplot using facet_wrap
ggplot(all_coefs %>% filter(outcome == "Share Consumption"), aes(x = `Floor_Area`, y = Estimate, fill = `Floor_Area`)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, color = "grey") +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
  geom_hline(aes(yintercept = average), linetype = "dashed", color = cosy_color, alpha = 0.6) +  # Add vertical line at average ATE
  scale_fill_manual(values = red_palette) +
  labs(
    x = "Floor Area Decile"
  ) +
  scale_y_continuous(
    name = "Share of Daily Comsumption (%)", 
    labels = scales::percent_format(),
  ) +  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Tilt x-axis labels for better readability
    legend.position = "none"  # Remove legend
  ) +
  facet_wrap(~ period, scales = "free_y")


# Save the combined plot
ggsave("../graphs/floor_area_share_combined.png", device = "png", width = 16, height = 12, units = "cm")



# Create the combined ggplot using facet_wrap
ggplot(all_coefs %>% filter(outcome == "Total Consumption", period != "Overall"), 
       aes(x = `Floor_Area`, y = Estimate, fill = `Floor_Area`)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, color="grey") +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
  geom_hline(aes(yintercept = average), linetype = "dashed", color = cosy_color, alpha = 0.6) +  # Add vertical line at average ATE
  scale_fill_manual(values = red_palette) +
  labs(
    x = "Floor Area Decile",
  ) +
  scale_y_continuous(
    name = "Estimate (kWh)"  ) +  
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Tilt x-axis labels for better readability
    legend.position = "none"  # Remove legend
  ) +
  facet_wrap(~ period)


# Save the combined plot
ggsave("../graphs/floor_area_combined.png", device = "png", width = 16, height = 12, units = "cm")



```

### Property values

```{r property-value}

gc()

# Create unique breaks for property_value
breaks <- unique(quantile(aggregated_data[!is.na(aggregated_data$property_value),]$property_value, 
                          probs = seq(0, 1, by = 0.1)))

# Create pretty labels for the categories
labels <- sapply(1:(length(breaks)-1), function(i) paste0("£", round(breaks[i]/1000, 0), "k to £", 
                                                          round(breaks[i+1]/1000, 0), "k"))
labels[length(labels)] <- paste0("£", round(breaks[length(breaks)-1]/1000), "+")

# Create the categories for property_value
aggregated_data <- aggregated_data %>%
  mutate(property_value_category = cut(property_value, 
                                       breaks = breaks, 
                                       include.lowest = TRUE,
                                       labels = labels))


m_property_value <- feols(consumption_hh ~ i(cosy_contract_active, property_value_category, ref =0) 
                          | date +  account_id + daily_avg_heating_degree,
                          data = aggregated_data %>% filter(!is.na(property_value_category)),
                          split = ~ rate_period,
                          cluster = ~account_id)

m_property_value_share <- feols(share_consumption ~ i(cosy_contract_active, property_value_category, ref =0)
                                | date +  account_id + daily_avg_heating_degree,
                                data = aggregated_data %>% 
                                  filter(!is.na(property_value_category), !rate_period=="Overall") %>%
                                  group_by(account_id, date) %>%
                                  mutate(share_consumption = total_consumption/sum(total_consumption)),
                                split = ~ rate_period,
                                cluster = ~account_id)

# Initialize an empty data frame to store all coefficients
all_coefs <- data.frame()

for (i in 1:5) {
  
  # Find model
  val <- m_property_value[[i]]$model_info$sample$value
  j <- which(sapply(1:5, function(j) m1[[j]]$model_info$sample$value) == val)
  
  # Extract coefficients and standard errors for total_consumption
  coefs_total <- coeftable(m_property_value[i]) %>%
    data.frame() %>%
    separate(coefficient, into = c("cosy_contract_active", "remove1", "Property Value", "remove2"), 
             sep = "::") %>%
    mutate(lower_ci = Estimate - 1.96 * `Std..Error`,
           upper_ci = Estimate + 1.96 * `Std..Error`,
           outcome = "Total Consumption",
           period = factor(sample, levels = c("Morning Cosy",
                                              "Afternoon Cosy",
                                              "Peak Rate",
                                              "Other", 
                                              "Overall")),
           `Property Value` = factor(`Property Value`, levels = labels),
           average = m1[[j]]$coefficients)
  
  all_coefs <- bind_rows(all_coefs, coefs_total)
  
  # Define the shades of reds
  red_palette <- c("#FF9999", "#FF8080", "#FF6666", "#FF4D4D", "#FF3333", "#FF1A1A", "#FF0000", "#E60000", "#CC0000", "#B20000")
  
  # Create the ggplot
  ggplot(coefs_total, aes(x = `Property Value`, y = Estimate, fill = `Property Value`)) +
    geom_bar(stat = "identity", show.legend = FALSE) +
    geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, color = "grey") +
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
    geom_hline(yintercept = m1[[j]]$coefficients, linetype = "dashed", color = cosy_color, alpha = 0.6) +  # Add horizontal line at ATE
    scale_fill_manual(values = red_palette) +
    labs(
      x = "Property Value Decile",
      y = "Half Hourly Consumption in kWh"
    ) +
    scale_y_continuous(
      name = "Estimate (kWh)", 
    ) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),  # Tilt x-axis labels for better readability
      legend.position = "none"  # Remove legend
    )
  
  # Print the plot
  ggsave(paste0("../graphs/property_value_", val %>% tolower() %>% str_replace(" ", "_"), ".png"),
         width = 16, height = 8, units = "cm")
  
}


for (i in 1:4) {
  
  # Find model
  val <- m_property_value_share[[i]]$model_info$sample$value
  j <- which(sapply(1:4, function(j) m1_share[[j]]$model_info$sample$value) == val)
  
  # Extract coefficients and standard errors for total_consumption
  coefs_total <- coeftable(m_property_value_share[i]) %>%
    data.frame() %>%
    separate(coefficient, into = c("cosy_contract_active", "remove1", "Property Value", "remove2"), sep = "::") %>%
    mutate(
      average = m1_share[[j]]$coefficients,
      lower_ci = Estimate - 1.96 * `Std..Error`,
      upper_ci = Estimate + 1.96 * `Std..Error`,
      `%_ATE` = Estimate / abs(m1_share[[j]]$coefficients) * 100,
      lower_ci_ATE = lower_ci / abs(m1_share[[j]]$coefficients) * 100,
      upper_ci_ATE = upper_ci / abs(m1_share[[j]]$coefficients) * 100,
      period = val,
      outcome = "Share Consumption",
      `Property Value` = factor(`Property Value`, levels = labels),
      period = factor(val, levels = c("Morning Cosy",
                                      "Afternoon Cosy",
                                      "Peak Rate",
                                      "Other", 
                                      "Overall")))
  
  all_coefs <- bind_rows(all_coefs, coefs_total)
  
  # Define the shades of reds
  red_palette <- c("#FF9999", "#FF8080", "#FF6666", "#FF4D4D", "#FF3333", "#FF1A1A", "#FF0000", "#E60000", "#CC0000", "#B20000")
  
  # Create the ggplot
  ggplot(coefs_total, aes(x = `Property Value`, y = Estimate, fill = `Property Value`)) +
    geom_bar(stat = "identity", show.legend = FALSE) +
    geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, color = "grey") +
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
    geom_hline(yintercept = m1_share[[j]]$coefficients, linetype = "dashed", color = cosy_color, alpha = 0.6) +  # Add horizontal line at ATE
    scale_fill_manual(values = red_palette) +
    labs(
      x = "Property Value Decile",
      y = "Half Hourly Consumption in kWh"
    ) +
    scale_y_continuous(
      name = "% of Daily Consumption",
      labels = scales::percent_format(),
      sec.axis = sec_axis(~ ./m1_share[[j]]$coefficients, name = "% of ATE", labels = scales::percent_format())
    ) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),  # Tilt x-axis labels for better readability
      legend.position = "none"  # Remove legend
    )
  
  # Print the plot
  ggsave(paste0("../graphs/share_property_value_", val %>% tolower() %>% str_replace(" ", "_"), ".png"),
         width = 16, height = 8, units = "cm")
  
}


# Define the shades of reds
red_palette <- c("#FF9999", "#FF8080", "#FF6666", "#FF4D4D", "#FF3333", "#FF1A1A", "#FF0000", "#E60000", "#CC0000", "#B20000")

# Create the combined ggplot using facet_wrap
ggplot(all_coefs %>% filter(outcome == "Share Consumption"), 
       aes(x = `Property Value`, y = Estimate, fill = `Property Value`)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, color = "grey") +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
  geom_hline(aes(yintercept = average), linetype = "dashed", color = cosy_color, alpha = 0.6) +  # Add vertical line at average ATE
  scale_fill_manual(values = red_palette) +
  labs(
    x = "Property Value Decile"
  ) +
  scale_y_continuous(
    name = "Share of Daily Comsumption (%)", 
    labels = scales::percent_format(),
  ) +  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Tilt x-axis labels for better readability
    legend.position = "none"  # Remove legend
  ) +
  facet_wrap(~ period, scales = "free_y")


# Save the combined plot
ggsave("../graphs/property_value_share_combined.png", device = "png", width = 16, height = 12, units = "cm")



# Create the combined ggplot using facet_wrap
ggplot(all_coefs %>% filter(outcome == "Total Consumption", period != "Overall"), 
       aes(x = `Property Value`, y = Estimate, fill = `Property Value`)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, color="grey") +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
  geom_hline(aes(yintercept = average), linetype = "dashed", color = cosy_color, alpha = 0.6) +  # Add vertical line at average ATE
  scale_fill_manual(values = red_palette) +
  labs(
    x = "Property Value Decile",
  ) +
  scale_y_continuous(
    name = "Estimate (kWh)"  ) +  
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Tilt x-axis labels for better readability
    legend.position = "none"  # Remove legend
  ) +
  facet_wrap(~ period)


# Save the combined plot
ggsave("../graphs/property_value_combined.png", device = "png", width = 16, height = 12, units = "cm")



```

### Figure A.36: Impact of Cosy by Region

```{r regions, eval=FALSE}

m_region <- feols(consumption_hh ~ i(cosy_contract_active, region, ref =0) 
                  | date +  account_id + daily_avg_heating_degree,
                  data = aggregated_data %>% filter(!is.na(region), !region==""),
                  split = ~ rate_period,
                  cluster = ~account_id)
etable(m_region, tex = TRUE, title = "Cosy Adoption by Region",
       label = "tab:regionaldid",
       fitstat = ~ N + g + pre_avg +t_obs + r2, 
       file = "../tables/did_region.tex", replace = TRUE)


# Extract coefficients for total consumption
all_coefs <- data.frame()
for (i in 1:5) {
  val <- m_region[[i]]$model_info$sample$value
  j <- which(sapply(1:5, function(j) m1[[j]]$model_info$sample$value) == val)
  
  coefs_total <- coeftable(m_region[[i]]) %>%
    data.frame() %>%
    tibble::rownames_to_column("term") %>%
    separate(term, into = c("cosy_contract_active", "remove1", "Region", "remove2"), sep = "::") %>%
    mutate(
      average = m1[[j]]$coefficients,
      lower_ci = Estimate - 1.96 * `Std..Error`,
      upper_ci = Estimate + 1.96 * `Std..Error`,
      `%_ATE` = Estimate / abs(m1[[j]]$coefficients) * 100,
      lower_ci_ATE = lower_ci / abs(m1[[j]]$coefficients) * 100,
      upper_ci_ATE = upper_ci / abs(m1[[j]]$coefficients) * 100,
      period = factor(val, levels = c("Morning Cosy",
                                      "Afternoon Cosy",
                                      "Peak Rate",
                                      "Other", 
                                      "Overall")))
  
  
  all_coefs <- bind_rows(all_coefs, coefs_total)
}

# Select a color palette from RColorBrewer
region_colors <- brewer.pal(n = length(unique(all_coefs$Region)), name = "Set3")

# Order regions by their estimate size for period == "Morning Cosy"
morning_cosy_order <- all_coefs %>%
  filter(period == "Morning Cosy") %>%
  arrange(desc(Estimate)) %>%
  pull(Region)

# Reorder the Region factor based on the estimate size in "Morning Cosy"
all_coefs <- all_coefs %>%
  mutate(Region = factor(Region, levels = morning_cosy_order))

# Create the ggplot
ggplot(all_coefs %>% filter(period != "Overall"), aes(x = Region, y = Estimate, fill = Region)) +
  geom_bar(stat = "identity") +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, color = "grey") +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
  geom_hline(aes(yintercept = average), linetype = "dashed", color = cosy_color, alpha = 0.6) +  # Add vertical line at average ATE
  scale_fill_manual(values = region_colors) +  # Apply random colors to regions
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Tilt x-axis labels for better readability
    legend.position = "none"  # Remove legend
  ) +
  facet_wrap(~ period)

# Save the plot
ggsave("../graphs/region_combined.png", device = "png", width = 16, height = 12, units = "cm")


```

### Figure A.35: Impact of Cosy Adoption by MSOA Income on Consumption

```{r income-msoa}
# Load and preprocess the cosy_hp_details data
cosy_hp_details <- fread("../data/input/cosy_-_cosy_details_2024_07_24.csv") %>%
  inner_join(aggregated_data %>% select(hashed_mpan) %>% distinct(), by = "hashed_mpan") %>%
  filter(!is.na(postcode)) %>%
  distinct(hashed_mpan, postcode)


postcode_msoa <- fread("../data/input/PCD_OA21_LSOA21_MSOA21_LAD_AUG23_UK_LU.csv") %>%
  left_join(cosy_hp_details, by = c("pcds" = "postcode")) %>%
  mutate(n = ifelse(is.na(n), 0, 1)) %>%
  select(msoa21cd, pcds) %>%
  distinct(pcds, .keep_all = TRUE)

income <- readxl::read_excel("../data/input/saiefy1920finalqaddownload280923.xlsx", sheet = "Total annual income", skip = 4) %>%
  select(`MSOA code`, `Total annual income (£)`) %>%
  distinct() %>%
  inner_join(postcode_msoa, by=c("MSOA code"="msoa21cd")) %>%
  distinct(pcds, .keep_all = TRUE)


# Create unique breaks for predicted_heatloss_watts
income_dist <- readxl::read_excel("../data/input/saiefy1920finalqaddownload280923.xlsx", sheet = "Total annual income", skip = 4) %>%
  select(`MSOA code`, `Total annual income (£)`) 


breaks <- unique(quantile(income_dist$`Total annual income (£)`/1000, probs = seq(0, 1, by = 0.1)))

# Create pretty labels for the categories
labels <- sapply(1:(length(breaks)-1), function(i) paste0("£", round(breaks[i]), "k-", round(breaks[i+1]), "k"))

aggregated_data <- aggregated_data[,1:53] %>%
  left_join(cosy_hp_details) %>%
  left_join(income, by=c("postcode"="pcds")) %>%
  mutate(income_category = cut(`Total annual income (£)`/1000, 
                               breaks = breaks, 
                               include.lowest = TRUE,
                               labels = labels))
# income check
m_income <- feols(consumption_hh ~ i(cosy_contract_active, income_category, ref =0) 
                  | date +  account_id + daily_avg_heating_degree,
                  data = aggregated_data,
                  split = ~ rate_period,
                  cluster = ~account_id)


m_income_share <- feols(share_consumption ~ i(cosy_contract_active, income_category, ref =0) 
                        | date +  account_id + daily_avg_heating_degree,
                        data = aggregated_data %>% 
                          filter(!is.na(income_category), !rate_period=="Overall") %>%
                          group_by(account_id, date) %>%
                          mutate(share_consumption = total_consumption/sum(total_consumption)),
                        split = ~ rate_period,
                        cluster = ~account_id)


for (i in 1:5) {
  
  # Find model
  val <- m_income[[i]]$model_info$sample$value
  j <- which(sapply(1:5, function(j) m1[[j]]$model_info$sample$value) == val)
  
  # Extract coefficients and standard errors for total_consumption
  coefs_total <- coeftable(m_income[i]) %>%
    data.frame() %>%
    separate(coefficient, into = c("cosy_contract_active", "remove1", "Income Category", "remove2"), sep = "::") %>%
    mutate(lower_ci = Estimate - 1.96 * `Std..Error`,
           upper_ci = Estimate + 1.96 * `Std..Error`,
           outcome = "Total Consumption") %>%
    mutate(`Income Category` = factor(`Income Category`, levels = labels))
  
  # Define the shades of reds
  red_palette <- c("#FF9999", "#FF8080", "#FF6666", "#FF4D4D", "#FF3333", "#FF1A1A", "#FF0000", "#E60000", "#CC0000", "#B20000")
  
  # Create the ggplot
  ggplot(coefs_total, aes(x = `Income Category`, y = Estimate, fill = `Income Category`)) +
    geom_bar(stat = "identity", show.legend = FALSE) +
    geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, color = "grey") +
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
    geom_hline(yintercept = m1[[j]]$coefficients, linetype = "dashed", color = cosy_color, alpha = 0.6) +  # Add horizontal line at ATE
    scale_fill_manual(values = red_palette) +
    labs(
      x = "Income Decile",
      y = "Half Hourly Consumption in kWh"
    ) +
    scale_y_continuous(
      name = "Estimate (kWh)", 
      sec.axis = sec_axis(~ ./m1[[j]]$coefficients, name = "% of ATE", labels = scales::percent_format())
      
    ) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),  # Tilt x-axis labels for better readability
      legend.position = "none"  # Remove legend
    )
  
  # Print the plot
  ggsave(paste0("../graphs/income_", val %>% tolower() %>% str_replace(" ", "_"), ".png"),
         width = 16, height = 8, units = "cm")
  
}


# Initialize an empty data frame to store all coefficients
all_coefs <- data.frame()

# Extract coefficients for total consumption
for (i in 1:5) {
  val <- m_income[[i]]$model_info$sample$value
  j <- which(sapply(1:5, function(j) m1[[j]]$model_info$sample$value) == val)
  
  coefs_total <- coeftable(m_income[[i]]) %>%
    data.frame() %>%
    tibble::rownames_to_column("term") %>%
    separate(term, into = c("cosy_contract_active", "remove1", "Income Category", "remove2"), sep = "::") %>%
    mutate(
      average = m1[[j]]$coefficients,
      lower_ci = Estimate - 1.96 * `Std..Error`,
      upper_ci = Estimate + 1.96 * `Std..Error`,
      `%_ATE` = Estimate / abs(m1[[j]]$coefficients) * 100,
      lower_ci_ATE = lower_ci / abs(m1[[j]]$coefficients) * 100,
      upper_ci_ATE = upper_ci / abs(m1[[j]]$coefficients) * 100,
      outcome = "Total Consumption",
      `Income Category` = factor(`Income Category`, levels = labels),
      period = factor(val, levels = c("Morning Cosy",
                                      "Afternoon Cosy",
                                      "Peak Rate",
                                      "Other", 
                                      "Overall")))
  
  all_coefs <- bind_rows(all_coefs, coefs_total)
}


# Define the shades of reds
red_palette <- c("#FF9999", "#FF8080", "#FF6666", "#FF4D4D", "#FF3333", "#FF1A1A", "#FF0000", "#E60000", "#CC0000", "#B20000")


# Create the combined ggplot using facet_wrap
ggplot(all_coefs %>% filter(outcome == "Total Consumption", period != "Overall"), 
       aes(x =`Income Category`, y = Estimate, fill = `Income Category`)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, color = "grey") +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
  geom_hline(aes(yintercept = average), linetype = "dashed", color = cosy_color, alpha = 0.6) +  # Add vertical line at average ATE
  scale_fill_manual(values = red_palette) +
  labs(
    x = "MSOA Income Decile",
  ) +
  scale_y_continuous(
    name = "Estimate (kWh)", 
  ) +  
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Tilt x-axis labels for better readability
    legend.position = "none"  # Remove legend
  ) +
  facet_wrap(~ period, scales = "free_y")


# Save the combined plot
ggsave("../graphs/income_category_combined.png", device = "png", width = 16, height = 12, units = "cm")


all_coefs <- list()
# Extract coefficients for share consumption
for (i in 1:4) {
  val <- m_income_share[[i]]$model_info$sample$value
  j <- which(sapply(1:4, function(j) m1_share[[j]]$model_info$sample$value) == val)
  
  coefs_share <- coeftable(m_income_share[[i]]) %>%
    data.frame() %>%
    tibble::rownames_to_column("term") %>%
    separate(term, into = c("cosy_contract_active", "remove1", "income_decile", "remove2"), sep = "::") %>%
    mutate(
      average = m1_share[[j]]$coefficients,
      lower_ci = Estimate - 1.96 * `Std..Error`,
      upper_ci = Estimate + 1.96 * `Std..Error`,
      `%_ATE` = Estimate / abs(m1_share[[j]]$coefficients) * 100,
      lower_ci_ATE = lower_ci / abs(m1_share[[j]]$coefficients) * 100,
      upper_ci_ATE = upper_ci / abs(m1_share[[j]]$coefficients) * 100,
      period = val,
      outcome = "Share Consumption",
      `income_decile` = factor(`income_decile`, levels = labels),
      period = factor(val, levels = c("Morning Cosy",
                                      "Afternoon Cosy",
                                      "Peak Rate",
                                      "Other", 
                                      "Overall")))
  
  all_coefs <- bind_rows(all_coefs, coefs_share)
}

# Define the shades of reds
red_palette <- c("#FF9999", "#FF8080", "#FF6666", "#FF4D4D", "#FF3333", "#FF1A1A", "#FF0000", "#E60000", "#CC0000", "#B20000")

# Create the combined ggplot using facet_wrap
ggplot(all_coefs %>% filter(outcome == "Share Consumption"), 
       aes(x = `income_decile`, y = Estimate, fill = `income_decile`)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, color = "grey") +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
  geom_hline(aes(yintercept = average), linetype = "dashed", color = cosy_color, alpha = 0.6) +  # Add vertical line at average ATE
  scale_fill_manual(values = red_palette) +
  labs(
    x = "MSOA Income Decile"
  ) +
  scale_y_continuous(
    name = "Share of Daily Comsumption (%)", 
    labels = scales::percent_format(),
  ) +  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Tilt x-axis labels for better readability
    legend.position = "none"  # Remove legend
  ) +
  facet_wrap(~ period, scales = "free_y")


# Save the combined plot
ggsave("../graphs/income_share_combined.png", device = "png", width = 16, height = 12, units = "cm")


```

### Table A.12: Cosy Adoption by Previous Tariff Type

```{r prev-tariff}

# Register the pre-treatment average fit statistic
fitstat_register("pre_avg_tou", function(x) {
  
  # Extract the formula
  formula <- x$fml_all$linear
  
  # Extract the outcome variable from the formula
  outcome_variable <- all.vars(formula)[1]
  
  # Extract the call object and evaluate the data argument
  call_object <- x$call
  data_expr <- call_object$data
  data <- eval(data_expr)
  
  # Get the logical vector of observations used in the model
  obs_used <- obs(x)
  
  # Subset the original dataset using this logical vector
  data_used <- data[obs_used, ]
  
  # Ensure the outcome variable is treated as a column name
  outcome_values <- data_used[[outcome_variable]]
  
  # Create pre-avg for non-HP installed group
  pre_avg <- mean(outcome_values[data_used$previous_is_charged_half_hourly == 1 & data_used$date < data_used$first_adoption], na.rm = TRUE)
  
  # Format the pre-avg
  formatted_pre_avg <- format_decimal(pre_avg)
  
  return(formatted_pre_avg)
}, "Half Hourly Consumption ToU")


# Register the pre-treatment average fit statistic
fitstat_register("pre_avg_nontou", function(x) {
  
  # Extract the formula
  formula <- x$fml_all$linear
  
  # Extract the outcome variable from the formula
  outcome_variable <- all.vars(formula)[1]
  
  # Extract the call object and evaluate the data argument
  call_object <- x$call
  data_expr <- call_object$data
  data <- eval(data_expr)
  
  # Get the logical vector of observations used in the model
  obs_used <- obs(x)
  
  # Subset the original dataset using this logical vector
  data_used <- data[obs_used, ]
  
  # Ensure the outcome variable is treated as a column name
  outcome_values <- data_used[[outcome_variable]]
  
  # Create pre-avg for non-HP installed group
  pre_avg <- mean(outcome_values[data_used$previous_is_charged_half_hourly == 0 & data_used$date < data_used$first_adoption], na.rm = TRUE)
  
  # Format the pre-avg
  formatted_pre_avg <- format_decimal(pre_avg)
  
  return(formatted_pre_avg)
}, "Half Hourly Consumption Non-ToU")


m3 <- feols(consumption_hh ~ i(cosy_contract_active) +  i(cosy_contract_active, previous_is_charged_half_hourly, ref=0) | 
              daily_avg_heating_degree + account_id + date, 
            data = aggregated_data, 
            cluster = ~account_id,
            split = ~ rate_period)

etable(m3, tex = TRUE, title = "Cosy Adoption by Previous Tariff Type",
       label = "tab:prevrav",
       fitstat = ~ N + g + pre_avg_nontou + pre_avg_tou +t_obs + r2,
       dict = c(previous_is_charged_half_hourly = "Prev is ToU"),
       file = "../tables/did_prevar.tex", replace = TRUE)

# Read the generated LaTeX file
file_content <- readLines("../tables/did_prevar.tex")

# Find the lines with the pre-treatment average and remove them
pre_avg_line_index <- grep("Half Hourly Consumption", file_content)[2]
pre_avg_line_index2 <- grep("Half Hourly Consumption", file_content)[3]
pre_avg_lines <- file_content[pre_avg_line_index:(pre_avg_line_index2)]
file_content <- file_content[-c(pre_avg_line_index, pre_avg_line_index2)]

# Find the position just after the coefficients
coeff_end_index <- grep("Cosy Contract Active", file_content)[2] + 2
if (length(coeff_end_index) > 1) {
  coeff_end_index <- coeff_end_index[-1]
}

# Insert the pre-treatment average row after the coefficients
file_content <- append(file_content, pre_avg_lines, after = coeff_end_index)

file_content <- append(file_content,"\\emph{Pre-Treatment Average}\\", after = coeff_end_index)

# Add a \midrule after the pre-treatment average
file_content <- append(file_content, "\\midrule", after = coeff_end_index+3)

# Write the modified content back to the LaTeX file
writeLines(file_content, "../tables/did_prevar.tex")  

```

### Figure A.21: Main Results Coefficients With and Without Controlling for Heat Pump
Installation

```{r hpinstallation}

# Register the pre-treatment average fit statistic
fitstat_register("pre_avg3", function(x) {
  
  # Extract the formula
  formula <- x$fml_all$linear
  
  # Extract the outcome variable from the formula
  outcome_variable <- all.vars(formula)[1]
  
  # Extract the call object and evaluate the data argument
  call_object <- x$call
  data_expr <- call_object$data
  data <- eval(data_expr)
  
  # Get the logical vector of observations used in the model
  obs_used <- obs(x)
  
  # Subset the original dataset using this logical vector
  data_used <- data[obs_used, ]
  
  # Ensure the outcome variable is treated as a column name
  outcome_values <- data_used[[outcome_variable]]
  
  # Create pre-avg for non-HP installed group
  pre_avg <- mean(outcome_values[data_used$is_hp_installed == 1 & data_used$cosy_contract_active == 1], na.rm = TRUE)
  
  # Format the pre-avg
  formatted_pre_avg <- format_decimal(pre_avg)
  
  return(formatted_pre_avg)
}, "Half Hourly Consumption Pre-Cosy")


# Register the pre-treatment average fit statistic
fitstat_register("pre_avg2", function(x) {
  
  # Extract the formula
  formula <- x$fml_all$linear
  
  # Extract the outcome variable from the formula
  outcome_variable <- all.vars(formula)[1]
  
  # Extract the call object and evaluate the data argument
  call_object <- x$call
  data_expr <- call_object$data
  data <- eval(data_expr)
  
  # Get the logical vector of observations used in the model
  obs_used <- obs(x)
  
  # Subset the original dataset using this logical vector
  data_used <- data[obs_used, ]
  
  # Ensure the outcome variable is treated as a column name
  outcome_values <- data_used[[outcome_variable]]
  
  # Create pre-avg for non-HP installed group
  pre_avg <- mean(outcome_values[data_used$is_hp_installed == 0], na.rm = TRUE)
  
  # Format the pre-avg
  formatted_pre_avg <- format_decimal(pre_avg)
  
  return(formatted_pre_avg)
}, "Half Hourly Consumption Pre-Heatpump")


# get the subsample with HP installation by OE
# get install date
hp_install_date <- fread("../data/input/cosy_-_hp_details_2024_06_25.csv") %>%
  select(account_id, installed_at) %>%
  mutate(installed_at = as.Date(installed_at))

# get people from the survey responders
survey_responses <- fread("../data/input/responses.csv") %>%
  select(-Other) %>% 
  rename(account_number = kid) %>%
  inner_join(fread("../data/input/survey_ids.csv")) %>%
  mutate(installed_at_2 = as.Date(`When was your heat pump installed?`),
         `Electric vehicle(s)` = as.numeric(`Electric vehicle(s)`=="Electric vehicle(s)"))

aggregated_data <- aggregated_data %>%
  left_join(hp_install_date)  %>%
  left_join(survey_responses)  %>%
  mutate(is_hp_installed = ifelse(!is.na(installed_at), 
                                  as.numeric(installed_at <= date),
                                  ifelse(!is.na(installed_at_2),  as.numeric(installed_at_2 <= date),
                                         NA)))


m_hp_cosy <- feols(consumption_hh ~ i(is_hp_installed) + i(cosy_contract_active) | daily_avg_heating_degree + account_id + date, 
                   data = aggregated_data, 
                   cluster = ~account_id, 
                   split = ~ rate_period)

etable(m_hp_cosy, tex=TRUE, title = "HP and Cosy Adoption",
       fitstat = ~ N + g + pre_avg2 + pre_avg3  +t_obs + r2, file = "../tables/did_hp_install.tex", replace = TRUE, label="tab:did-hp-install")



# Read the generated LaTeX file
file_content <- readLines("../tables/did_hp_install.tex")

# Find the lines with the pre-treatment average and remove them
pre_avg_line_index <- grep("Half Hourly Consumption Pre-Heatpump", file_content)
pre_avg_line_index2 <- grep("Half Hourly Consumption Pre-Cosy", file_content)
pre_avg_lines <- file_content[pre_avg_line_index]
pre_avg_lines2 <- file_content[pre_avg_line_index2]

file_content <- file_content[-c(pre_avg_line_index, pre_avg_line_index2)]

# Find the position just after the coefficients
coeff_end_index <- grep("Cosy Contract Active", file_content) + 2
if (length(coeff_end_index) > 1) {
  coeff_end_index <- coeff_end_index[-1]
}

# Insert the pre-treatment average row after the coefficients
file_content <- append(file_content, pre_avg_lines, after = coeff_end_index)
file_content <- append(file_content, pre_avg_lines2, after = coeff_end_index)
file_content <- append(file_content,"\\emph{Pre-Treatment Average}\\", after = coeff_end_index)
# Add a \midrule after the pre-treatment average
file_content <- append(file_content, "\\midrule", after = coeff_end_index + length(pre_avg_lines))

# Modify the label for "Size of the 'effective' sample" to "Number of Households"
sample_line <- grep("Size of the 'effective' sample", file_content)
file_content[sample_line] <- gsub("Size of the 'effective' sample", "Number of Households", file_content[sample_line])


# Write the modified content back to the LaTeX file
writeLines(file_content, "../tables/did_hp_install.tex")

# Write the modified content back to the LaTeX file
# plot the coefficients with and without controls

m_without_control <- feols(consumption_hh ~ i(cosy_contract_active) | daily_avg_heating_degree + account_id + date, 
                           data = aggregated_data %>% filter(!is.na(installed_at_2)), 
                           split = ~ rate_period,
                           cluster = ~account_id)
m_with_control <- feols(consumption_hh ~ i(cosy_contract_active) | daily_avg_heating_degree + account_id + date + is_hp_installed, 
                        data = aggregated_data %>% filter(!is.na(installed_at_2)), 
                        split = ~ rate_period,
                        cluster = ~account_id) 

# Extract coefficients and standard errors for total_consumption
coefs_total <- rbind(coeftable(m_without_control)  %>%
                       data.frame() %>%
                       mutate(lower_ci = Estimate - 1.96 * `Std..Error`,
                              upper_ci = Estimate + 1.96 * `Std..Error`,
                              model = "Without HP Installation Date"),
                     coeftable(m_with_control)  %>%
                       data.frame() %>%
                       mutate(lower_ci = Estimate - 1.96 * `Std..Error`,
                              upper_ci = Estimate + 1.96 * `Std..Error`,
                              model = "With HP Installation Date")) %>%
  mutate(rate_period = factor(sample, levels = c("Morning Cosy",
                                                 "Afternoon Cosy",
                                                 "Peak Rate",
                                                 "Other", 
                                                 "Overall")))

# Define custom colors
custom_colors <- c("Without HP Installation Date" = "#E8F5FF", "With HP Installation Date" = cosy_color)

# Create the ggplot
ggplot(coefs_total, aes(x = factor(rate_period), y = Estimate, fill = model)) +
  geom_bar(stat = "identity", position = position_dodge(width = 1), show.legend = TRUE) +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, position = position_dodge(width = 1), alpha=0.6) +
  scale_fill_manual(values = custom_colors) +
  labs(x = "Rate Period",
       y = "Coefficient Estimate",
       fill = "Model") +
  theme_minimal() +
  theme(legend.position = "bottom")

# Print the plot
ggsave(paste0("../graphs/did_controlling_hp_installation.png"),
       width = 16, height = 8, units = "cm")


etable(m_with_control, m_without_control, tex=TRUE, title = "HP and Cosy Adoption",
       fitstat = ~ N + g  + pre_avg2 + pre_avg3 +t_obs + r2, file = "../tables/did_hp_install_overall.tex", replace = TRUE, label="tab:did-hp-install-overall")


# Read the generated LaTeX file
file_content <- readLines("../tables/did_hp_install_overall.tex")

# F# Find the lines with the pre-treatment average and remove them
pre_avg_line_index <- grep("Half Hourly Consumption Pre-Heatpump", file_content)
pre_avg_line_index2 <- grep("Half Hourly Consumption Pre-Cosy", file_content)
pre_avg_lines <- file_content[pre_avg_line_index]
pre_avg_lines2 <- file_content[pre_avg_line_index2]

file_content <- file_content[-c(pre_avg_line_index, pre_avg_line_index2)]

# Find the position just after the coefficients
coeff_end_index <- grep("Cosy Contract Active", file_content) + 2
if (length(coeff_end_index) > 1) {
  coeff_end_index <- coeff_end_index[-1]
}

# Insert the pre-treatment average row after the coefficients
file_content <- append(file_content, pre_avg_lines, after = coeff_end_index)
file_content <- append(file_content, pre_avg_lines2, after = coeff_end_index)
file_content <- append(file_content,"\\emph{Pre-Treatment Average}\\", after = coeff_end_index)
# Add a \midrule after the pre-treatment average
file_content <- append(file_content, "\\midrule", after = coeff_end_index + length(pre_avg_lines))

# Modify the label for "Size of the 'effective' sample" to "Number of Households"
sample_line <- grep("Size of the 'effective' sample", file_content)
file_content[sample_line] <- gsub("Size of the 'effective' sample", "Number of Households", file_content[sample_line])

# Write the modified content back to the LaTeX file
writeLines(file_content, "../tables/did_hp_install_overall.tex")
```



