---
title: "Heatpump analysis"
author: "Louise Bernard"
date: "2024-06-04"
output: html_document
---

- get gas data for HP installation
- add EV/ export checks on cosy analysis
- change everything to half hourly average
- add overall daily estimates 
- create the main headlines graphs for electricity curve, HP installation, cosy adoption


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include=FALSE, warning  = FALSE, fig.pos = "H", out.extra = "")

# Load necessary libraries
library(knitr)
library(kableExtra)
library(fixest)
library(data.table)
library(lubridate)
library(dplyr)
library(ggplot2)
library(RColorBrewer)
library(tidyr)
library(scales)  # For date formatting
library(viridis)  # Load the viridis package for better color options
library(stringr)
library(did)
library(readxl)
library(stargazer)

# set dictionary
setFixest_dict(c(consumption_hh = "Consumption in kWh per half hour",
                 total_consumption = "Weekly Energy Consumption in kWh", 
                 daily_consumption = "Consumption in kWh per day",
                 share_consumption = "Share of daily consumption",
                 weekly_consumption = "Weekly Gas Consumption in kWh",
                 is_hp_installed = "OnCosy",
                 daily_avg_heating_degree = "HDD",
                 avg_heating_degree = "HDD",
                 date = "Day", 
                 settlement_week = "Week",
                 account_id = "Household", 
                 corrected_consumption = "Monthly Gas Consumption in kWh",
                 account_closed = "Account Closed",
                 tariff_gsp_group_id = "GSP", 
                 rate_period = "Rate period",
                 is_variable = "Variable Tariff",
                 energy_efficiency = "Energy Efficiency",
                 estimated_annual_consumption = "EAC",
                 eac_mwh = "EAC in mWh",
                 is_hp_installed = "Is HP Installed",
                 predicted_is_installed = "Is HP Installed",
                 elec_consumption = "Weekly Electricity Consumption (kWh)",
                 gas_consumption = "Weekly Gas Consumption (kWh)",
                 month_date = "Month",
                 is_winter = "Winter",
                 previous_is_variable = "Prev Is Variable",
                 epc_letter = "EPC",
                 latest_survey_heat_loss = "Heatloss (W)",
                 urban = "Urban",
                 hp_survey_is_solar_present = "Has Solar PV",
                 floor_area = "Floor area",
                 property_value = "Property value",
                 months_since_hp_rec = "Months Since HP Installation",
                 ev_charging = "EV Charging",
                 has_ev = "EV User"))

hp_color <- "#AD87CA"
not_hp_color <- "#2D354A"


```


```{r define-functions}

CleanPreAverage <- function(file_path) {
  
  # Read the generated LaTeX file
  file_content <- readLines(file_path)
  
  # Find the lines with the pre-treatment average and remove them
  if (length(grep("Yearly Consumption", file_content))==1) {
    pre_avg_line_index <- grep("Yearly Consumption", file_content)
  } else {
    pre_avg_line_index <- grep("Yearly Consumption", file_content)[2]
  }
  
  # Find the lines with the pre-treatment average and remove them
  pre_avg_lines <- file_content[pre_avg_line_index:(pre_avg_line_index)]
  file_content <- file_content[-c(pre_avg_line_index, pre_avg_line_index)]
  
  # Find the position just after the coefficients
  coeff_end_index <- grep("Is HP Installed", file_content)[length(grep("Is HP Installed", file_content))] + 2
  
  # Insert the pre-treatment average row after the coefficients
  file_content <- append(file_content, pre_avg_lines, after = coeff_end_index)
  file_content <- append(file_content, "\\emph{Pre-Treatment Average}\\\\", after = coeff_end_index)
  
  # Add a \midrule after the pre-treatment average
  file_content <- append(file_content, "\\midrule", after = coeff_end_index + length(pre_avg_lines)+1)
  
  # Modify the label for "Size of the 'effective' sample" to "Number of Households"
  sample_line <- grep("Size of the 'effective' sample", file_content)
  file_content[sample_line] <- gsub("Size of the 'effective' sample", "Number of Households", file_content[sample_line])
  
  # Write the modified content back to the LaTeX file
  writeLines(file_content, file_path)
}



# Function to format numbers
format_number <- function(number) {
  return(format(round(number), big.mark = ",", scientific = FALSE))
}

# Function to format numbers with four decimal places
format_decimal <- function(number, digits = 2) {
  return(format(round(number, digits), nsmall = digits, big.mark = ",", scientific = FALSE))
}


# Register the pre-treatment average fit statistic
fitstat_register("pre_avg", function(x) {
  
  # Directly use the model's data
  model_data <- eval(x$call$data, envir = x$call_env)
  
  # Extract the outcome variable from the formula
  outcome_variable <- all.vars(x$fml_all$linear)[1]
  
  # Get the logical vector of observations used in the model
  obs_used <- obs(x)
  
  # Ensure `obs_used` correctly subsets the data
  if (is.logical(obs_used) && length(obs_used) == nrow(model_data)) {
    data_used <- model_data[obs_used, ]
  } else if (is.numeric(obs_used) && all(obs_used <= nrow(model_data))) {
    data_used <- model_data[obs_used, ]
  } else {
    stop("Unable to correctly subset data. Check the obs_used vector.")
  }
  
  # Extract the outcome values
  outcome_values <- data_used[[outcome_variable]]
  
  # Create pre-avg for non-HP installed group
  pre_avg <- mean(outcome_values[data_used$is_hp_installed == 0], na.rm = TRUE)
  
  # Format the pre-avg
  formatted_pre_avg <- format_decimal(pre_avg)
  
  return(formatted_pre_avg)
}, "Yearly Consumption")




# Add number of time periods
fitstat_register("t_obs", function(x) {
  
  # time variable
  t_var <- x$fixef_vars[3]
  
  # nbr of unique val for t var
  t_obs <- x$fixef_sizes[t_var]
  
  return(format_number(t_obs))
}, "Number of Time Periods")


```


# Load data and summary statistics

## Dataset used

- cosy - hp users gas: weekly gas consumption for customers that have a HP installation booked or HP installed by OE
- cosy - hp details: customers characteristics
- cosy - ev detection query: ev detection for customers that have HP booked 
- cosy - hp electricty readings: electricty data by periods for customers that have a HP installation booked or HP installed by OE
- cosy - hp cost: quoted costs of install


- cosy - cosy adopters gas readings: weekly gas consumption for customers that have adopted cosy
- cosy - cosy electricity readings: electricity data by periods for customers that have adopted cosy
- cosy - cosy details: customers characteristics
- cosy - agreement data



## Load data

```{r load-dataset}


# get consumption by period
hp_installed_period <- fread("../data/input/cosy_-_hp_aggregated_up_2024_06_18.csv") %>%
  rename(total_consumption=total_read_value,
         date = settlement_date) %>%
  mutate(consumption_hh = ifelse(rate_period == "Other", 
                                 total_consumption/30, total_consumption/6),
         date = as.Date(date))

# aggreate up to get overall
hp_installed_daily <- hp_installed_period %>%
  group_by(account_id, hashed_mpan, date) %>%
  summarise(total_consumption = sum(total_consumption)) %>%
  mutate(consumption_hh = total_consumption / 48,
         rate_period = factor("Overall")) 

# merge together to make regressions easier
hp_installed <- full_join(hp_installed_period,
                          hp_installed_daily) %>%
  inner_join(fread("../data/input/cosy_-_hp_details_2024_06_25.csv"), by=c("account_id","hashed_mpan"))

# add daily weather data
weather <- fread("../data/input/Cosy Analysis Weather Mar 26 daily.csv") %>% 
  rename_with(.cols = starts_with("weekly"), 
              .fn = ~ sub("^weekly", "daily", .)) %>%
  rename(tariff_gsp_group_id=gsp_group_id) %>%
  mutate(date_day=as.Date(date_day, format = "%Y-%m-%d")) %>%
  rename(date = date_day)

# merge weather
hp_installed <- hp_installed %>%
  left_join(weather)


rm(weather, combined_df, combined_df2, hp_installed_daily, hp_installed_period)

# hp_installed <- hp_installed %>%
#   left_join(readRDS("../data/scratch/ev_mpan.RDS")) %>%
#   mutate(has_ev = ifelse(!is.na(ev_start), as.numeric(date >= ev_start), 0))

# clean up
hp_installed <- hp_installed %>%
  mutate(date = as.Date(date),
         is_hp_installed = as.numeric(installed_at <= date)) %>%
  mutate(rate_period = factor(rate_period, levels = c("Morning Cosy",
                                                      "Afternoon Cosy",
                                                      "Peak Rate",
                                                      "Other", 
                                                      "Overall"))) %>%
  group_by(account_id) %>%
  mutate(treated = max(is_hp_installed)) %>% # identify treated versus not yet treated
  distinct(account_id, date, rate_period, .keep_all = TRUE)

# summary statistics
summary(hp_installed)

# Check number of accounts
hp_installed %>% ungroup() %>% filter(treated==1) %>% select(account_id) %>% distinct() %>% dim()

# Load weather data
weather <- fread("../data/input/cosy_-_weather_weekly_2024_06_13.csv")

# Load and preprocess gas consumption data
# previous 2024_06_13.csv
cosy_hp_install_gas_consumption <- fread("../data/input/cosy_-_hp_users_gas_2024_06_13.csv") %>%
  group_by(account_id) %>%
  mutate(is_hp_installed = as.numeric(installed_at <= settlement_week),
         treated = max(is_hp_installed),
         min_settlement_week = min(settlement_week)) %>%
  left_join(weather, by = c("gsp_group_id", "settlement_week" = "week_date")) %>%
  distinct(account_id, settlement_week, .keep_all = TRUE)

# Create a sequence of weeks
min_date <- min(cosy_hp_install_gas_consumption$settlement_week)
max_date <- max(cosy_hp_install_gas_consumption$settlement_week)
all_weeks <- seq(min_date, max_date, by = "week")

# Create a data frame with all combinations of account_id and settlement_week
all_combinations <- expand.grid(
  account_id = unique(cosy_hp_install_gas_consumption$account_id),
  settlement_week = all_weeks
)

# Merge with original data
merged_data <- all_combinations %>%
  left_join(cosy_hp_install_gas_consumption %>% select(account_id, gsp_group_id, installed_at, min_settlement_week) %>% distinct()) %>%
  left_join(cosy_hp_install_gas_consumption %>% select(account_id, settlement_week, weekly_consumption) %>% distinct()) %>%
  filter(min_settlement_week < settlement_week) %>%
  mutate(
    account_closed = ifelse(is.na(weekly_consumption), 1, 0),
    is_hp_installed = as.numeric(installed_at < settlement_week),
    weekly_consumption = ifelse(is.na(weekly_consumption), 0, weekly_consumption)
  ) %>%
  left_join(weather, by = c("gsp_group_id", "settlement_week" = "week_date")) 

# Define overall_weekly by merging with electricity data
overall_weekly <- hp_installed %>%
  filter(rate_period == "Overall") %>%
  mutate(settlement_week = floor_date(date, "week") + 1,
         is_hp_installed = as.numeric(installed_at <= settlement_week)) %>%
  group_by(account_id, hashed_mpan, tariff_gsp_group_id, settlement_week, treated, installed_at, is_hp_installed) %>%
  summarise(elec_consumption = sum(total_consumption)) %>%
  rename(gsp_group_id = tariff_gsp_group_id) %>%
  left_join(merged_data %>%
              select(account_id, settlement_week, weekly_consumption) %>%
              rename(gas_consumption = weekly_consumption)) %>%
  left_join(weather %>% rename(settlement_week = week_date)) %>%
  mutate(
    gas_consumption = 52.25 * gas_consumption,
    elec_consumption = 52.25 * elec_consumption,
    total_consumption = gas_consumption + elec_consumption
  ) 

rm(all_combinations, cosy_hp_install_gas_consumption, merged_data, weather, all_weeks, max_date, min_date)
```

## Summary statistics {#sec:sumstats}

```{r introduction-graphs}
# Prepare the data for installations
weekly_installations <- hp_installed %>%
  group_by(account_id) %>%
  mutate(treated = max(is_hp_installed)) %>%
  filter(treated ==1) %>%
  ungroup() %>%
  select(account_id, installed_at) %>%
  distinct() %>%
  mutate(first_week = as.Date(floor_date(installed_at, "week"))) %>%
  group_by(first_week) %>%
  summarise(installations = n())

# Prepare the data for deals
weekly_deals <- hp_installed %>%
  group_by(account_id) %>%
  mutate(treated = max(is_hp_installed)) %>%
  filter(treated==1) %>%
  ungroup() %>%
  filter(year(deal_created_at)>2000)%>%
  select(account_id, deal_created_at) %>%
  distinct() %>%
  mutate(first_week = as.Date(floor_date(deal_created_at, "week"))) %>%
  group_by(first_week) %>%
  summarise(deals = n())

# Define the date for the announcement
announcement_date <- as.Date("2023-08-31")

# Choose colors from the Brewer palette
color_installations <- hp_color
color_deals <- hp_color

# Create the combined plot
ggplot() +
  # Plot for deals
  geom_line(data = weekly_deals, aes(x = first_week, y = deals, color = "Deals"), linetype = "dashed") +
  geom_vline(xintercept = as.numeric(announcement_date), linetype = "dashed", color = color_deals) +
  # Plot for installations
  geom_line(data = weekly_installations, aes(x = first_week, y = installations, color = "Installations")) +
  geom_point(data = weekly_installations, aes(x = first_week, y = installations, color = "Installations")) +
  annotate("text", x = announcement_date - weeks(1), y = max(weekly_deals$deals) * 0.9,
           label = "Announcement:\nBoiler Upgrade Scheme\nincrease to £7,500", hjust = 1, 
           color = color_deals) +
  labs(
    x = "Week",
    y = "Number of Installations/Deals",
    color = "Metric"
  ) +
  scale_x_date(
    labels = scales::date_format("%b %y"),
    date_breaks = "3 month"
  ) +
  scale_color_manual(values = c("Installations" = color_installations, "Deals" = "grey")) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

# Save the combined plot
ggsave("../graphs/combined_weekly_installations_deals.png", width = 15, height = 10, units = "cm", dpi = 300)
```

## HP Installation Costs

```{r sumstat-cost}
# Read the data
hp_cost <- fread("../data/input/cosy_-_hp_cost_2024_07_02.csv") %>%
  inner_join(hp_installed %>% filter(treated==1) %>% select(account_id) %>% distinct()) %>%
  mutate(`waiting_time (weeks)` = round(as.numeric(difftime(installed_at, deal_created_at, units = "weeks"))),
         `waiting_time (weeks)` = ifelse(`waiting_time (weeks)` > 1000, NA, `waiting_time (weeks)`))


hp_manufacturers <-  fread("../data/input/cosy - hp manufacturers.csv") %>%
  mutate(kW_rating = as.numeric(kW_rating)) %>%
  inner_join(hp_installed %>% filter(treated==1) %>% select(account_id) %>% distinct()) 

hist(hp_manufacturers$kW_rating)


# Create a histogram of unit_rate
ggplot(hp_manufacturers, aes(x = kW_rating)) +
  geom_histogram(binwidth = 1, fill = "skyblue", color = "black", alpha = 0.7) +
  labs(title = "Histogram of kW Ratings",
       x = "kW Rating",
       y = "Frequency") +
  theme_minimal() + 
  theme(legend.position = "none")

ggsave("../graphs/Histogram_of_kW_Ratings.png", width = 10, height = 6, dpi = 300)

```

```{r sumtable}
hp_cost <- hp_cost %>%
  select(-installed_at) %>%
  left_join(hp_manufacturers)

# Define the selected variables
selected_vars <- c("heatpump_cost_gbp", "electrical_cost_gbp", "radiator_cost_gbp", 
                   "cylinder_cost_gbp", "plumbing_cost_gbp", "bus_cost_gbp", 
                   "waste_collection_gbp", "additional_services_gbp", 
                   "labour_total_cost_gbp", "number_of_labour_days_quoted", 
                   "total_material_cost_gbp", "total_quote_cost_gbp", "waiting_time (weeks)", "kW_rating")

# Selecting only the specified columns and filtering out rows with NA in heatpump_cost_gbp
hp_cost <- hp_cost %>% 
  select(all_of(selected_vars)) %>% 
  filter(!is.na(heatpump_cost_gbp))

# Function to transform variable names
rename_variable <- function(var_name) {
  var_name <- str_replace_all(var_name, "_", " ")
  var_name <- str_replace_all(var_name, "gbp", "£")
  var_name <- str_to_title(var_name)
  var_name <- str_replace_all(var_name, "Bus", "BUS")
  return(var_name)
}

# Apply the function to the selected variables
new_var_names <- sapply(selected_vars, rename_variable)

# Rename the columns in the data frame
colnames(hp_cost) <- new_var_names

# Generating summary statistics using the psych package
summary_stats <- summary(hp_cost)

# Printing the summary statistics
stargazer(hp_cost, type = "latex", title = "HP Costs Summary Statistics", digits=0, style="aer", out="../tables/summary_stats_costs.tex")

# Print summary_stats
print(summary_stats)

```



```{r stripdown1}

# get consumption by period
hp_installed <- fread("../data/input/cosy_-_hp_aggregated_up_2024_06_18.csv") %>%
  group_by(account_id, settlement_date) %>%
  summarise(total_consumption = sum(total_read_value)) %>%
  mutate(consumption_hh = total_consumption / 48) %>%
  inner_join(fread("../data/input/cosy_-_hp_details_2024_06_25.csv") %>%
               distinct(account_id, .keep_all = TRUE),
             by=c("account_id")) %>%
  mutate(date = as.Date(settlement_date),
         is_hp_installed = as.numeric(installed_at <= date))%>%
  group_by(account_id) %>%
  mutate(treated = max(is_hp_installed))  # identify treated versus not yet treated

# Check number of accounts
hp_installed %>% ungroup() %>% filter(treated==1) %>% select(account_id) %>% distinct() %>% dim()

# Load and preprocess gas consumption data
# previous 2024_06_13.csv
cosy_hp_install_gas_consumption <- fread("../data/input/cosy_-_hp_users_gas_2024_06_13.csv") %>%
  group_by(account_id) %>%
  mutate(is_hp_installed = as.numeric(installed_at <= settlement_week),
         treated = max(is_hp_installed),
         min_settlement_week = min(settlement_week)) %>%
  distinct(account_id, settlement_week, .keep_all = TRUE)

# Create a sequence of weeks
min_date <- min(cosy_hp_install_gas_consumption$settlement_week)
max_date <- max(cosy_hp_install_gas_consumption$settlement_week)
all_weeks <- seq(min_date, max_date, by = "week")

# Create a data frame with all combinations of account_id and settlement_week
all_combinations <- expand.grid(
  account_id = unique(cosy_hp_install_gas_consumption$account_id),
  settlement_week = all_weeks
)

# Merge with original data
merged_data <- all_combinations %>%
  left_join(cosy_hp_install_gas_consumption %>% 
              distinct(account_id, settlement_week, weekly_consumption, 
                       min_settlement_week, installed_at)) %>%
  filter(min_settlement_week < settlement_week) %>%
  mutate(
    is_hp_installed = as.numeric(installed_at < settlement_week),
    weekly_consumption = ifelse(is.na(weekly_consumption), 0, weekly_consumption)
  ) 

# Define overall_weekly by merging with electricity data
overall_weekly <- hp_installed %>%
  mutate(settlement_week = floor_date(date, "week") + 1,
         is_hp_installed = as.numeric(installed_at <= settlement_week)) %>%
  group_by(account_id, hashed_mpan, tariff_gsp_group_id, settlement_week, treated, installed_at, is_hp_installed) %>%
  summarise(elec_consumption = sum(total_consumption)) %>%
  left_join(merged_data %>%
              select(account_id, settlement_week, weekly_consumption) %>%
              rename(gas_consumption = weekly_consumption)) %>%
  mutate(
    gas_consumption = 52.25 * gas_consumption,
    elec_consumption = 52.25 * elec_consumption,
    total_consumption = gas_consumption + elec_consumption
  ) 

rm(hp_installed)


```


```{r pop-weighted-msoas}
# Function to calculate weighted standard deviation
weighted_sd <- function(x, w) {
  sum_w <- sum(w, na.rm = TRUE)
  mean_w <- sum(w * x, na.rm = TRUE) / sum_w
  sqrt(sum(w * (x - mean_w)^2, na.rm = TRUE) / sum_w)
}

# Function to perform weighted t-test
weighted_t_test <- function(x, w, y, v) {
  n_x <- sum(w, na.rm = TRUE)
  n_y <- sum(v, na.rm = TRUE)
  mean_x <- sum(w * x, na.rm = TRUE) / n_x
  mean_y <- sum(v * y, na.rm = TRUE) / n_y
  var_x <- sum(w * (x - mean_x)^2, na.rm = TRUE) / n_x
  var_y <- sum(v * (y - mean_y)^2, na.rm = TRUE) / n_y
  t_stat <- (mean_x - mean_y) / sqrt(var_x / n_x + var_y / n_y)
  df <- (var_x / n_x + var_y / n_y)^2 / ((var_x / n_x)^2 / (n_x - 1) + (var_y / n_y)^2 / (n_y - 1))
  p_value <- 2 * pt(-abs(t_stat), df)
  return(p_value)
}

# Function to summarize and test
summarize_and_test <- function(data, var_name, weight_name) {
  # Calculate weighted means, standard deviations, and non-missing observation counts for each treatment group
  summary_stats <- data %>%
    group_by(treated) %>%
    summarise(
      N = sum(!is.na(.data[[var_name]])), # Count non-missing observations
      Weighted_Mean = weighted.mean(.data[[var_name]], .data[[weight_name]], na.rm = TRUE),
      SD = weighted_sd(.data[[var_name]], .data[[weight_name]]),
      .groups = 'drop'
    ) %>%
    pivot_wider(names_from = treated, values_from = c("N", "Weighted_Mean", "SD"), names_sep = " ")
  
  # Prepare for weighted t-test by separating data and weights
  data1 <- filter(data, treated == 1)[[var_name]]
  weights1 <- filter(data, treated == 1)[[weight_name]]
  data2 <- filter(data, treated == 0)[[var_name]]
  weights2 <- filter(data, treated == 0)[[weight_name]]
  
  # Check if both groups have sufficient data for weighted t-test
  if (length(unique(data1)) > 1 && length(unique(data2)) > 1 && length(data1) > 1 && length(data2) > 1) {
    p_value <- weighted_t_test(data1, weights1, data2, weights2)
  } else {
    p_value <- NA_real_ # Insufficient data or variability
  }
  
  # Combine results
  tibble(Variable = var_name) %>%
    bind_cols(summary_stats) %>%
    mutate(`P Value` = p_value)
}

# Read and process each dataset
population2022 <- read_excel("../data/input/sapemsoasyoatablefinal.xlsx", sheet = "Mid-2022 MSOA 2021", skip = 3)

cosy_hp_details <- fread("../data/input/cosy_-_hp_details_2024_07_03.csv") %>%
  inner_join(hp_installed %>% filter(treated == 1) %>% select(account_id) %>% distinct()) %>%
  select(account_id, postcode) %>%
  distinct() %>%
  group_by(postcode) %>%
  tally() %>%
  filter(!postcode == "")

postcode_msoa <- fread("../data/input/PCD_OA21_LSOA21_MSOA21_LAD_AUG23_UK_LU.csv") %>%
  left_join(cosy_hp_details, by = c("pcds" = "postcode")) %>%
  mutate(n = ifelse(is.na(n), 0, 1)) %>%
  select(msoa21cd, n) %>%
  group_by(msoa21cd) %>%
  summarise(treated = sum(n))

income <- readxl::read_excel("../data/input/saiefy1920finalqaddownload280923.xlsx", sheet = "Total annual income", skip = 4) %>%
  select(`MSOA code`, `Total annual income (£)`) %>%
  distinct() 

net_income <- readxl::read_excel("../data/input/saiefy1920finalqaddownload280923.xlsx", sheet = "Net annual income", skip = 4) %>%
  select(`MSOA code`, `Net annual income (£)`) %>%
  distinct() 

net_housing_income <- readxl::read_excel("../data/input/saiefy1920finalqaddownload280923.xlsx", sheet = "Net income after housing costs", skip = 4) %>%
  select(`MSOA code`, `Net annual income after housing costs (£)`) %>%
  distinct()

# Load and preprocess the property_prices data
property_prices <- read_excel("../data/input/HPSSA Dataset 3 - Mean price paid by MSOA.xls", 
                              sheet = "1a", skip = 4) %>%
  select(`MSOA code`, `Year ending Mar 2023`) %>%
  rename(msoa21cd = `MSOA code`, `Property price (£)` = `Year ending Mar 2023`)

hh_size <- fread("../data/input/custom-filtered-2024-07-03T10_58_30Z.csv") %>%
  group_by(`Middle layer Super Output Areas Code`) %>%
  mutate(sum_obs = sum(Observation), weight = Observation / sum_obs) %>%
  summarise(`Average HH Size` = sum(weight * `Household size (9 categories) Code`))

hh_deprivaton <- fread("../data/input/custom-filtered-2024-07-03T10_43_12Z.csv") %>%
  group_by(`Middle layer Super Output Areas Code`) %>%
  mutate(sum_obs = sum(Observation), `HH Not Deprived in Any Dim. (%)` = 100 * Observation / sum_obs) %>%
  filter(`Household deprivation (6 categories) Code` == 1)

avg_age <- fread("../data/input/custom-filtered-2024-07-03T11_15_15Z.csv") %>%
  group_by(`Middle layer Super Output Areas Code`) %>%
  mutate(sum_obs = sum(Observation), weight = Observation / sum_obs) %>%
  summarise(`Average Age` = sum(weight * `Age (101 categories) Code`))

education <- fread("../data/input/custom-filtered-2024-07-03T11_22_39Z.csv") %>%
  group_by(`Middle layer Super Output Areas Code`) %>%
  mutate(sum_obs = sum(Observation), `Share Level 4 Qualifications (%)` = 100 * Observation / sum_obs) %>%
  filter(`Highest level of qualification (7 categories) Code` == 4)

# Merge all datasets by `MSOA code` or `Middle layer Super Output Areas Code`
merged_data <- postcode_msoa %>%
  inner_join(income, by = c("msoa21cd"="MSOA code")) %>%
  inner_join(property_prices,by = c("msoa21cd"="msoa21cd")) %>%
  inner_join(hh_size, by = c("msoa21cd" = "Middle layer Super Output Areas Code")) %>%
  inner_join(hh_deprivaton, by = c("msoa21cd" = "Middle layer Super Output Areas Code")) %>%
  inner_join(avg_age, by = c("msoa21cd" = "Middle layer Super Output Areas Code")) %>%
  inner_join(education, by = c("msoa21cd" = "Middle layer Super Output Areas Code")) %>%
  inner_join(population2022 %>% select(`MSOA 2021 Code`, Total), by = c("msoa21cd" = "MSOA 2021 Code")) %>%
  mutate(country = substr(msoa21cd, 1, 1),
         treated = as.numeric(treated > 0)) %>%
  filter(!msoa21cd == "", country %in% c("E", "W"))

# List of variables of interest
variables <- c(
  "Total annual income (£)",
  "Property price (£)",
  "Average HH Size",
  "HH Not Deprived in Any Dim. (%)",
  "Average Age",
  "Share Level 4 Qualifications (%)"
)

# Applying the function across all variables
results <- purrr::map_dfr(variables, ~summarize_and_test(merged_data, .x, "Total")) %>%
  as.data.frame()

# Format the counts with thousand separators
results <- results %>%
  mutate(`N 1` = format(`N 1`, big.mark = ",", scientific = FALSE),
         `N 0` = format(`N 0`, big.mark = ",", scientific = FALSE))

# Adjust the format of the table for LaTeX output
formatted_results <- results %>%
  select(Variable, `Weighted_Mean 1`, `SD 1`, `Weighted_Mean 0`, `SD 0`, `P Value`) %>%
  rename(
    `Weighted Mean Treated` = `Weighted_Mean 1`,
    `SD Treated` = `SD 1`,
    `Weighted Mean Others` = `Weighted_Mean 0`,
    `SD Others` = `SD 0`
  ) %>%
  mutate(
    `Weighted Mean Treated` = paste0(format(round(`Weighted Mean Treated`, 2), big.mark = ",", nsmall = 2), " (", format(round(`SD Treated`, 2), big.mark = ",", nsmall = 2), ")"),
    `Weighted Mean Others` = paste0(format(round(`Weighted Mean Others`, 2), big.mark = ",", nsmall = 2), " (", format(round(`SD Others`, 2), big.mark = ",", nsmall = 2), ")"),
    `P Value` = format(round(`P Value`, 2), nsmall = 2)
  ) %>%
  select(Variable, `Weighted Mean Treated`, `Weighted Mean Others`)

# Add the N values to the column names
colnames(formatted_results)[2] <- paste0("MSOAs with HP Installations (N = ", results$`N 1`[1], ")")
colnames(formatted_results)[3] <- paste0("Other MSOAs (N = ", results$`N 0`[1], ")")

# Create the LaTeX table using stargazer
stargazer(formatted_results, type = "latex", summary = FALSE, 
          title = "External Validity by Area for Heat Pump Installations",
          rownames = FALSE,
          digits = 2,
          label = "tab:msoa_stats",
          out = "../tables/balance_table_temp.tex")

# Read the content of the generated LaTeX table
latex_table <- readLines("../tables/balance_table_temp.tex")

# Insert custom headers with multicolumn
header_row <- " & \\multicolumn{2}{c}{Weighted Mean} \\\\"
position <- grep("\\\\begin\\{tabular\\}", latex_table) + 1
latex_table <- append(latex_table, header_row, after = position)

# Replace the first and last instances of \hline \\[-1.8ex] with \hline \hline \\[-1.8ex]
hline_ex_lines <- grep("\\hline" , latex_table)
if (length(hline_ex_lines) >= 2) {
  latex_table[hline_ex_lines[1]] <- gsub("\\hline", "\\hline\\hline", latex_table[hline_ex_lines[1]], fixed = TRUE)
  latex_table[hline_ex_lines[length(hline_ex_lines)]] <- gsub("\\hline", "\\hline\\hline", latex_table[hline_ex_lines[length(hline_ex_lines)]], fixed = TRUE)
}

# Write the modified LaTeX table to a new file
writeLines(latex_table, "../tables/balance_table.tex")
```

## Property value

```{r}

# Read and process each dataset
population2022 <- read_excel("../data/input/sapemsoasyoatablefinal.xlsx", sheet = "Mid-2022 MSOA 2021", skip = 3)

# Load and preprocess the cosy_hp_details data
cosy_hp_details <- fread("../data/input/cosy_-_cosy_details_2024_07_24.csv") %>%
  inner_join(hp_installed %>% select(hashed_mpan) %>% distinct(), by = "hashed_mpan") %>%
  select(hashed_mpan, postcode, property_value) %>%
  distinct() %>%
  group_by(postcode) %>%
  summarise(property_value = mean(property_value, na.rm = TRUE)) %>%
  filter(postcode != "")

# Load and preprocess the postcode_msoa data
postcode_msoa <- fread("../data/input/PCD_OA21_LSOA21_MSOA21_LAD_AUG23_UK_LU.csv") %>%
  left_join(cosy_hp_details, by = c("pcds" = "postcode")) %>%
  mutate(treated = ifelse(is.na(property_value), 0, 1)) %>%
  select(msoa21cd, treated, property_value)

# Load and preprocess the property_prices data
property_prices <- read_excel("../data/input/HPSSA Dataset 3 - Mean price paid by MSOA.xls", 
                              sheet = "1a", skip = 4) %>%
  select(`MSOA code`, `Year ending Mar 2023`) %>%
  rename(msoa21cd = `MSOA code`, year_ending_mar_2023 = `Year ending Mar 2023`)

# Merge all datasets
merged_data <- postcode_msoa %>%
  inner_join(property_prices, by = "msoa21cd") %>%
  mutate(country = substr(msoa21cd, 1, 1)) %>%
  filter(msoa21cd != "", country %in% c("E", "W"))

# Create combined data frame for plotting
treated_1 <- merged_data %>%
  filter(treated == 1) %>%
  select(property_value = year_ending_mar_2023) %>%
  mutate(group = "MSOAs with Heat Pump Installations")

treated_0 <- merged_data %>%
  filter(treated == 0) %>%
  select(property_value = year_ending_mar_2023) %>%
  mutate(group = "MSOAs without Heat Pump Installations")

property_value_data <- merged_data %>%
  filter(!is.na(property_value)) %>%
  select(property_value) %>%
  mutate(group = "Heat Pump Installations")

combined_data <- bind_rows(
  treated_1,
  treated_0,
  property_value_data
)

# Trim outliers by removing values outside the 1st and 99th percentiles
trimmed_combined_data <- combined_data %>%
  group_by(group) %>%
  filter(property_value > quantile(property_value, 0.01) & property_value < quantile(property_value, 0.99))

# Calculate means for each group
means <- trimmed_combined_data %>%
  group_by(group) %>%
  summarise(mean_value = mean(property_value, na.rm = TRUE))

medians <- trimmed_combined_data %>%
  group_by(group) %>%
  summarise(median_value = median(property_value, na.rm = TRUE))



ggplot(trimmed_combined_data, aes(x = property_value, color = group, fill = group)) +
  geom_density(alpha = 0.5, aes(y = ..scaled..)) +
  geom_vline(data = medians, aes(xintercept = median_value, color = group), linetype = "dashed") +
  scale_color_manual(values = c("skyblue", "lightgreen", "orange")) +
  scale_fill_manual(values = c("skyblue", "lightgreen", "orange")) +
  scale_x_continuous(labels = dollar_format(prefix = "£", suffix = "k", scale = 1e-3, big.mark = ",")) +
  labs(
    title = "Density Plot of Property Prices",
    x = "Property Value",
    y = "Density",
    caption = "Dashed lines represent the medians",
    color = NULL,  # Remove the legend title for color
    fill = NULL    # Remove the legend title for fill
  ) +
  theme_classic() +
  theme(legend.position = "bottom")


ggsave("../graphs/average_property_price.png", width = 12, height = 8, dpi = 300)

```

# Analysis: Overall energy consumption


```{r stripdown-code}

# Example for a dataset named `overall_weekly`
start_date <- min(overall_weekly$settlement_week)
did_data <- overall_weekly %>%
  ungroup() %>%
  mutate(
    week = as.numeric(difftime(settlement_week, start_date, units = "weeks")) %/% 1 + 1,
    firstweek = as.numeric(difftime(installed_at, start_date, units = "weeks")) %/% 1 + 1
  ) %>%
  group_by(account_id) %>%
  mutate(id = cur_group_id()) %>%
  ungroup() %>%
  select(id, firstweek, week, total_consumption, elec_consumption, gas_consumption) %>%
  filter(week <= 129, firstweek <= 129) 

# Step 2: Estimate CS models and save results

# Define the output filenames for the main analysis
output_filenames <- c(
  "../data/scratch/est_cs_total_weekly.RDS",
  "../data/scratch/est_cs_elec_weekly.RDS",
  "../data/scratch/est_cs_gas_weekly.RDS"
)

# Define the corresponding variable names
yname_vars <- c("total_consumption", "elec_consumption", "gas_consumption")

# Estimate and save the results for the main analysis (not yet treated control group)
for (i in seq_along(yname_vars)) {
  yname <- yname_vars[i]
  filename <- output_filenames[i]
  
  message("Estimating treatment effect for ", yname, " and saving to ", filename)
  
  est_cs <- att_gt(yname = yname,
                   tname = "week",
                   idname = "id",
                   gname = "firstweek",
                   data = did_data,
                   anticipation = 1,
                   clustervars = "id",
                   control_group = c("notyettreated"),
                   allow_unbalanced_panel = TRUE,
                   base_period = "varying")
  
  saveRDS(est_cs, filename)
  message("Saved: ", filename)
}

# Robustness check with base_period = "universal"
robust_output_filenames <- gsub("\\.RDS$", "_robust_universal.RDS", output_filenames)

for (i in seq_along(yname_vars)) {
  yname <- yname_vars[i]
  filename <- robust_output_filenames[i]
  
  message("Estimating treatment effect for ", yname, " with universal base period and saving to ", filename)
  
  est_cs <- att_gt(yname = yname,
                   tname = "week",
                   idname = "id",
                   gname = "firstweek",
                   data = did_data,
                   anticipation = 1,
                   clustervars = "id",
                   control_group = c("notyettreated"),
                   allow_unbalanced_panel = TRUE,
                   base_period = "universal")
  
  saveRDS(est_cs, filename)
  message("Saved: ", filename)
}

# Step 3: Estimate CS models for the "never treated" control group

never_treated_output_filenames <- gsub("est_cs_", "est_cs_never_treated_", output_filenames)

did_data <- overall_weekly %>%
  ungroup() %>%
  mutate(
    week = as.numeric(difftime(settlement_week, start_date, units = "weeks")) %/% 1 + 1,
    firstweek = as.numeric(difftime(installed_at, start_date, units = "weeks")) %/% 1 + 1
  ) %>%
  group_by(account_id, firstweek, week) %>%
  mutate(id = cur_group_id(),
         firstweek = ifelse(firstweek>129, 0, firstweek)) %>%
  ungroup() %>%
  select(id, firstweek, week, total_consumption, elec_consumption, gas_consumption) %>%
  filter(week <= 129) 

for (i in seq_along(yname_vars)) {
  yname <- yname_vars[i]
  filename <- never_treated_output_filenames[i]
  
  message("Estimating treatment effect for ", yname, " with 'never treated' control group and saving to ", filename)
  
  est_cs <- att_gt(yname = yname,
                   tname = "week",
                   idname = "id",
                   gname = "firstweek",
                   data = did_data,
                   anticipation = 1,
                   clustervars = "id",
                   control_group = c("notyettreated", "nevertreated"),
                   allow_unbalanced_panel = TRUE,
                   base_period = "varying")
  
  saveRDS(est_cs, filename)
  message("Saved: ", filename)
}

# Step 4: Estimate CS models for the gas-only subset

did_data <- overall_weekly %>%
  ungroup() %>%
  mutate(
    week = as.numeric(difftime(settlement_week, start_date, units = "weeks")) %/% 1 + 1,
    firstweek = as.numeric(difftime(installed_at, start_date, units = "weeks")) %/% 1 + 1
  ) %>%
  group_by(account_id, firstweek, week) %>%
  mutate(id = cur_group_id()) %>%
  ungroup() %>%
  select(id, firstweek, week, total_consumption, elec_consumption, gas_consumption) %>%
  filter(week <= 129, firstweek <= 129)  %>% 
  filter(!is.na(gas_consumption))

gas_only_output_filename <- "../data/scratch/est_cs_elec_weekly_gas_only.RDS"

message("Estimating treatment effect for electricity consumption in gas-only sample and saving to ", gas_only_output_filename)

est_cs_gas_only <- att_gt(yname = "elec_consumption",
                          tname = "week",
                          idname = "id",
                          gname = "firstweek",
                          data = did_data,
                          anticipation = 1,
                          clustervars = "id",
                          control_group = c("notyettreated"),
                          allow_unbalanced_panel = TRUE,
                          base_period = "varying")

saveRDS(est_cs_gas_only, gas_only_output_filename)
message("Saved: ", gas_only_output_filename)

```


```{r define-function-cs-twfe-analysis}
# Function to estimate treatment effect and save RDS file
estimate_and_save <- function(yname, filename, data, base_period = "varying", control_group = c("notyettreated")) {
  #if (!file.exists(filename)) {
  message("Estimating treatment effect for ", yname, " with base period ", base_period, " and saving to ", filename)
  est_cs <- att_gt(yname = yname,
                   tname = "week",
                   idname = "id",
                   gname = "firstweek",
                   data = data,
                   anticipation = 1,
                   clustervars = "id",
                   control_group = control_group,
                   allow_unbalanced_panel = TRUE,
                   base_period = base_period)
  saveRDS(est_cs, filename)
  message("Saved: ", filename)
  #} else {
  #message("File already exists: ", filename)
  #}
}

# Function to apply the TWFE models
apply_twfe_models <- function(data, filename_prefix) {
  message("Applying TWFE models and saving to ", paste0(filename_prefix, "_twfe.tex"))
  
  # Apply the TWFE models
  
  m1 <- feols(elec_consumption ~ i(is_hp_installed) | account_id + avg_heating_degree + settlement_week, 
              data = data, cluster = ~ account_id)
  m2 <- feols(gas_consumption ~ i(is_hp_installed) | account_id + avg_heating_degree + settlement_week, 
              data = data, cluster = ~ account_id)
  m3 <- feols(total_consumption ~ i(is_hp_installed) | account_id + avg_heating_degree + settlement_week, 
              data = data, cluster = ~ account_id)  
  # Save the models in a LaTeX table
  etable(m1, m2, m3, 
         headers = c("Electricity", "Gas", "Total"),
         depvar = FALSE, tex = TRUE, 
         title = "HP Installation on Yearly Energy Consumption in kWh",
         fitstat = ~ N + g + pre_avg + t_obs + r2, 
         file = paste0(filename_prefix, "_twfe.tex"), replace = TRUE)
  CleanPreAverage(paste0(filename_prefix, "_twfe.tex"))
  
  # Generate the initial LaTeX table with TWFE models
  etable(m1, m2, m3, 
         m1, m2, m3,
         headers = list(list("TWFE" = 3, "CS" = 3),
                        list(rep(c("Electricity", "Gas", "Total"), times = 2))),
         depvar = FALSE,
         tex=TRUE, title = "HP Installation on Yearly Energy Consumption in kWh",
         fitstat = ~ N + g + pre_avg + t_obs + r2, 
         file = paste0(filename_prefix, "_detailed.tex"), replace = TRUE, 
         label="tab:hp-did-overall-conso-detailed")
  CleanPreAverage(paste0(filename_prefix, "_detailed.tex"))
  
  
  message("TWFE models saved to ", paste0(filename_prefix, "_twfe.tex"), " and ", paste0(filename_prefix, "_detailed.tex"))
  
}

# Function to generate CS models
generate_cs_models <- function(data, prefix, control_group = c("notyettreated")) {
  message("Generating CS models with prefix: ", prefix)
  
  output_filenames <- c(
    paste0("../data/scratch/", prefix, "_total_weekly.RDS"),
    paste0("../data/scratch/", prefix, "_elec_weekly.RDS"),
    paste0("../data/scratch/", prefix, "_gas_weekly.RDS")
  )
  
  yname_vars <- c("total_consumption", "elec_consumption", "gas_consumption")
  
  # Default base_period
  mapply(estimate_and_save, yname_vars, output_filenames, MoreArgs = list(data = data, control_group = control_group))
  
  # Robustness checks with base_period = "universal"
  robust_output_filenames <- gsub("\\.RDS$", "_robust_universal.RDS", output_filenames)
  mapply(estimate_and_save, yname_vars, robust_output_filenames, MoreArgs = list(data = data, base_period = "universal", control_group = control_group))
  
  # Gas-only section
  estimate_and_save("elec_consumption", paste0("../data/scratch/", prefix, "_elec_weekly_gas_only.RDS"), data %>% filter(!is.na(gas_consumption)), control_group = control_group)
  estimate_and_save("elec_consumption", paste0("../data/scratch/", prefix, "_elec_weekly_gas_only_robust_universal.RDS"), data %>% filter(!is.na(gas_consumption)), base_period = "universal", control_group = control_group)
  
  message("CS models generation completed for prefix: ", prefix)
}

# Function to modify LaTeX tables
modify_latex_table <- function(cs_files, tex_file) {
  message("Modifying LaTeX table: ", tex_file)
  
  # Read the CS model estimates
  cs_estimates <- list()
  cs_se <- list()
  cs_n <- list()
  cs_nG <- list()
  cs_nT <- list()
  cs_pre_avg <- list()
  
  for(period in names(cs_files)) {
    message("Processing ", period, " from ", cs_files[[period]])
    est_cs <- readRDS(cs_files[[period]])
    aggte_simple <- aggte(est_cs, type = "simple", na.rm = TRUE, clustervars = "id", bstrap = TRUE, alp = 0.01)
    
    cs_estimates[[period]] <- format_decimal(aggte_simple$overall.att, 1)
    cs_se[[period]] <- format_decimal(aggte_simple$overall.se, 1)
    cs_n[[period]] <- format_number(aggte_simple$DIDparams$n)
    cs_nG[[period]] <- format_number(aggte_simple$DIDparams$nG)
    cs_nT[[period]] <- format_number(aggte_simple$DIDparams$nT)
    cs_pre_avg[[period]] <-  format_decimal(mean(aggte_simple$DIDparams$data[aggte_simple$DIDparams$data$week < aggte_simple$DIDparams$data$firstweek -1, 3]), 2)
  }
  
  # Read the existing LaTeX table
  file_content <- readLines(tex_file)
  
  # Create the replacement values for CS estimates and SEs
  new_cs_estimates <- c(paste0(cs_estimates[["Electricity"]], "$^{***}$"), 
                        paste0(cs_estimates[["Gas"]], "$^{***}$"),
                        paste0(cs_estimates[["Total"]], "$^{***}$"))
  new_cs_se <- c(paste0("(", cs_se[["Electricity"]], ")"), 
                 paste0("(", cs_se[["Gas"]], ")"),
                 paste0("(", cs_se[["Total"]], ")"))
  
  # Locate the necessary lines to update in the LaTeX file
  coeff_line <- grep("Is HP Installed \\$=\\$ 1", file_content)
  se_line <- coeff_line + 1
  obs_line <- grep("Observations", file_content)
  sample_line <- grep("Number of Households", file_content)
  periods_line <- grep("Number of Time Periods", file_content)
  hdd_line <- grep("HDD", file_content)
  mpan_line <- grep("Household", file_content)[1]
  day_line <- grep("Week", file_content)
  r2_line <- grep("R", file_content)
  pre_avg_line <- grep("Yearly Consumption", file_content)
  
  # Function to replace the 6th to 8th columns in a LaTeX table row
  replace_columns <- function(line, new_values) {
    parts <- strsplit(line, "&")[[1]]
    for (i in seq_along(new_values)) {
      parts[4 + i] <- trimws(new_values[[i]])
    }
    return(paste(parts, collapse = " & "))
  }
  
  # Function to clear the 6th to 8th columns in a LaTeX table row
  clear_columns <- function(line) {
    parts <- strsplit(line, "&")[[1]]
    for (i in 5:7) {
      parts[i] <- ""
    }
    return(paste(parts, collapse = " & "))
  }
  
  # Update the LaTeX table content with CS estimates and standard errors
  file_content[sample_line] <- replace_columns(file_content[sample_line], cs_n) %>% paste0(" \\\\")
  file_content[coeff_line] <- replace_columns(file_content[coeff_line], new_cs_estimates) %>% paste0(" \\\\")
  file_content[se_line] <- replace_columns(file_content[se_line], new_cs_se) %>% paste0(" \\\\")
  file_content[pre_avg_line] <- replace_columns(file_content[pre_avg_line], cs_pre_avg) %>% paste0(" \\\\")
  file_content[periods_line] <- replace_columns(file_content[periods_line], cs_nT) %>% paste0(" \\\\")
  file_content[obs_line] <- clear_columns(file_content[obs_line]) %>% paste0(" \\\\")
  file_content[hdd_line] <- clear_columns(file_content[hdd_line]) %>% paste0(" \\\\")
  file_content[mpan_line] <- clear_columns(file_content[mpan_line]) %>% paste0(" \\\\")
  file_content[day_line] <- clear_columns(file_content[day_line]) %>% paste0(" \\\\")
  file_content[r2_line] <- clear_columns(file_content[r2_line]) %>% paste0(" \\\\")
  
  # Modify the clustering information in the LaTeX table
  clustering_line_index <- grep("Clustered \\(Household\\)", file_content)
  if (length(clustering_line_index) > 0) {
    file_content[clustering_line_index] <- "\\multicolumn{10}{l}{\\emph{Clustered (Household) standard-errors in parentheses for TWFE}}\\\\"
  }
  
  # Add CS clustering explanation
  new_row <- "\\multicolumn{10}{l}{\\emph{Clustered cohort (Week of adoption) standard-errors in parentheses for CS}}\\\\"
  file_content <- append(file_content, new_row, after = clustering_line_index)
  
  # Add new row for "Number of cohorts (CS)"
  new_row <- paste0("Number of cohorts (CS) & & & & ", cs_nG[["Electricity"]], " & ", cs_nG[["Gas"]], " & ", cs_nG[["Total"]], " \\\\")
  file_content <- append(file_content, new_row, after = sample_line)
  
  # Write the modified content back to the LaTeX file
  writeLines(file_content, tex_file)
  
  message("Modified LaTeX table saved as ", tex_file)
}

# Function to process a given dataset
process_data <- function(overall_weekly_subset, prefix, control_group = c("notyettreated")) {
  message("Processing dataset with prefix: ", prefix)
  
  # Apply TWFE models
  # apply_twfe_models(overall_weekly_subset, paste0("../tables/", prefix))
  
  # Prepare data for Callaway and Sant'Anna method
  start_date <- min(overall_weekly_subset$settlement_week)
  did_data <- overall_weekly_subset %>%
    ungroup() %>%
    mutate(
      week = as.numeric(difftime(settlement_week, start_date, units = "weeks")) %/% 1 + 1,
      firstweek = as.numeric(difftime(installed_at, start_date, units = "weeks")) %/% 1 + 1
    ) %>%
    group_by(account_id, firstweek, week) %>%
    mutate(id = cur_group_id()) %>%
    ungroup()
  
  # Generate CS models
  generate_cs_models(did_data, prefix, control_group)
  
  message("Processing completed for prefix: ", prefix)
}


```


``` {r apply-functions}
# Process treated-only data
overall_weekly_treated <- overall_weekly %>% filter(treated == 1)
process_data(overall_weekly_treated, "est_cs")

# Process all data including never treated
overall_weekly_all <- overall_weekly
process_data(overall_weekly_all, "est_cs_never_treated", control_group = c("notyettreated", "nevertreated"))

# Modify LaTeX table for treated-only data
modify_latex_table(cs_files = list(
  Electricity = "../data/scratch/est_cs_elec_weekly.RDS",
  Gas = "../data/scratch/est_cs_gas_weekly.RDS",
  Total = "../data/scratch/est_cs_total_weekly.RDS"
), tex_file = "../tables/est_cs_detailed.tex")

# Modify LaTeX table for all data including never treated
modify_latex_table(cs_files = list(
  Electricity = "../data/scratch/est_cs_never_treated_elec_weekly.RDS",
  Gas = "../data/scratch/est_cs_never_treated_gas_weekly.RDS",
  Total = "../data/scratch/est_cs_never_treated_total_weekly.RDS"
), tex_file = "../tables/est_cs_never_treated_detailed.tex")



```


# legacy

```{r gas-data}

# Treat closed accounts as 0 consumption
weather <- fread("../data/input/cosy_-_weather_weekly_2024_06_13.csv") 

cosy_hp_install_gas_consumption <- fread("../data/input/cosy_-_hp_users_gas_2024_06_13.csv") %>%
  group_by(account_id) %>%
  mutate(is_hp_installed = as.numeric(installed_at<=settlement_week),
         treated = max(is_hp_installed),
         min_settlement_week = min(settlement_week)) %>%
  filter( treated==1) %>%
  left_join(weather, by =c("gsp_group_id", "settlement_week" = "week_date"))  %>%
  distinct(account_id, settlement_week, .keep_all = TRUE)


# Create a sequence of dates for each account_id
min_date <- min(cosy_hp_install_gas_consumption$settlement_week)
max_date <- max(cosy_hp_install_gas_consumption$settlement_week)

# Create a sequence of months
all_weeks <- seq(min_date, max_date, by = "week")

# Create a data frame with all combinations of mpan and months
all_combinations <- expand.grid(
  account_id = unique(cosy_hp_install_gas_consumption$account_id),
  settlement_week = all_weeks
)


# Merge with original data
merged_data <- all_combinations %>%
  left_join(cosy_hp_install_gas_consumption %>% select(account_id, gsp_group_id, installed_at, min_settlement_week) %>% distinct()) %>%
  left_join(cosy_hp_install_gas_consumption%>% select(account_id, settlement_week, weekly_consumption) %>% distinct()) %>%
  filter(min_settlement_week < settlement_week) %>%
  mutate(
    account_closed = ifelse(is.na(weekly_consumption), 1, 0),
    is_hp_installed = as.numeric(installed_at<settlement_week),
    weekly_consumption = ifelse(is.na(weekly_consumption), 0, weekly_consumption)) %>%
  left_join(weather, by =c("gsp_group_id", "settlement_week" = "week_date"))

# Merge gas, electricity and total
overall_weekly <- hp_installed %>%
  filter(rate_period=="Overall") %>%
  mutate(settlement_week = floor_date(date, "week")+1,
         is_hp_installed = as.numeric(installed_at<=settlement_week)) %>%
  group_by(account_id, hashed_mpan, tariff_gsp_group_id, settlement_week, treated, installed_at, is_hp_installed) %>%
  summarise(elec_consumption = sum(total_consumption)) %>%
  rename(gsp_group_id = tariff_gsp_group_id) %>%
  left_join(merged_data %>%
              select(account_id, settlement_week, weekly_consumption) %>%
              rename(gas_consumption = weekly_consumption)) %>%
  left_join(weather %>% rename(settlement_week=week_date)) %>%
  mutate(gas_consumption = 52.25*gas_consumption,
         elec_consumption = 52.25*elec_consumption,
         total_consumption = gas_consumption +elec_consumption) %>%
  filter(settlement_week <= max_date, installed_at <= "2024-05-29")  # filter to make sure only treated accounts are included

# TWFE regressions
m1_overall <- feols(total_consumption ~ i(is_hp_installed) | account_id  + avg_heating_degree + settlement_week, 
                    data = overall_weekly %>% filter(treated==1), cluster = ~ account_id)

m2_overall <- feols(elec_consumption ~ i(is_hp_installed) | account_id  + avg_heating_degree + settlement_week, 
                    data = overall_weekly %>% filter(treated==1), cluster = ~ account_id)

m3_overall <- feols(gas_consumption ~ i(is_hp_installed) | account_id  + avg_heating_degree + settlement_week, 
                    data = overall_weekly %>% filter(treated==1), cluster = ~ account_id)

m4_overall <- feols(elec_consumption ~ i(is_hp_installed) | account_id  + avg_heating_degree + settlement_week, 
                    data = overall_weekly %>% filter(treated==1, !is.na(gas_consumption)), cluster = ~ account_id)

# Generate the initial LaTeX table with TWFE models
etable(m1_overall, m2_overall, m3_overall,  
       headers = c("Overall", "Electricity", "Gas"),
       depvar = FALSE,
       tex=TRUE, title = "HP Installation on Yearly Energy Consumption in kWh",
       fitstat = ~ N + g + pre_avg + t_obs + r2, file = "../tables/hp_did_overall_twfe.tex", replace = TRUE, label="tab:hp-did-twfe")

# CS
start_date <- min(overall_weekly$settlement_week)
did_data <- overall_weekly %>%
  filter(treated==1) %>%
  ungroup() %>%
  mutate(
    # Calculate the difference in weeks from the start_date
    week = as.numeric(difftime(settlement_week, start_date, units = "weeks")) %/% 1 + 1,
    # Assuming you have a way to determine 'firstweek', adjust similarly if needed
    firstweek = as.numeric(difftime(installed_at, start_date, units = "weeks")) %/% 1 + 1) %>%
  filter(firstweek <= max(week)) %>%
  group_by(account_id, firstweek, week) %>%
  group_by(account_id) %>%
  mutate(id = cur_group_id()) %>%
  ungroup()
summary(did_data)

# Function to estimate treatment effect and save RDS file
estimate_and_save <- function(yname, filename, data, base_period = "varying") {
  if (!file.exists(filename)) {
    est_cs <- att_gt(yname = yname,
                     tname = "week",
                     idname = "id",
                     gname = "firstweek",
                     data = data,
                     anticipation = 1,
                     clustervars = "id",
                     control_group = c("notyettreated"),
                     allow_unbalanced_panel = TRUE,
                     base_period = base_period)
    
    saveRDS(est_cs, filename)
  }
}

# Data and parameters
output_filenames <- c("../data/scratch/est_cs_overall_weekly.RDS",
                      "../data/scratch/est_cs_elec_weekly.RDS",
                      "../data/scratch/est_cs_gas_weekly.RDS")
yname_vars <- c("total_consumption", "elec_consumption", "gas_consumption")

# Apply function for each combination of yname and filename with default base_period
mapply(estimate_and_save, yname_vars, output_filenames, MoreArgs = list(data = did_data))

# Apply function for each combination of yname and filename with base_period = "universal" (Robustness checks)
robust_output_filenames <- gsub("\\.RDS$", "_robust_universal.RDS", output_filenames)
mapply(estimate_and_save, yname_vars, robust_output_filenames, MoreArgs = list(data = did_data, base_period = "universal"))

# Gas-only section (handled separately due to filter condition) with default base_period
estimate_and_save("elec_consumption",
                  "../data/scratch/est_cs_elec_weekly_gas_only.RDS",
                  did_data %>% filter(!is.na(gas_consumption)))

# Gas-only section with base_period = "universal" (Robustness check)
estimate_and_save("elec_consumption",
                  "../data/scratch/est_cs_elec_weekly_gas_only_robust_universal.RDS",
                  did_data %>% filter(!is.na(gas_consumption)),
                  base_period = "universal")


```

```{r modify-main-table}
# Define the main periods
main_periods <- c("Overall", "Electricity", "Gas")

# Initialize variables to store estimates and standard errors
cs_estimates <- list()
cs_se <- list()
cs_n <- list()
cs_nG <- list()
cs_nT <- list()

# Define paths to the RDS files for CS estimates
cs_files <- list(
  Overall = "../data/scratch/est_cs_total_weekly.RDS",
  Electricity = "../data/scratch/est_cs_elec_weekly.RDS",
  Gas = "../data/scratch/est_cs_gas_weekly.RDS"
)


# Loop through each period to get the Callaway and Sant'Anna estimates
for(period in main_periods) {
  est_cs <- readRDS(cs_files[[period]])
  aggte_simple <- aggte(est_cs, type = "simple", na.rm = TRUE, clustervars="id", bstrap=TRUE, alp = 0.01)
  
  cs_estimates[[period]] <- format_decimal(aggte_simple$overall.att, 1)
  cs_se[[period]] <- format_decimal(aggte_simple$overall.se, 1)
  cs_n[[period]] <- format_number(aggte_simple$DIDparams$n)
  cs_nG[[period]] <- format_number(aggte_simple$DIDparams$nG)
  cs_nT[[period]] <- format_number(aggte_simple$DIDparams$nT)
}


# Generate the initial LaTeX table with TWFE models
etable(m1_overall, m2_overall, m3_overall,  
       headers = c("Overall", "Electricity", "Gas"),
       depvar = FALSE,
       tex=TRUE, title = "HP Installation on Yearly Energy Consumption in kWh",
       fitstat = ~ N + g + pre_avg + t_obs + r2, file = "../tables/hp_did_overall_twfe.tex", replace = TRUE, label="tab:hp-did-twfe")

CleanPreAverage("../tables/hp_did_overall_twfe.tex")

# Generate the initial LaTeX table with TWFE models
etable(m2_overall, m3_overall, m1_overall, 
       m2_overall, m3_overall, m1_overall,
       headers = list(list("TWFE" = 3, "CS" = 3),
                      list(rep(c("Electricity", "Gas", "Overall"), times = 2))),
       depvar = FALSE,
       tex=TRUE, title = "HP Installation on Yearly Energy Consumption in kWh",
       fitstat = ~ N + g + pre_avg + t_obs + r2, file = "../tables/hp_did_overall_detailed.tex", replace = TRUE, label="tab:hp-did-overall-conso-detailed")


CleanPreAverage("../tables/hp_did_overall_detailed.tex")

# Read the generated LaTeX file
file_path <- "../tables/hp_did_overall_detailed.tex"
file_content <- readLines(file_path)

# Function to replace the 6th to 8th columns in a LaTeX table row
replace_columns <- function(line, new_values) {
  parts <- str_split(line, "&")[[1]]
  for (i in seq_along(new_values)) {
    parts[4 + i] <- str_trim(new_values[[i]])
  }
  return(paste(parts, collapse = " & "))
}

# Function to clear the 6th to 8th columns in a LaTeX table row
clear_columns <- function(line) {
  parts <- str_split(line, "&")[[1]]
  for (i in 5:7) {
    parts[i] <- ""
  }
  return(paste(parts, collapse = " & "))
}

# Ensure each replacement maintains the LaTeX table structure
new_estimates <- c(paste0(cs_estimates[["Electricity"]], "$^{***}$"), 
                   paste0(cs_estimates[["Gas"]], "$^{***}$"),
                   paste0(cs_estimates[["Overall"]], "$^{***}$"))
new_se <- c(paste0("(", cs_se[["Electricity"]], ")"), 
            paste0("(", cs_se[["Gas"]], ")"),
            paste0("(", cs_se[["Overall"]], ")"))

# Find the rows that need to be updated
coeff_line <- grep("Is HP Installed \\$=\\$ 1", file_content)
se_line <- coeff_line + 1
obs_line <- grep("Observations", file_content)
sample_line <- grep("Size of the 'effective' sample", file_content)
periods_line <- grep("Number of Time Periods", file_content)
hdd_line <- grep("HDD", file_content)
mpan_line <- grep("Household", file_content)[1]
day_line <- grep("Week", file_content)
r2_line <- grep("R", file_content)

# Replace estimates and standard errors in the LaTeX file
file_content[sample_line] <- replace_columns(file_content[sample_line], cs_n) %>% paste0(" \\\\")
file_content[coeff_line] <- replace_columns(file_content[coeff_line], new_estimates) %>% paste0(" \\\\")
file_content[se_line] <- replace_columns(file_content[se_line], new_se) %>% paste0(" \\\\")
file_content[periods_line] <- replace_columns(file_content[periods_line], cs_nT) %>% paste0(" \\\\")
file_content[obs_line] <- clear_columns(file_content[obs_line]) %>% paste0(" \\\\")
file_content[hdd_line] <- clear_columns(file_content[hdd_line]) %>% paste0(" \\\\")
file_content[mpan_line] <- clear_columns(file_content[mpan_line]) %>% paste0(" \\\\")
file_content[day_line] <- clear_columns(file_content[day_line]) %>% paste0(" \\\\")
file_content[r2_line] <- clear_columns(file_content[r2_line]) %>% paste0(" \\\\")

# Update the line with the clustering information
clustering_line_index <- grep("Clustered \\(Household\\)", file_content)
if (length(clustering_line_index) > 0) {
  file_content[clustering_line_index] <- "\\multicolumn{10}{l}{\\emph{Clustered (Household) standard-errors in parentheses for TWFE}}\\\\"
}

# Modify the label for "Size of the 'effective' sample" to "Number of Households"
file_content[sample_line] <- gsub("Size of the 'effective' sample", "Number of Households", file_content[sample_line])

# Add CS clustering explanation
new_row <- "\\multicolumn{10}{l}{\\emph{Clustered cohort (Week of adoption) standard-errors in parentheses for CS}}\\\\"
file_content <- append(file_content, new_row, after = clustering_line_index)

# Add new row for "Number of cohorts (CS)"
new_row <- paste0("Number of cohorts (CS) & & & & ", cs_nG[["Electricity"]], " & ", cs_nG[["Gas"]], " & ", cs_nG[["Overall"]], " \\\\")
file_content <- append(file_content, new_row, after = sample_line)

# Write the modified content back to the LaTeX file
writeLines(file_content, file_path)

```

```{r combine-graph}

# Define the paths to the RDS files for electricity and gas
rds_files <- list(
  Overall =  "../data/scratch/est_cs_total_weekly.RDS",
  Electricity = "../data/scratch/est_cs_elec_weekly.RDS",
  Gas = "../data/scratch/est_cs_gas_weekly.RDS"
)

# define the start date
start_date <- min(overall_weekly$settlement_week)

# Load the data
elec_data <- aggte(readRDS(rds_files$Electricity), type = "calendar", na.rm = TRUE, clustervars = "id", bstrap = TRUE)
gas_data <- aggte(readRDS(rds_files$Gas), type = "calendar", na.rm = TRUE, clustervars = "id", bstrap = TRUE)

# Create the combined plot
# Extract estimates, standard errors, and event time for electricity
elec_estimates <- elec_data$att.egt/52.25
elec_standard_errors <- elec_data$se.egt/52.25
elec_event_time <- elec_data$egt

# Extract estimates, standard errors, and event time for gas
gas_estimates <- gas_data$att.egt/52.25
gas_standard_errors <- gas_data$se.egt/52.25
gas_event_time <- gas_data$egt

# Calculate the week dates based on the start_date
elec_week_dates <- start_date + weeks(elec_event_time)
gas_week_dates <- start_date + weeks(gas_event_time)

# Align the lengths of the data
max_length <- max(length(elec_estimates), length(gas_estimates))

elec_estimates <- c(elec_estimates, rep(NA, max_length - length(elec_estimates)))
elec_standard_errors <- c(elec_standard_errors, rep(NA, max_length - length(elec_standard_errors)))
elec_week_dates <- c(elec_week_dates, rep(NA, max_length - length(elec_week_dates)))

gas_estimates <- c(gas_estimates, rep(NA, max_length - length(gas_estimates)))
gas_standard_errors <- c(gas_standard_errors, rep(NA, max_length - length(gas_standard_errors)))
gas_week_dates <- c(gas_week_dates, rep(NA, max_length - length(gas_week_dates)))

# Create a data frame for plotting
plot_data <- data.frame(
  week_date = c(elec_week_dates, gas_week_dates),
  estimate = c(elec_estimates, gas_estimates),
  lower_ci = c(elec_estimates - 1.96 * elec_standard_errors, gas_estimates - 1.96 * gas_standard_errors),
  upper_ci = c(elec_estimates + 1.96 * elec_standard_errors, gas_estimates + 1.96 * gas_standard_errors),
  type = rep(c("Electricity", "Gas"), each = max_length)
)

# Define colors for electricity and gas
elec_color <- hp_color
gas_color <- not_hp_color

# Create the ggplot for combined effect
ggplot(plot_data, aes(x = as.Date(week_date), y = estimate, color = type)) +
  geom_point(aes(shape = type), size = 3) +  # Different shapes for Electricity and Gas
  geom_line() +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, alpha = 0.6) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
  scale_x_date(
    labels = scales::date_format("%b %y"),  # Formatting months and years
    date_breaks = "3 month"  # Adjust this based on your data density
  ) +
  scale_colour_manual(name = "Type",
                      labels = c("Electricity", "Gas"),
                      values = c(Electricity = elec_color, Gas = gas_color)) +   
  scale_shape_manual(name = "Type",
                     labels =  c("Electricity", "Gas"),
                     values = c(16, 17)) + 
  labs(
    x = "Week",
    y = "Calendar ATT for Weekly Consumption (kWh)",
    color = "Type",
    shape = "Type"
  ) +
  theme_minimal() +
  theme(legend.position = "bottom") + # Move the legend to the bottom
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate x-axis labels for better readability

# Define the filename
file_name <- "../graphs/hp_calendarplot_combined.png"

# Save the plot
ggsave(file_name, device = "png", width = 8, height = 6, dpi = 300)

```

```{r event-study-style}

# Function to create the ggplot for each period
create_ggplot <- function(elec_data, gas_data) {
  # Extract coefficients, standard errors, and event time for electricity
  elec_coefficients <- elec_data$att.egt/52.25
  elec_standard_errors <- elec_data$se.egt/52.25
  elec_event_time <- elec_data$egt
  
  # Extract coefficients, standard errors, and event time for gas
  gas_coefficients <- gas_data$att.egt/52.25
  gas_standard_errors <- gas_data$se.egt/52.25
  gas_event_time <- gas_data$egt
  
  # Create a data frame for plotting
  plot_data <- data.frame(
    event_time = c(elec_event_time, gas_event_time),
    coefficient = c(elec_coefficients, gas_coefficients),
    lower_ci = c(elec_coefficients - 1.96 * elec_standard_errors, gas_coefficients - 1.96 * gas_standard_errors),
    upper_ci = c(elec_coefficients + 1.96 * elec_standard_errors, gas_coefficients + 1.96 * gas_standard_errors),
    type = rep(c("Electricity", "Gas"), each = length(elec_event_time))
  )
  
  # Create the ggplot
  p <- ggplot(plot_data, aes(x = event_time, y = coefficient, group = type)) +
    geom_line(aes(color = type)) +
    geom_point(aes(color = type, shape = type), size = 3) +
    geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci, color = type), width = 0.2, alpha = 0.6) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
    scale_x_continuous(breaks = seq(floor(min(plot_data$event_time) / 10) * 10, ceiling(max(plot_data$event_time) / 10) * 10, 10)) +
    scale_colour_manual(name = "Type",
                        labels = c("Electricity", "Gas"),
                        values = c(Electricity = elec_color, Gas = gas_color)) +   
    scale_shape_manual(name = "Type",
                       labels =  c("Electricity", "Gas"),
                       values = c(16, 17)) + 
    labs(
      x = "Weeks since adoption",
      y = "Dynamic ATT for Weekly Consumption (kWh)"
    ) +
    theme_minimal() +
    theme(legend.position = "bottom")  # Move the legend to the bottom
  
  
  return(p)
}

# Load the data
elec_data <- aggte(readRDS(rds_files$Electricity), type = "dynamic",
                   na.rm = TRUE, clustervars = "id", bstrap = TRUE, min_e = -90, max_e = 90)
gas_data <- aggte(readRDS(rds_files$Gas), type = "dynamic",
                  na.rm = TRUE, clustervars = "id", bstrap = TRUE, min_e = -90, max_e = 90)

# Create the plot
p <- create_ggplot(elec_data, gas_data)
p

# Define the filename
file_name <- "../graphs/dynamic_hp_plot_combined.png"

# Save the plot
ggsave(file_name, plot = p, device = "png", width = 10, height = 8, dpi = 300)



```


```{r results-table-cs-only} 
# Function to format numbers with thousands separator
format_decimal <- function(x, digits) {
  formatC(x, format = "f", digits = digits, big.mark = ",")
}

format_number <- function(x) {
  formatC(x, format = "d", big.mark = ",")
}

# Function to check if the confidence interval contains zero
confidence_star <- function(coefficient, se, alpha) {
  ci_lower <- coefficient - qnorm(1 - alpha / 2) * se
  ci_upper <- coefficient + qnorm(1 - alpha / 2) * se
  if (ci_lower > 0 | ci_upper < 0) {
    return("*")
  } else {
    return("")
  }
}

# Function to create LaTeX table
create_latex_table <- function(models, headers, title, file, label, pre_treatment_averages) {
  # Extract data from models
  coefficients <- sapply(models, function(model) {
    coef <- model$overall.att
    se <- model$overall.se
    alpha <- model$DIDparams$alp
    paste0(format_decimal(coef, 1), confidence_star(coef, se, alpha))
  })
  standard_errors <- sapply(models, function(model) paste0("(", format_decimal(model$overall.se, 1), ")"))
  observations <- sapply(models, function(model) format_number(model$DIDparams$n))
  nG <- sapply(models, function(model) format_number(model$DIDparams$nG))
  nT <- sapply(models, function(model) format_number(model$DIDparams$nT))
  alpha <- models[[1]]$DIDparams$alp
  conf_level <- (1 - alpha) * 100
  
  # Pre-treatment averages
  pre_treatment_averages <- pre_treatment_averages %>%
    summarise_all(mean)
  pre_treatment_values <- c(
    format_decimal(pre_treatment_averages$elec_consumption, 1),
    format_decimal(pre_treatment_averages$gas_consumption, 1),
    format_decimal(pre_treatment_averages$total_consumption, 1))
  
  # Begin LaTeX table
  latex_table <- "\\begin{table}[htbp]\n"
  latex_table <- paste0(latex_table, "   \\caption{\\label{", label, "} ", title, "}\n")
  latex_table <- paste0(latex_table, "   \\centering\n")
  latex_table <- paste0(latex_table, "   \\begin{tabular}{l", paste(rep("c", length(headers)), collapse = ""), "}\n")
  latex_table <- paste0(latex_table, "      \\tabularnewline \\midrule \\midrule\n")
  latex_table <- paste0(latex_table, "                                     & ", paste(headers, collapse = "     & "), " \\\\   \n")
  latex_table <- paste0(latex_table, "      Model:                         & ", paste(paste0("(", 1:length(headers), ")"), collapse = "              & "), "\\\\  \n")
  latex_table <- paste0(latex_table, "      \\midrule\n")
  latex_table <- paste0(latex_table, "      \\emph{Variable}\\\\\n")
  latex_table <- paste0(latex_table, "      Is HP Installed $=$ 1          & ", paste(coefficients, collapse = " & "), "\\\\   \n")
  latex_table <- paste0(latex_table, "                                     & ", paste(standard_errors, collapse = "         & "), "\\\\   \n")
  latex_table <- paste0(latex_table, "      \\midrule\n")
  latex_table <- paste0(latex_table, "      \\emph{Pre-treatment Average}\\\\\n")
  latex_table <- paste0(latex_table, "      Yearly Consumption              & ", pre_treatment_values[1], " & ", pre_treatment_values[2], " & ", pre_treatment_values[3], "\\\\   \n")
  latex_table <- paste0(latex_table, "      \\midrule\n")
  latex_table <- paste0(latex_table, "      \\emph{Fit statistics}\\\\\n")
  latex_table <- paste0(latex_table, "      Number of Households                   & ", paste(observations, collapse = "           & "), "\\\\  \n")
  latex_table <- paste0(latex_table, "      Number of Cohorts              & ", paste(nG, collapse = "              & "), "\\\\  \n")
  latex_table <- paste0(latex_table, "      Number of Time Periods         & ", paste(nT, collapse = "             & "), "\\\\  \n")
  latex_table <- paste0(latex_table, "      \\midrule \\midrule\n")
  latex_table <- paste0(latex_table, "      \\multicolumn{", length(headers) + 1, "}{l}{Clustered (Household) standard-errors in parentheses}\\\\\n")
  latex_table <- paste0(latex_table, "      \\multicolumn{", length(headers) + 1, "}{l}{Estimation Method: Doubly Robust}\\\\\n")
  latex_table <- paste0(latex_table, "      \\multicolumn{", length(headers) + 1, "}{l}{Control Group: Not Yet Treated, Anticipation Periods: 1}\\\\\n")
  latex_table <- paste0(latex_table, "      \\multicolumn{", length(headers) + 1, "}{l}{Signif. Codes: *** ", conf_level, "\\% confidence band does not cover 0}\\\\\n")
  latex_table <- paste0(latex_table, "   \\end{tabular}\n")
  latex_table <- paste0(latex_table, "\\end{table}\n")
  
  # Write to file
  writeLines(latex_table, file)
}


# Example usage
aggte_simple_overall <- aggte(readRDS(rds_files$Overall), type = "simple", na.rm = TRUE, clustervars = "id", bstrap = TRUE, alp = 0.01)
aggte_simple_elec <- aggte(readRDS(rds_files$Electricity), type = "simple", na.rm = TRUE, clustervars = "id", bstrap = TRUE, alp = 0.01)
aggte_simple_gas <- aggte(readRDS(rds_files$Gas), type = "simple", na.rm = TRUE, clustervars = "id", bstrap = TRUE, alp = 0.01)

# Pre treatment average
pre_treatment_averages <- as_tibble(
  bind_cols(
    aggte_simple_elec$DIDparams$data %>%
      ungroup() %>%
      filter(week < firstweek - 1) %>%
      summarise(elec_consumption = mean(elec_consumption)),
    
    aggte_simple_gas$DIDparams$data %>%
      ungroup() %>%
      filter(week < firstweek - 1) %>%
      summarise(gas_consumption = mean(gas_consumption)),
    
    aggte_simple_overall$DIDparams$data %>%
      ungroup() %>%
      filter(week < firstweek - 1) %>%
      summarise(total_consumption = mean(total_consumption))
  )
)


models <- list(Electricity = aggte_simple_elec, Gas = aggte_simple_gas, Overall = aggte_simple_overall)
headers <- c( "Electricity", "Gas", "Overall")
title <- "HP Installation on Yearly Energy Consumption in kWh"
file <- "../tables/hp_did_overall_cs.tex"
label <- "tab:hp-did-cs"

create_latex_table(models, headers, title, file, label, pre_treatment_averages)





```


# Analysis: Electricity

### CS with never treated group

```{r callsanta-never-treated}


# Treat closed accounts as 0 consumption
weather <- fread("../data/input/cosy_-_weather_weekly_2024_06_13.csv") 

cosy_hp_install_gas_consumption <- fread("../data/input/cosy_-_hp_users_gas_2024_06_13.csv") %>%
  group_by(account_id) %>%
  mutate(is_hp_installed = as.numeric(installed_at<=settlement_week),
         treated = max(is_hp_installed),
         min_settlement_week = min(settlement_week)) %>%
  left_join(weather, by =c("gsp_group_id", "settlement_week" = "week_date"))  %>%
  distinct(account_id, settlement_week, .keep_all = TRUE)


# Create a sequence of dates for each account_id
min_date <- min(cosy_hp_install_gas_consumption$settlement_week)
max_date <- max(cosy_hp_install_gas_consumption$settlement_week)

# Create a sequence of months
all_weeks <- seq(min_date, max_date, by = "week")

# Create a data frame with all combinations of mpan and months
all_combinations <- expand.grid(
  account_id = unique(cosy_hp_install_gas_consumption$account_id),
  settlement_week = all_weeks
)


# Merge with original data
merged_data <- all_combinations %>%
  left_join(cosy_hp_install_gas_consumption %>% select(account_id, gsp_group_id, installed_at, min_settlement_week) %>% distinct()) %>%
  left_join(cosy_hp_install_gas_consumption%>% select(account_id, settlement_week, weekly_consumption) %>% distinct()) %>%
  filter(min_settlement_week < settlement_week) %>%
  mutate(
    account_closed = ifelse(is.na(weekly_consumption), 1, 0),
    is_hp_installed = as.numeric(installed_at<settlement_week),
    weekly_consumption = ifelse(is.na(weekly_consumption), 0, weekly_consumption)) %>%
  left_join(weather, by =c("gsp_group_id", "settlement_week" = "week_date"))


overall_weekly <- hp_installed %>%
  filter(rate_period=="Overall") %>%
  mutate(settlement_week = floor_date(date, "week")+1,
         is_hp_installed = as.numeric(installed_at<=settlement_week)) %>%
  group_by(account_id, hashed_mpan, tariff_gsp_group_id, settlement_week, treated, installed_at, is_hp_installed) %>%
  summarise(elec_consumption = sum(total_consumption)) %>%
  rename(gsp_group_id = tariff_gsp_group_id) %>%
  left_join(merged_data %>%
              select(account_id, settlement_week, weekly_consumption) %>%
              rename(gas_consumption = weekly_consumption)) %>%
  left_join(weather %>% rename(settlement_week=week_date)) %>%
  mutate(gas_consumption = 52.25*gas_consumption,
         elec_consumption = 52.25*elec_consumption,
         total_consumption = gas_consumption +elec_consumption)

# across(deal_created_at:treated)

m1_overall <- feols(total_consumption ~ i(is_hp_installed) | account_id  + avg_heating_degree + settlement_week, 
                    data = overall_weekly, cluster = ~ account_id)

m2_overall <- feols(elec_consumption ~ i(is_hp_installed) | account_id  + avg_heating_degree + settlement_week, 
                    data = overall_weekly, cluster = ~ account_id)

m3_overall <- feols(gas_consumption ~ i(is_hp_installed) | account_id  + avg_heating_degree + settlement_week, 
                    data = overall_weekly, cluster = ~ account_id)

m4_overall <- feols(elec_consumption ~ i(is_hp_installed) | account_id  + avg_heating_degree + settlement_week, 
                    data = overall_weekly %>% filter(!is.na(gas_consumption)), cluster = ~ account_id)

# Generate the initial LaTeX table with TWFE models
etable( m2_overall, m3_overall, m1_overall,
        m2_overall, m3_overall, m1_overall,
        headers = list(list("TWFE" = 3, "CS" = 3),
                       list(rep(c("Electricity", "Gas", "Overall"), times = 2))),
        depvar = FALSE,
        tex=TRUE, title = "HP Installation on Yearly Energy Consumption in kWh",
        fitstat = ~ N + g + pre_avg + t_obs + r2, file = "../tables/hp_did_never_treated.tex", 
        replace = TRUE, label="tab:hp-did-never-treated")
CleanPreAverage("../tables/hp_did_never_treated.tex")

# CS
start_date <- min(overall_weekly$settlement_week)
did_data <- overall_weekly %>%
  ungroup() %>%
  mutate(
    # Calculate the difference in weeks from the start_date
    week = as.numeric(difftime(settlement_week, start_date, units = "weeks")) %/% 1 + 1,
    # Assuming you have a way to determine 'firstweek', adjust similarly if needed
    firstweek = as.numeric(difftime(installed_at, start_date, units = "weeks")) %/% 1 + 1) %>%
  group_by(account_id, firstweek, week) %>%
  group_by(account_id) %>%
  mutate(id = cur_group_id(),
         firstweek = ifelse(firstweek>131, 0, firstweek)) %>%
  ungroup()
summary(did_data)

if (!file.exists("../data/scratch/never_treated_overall_weekly.RDS")) {
  # Estimating the treatment effect using the Callaway and Sant'Anna method
  est_cs <- att_gt(yname = "total_consumption",
                   tname = "week",
                   idname = "id",
                   gname = "firstweek",
                   data = did_data,
                   anticipation = 1,
                   clustervars = "id",
                   control_group=c("notyettreated", "nevertreated"),
                   allow_unbalanced_panel = TRUE)
  
  saveRDS(est_cs, "../data/scratch/never_treated_overall_weekly.RDS")
} 

if (!file.exists("../data/scratch/never_treated_elec_weekly.RDS")) {
  # Estimating the treatment effect using the Callaway and Sant'Anna method
  est_cs <- att_gt(yname = "elec_consumption",
                   tname = "week",
                   idname = "id",
                   gname = "firstweek",
                   data = did_data,
                   anticipation = 1,
                   clustervars = "id",
                   control_group=c("notyettreated", "nevertreated"),
                   allow_unbalanced_panel = TRUE)
  
  saveRDS(est_cs, "../data/scratch/never_treated_elec_weekly.RDS")
} 

if (!file.exists("../data/scratch/never_treated_weekly_gas_only.RDS")) {
  # Estimating the treatment effect using the Callaway and Sant'Anna method
  est_cs <- att_gt(yname = "elec_consumption",
                   tname = "week",
                   idname = "id",
                   gname = "firstweek",
                   data = did_data %>% 
                     filter(!is.na(gas_consumption)),
                   anticipation = 1,
                   clustervars = "id",
                   control_group=c("notyettreated", "nevertreated"),
                   allow_unbalanced_panel = TRUE)
  
  saveRDS(est_cs, "../data/scratch/never_treated_weekly_gas_only.RDS")
} 

if (!file.exists("../data/scratch/never_treated_gas_weekly.RDS")) {
  # Estimating the treatment effect using the Callaway and Sant'Anna method
  est_cs <- att_gt(yname = "gas_consumption",
                   tname = "week",
                   idname = "id",
                   gname = "firstweek",
                   data = did_data,
                   clustervars = "id",
                   anticipation = 1,
                   control_group=c("notyettreated", "nevertreated"),
                   allow_unbalanced_panel = TRUE)
  
  saveRDS(est_cs, "../data/scratch/never_treated_gas_weekly.RDS")
}

# Define the main periods
main_periods <- c( "Electricity", "Gas", "Overall")

# Initialize variables to store estimates and standard errors
cs_estimates <- list()
cs_se <- list()
cs_n <- list()
cs_nG <- list()
cs_nT <- list()

# Define paths to the RDS files for CS estimates
cs_files <- list(
  Electricity = "../data/scratch/never_treated_elec_weekly.RDS",
  Gas = "../data/scratch/never_treated_gas_weekly.RDS",
  Overall = "../data/scratch/never_treated_overall_weekly.RDS"
)

# Loop through each period to get the Callaway and Sant'Anna estimates
for(period in main_periods) {
  est_cs <- readRDS(cs_files[[period]])
  aggte_simple <- aggte(est_cs, type = "simple", na.rm = TRUE, clustervars="id", bstrap=TRUE, alp = 0.01)
  
  cs_estimates[[period]] <- format_decimal(aggte_simple$overall.att, 1)
  cs_se[[period]] <- format_decimal(aggte_simple$overall.se, 1)
  cs_n[[period]] <- format_number(aggte_simple$DIDparams$n)
  cs_nG[[period]] <- format_number(aggte_simple$DIDparams$nG)
  cs_nT[[period]] <- format_number(aggte_simple$DIDparams$nT)
}


# Read the generated LaTeX file
file_path <- "../tables/hp_did_never_treated.tex"
file_content <- readLines(file_path)

# Function to replace the 6th to 8th columns in a LaTeX table row
replace_columns <- function(line, new_values) {
  parts <- str_split(line, "&")[[1]]
  for (i in seq_along(new_values)) {
    parts[4 + i] <- str_trim(new_values[[i]])
  }
  return(paste(parts, collapse = " & "))
}

# Function to clear the 6th to 8th columns in a LaTeX table row
clear_columns <- function(line) {
  parts <- str_split(line, "&")[[1]]
  for (i in 5:7) {
    parts[i] <- ""
  }
  return(paste(parts, collapse = " & "))
}

# Ensure each replacement maintains the LaTeX table structure
new_estimates <- c(paste0(cs_estimates[["Electricity"]], "$^{***}$"), 
                   paste0(cs_estimates[["Gas"]], "$^{***}$"),
                   paste0(cs_estimates[["Overall"]], "$^{***}$"))
new_se <- c(paste0("(", cs_se[["Electricity"]], ")"), 
            paste0("(", cs_se[["Gas"]], ")"),
            paste0("(", cs_se[["Overall"]], ")"))

# Find the rows that need to be updated
coeff_line <- grep("Is HP Installed \\$=\\$ 1", file_content)
se_line <- coeff_line + 1
obs_line <- grep("Observations", file_content)
sample_line <- grep("Size of the 'effective' sample", file_content)
periods_line <- grep("Number of Time Periods", file_content)
hdd_line <- grep("HDD", file_content)
mpan_line <- grep("Household", file_content)[1]
day_line <- grep("Week", file_content)
r2_line <- grep("R", file_content)

# Replace estimates and standard errors in the LaTeX file
file_content[sample_line] <- replace_columns(file_content[sample_line], cs_n) %>% paste0(" \\\\")
file_content[coeff_line] <- replace_columns(file_content[coeff_line], new_estimates) %>% paste0(" \\\\")
file_content[se_line] <- replace_columns(file_content[se_line], new_se) %>% paste0(" \\\\")
file_content[periods_line] <- replace_columns(file_content[periods_line], cs_nT) %>% paste0(" \\\\")
file_content[obs_line] <- clear_columns(file_content[obs_line]) %>% paste0(" \\\\")
file_content[hdd_line] <- clear_columns(file_content[hdd_line]) %>% paste0(" \\\\")
file_content[mpan_line] <- clear_columns(file_content[mpan_line]) %>% paste0(" \\\\")
file_content[day_line] <- clear_columns(file_content[day_line]) %>% paste0(" \\\\")
file_content[r2_line] <- clear_columns(file_content[r2_line]) %>% paste0(" \\\\")

# Update the line with the clustering information
clustering_line_index <- grep("Clustered \\(Household\\)", file_content)
if (length(clustering_line_index) > 0) {
  file_content[clustering_line_index] <- "\\multicolumn{10}{l}{\\emph{Clustered (Household) standard-errors in parentheses for TWFE}}\\\\"
}

# Modify the label for "Size of the 'effective' sample" to "Number of Households"
file_content[sample_line] <- gsub("Size of the 'effective' sample", "Number of Households", file_content[sample_line])

# Add CS clustering explanation
new_row <- "\\multicolumn{10}{l}{\\emph{Clustered cohort (Week of adoption) standard-errors in parentheses for CS}}\\\\"
file_content <- append(file_content, new_row, after = clustering_line_index)

# Add new row for "Number of cohorts (CS)"
new_row <- paste0("Number of cohorts (CS) & & & & ",  cs_nG[["Electricity"]], " & ", cs_nG[["Gas"]]," & ", cs_nG[["Overall"]], " \\\\")
file_content <- append(file_content, new_row, after = sample_line)

# Write the modified content back to the LaTeX file
writeLines(file_content, file_path)
```


## EV detection 

```{r ev-detection}

# ev half hours 
# Read the CSV file
ev_charging <- fread("../data/input/cosy_-_ev_detection_2024_07_04.csv") %>%
  mutate(ev_charging = 1,
         date = as.Date(interval_start),
         interval_start = as.POSIXct(interval_start, format="%Y-%m-%d %H:%M:%S"),
         hour = as.integer(format(interval_start, "%H")),
         rate_period = case_when(
           hour >= 4 & hour < 7 ~ "Morning Cosy",
           hour >= 13 & hour < 16 ~ "Afternoon Cosy",
           hour >= 16 & hour < 19 ~ "Peak Rate",
           TRUE ~ "Other"
         )
  )

# Aggregate at the account id, mpan, date and rate period level
ev_charging_agg <- rbind(ev_charging %>%
                           group_by(account_id,  hashed_mpan, date, rate_period) %>%
                           tally(),
                         ev_charging %>%
                           group_by(account_id,  hashed_mpan, date) %>%
                           tally() %>% 
                           mutate(rate_period="Overall")) %>%
  rename(ev_charging=n)

# EV users details
ev_users <- ev_charging %>%
  group_by(account_id) %>%
  summarise(is_ev_detected= min(as.Date(interval_start)))

# Update hp_installed with the new ev_charging values using case_when
hp_installed <- hp_installed %>%
  left_join(ev_charging_agg) %>%
  mutate(ev_charging = ifelse(is.na(ev_charging), 0, ev_charging),
         ev_charging = case_when(
           rate_period == "Overall" ~ ev_charging / 48,
           rate_period == "Other" ~ ev_charging / 30,
           TRUE ~ ev_charging / 6
         )
  ) %>%
  left_join(ev_users) %>%
  mutate(has_ev = as.numeric(is_ev_detected <= date),
         has_ev = ifelse(is.na(has_ev), 0, has_ev))

# Fit the model
m1 <- feols(total_consumption ~ i(is_hp_installed, ref=0)  |
              daily_avg_heating_degree + account_id + date, 
            data = hp_installed %>% 
              filter(treated==1, rate_period %in% c("Overall")) %>% 
              mutate(total_consumption=365.25*total_consumption) %>%
              ungroup(), 
            cluster = ~account_id)

m1c <- feols(total_consumption  ~ i(is_hp_installed, ref=0) + has_ev + i(is_hp_installed, has_ev, ref=0) |
               daily_avg_heating_degree + account_id + date, 
             data = hp_installed %>% 
               filter(treated==1, rate_period %in% c("Overall")) %>% 
               mutate(total_consumption=365.25*total_consumption) %>%
               ungroup(), 
             cluster = ~account_id)

# Generate the initial LaTeX table
etable(m1, m1c, tex = TRUE, title = "HP Installation on Electricity Consumption Controlling for EV Ownership", 
       dict = c("total_consumption" = "Yearly Consumption in kWh"),
       fitstat = ~ N + g + pre_avg + t_obs + r2, 
       file = "../tables/hp_did_ev.tex", replace = TRUE, label = "tab:hp-did-ev")

CleanPreAverage("../tables/hp_did_ev.tex")

```

```{r charging-time}

# Identify the period with the highest EV charging for each mpan and date
ev_charging_max <- ev_charging %>%
  group_by(account_id, hashed_mpan, date, rate_period) %>%
  summarise(ev_charging = sum(ev_charging, na.rm = TRUE)) %>%
  group_by(account_id, hashed_mpan, date) %>%
  filter(ev_charging == max(ev_charging)) %>%
  mutate(highest_ev_charging = 1) %>%
  ungroup()

ev_charging_max <- ev_charging_max %>%
  left_join(hp_installed %>% select(account_id, hashed_mpan, date, is_hp_installed) %>% distinct())

# Create dummy variables for rate periods
ev_charging_max <- ev_charging_max %>%
  mutate(
    Morning_Cosy = ifelse(rate_period == "Morning Cosy", 1, 0),
    Afternoon_Cosy = ifelse(rate_period == "Afternoon Cosy", 1, 0),
    Peak_Rate = ifelse(rate_period == "Peak Rate", 1, 0),
    Other = ifelse(rate_period == "Other", 1, 0)
  )

# Run the fixed effects models
m_charging1 <- feols(Morning_Cosy ~ i(is_hp_installed) | account_id + date, data = ev_charging_max, cluster = ~ account_id)
m_charging2 <- feols(Afternoon_Cosy ~ i(is_hp_installed) | account_id + date, data = ev_charging_max, cluster = ~ account_id)
m_charging3 <- feols(Peak_Rate ~ i(is_hp_installed) | account_id + date, data = ev_charging_max, cluster = ~ account_id)
m_charging4 <- feols(Other ~ i(is_hp_installed) | account_id + date, data = ev_charging_max, cluster = ~ account_id)


# Generate the LaTeX table with the dependent variable named "Charging EV"
etable(m_charging1, m_charging2, m_charging3, m_charging4, 
       tex = TRUE, 
       title = "HP Installation on Probability of Charging EV by Period", 
       headers = c("Morning Cosy", "Afternoon Cosy", "Peak Rate", "Other"),
       fitstat = ~ N + g + pre_avg + r2, 
       file = "../tables/hp_ev_charging.tex", 
       replace = TRUE, 
       label = "tab:hp-ev-charging",
       dict = c(Morning_Cosy = "Charging EV", 
                Afternoon_Cosy = "Charging EV", 
                Peak_Rate = "Charging EV", 
                Other = "Charging EV"))

# Read the generated LaTeX file
file_path <- "../tables/hp_ev_charging.tex"
CleanPreAverage("../tables/hp_ev_charging.tex")

```


```{r smart-tariff}

Cosy_hp_agreements_data_2024_07_05 <- fread("../data/input/Cosy_-_hp_agreements_data_2024_07_05.csv") %>%
  mutate(time_since_hp = round(as.numeric(difftime(agreement_valid_from, installed_at, units = "week"))/(4.43)),
         time_since_hp = case_when(time_since_hp < -15 ~ -15,
                                   time_since_hp > 15 ~ 15,
                                   TRUE ~ time_since_hp),
         smart_tariff = as.numeric(product_display_name %in% c("Agile Octopus","Intelligent Octopus Go", "Cosy Octopus", "Octopus Go", "Octopus Flux Import", "Intelligent Octopus Flux Import", "Octopus Go Faster")),
         year = year(agreement_valid_from))
table(Cosy_hp_agreements_data_2024_07_05$time_since_hp)

m_tariff <- feols(smart_tariff ~ i(time_since_hp, ref= -1) | account_id + year, data = Cosy_hp_agreements_data_2024_07_05, cluster = ~ account_id)

# Extract coefficients and standard errors
coefs <- coeftable(m_tariff) %>%
  data.frame() %>%
  tibble::rownames_to_column("term") %>%
  separate(term, into = c( "remove1", "time_since_hp"), sep = "::") %>%
  mutate(time_since_hp = as.numeric(time_since_hp), 
         lower_ci = Estimate - 1.96 * `Std..Error`,
         upper_ci = Estimate + 1.96 * `Std..Error`,
         post = (time_since_hp>=0)
  )

# Create the ggplot
ggplot(coefs, aes(x = time_since_hp, y = Estimate, color = post)) +
  geom_point(stat = "identity") +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, alpha=0.5) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(
    x = "Months Since HP Installation",
    y = "Probability of Having a Smart Tariff",
    color = "Is HP Installed"  # Update legend title
  ) +
  scale_color_manual(
    values = c("TRUE" = hp_color, "FALSE" = not_hp_color),  # Set custom colors
    labels = c("No", "Yes")  # Update legend labels
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
  theme_minimal()

ggsave("../graphs/hp_switch_to_smart_tariff.png")
```


## Pre-post

### Before treatment 

```{r barplots}

hp_data <- hp_installed  %>%
  filter(treated ==1, is_hp_installed==0) %>%
  group_by(is_hp_installed, rate_period) %>%
  summarise(consumption_hh = mean(consumption_hh))

```


### Plot by period

```{r mainplot}

# Fit the model
m1 <- feols(consumption_hh ~ i(is_hp_installed) | daily_avg_heating_degree + account_id + date, 
            data = hp_installed %>% filter(treated == 1) %>% ungroup(), 
            cluster = ~account_id, 
            split = ~ rate_period)

# Generate the initial LaTeX table
etable(m1,  tex = TRUE, title = "HP Installation on Electricity Consumption (All Periods)", 
       fitstat = ~ N + g + pre_avg +t_obs + r2, 
       file = "../tables/hp_did_full.tex", replace = TRUE, label = "tab:hp-did-full")


CleanPreAverage("../tables/hp_did_full.tex")
```


## Heterogeneity analysis

### Winter analysis [not updated]

```{r checks-winter}


# Register the pre-treatment average fit statistic
fitstat_register("pre_avg_winter", function(x) {
  
  # Extract the formula
  formula <- x$fml_all$linear
  
  # Extract the outcome variable from the formula
  outcome_variable <- all.vars(formula)[1]
  
  # Extract the call object and evaluate the data argument
  call_object <- x$call
  data_expr <- call_object$data
  data <- eval(data_expr)
  
  # Get the logical vector of observations used in the model
  obs_used <- obs(x)
  
  # Subset the original dataset using this logical vector
  data_used <- data[obs_used, ]
  
  # Ensure the outcome variable is treated as a column name
  outcome_values <- data_used[[outcome_variable]]
  
  # Create pre-avg for non-HP installed group
  pre_avg <- mean(outcome_values[data_used$is_hp_installed == 0 & data_used$is_winter == 1], na.rm = TRUE)
  
  # Format the pre-avg
  formatted_pre_avg <- format_decimal(pre_avg)
  
  return(formatted_pre_avg)
}, "Pre-Treatment Winter")



# Register the pre-treatment average fit statistic
fitstat_register("pre_avg_rest", function(x) {
  
  # Extract the formula
  formula <- x$fml_all$linear
  
  # Extract the outcome variable from the formula
  outcome_variable <- all.vars(formula)[1]
  
  # Extract the call object and evaluate the data argument
  call_object <- x$call
  data_expr <- call_object$data
  data <- eval(data_expr)
  
  # Get the logical vector of observations used in the model
  obs_used <- obs(x)
  
  # Subset the original dataset using this logical vector
  data_used <- data[obs_used, ]
  
  # Ensure the outcome variable is treated as a column name
  outcome_values <- data_used[[outcome_variable]]
  
  # Create pre-avg for non-HP installed group
  pre_avg <- mean(outcome_values[data_used$is_hp_installed == 0 & data_used$is_winter == 0], na.rm = TRUE)
  
  # Format the pre-avg
  formatted_pre_avg <- format_decimal(pre_avg)
  
  return(formatted_pre_avg)
}, "Pre-Treatment Not Winter")



if (!file.exists("../tables/hp_did_seasons.tex")) {
  
  m_winter <- feols(consumption_hh ~ i(is_hp_installed, ref=0)+
                      i(is_hp_installed, is_winter, ref=0) | 
                      daily_avg_heating_degree + account_id + date, 
                    data = hp_installed %>% filter(treated==1, rate_period %in% c("Peak Rate", "Overall")) %>% 
                      mutate(    # Extract the month as a numerical value
                        month_num = month(date),
                        # Mark as winter if the month is within November to April
                        is_winter = (month_num >= 11 | month_num <= 3)), 
                    cluster = ~account_id, 
                    split = ~ rate_period)
  
  
  etable(m_winter, tex=TRUE, title = "HP Impact in kWh per day (Winter vs. the Rest of the Year)",
         fitstat = ~ N + g + pre_avg_winter + pre_avg_rest + t_obs + r2, file = "../tables/hp_did_seasons.tex", 
         replace = TRUE, label="tab:did-seasons")
  
  CleanPreAverage("../tables/hp_did_seasons.tex")
} 
```


### Temperature analysis 

```{r temperature-analysis, eval=TRUE}
rm(m1, m1c, m_solar, ev_charging, ev_users, ev_charging_agg)

# Fit the model
m1 <- feols(consumption_hh ~ i(is_hp_installed) | daily_avg_heating_degree + account_id + date, 
            data = hp_installed %>% filter(treated == 1) %>% ungroup(), 
            cluster = ~account_id, 
            split = ~ rate_period)

# Unique periods 
periods <- unique(hp_installed$rate_period)

# Round degrees Celsius 
hp_installed <- hp_installed %>% mutate(temp_degree = factor(
  case_when(
    daily_avg_air_temperature_celsius < 0 ~ 0,
    daily_avg_air_temperature_celsius < 25 ~ round(daily_avg_air_temperature_celsius),
    TRUE ~ 25
  )
))

# Run the regression model
tempreg <- feols(consumption_hh ~ i(is_hp_installed, temp_degree, ref=0) |
                   account_id + temp_degree  + date,
                 data = hp_installed %>% filter(treated==1),
                 split = ~ rate_period,
                 cluster = ~account_id)
for (i in 1:5) {
  
  # Find model
  val <- tempreg[[i]]$model_info$sample$value
  j <- which(sapply(1:5, function(j) m1[[j]]$model_info$sample$value) == val)
  
  # Extract coefficients and standard errors
  coefs <- coeftable(tempreg[[i]]) %>%
    data.frame() %>%
    tibble::rownames_to_column("term") %>%
    as_tibble() %>%
    separate(term, into = c("is_hp_installed", "remove1", "daily_avg_air_temperature_celsius", "remove2"), sep = "::") %>%
    mutate(daily_avg_air_temperature_celsius = as.numeric(daily_avg_air_temperature_celsius),
           lower_ci = Estimate - 1.96 * `Std..Error`,
           upper_ci = Estimate + 1.96 * `Std..Error`
    ) %>%
    mutate(`/% ATE` = Estimate / m1[[j]]$coefficients * 100,     
           lower_ci_ATE = `/% ATE` - 1.96 * (`Std..Error` / m1[[j]]$coefficients * 100),
           upper_ci_ATE = `/% ATE` + 1.96 * (`Std..Error` / m1[[j]]$coefficients * 100)
    )
  
  # Create the ggplot
  ggplot(coefs, aes(x = daily_avg_air_temperature_celsius, y = Estimate)) +
    geom_point(color = hp_color) +
    geom_line(color = hp_color) +
    geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, alpha = 0.6, color = hp_color) +
    geom_hline(yintercept = m1[[j]]$coefficients, linetype = "dashed", alpha = 0.6, color = hp_color) +  # Add horizontal line at 100% ATE
    scale_y_continuous(
      sec.axis = sec_axis(~ ./m1[[j]]$coefficients, name = "% of ATE", labels = scales::percent_format())
    ) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
    labs(
      x = "Average Temperature in Degrees",
      y = "Estimate (kWh)"
    ) +
    theme_minimal()
  
  # Print the plot
  ggsave(paste0("../graphs/hp_temperature_", tolower(gsub(" ", "_", val)), ".png"),
         width = 16, height = 8, units = "cm")
}

```

## EPC 

```{r epc-analysis, eval=TRUE}
rm(tempreg)

m2a <- feols(consumption_hh ~ i(is_hp_installed, epc_letter, ref=0)  | 
               daily_avg_heating_degree + account_id + date,
             data = hp_installed %>%  
               filter(treated==1) %>%
               mutate(epc_letter = case_when(
                 energy_efficiency >= 91 ~ "A",
                 energy_efficiency >= 81 & energy_efficiency <= 90 ~ "B",
                 energy_efficiency >= 69 & energy_efficiency <= 80 ~ "C",
                 energy_efficiency >= 55 & energy_efficiency <= 68 ~ "D",
                 energy_efficiency >= 39 & energy_efficiency <= 54 ~ "E",
                 energy_efficiency >= 21 & energy_efficiency <= 38 ~ "F",
                 energy_efficiency <= 20 ~ "G",
                 TRUE ~ NA_character_
               )), 
             split = ~ rate_period,
             cluster = ~ account_id)

# Define colors to match the Energy Efficiency Rating chart
rating_colors <- c(
  "A" = "#00CC00",  # Green
  "B" = "#66FF33",  # Light Green
  "C" = "#FFFF00",  # Yellow
  "D" = "#FF9900",  # Orange
  "E" = "#FF6600",  # Dark Orange
  "F" = "#FF0000",  # Red
  "G" = "#990000"   # Dark Red
)

for (i in 1:5) {
  # Find model
  val <- m2a[[i]]$model_info$sample$value
  j <- which(sapply(1:5, function(j) m1[[j]]$model_info$sample$value) == val)
  
  # Extract coefficients and standard errors
  coefs <- coeftable(m2a[[i]]) %>%
    data.frame() %>%
    tibble::rownames_to_column("term") %>%
    separate(term, into = c("is_hp_installed", "remove1", "EPC_letter", "remove2"), sep = "::") %>%
    mutate(lower_ci = Estimate - 1.96 * `Std..Error`,
           upper_ci = Estimate + 1.96 * `Std..Error`
    ) %>%
    mutate(`% ATE` = Estimate / m1[[j]]$coefficients * 100,
           lower_ci_ATE = lower_ci / m1[[j]]$coefficients * 100,
           upper_ci_ATE = upper_ci / m1[[j]]$coefficients * 100)
  
  # Assuming coefs is your data frame and rating_colors is your color vector
  coefs <- coefs %>%
    mutate(EPC_label_position = max(`% ATE`) * 0.1)  # Position for EPC labels on the right
  
  # Create the ggplot
  if (mean(coefs$Estimate) > 0) {
    nudge_x <-  0.01
    
  } else {
    nudge_x <- -0.01
  }
  
  ggplot(coefs, aes(y = factor(EPC_letter, levels = rev(unique(EPC_letter))), x = Estimate, fill = factor(EPC_letter))) +
    geom_bar(stat = "identity", show.legend = FALSE) +
    geom_errorbar(aes(xmin = lower_ci, xmax = upper_ci), width = 0.2, color="grey") +
    geom_vline(xintercept = 0, linetype = "dashed", color = "black") +  # Add vertical line at x = 0
    geom_vline(xintercept = m1[[j]]$coefficients, linetype = "dashed", color = hp_color, alpha = 0.6) +  # Add vertical line at 100% ATE
    scale_fill_manual(values = rating_colors, name = "EPC Letter") +  # Use the defined colors
    geom_hline(yintercept = m1[[j]]$coefficients, linetype = "dashed", alpha = 0.6, color = hp_color) +  # Add horizontal line at 100% ATE
    # Add black "shadow" text for border effect
    geom_text(aes(label = EPC_letter, x = Estimate-nudge_x),  
              size = 4,
              color = "black",  # Black shadow
              fontface = "bold") +
    
    # Add white text on top
    geom_text(aes(label = EPC_letter, x = Estimate-nudge_x),  
              size = 4,
              color = "white",  # White text on top
              fontface = "bold") +
    scale_x_continuous(
      sec.axis = sec_axis(~ ./m1[[j]]$coefficients, name = "% of ATE", labels = scales::percent_format())
    ) +
    labs(
      x = "Estimate (kWh)",
      y = "EPC Letter"
    ) +
    theme_minimal() +
    theme(
      axis.text.y = element_blank(),  # Hide original y-axis text
      axis.ticks.y = element_blank(),  # Hide original y-axis ticks
      axis.text.y.right = element_text(hjust = 0.5),  # Center the text on the right-hand side
      axis.title.y.right = element_text(margin = margin(l = 10)),  # Add margin to right y-axis title
      legend.position = "none"  # Remove legend
    )
  
  # Print the plot
  ggsave(paste0("../graphs/hp_epc_", tolower(gsub(" ", "_", val)), ".png"),
         width = 16, height = 8, units = "cm")
}

rm(m2a)
```

## Heat Sources

```{r hs-analysis, eval=TRUE}

m_sources <- feols(consumption_hh ~ i(is_hp_installed, hp_survey_outcome_existing_heat_source, ref=0)  | 
                     daily_avg_heating_degree + account_id + date,
                   data = hp_installed %>% filter(treated == 1, !hp_survey_outcome_existing_heat_source==""), 
                   split = ~ rate_period,
                   cluster = ~ account_id)

# Count unique occurrences per 'heat_source'
heat_source_counts <- hp_installed %>%
  filter(treated == 1, !hp_survey_outcome_existing_heat_source=="") %>%
  select(hp_survey_outcome_existing_heat_source, account_id) %>%   
  distinct() %>%
  group_by(hp_survey_outcome_existing_heat_source) %>%
  tally() %>%
  mutate(share = round(100*n/sum(n), digits=2))


for (i in 1:5) {
  # Find model
  val <- m_sources[[i]]$model_info$sample$value
  j <- which(sapply(1:5, function(j) m1[[j]]$model_info$sample$value) == val)
  
  # Assuming m_sources[[i]] is a model object that has already been defined
  coefs <- coeftable(m_sources[[i]]) %>%
    data.frame() %>%
    tibble::rownames_to_column("term") %>%
    separate(term, into = c("is_hp_installed", "remove1", "hp_survey_outcome_existing_heat_source", "remove2"), sep = "::") %>%
    mutate(
      heat_source = str_remove_all(hp_survey_outcome_existing_heat_source, "[{}]"),  # Remove curly braces
      heat_source = str_replace_all(heat_source, "_", " "),  # Replace underscores with spaces
      heat_source = str_to_title(heat_source),  # Capitalize the first letter of each word
      # Special handling for specific terms like 'LPG'
      heat_source = stringr::str_replace_all(heat_source, regex("Lpg", ignore_case = TRUE), "LPG"),
      lower_ci = Estimate - 1.96 * `Std..Error`,
      upper_ci = Estimate + 1.96 * `Std..Error`
    ) %>%
    inner_join(heat_source_counts, by = "hp_survey_outcome_existing_heat_source") %>%
    mutate(`% ATE` = Estimate / m1[[j]]$coefficients * 100,
           lower_ci_ATE = lower_ci / m1[[j]]$coefficients * 100,
           upper_ci_ATE = upper_ci / m1[[j]]$coefficients * 100)
  
  # Ensure that 'heat_source' is a factor ordered by 'Estimate' values
  coefs <- coefs %>%
    mutate(heat_source = factor(heat_source, levels = heat_source[order(Estimate)]))
  
  # Create the ggplot
  ggplot(coefs, aes(x = heat_source, y = Estimate, fill = Estimate)) +
    geom_bar(stat = "identity", show.legend = FALSE) +
    geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, color="grey") +
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
    geom_hline(yintercept = m1[[j]]$coefficients, linetype = "dashed", color = hp_color, alpha = 0.6) +  # Add horizontal line at 100% ATE
    scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint = 0) +  # Color scale from blue to red with white at 0  
    scale_x_discrete(labels = function(x) paste(x, "\n(", coefs$share[match(x, coefs$heat_source)], "%)", sep="")) +
    scale_y_continuous(
      sec.axis = sec_axis(~ ./m1[[j]]$coefficients, name = "% of ATE", labels = scales::percent_format())
    ) +
    labs(
      x = "Previous Heat Source",
      y = "Estimate (kWh)"
    ) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),  # Tilt x-axis labels for better readability
      legend.position = "none"  # Remove legend
    )
  
  # Print the plot
  ggsave(paste0("../graphs/hp_hs_", tolower(gsub(" ", "_", val)), ".png"),
         width = 20, height = 12, units = "cm")
}

rm(m_sources)
```

## Income

```{r income}
# Load and preprocess the cosy_hp_details data

cosy_hp_details <- fread("../data/input/cosy_-_hp_details_2024_07_03.csv") %>%
  inner_join(hp_installed %>% filter(treated == 1) %>% select(account_id) %>% distinct()) %>%
  filter(!postcode=="") %>%
  select(account_id, postcode)

postcode_msoa <- fread("../data/input/PCD_OA21_LSOA21_MSOA21_LAD_AUG23_UK_LU.csv") %>%
  left_join(cosy_hp_details, by = c("pcds" = "postcode")) %>%
  select(msoa21cd, pcds) %>%
  distinct(pcds, .keep_all = TRUE)

income <- readxl::read_excel("../data/input/saiefy1920finalqaddownload280923.xlsx", sheet = "Total annual income", skip = 4) %>%
  select(`MSOA code`, `Total annual income (£)`) %>%
  distinct() %>%
  inner_join(postcode_msoa, by=c("MSOA code"="msoa21cd")) %>%
  distinct(pcds, .keep_all = TRUE)


# Create unique breaks for predicted_heatloss_watts
income_dist <- readxl::read_excel("../data/input/saiefy1920finalqaddownload280923.xlsx", sheet = "Total annual income", skip = 4) %>%
  select(`MSOA code`, `Total annual income (£)`) 


breaks <- unique(quantile(income_dist$`Total annual income (£)`/1000, probs = seq(0, 1, by = 0.1)))

# Create pretty labels for the categories
labels <- sapply(1:(length(breaks)-1), function(i) paste0("£", round(breaks[i]), "k-", round(breaks[i+1]), "k"))

hp_installed <- hp_installed %>%
  left_join(cosy_hp_details) %>%
  left_join(income, by=c("postcode"="pcds")) %>%
  mutate(income_category = cut(`Total annual income (£)`/1000, 
                               breaks = breaks, 
                               include.lowest = TRUE,
                               labels = labels))
# income check
m_income <- feols(consumption_hh ~ i(is_hp_installed, income_category, ref =0) 
                  | date +  account_id + daily_avg_heating_degree,
                  data = hp_installed,
                  split = ~ rate_period,
                  cluster = ~account_id)

for (i in 1:5) {
  
  # Find model
  val <- m_income[[i]]$model_info$sample$value
  j <- which(sapply(1:5, function(j) m1[[j]]$model_info$sample$value) == val)
  
  # Extract coefficients and standard errors for total_consumption
  coefs_total <- coeftable(m_income[i]) %>%
    data.frame() %>%
    separate(coefficient, into = c("cosy_contract_active", "remove1", "Income Category", "remove2"), sep = "::") %>%
    mutate(lower_ci = Estimate - 1.96 * `Std..Error`,
           upper_ci = Estimate + 1.96 * `Std..Error`,
           outcome = "Total Consumption") %>%
    mutate(`Income Category` = factor(`Income Category`, levels = labels))
  
  # Define the shades of reds
  red_palette <- c("#FF9999", "#FF8080", "#FF6666", "#FF4D4D", "#FF3333", "#FF1A1A", "#FF0000", "#E60000", "#CC0000", "#B20000")
  
  # Create the ggplot
  ggplot(coefs_total, aes(x = `Income Category`, y = Estimate, fill = `Income Category`)) +
    geom_bar(stat = "identity", show.legend = FALSE) +
    geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, color = "grey") +
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
    geom_hline(yintercept = m1[[j]]$coefficients, linetype = "dashed", color = hp_color, alpha = 0.6) +  # Add horizontal line at ATE
    scale_fill_manual(values = red_palette) +
    labs(
      x = "Income Decile",
      y = "Estimate (kWh)"
    ) +
    scale_y_continuous(
      sec.axis = sec_axis(~ ./(m1[[j]]$coefficients), name = "% of ATE", labels = scales::percent_format())
    ) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),  # Tilt x-axis labels for better readability
      legend.position = "none"  # Remove legend
    )
  
  # Print the plot
  ggsave(paste0("../graphs/hp_income_", val %>% tolower() %>% str_replace(" ", "_"), ".png"),
         width = 16, height = 8, units = "cm")
  
}


# Initialize an empty data frame to store all coefficients
all_coefs <- data.frame()

# Extract coefficients for total consumption
for (i in 1:5) {
  val <- m_income[[i]]$model_info$sample$value
  j <- which(sapply(1:5, function(j) m1[[j]]$model_info$sample$value) == val)
  
  coefs_total <- coeftable(m_income[[i]]) %>%
    data.frame() %>%
    tibble::rownames_to_column("term") %>%
    separate(term, into = c("cosy_contract_active", "remove1", "Income Category", "remove2"), sep = "::") %>%
    mutate(
      lower_ci = Estimate - 1.96 * `Std..Error`,
      upper_ci = Estimate + 1.96 * `Std..Error`,
      `%_ATE` = Estimate / abs(m1[[j]]$coefficients) * 100,
      lower_ci_ATE = lower_ci / abs(m1[[j]]$coefficients) * 100,
      upper_ci_ATE = upper_ci / abs(m1[[j]]$coefficients) * 100,
      outcome = "Total Consumption",
      `Floor_Area` = factor(`Income Category`, levels = labels),
      period = factor(val, levels = c("Morning Cosy",
                                      "Afternoon Cosy",
                                      "Peak Rate",
                                      "Other", 
                                      "Overall")))
  
  all_coefs <- bind_rows(all_coefs, coefs_total)
}


# Define the shades of reds
red_palette <- c("#FF9999", "#FF8080", "#FF6666", "#FF4D4D", "#FF3333", "#FF1A1A", "#FF0000", "#E60000", "#CC0000", "#B20000")


# Create the combined ggplot using facet_wrap
ggplot(all_coefs %>% filter(outcome == "Total Consumption", period != "Overall"), 
       aes(x = `Income Category`, 
           y = Estimate, fill = `Income Category`)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, color = "grey") +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
  scale_fill_manual(values = red_palette) +
  labs(
    x = "Income Category Decile",
    y = "Estimate (kWh)"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Tilt x-axis labels for better readability
    legend.position = "none"  # Remove legend
  ) +
  facet_wrap(~ period)


# Save the combined plot
ggsave("../graphs/hp_income_category_combined.png", device = "png", width = 16, height = 12, units = "cm")
```

## Heatloss 
```{r heatloss-analysis, eval=TRUE}

hp_installed <- hp_installed %>%
  left_join(fread("../data/input/cosy_-_hp_details_2024_07_03.csv") %>%
              distinct(account_id, latest_survey_heat_loss) %>% filter(!is.na(latest_survey_heat_loss)))

# Create unique breaks for predicted_heatloss_watts
breaks <- unique(quantile(hp_installed[!is.na(hp_installed$latest_survey_heat_loss),]$latest_survey_heat_loss/1000, probs = seq(0, 1, by = 0.1)))

# Create pretty labels for the categories
labels <- sapply(1:(length(breaks)-1), function(i) paste0(round(breaks[i], 1), " mW to ", round(breaks[i+1], 1), " mW"))

# Create the categories for latest_survey_heat_loss
hp_installed <- hp_installed %>%
  mutate(latest_survey_heat_loss_category = cut(latest_survey_heat_loss/1000, 
                                                breaks = breaks, 
                                                include.lowest = TRUE,
                                                labels = labels))

m_heatloss <- feols(consumption_hh ~ i(is_hp_installed, latest_survey_heat_loss_category, ref =0) 
                    | account_id + daily_avg_heating_degree + date,
                    data = hp_installed %>% filter(!is.na(latest_survey_heat_loss_category)),
                    split = ~ rate_period,
                    cluster = ~account_id)

for (i in 1:5) {
  
  # Find model
  val <- m_heatloss[[i]]$model_info$sample$value
  j <- which(sapply(1:5, function(j) m1[[j]]$model_info$sample$value) == val)
  
  # Extract coefficients and standard errors for total_consumption
  coefs_total <- coeftable(m_heatloss[i]) %>%
    data.frame() %>%
    separate(coefficient, into = c("cosy_contract_active", "remove1", "Heatloss MW Category", "remove2"), sep = "::") %>%
    mutate(lower_ci = Estimate - 1.96 * `Std..Error`,
           upper_ci = Estimate + 1.96 * `Std..Error`,
           outcome = "Total Consumption") %>%
    mutate(`Heatloss MW Category` = factor(`Heatloss MW Category`, levels = labels))
  
  # Define the shades of reds
  red_palette <- c("#FF9999", "#FF8080", "#FF6666", "#FF4D4D", "#FF3333", "#FF1A1A", "#FF0000", "#E60000", "#CC0000", "#B20000")
  
  # Create the ggplot
  ggplot(coefs_total, aes(x = `Heatloss MW Category`, y = Estimate, fill = `Heatloss MW Category`)) +
    geom_bar(stat = "identity", show.legend = FALSE) +
    geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, color="grey") +
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
    geom_hline(yintercept = m1[[j]]$coefficients, linetype = "dashed", color = hp_color, alpha = 0.6) +  # Add horizontal line at ATE
    scale_fill_manual(values = red_palette) +
    labs(
      x = "Heatloss MW Decile",
      y = "Half Hourly Consumption in kWh"
    ) +
    scale_y_continuous(
      sec.axis = sec_axis(~ ./m1[[j]]$coefficients, name = "% of ATE", labels = scales::percent_format())
    ) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),  # Tilt x-axis labels for better readability
      legend.position = "none"  # Remove legend
    )
  
  # Print the plot
  ggsave(paste0("../graphs/hp_heatloss_", val %>% tolower() %>% str_replace(" ", "_"), ".png"),
         width = 16, height = 8, units = "cm")
  
}

```


### Regions


```{r regions, eval=FALSE}

m_region <- feols(consumption_hh ~ i(is_hp_installed, region, ref =0) | 
                    account_id + daily_avg_heating_degree + date,
                  data = hp_installed %>% filter(!is.na(region), !region=="", rate_period == "Overall"),
                  cluster = ~account_id)


coefs_total <- coeftable(m_region) %>%
  data.frame() %>%
  tibble::rownames_to_column("term") %>%
  separate(term, into = c("is_hp_installed", "remove1", "Region", "remove2"), sep = "::") %>%
  mutate(
    average = m1[[4]]$coefficients,
    lower_ci = Estimate - 1.96 * `Std..Error`,
    upper_ci = Estimate + 1.96 * `Std..Error`,
    `%_ATE` = Estimate / abs(m1[[4]]$coefficients) * 100,
    lower_ci_ATE = lower_ci / abs(m1[[4]]$coefficients) * 100,
    upper_ci_ATE = upper_ci / abs(m1[[4]]$coefficients) * 100)

# Select a color palette from RColorBrewer
region_colors <- brewer.pal(n = length(unique(coefs_total$Region)), name = "Set3")

# Order regions by their estimate size for period == "Morning Cosy"
hp_order <- coefs_total %>%
  arrange(desc(Estimate)) %>%
  pull(Region)

# Reorder the Region factor based on the estimate size in "Morning Cosy"
coefs_total <- coefs_total %>%
  mutate(Region = factor(Region, levels = hp_order))

# Create the ggplot
ggplot(coefs_total, aes(x = Region, y = Estimate, fill = Region)) +
  geom_bar(stat = "identity") +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, color = "grey") +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
  geom_hline(aes(yintercept = m1[[4]]$coefficients), linetype = "dashed", color = hp_color, alpha = 0.6) +  # Add vertical line at average ATE
  scale_fill_manual(values = region_colors) +  # Apply random colors to regions
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Tilt x-axis labels for better readability
    legend.position = "none"  # Remove legend
  ) 

# Save the plot
ggsave("../graphs/hp_region_combined.png", device = "png", width = 16, height = 12, units = "cm")







```
### Floor area


```{r floor-area, eval=FALSE}

# Create unique breaks for total_floor_area
breaks <- unique(quantile(hp_installed[!is.na(hp_installed$total_floor_area),]$total_floor_area, 
                          probs = seq(0, 1, by = 0.1)))

# Create pretty labels for the categories
labels <- sapply(1:(length(breaks)-1), function(i) paste0(round(breaks[i], 0), " to ", round(breaks[i+1], 0), "m sq."))

# Create the categories for total_floor_area
hp_installed <- hp_installed %>%
  mutate(total_floor_area_category = cut(total_floor_area, 
                                         breaks = breaks, 
                                         include.lowest = TRUE,
                                         labels = labels))


m_floor <- feols(consumption_hh ~ i(is_hp_installed, total_floor_area_category, ref =0) 
                 | date +  account_id + daily_avg_heating_degree,
                 data = hp_installed %>% filter(!is.na(total_floor_area_category), treated==1),
                 split = ~ rate_period,
                 cluster = ~account_id)

for (i in 1:5) {
  
  # Find model
  val <- m_floor[[i]]$model_info$sample$value
  j <- which(sapply(1:5, function(j) m1[[j]]$model_info$sample$value) == val)
  
  # Extract coefficients and standard errors for total_consumption
  coefs_total <- coeftable(m_floor[i]) %>%
    data.frame() %>%
    separate(coefficient, into = c("cosy_contract_active", "remove1", "Floor_Area", "remove2"), sep = "::") %>%
    mutate(lower_ci = Estimate - 1.96 * `Std..Error`,
           upper_ci = Estimate + 1.96 * `Std..Error`,
           outcome = "Total Consumption") %>%
    mutate(`Floor_Area` = factor(`Floor_Area`, levels = labels),
           `% ATE` = Estimate / m1[[j]]$coefficients * 100,
           lower_ci_ATE = lower_ci / m1[[j]]$coefficients * 100,
           upper_ci_ATE = upper_ci / m1[[j]]$coefficients * 100)
  
  # Define the shades of reds
  red_palette <- c("#FF9999", "#FF8080", "#FF6666", "#FF4D4D", "#FF3333", "#FF1A1A", "#FF0000", "#E60000", "#CC0000", "#B20000")
  
  # Create the ggplot
  ggplot(coefs_total, aes(x = `Floor_Area`, y = Estimate, fill = `Floor_Area`)) +
    geom_bar(stat = "identity", show.legend = FALSE) +
    geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, color = "grey") +
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
    geom_hline(yintercept = m1[[j]]$coefficients, linetype = "dashed", color = hp_color, alpha = 0.6) +  # Add horizontal line at 100% ATE
    scale_fill_manual(values = red_palette) +
    scale_y_continuous(
      sec.axis = sec_axis(~ ./(m1[[j]]$coefficients), name = "% of ATE", labels = scales::percent_format())
    ) +
    labs(
      x = "Floor Area Decile",
      y = "Estimate (kWh)"
    ) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),  # Tilt x-axis labels for better readability
      legend.position = "none"  # Remove legend
    )
  
  # Print the plot
  ggsave(paste0("../graphs/hp_floor_area_", tolower(gsub(" ", "_", val)), ".png"),
         width = 16, height = 8, units = "cm")
}



m_floor_share <- feols(share_consumption ~ i(is_hp_installed, total_floor_area_category, ref =0)
                       | date +  account_id + daily_avg_heating_degree,
                       data = hp_installed %>% 
                         filter(!is.na(total_floor_area_category), !rate_period=="Overall", treated==1) %>%
                         group_by(account_id, date) %>%
                         mutate(share_consumption = total_consumption/sum(total_consumption)),
                       split = ~ rate_period,
                       cluster = ~account_id)

m1_share <- feols(share_consumption ~ i(is_hp_installed, ref =0)
                  | date +  account_id + daily_avg_heating_degree,
                  data = hp_installed %>% 
                    filter(!rate_period=="Overall", treated==1) %>%
                    group_by(account_id, date) %>%
                    mutate(share_consumption = total_consumption/sum(total_consumption)),
                  split = ~ rate_period,
                  cluster = ~account_id)

for (i in 1:4) {
  
  # Find model
  val <- m_floor_share[[i]]$model_info$sample$value
  j <- which(sapply(1:4, function(j) m1_share[[j]]$model_info$sample$value) == val)
  
  # Extract coefficients and standard errors for total_consumption
  coefs_total <- coeftable(m_floor_share[i]) %>%
    data.frame() %>%
    separate(coefficient, into = c("cosy_contract_active", "remove1", "Floor_Area", "remove2"), sep = "::") %>%
    mutate(lower_ci = Estimate - 1.96 * `Std..Error`,
           upper_ci = Estimate + 1.96 * `Std..Error`,
           outcome = "Total Consumption") %>%
    mutate(`Floor_Area` = factor(`Floor_Area`, levels = labels),
           `% ATE` = Estimate / m1_share[[j]]$coefficients * 100,
           lower_ci_ATE = lower_ci / m1_share[[j]]$coefficients * 100,
           upper_ci_ATE = upper_ci / m1_share[[j]]$coefficients * 100)
  
  # Define the shades of reds
  red_palette <- c("#FF9999", "#FF8080", "#FF6666", "#FF4D4D", "#FF3333", "#FF1A1A", "#FF0000", "#E60000", "#CC0000", "#B20000")
  
  # Create the ggplot
  ggplot(coefs_total, aes(x = `Floor_Area`, y = Estimate, fill = `Floor_Area`)) +
    geom_bar(stat = "identity", show.legend = FALSE) +
    geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, color = "grey") +
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
    geom_hline(yintercept = m1_share[[j]]$coefficients, linetype = "dashed", color = hp_color, alpha = 0.6) +  # Add horizontal line at 100% ATE
    scale_fill_manual(values = red_palette) +
    labs(
      x = "Floor Area Decile",
      y = "Share of Daily Consumption (%)"
    ) +
    scale_y_continuous(
      breaks = seq(0, max(coefs_total$`% ATE`, na.rm = TRUE)),  # Set y-axis to % ATE with breaks at 100% intervals
      labels = function(x) paste0(x, "%")
    ) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),  # Tilt x-axis labels for better readability
      legend.position = "none"  # Remove legend
    )
  
  # Print the plot
  ggsave(paste0("../graphs/hp_share_floor_area_", tolower(gsub(" ", "_", val)), ".png"),
         width = 16, height = 8, units = "cm")
}

```

### Solar PV 

```{r solar}

# Register the pre-treatment average fit statistic
fitstat_register("pre_avg_solar", function(x) {
  
  # Extract the formula
  formula <- x$fml_all$linear
  
  # Extract the outcome variable from the formula
  outcome_variable <- all.vars(formula)[1]
  
  # Extract the call object and evaluate the data argument
  call_object <- x$call
  data_expr <- call_object$data
  data <- eval(data_expr)
  
  # Get the logical vector of observations used in the model
  obs_used <- obs(x)
  
  # Subset the original dataset using this logical vector
  data_used <- data[obs_used, ]
  
  # Ensure the outcome variable is treated as a column name
  outcome_values <- data_used[[outcome_variable]]
  
  # Create pre-avg for non-HP installed group
  pre_avg <- mean(outcome_values[data_used$is_hp_installed == 0 & data_used$hp_survey_is_solar_present == TRUE], na.rm = TRUE)
  
  # Format the pre-avg
  formatted_pre_avg <- format_decimal(pre_avg)
  
  return(formatted_pre_avg)
}, "Yearly Consumption Has Solar PV")



# Register the pre-treatment average fit statistic
fitstat_register("pre_avg_rest", function(x) {
  
  # Extract the formula
  formula <- x$fml_all$linear
  
  # Extract the outcome variable from the formula
  outcome_variable <- all.vars(formula)[1]
  
  # Extract the call object and evaluate the data argument
  call_object <- x$call
  data_expr <- call_object$data
  data <- eval(data_expr)
  
  # Get the logical vector of observations used in the model
  obs_used <- obs(x)
  
  # Subset the original dataset using this logical vector
  data_used <- data[obs_used, ]
  
  # Ensure the outcome variable is treated as a column name
  outcome_values <- data_used[[outcome_variable]]
  
  # Create pre-avg for non-HP installed group
  pre_avg <- mean(outcome_values[data_used$is_hp_installed == 0 & data_used$hp_survey_is_solar_present == FALSE], na.rm = TRUE)
  
  # Format the pre-avg
  formatted_pre_avg <- format_decimal(pre_avg)
  
  return(formatted_pre_avg)
}, "Yearly Consumption No Solar PV")


# Fit the model
m_solar <- feols(total_consumption ~ i(is_hp_installed) + i(is_hp_installed, hp_survey_is_solar_present, ref = 0) | 
                   daily_avg_heating_degree + account_id + date, 
                 data = hp_installed %>% filter(treated == 1) %>% ungroup()  %>% 
                   mutate(total_consumption=365.25*total_consumption,   rate_period = factor(rate_period, levels = c("Morning Cosy",                                                                                                             "Afternoon Cosy","Peak Rate","Other", "Overall"))), 
                 cluster = ~account_id, 
                 split = ~ rate_period)

# Generate the initial LaTeX table
etable(m_solar,  tex = TRUE, title = "HP Installation and Solar PV on Electricity Consumption ", 
       fitstat = ~ N + g + pre_avg_rest + pre_avg_solar +t_obs + r2, 
       dict = c("total_consumption" = "Yearly Consumption in kWh"),
       file = "../tables/hp_did_solar.tex", replace = TRUE, label = "tab:hp-did-solar")

# Read the generated LaTeX file
file_content <- readLines("../tables/hp_did_solar.tex")

# Find the lines with the pre-treatment average and remove them
pre_avg_line_index <- grep("Yearly Consumption No Solar PV", file_content)
pre_avg_line_index2 <- grep("Yearly Consumption Has Solar PV", file_content)
pre_avg_lines <- file_content[pre_avg_line_index:(pre_avg_line_index2)]
file_content <- file_content[-c(pre_avg_line_index, pre_avg_line_index2)]

# Find the position just after the coefficients
coeff_end_index <- grep("Is HP Installed", file_content)[2] + 2
if (length(coeff_end_index) > 1) {
  coeff_end_index <- coeff_end_index[-1]
}

# Insert the pre-treatment average row after the coefficients
file_content <- append(file_content, pre_avg_lines, after = coeff_end_index)
file_content <- append(file_content, "\\emph{Pre-Treatment Average}\\\\", after = coeff_end_index)

# Add a \midrule after the pre-treatment average
file_content <- append(file_content, "\\midrule", after = coeff_end_index + 3)

# Modify the label for "Size of the 'effective' sample" to "Number of Households"
sample_line <- grep("Size of the 'effective' sample", file_content)
file_content[sample_line] <- gsub("Size of the 'effective' sample", "Number of Households", file_content[sample_line])

# Write the modified content back to the LaTeX file
writeLines(file_content, "../tables/hp_did_solar.tex")  

```

## DID checks

### Panel structure 

```{r panelview, eval=FALSE}

library(panelView)

plot_panel <- panelview(consumption_hh ~ is_hp_installed + daily_avg_heating_degree, 
                        data = hp_installed %>% filter(rate_period=="Overall") %>% select(consumption_hh, account_id, date, is_hp_installed, daily_avg_heating_degree) %>% distinct(), index = c("account_id","date"), 
                        xlab = "Time", ylab = "MPAN", by.timing = TRUE, pre.post = TRUE, gridOff = TRUE, axis.lab.gap = c(100),
                        main = "Smart Meter Data Availability",
                        background = NULL,
                        legend.labs = c("Never Treated (Installation in Future)", "Before HP Installation", "After HP Installation", "No smart meter data"), collapse.history = "TRUE")
ggsave("../graphs/hp_data_availability.png")

```

### CS parallele trends checks

```{r honestdid, eval=FALSE}
# # install from github
# remotes::install_github("asheshrambachan/HonestDiD")
library(HonestDiD)
honest_did <- function(es,
                       e          = 0,
                       type       = c("smoothness", "relative_magnitude"),
                       gridPoints = 100,
                       ...) {
  
  type <- match.arg(type)
  
  # Make sure that user is passing in an event study
  if (es$type != "dynamic") {
    stop("need to pass in an event study")
  }
  
  # Check if used universal base period and warn otherwise
  if (es$DIDparams$base_period != "universal") {
    stop("Use a universal base period for honest_did")
  }
  
  # Recover influence function for event study estimates
  es_inf_func <- es$inf.function$dynamic.inf.func.e
  
  # Recover variance-covariance matrix
  n <- nrow(es_inf_func)
  V <- t(es_inf_func) %*% es_inf_func / n / n
  
  # Check time vector is consecutive with referencePeriod = -1
  referencePeriod <- -1
  consecutivePre  <- !all(diff(es$egt[es$egt <= referencePeriod]) == 1)
  consecutivePost <- !all(diff(es$egt[es$egt >= referencePeriod]) == 1)
  if ( consecutivePre | consecutivePost ) {
    msg <- "honest_did expects a time vector with consecutive time periods;"
    msg <- paste(msg, "please re-code your event study and interpret the results accordingly.", sep="\n")
    stop(msg)
  }
  
  # Remove the coefficient normalized to zero
  hasReference <- any(es$egt == referencePeriod)
  if ( hasReference ) {
    referencePeriodIndex <- which(es$egt == referencePeriod)
    V    <- V[-referencePeriodIndex,-referencePeriodIndex]
    beta <- es$att.egt[-referencePeriodIndex]
  } else {
    beta <- es$att.egt
  }
  
  nperiods <- nrow(V)
  npre     <- sum(1*(es$egt < referencePeriod))
  npost    <- nperiods - npre
  if ( !hasReference & (min(c(npost, npre)) <= 0) ) {
    if ( npost <= 0 ) {
      msg <- "not enough post-periods"
    } else {
      msg <- "not enough pre-periods"
    }
    msg <- paste0(msg, " (check your time vector; note honest_did takes -1 as the reference period)")
    stop(msg)
  }
  
  baseVec1 <- basisVector(index=(e+1),size=npost)
  orig_ci  <- constructOriginalCS(betahat        = beta,
                                  sigma          = V,
                                  numPrePeriods  = npre,
                                  numPostPeriods = npost,
                                  l_vec          = baseVec1)
  
  if (type=="relative_magnitude") {
    robust_ci <- createSensitivityResults_relativeMagnitudes(betahat        = beta,
                                                             sigma          = V,
                                                             numPrePeriods  = npre,
                                                             numPostPeriods = npost,
                                                             l_vec          = baseVec1,
                                                             gridPoints     = gridPoints,
                                                             ...)
    
  } else if (type == "smoothness") {
    robust_ci <- createSensitivityResults(betahat        = beta,
                                          sigma          = V,
                                          numPrePeriods  = npre,
                                          numPostPeriods = npost,
                                          l_vec          = baseVec1,
                                          ...)
  }
  
  return(list(robust_ci=robust_ci, orig_ci=orig_ci, type=type))
}

# start date
start_date <- hp_installed %>% select(date) %>% distinct() %>% summarise(date = min(date))
start_date <- start_date$date

# Adjust your existing code to calculate 'week' and 'firstweek' as the number of weeks from the start_date
did_data <- hp_installed %>%
  filter(rate_period == "Overall") %>%
  mutate(
    # Calculate the difference in weeks from the start_date
    week = as.numeric(difftime(date, start_date, units = "weeks")) %/% 1 + 1,
    # Assuming you have a way to determine 'firstweek', adjust similarly if needed
    firstweek = as.numeric(difftime(installed_at, start_date, units = "weeks")) %/% 1 + 1) %>%
  group_by(account_id, firstweek, week) %>%
  summarise(consumption = mean(consumption_hh)) %>%
  mutate(
    firstweek = as.numeric(firstweek),
    week = as.numeric(week),
    firstweek = ifelse(firstweek>=117, 0, firstweek) # not treated needs to be 0 
  ) %>%
  group_by(account_id) %>%
  mutate(id = cur_group_id())  # all variables need to be numeric


did_data_subset <- did_data %>% filter(firstweek !=81) # >= 100 worked, firstweek >= 57 & firstweek < 81

est_cs <- att_gt(yname = "consumption",
                 tname = "week",
                 idname = "id",
                 gname = "firstweek",
                 data = did_data_subset,
                 clustervars = "id",
                 control_group=c("notyettreated", "nevertreated"),
                 base_period = "universal",
                 allow_unbalanced_panel = TRUE,
                 print_details = FALSE)

es <- did::aggte(est_cs, type = "dynamic",
                 min_e = -5, max_e = 5, na.rm = TRUE)

#Run sensitivity analysis for relative magnitudes
sensitivity_results <- honest_did(es, e=0,type="relative_magnitude",Mbarvec=seq(from = 0.5, to = 2, by = 0.5))

HonestDiD::createSensitivityPlot_relativeMagnitudes(sensitivity_results$robust_ci,
                                                    sensitivity_results$orig_ci)

ggsave("../graphs/hp_sensitivity_results.png")

```

## Event study

```{r event-study-plot}
# create df
event_study_df <- hp_installed %>%
  mutate(weeks_since_hp = as.numeric(difftime(date, installed_at, units = "weeks")) %/% 1 + 1,
         weeks_since_hp = case_when(
           weeks_since_hp < -52 ~ -52,
           weeks_since_hp > 52 ~ 52,
           TRUE ~ weeks_since_hp)) %>%
  select(account_id, weeks_since_hp, consumption_hh, daily_avg_heating_degree, date, rate_period)

rm(hp_installed)
gc()

m_event_study <- feols(consumption_hh ~ i(weeks_since_hp, ref=-1) | account_id + daily_avg_heating_degree + date, 
                       data = event_study_df %>% filter(rate_period=="Overall") %>% 
                         mutate(),
                       cluster = ~ account_id)

etable(m_event_study)

# plot the coefficients
# Extract coefficients and standard errors
coefs <- coeftable(m_event_study)%>%
  data.frame() %>%
  tibble::rownames_to_column("term")%>%
  as_tibble() %>%
  separate(term, into = c("var",  "weeks_since_hp"), sep = "::") %>%
  mutate(lower_ci = Estimate - 1.96 * `Std..Error`,
         upper_ci = Estimate + 1.96 * `Std..Error`,
         outcome = "Half Hourly Consumption") %>%
  mutate(weeks_since_hp = as.numeric(weeks_since_hp),
         post = (weeks_since_hp >-1))

# Create the plot
ggplot(coefs, aes(x = weeks_since_hp, y = Estimate, color = post)) +
  geom_point(stat = "identity", show.legend = TRUE) +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  labs(
    x = "Weeks Since HP Installation",
    y = "Half Hourly Consumption in kWh",
    color = "Is HP Installed"  # Update legend title
  ) +
  scale_color_manual(
    values = c("TRUE" = hp_color, "FALSE" = not_hp_color),  # Set custom colors
    labels = c("No", "Yes")  # Update legend labels
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Tilt x-axis labels for better readability
    legend.position = "right"  # Show legend
  )


# Print the plot
ggsave(paste0("../graphs/hp_event_study_overall.png"),
       width = 16, height = 8, units = "cm")

rm(m_event_study, hp_installed)


m_event_study <- feols(consumption_hh ~ i(weeks_since_hp, ref=-1) | account_id + daily_avg_heating_degree + date, 
                       data = event_study_df %>% filter(rate_period=="Peak Rate") %>% 
                         mutate(),
                       cluster = ~ account_id)

etable(m_event_study)

# plot the coefficients
# Extract coefficients and standard errors
coefs <- coeftable(m_event_study)%>%
  data.frame() %>%
  tibble::rownames_to_column("term")%>%
  as_tibble() %>%
  separate(term, into = c("var",  "weeks_since_hp"), sep = "::") %>%
  mutate(lower_ci = Estimate - 1.96 * `Std..Error`,
         upper_ci = Estimate + 1.96 * `Std..Error`,
         outcome = "Half Hourly Consumption") %>%
  mutate(weeks_since_hp = as.numeric(weeks_since_hp),
         post = (weeks_since_hp >-1))

# Create the plot
ggplot(coefs, aes(x = weeks_since_hp, y = Estimate, color = post)) +
  geom_point(stat = "identity", show.legend = TRUE) +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  labs(
    x = "Weeks Since HP Installation",
    y = "Half Hourly Consumption in kWh",
    color = "Is HP Installed"  # Update legend title
  ) +
  scale_color_manual(
    values = c("TRUE" = hp_color, "FALSE" = not_hp_color),  # Set custom colors
    labels = c("No", "Yes")  # Update legend labels
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Tilt x-axis labels for better readability
    legend.position = "right"  # Show legend
  )


# Print the plot
ggsave(paste0("../graphs/hp_event_study_peak_rate.png"),
       width = 16, height = 8, units = "cm")


```

# Gas analysis

## CS 

```{r callaway-gas}
cosy_hp_install_gas_consumption <- fread("../data/input/cosy_-_hp_users_gas_2024_06_13.csv") %>%
  left_join(hp_installed %>% distinct(account_id, treated, hp_survey_outcome_existing_heat_source)) %>%
  filter(hp_survey_outcome_existing_heat_source=='{GAS_BOILER}', treated==1) %>%
  distinct(account_id, settlement_week, .keep_all = TRUE)

start_date <- min(cosy_hp_install_gas_consumption$settlement_week) 

did_data <- cosy_hp_install_gas_consumption %>%
  ungroup() %>%
  mutate(
    # Calculate the difference in weeks from the start_date
    week = as.numeric(difftime(settlement_week, start_date, units = "weeks")) %/% 1 + 1,
    # Assuming you have a way to determine 'firstweek', adjust similarly if needed
    firstweek = as.numeric(difftime(installed_at, start_date, units = "weeks")) %/% 1 + 1) %>%
  group_by(account_id, firstweek, week) %>%
  group_by(account_id) %>%
  mutate(id = cur_group_id()) %>%
  ungroup()
summary(did_data)

# Estimating the treatment effect using the Callaway and Sant'Anna method
if (!file.exists("../data/scratch/est_cs_gas_weekly.RDS")) {
  est_cs <- att_gt(yname = "weekly_consumption",
                   tname = "week",
                   idname = "id",
                   gname = "firstweek",
                   data = did_data,
                   clustervars = "id",
                   control_group=c("notyettreated"),
                   allow_unbalanced_panel = TRUE)
  
  saveRDS(est_cs, "../data/scratch/est_cs_gas_weekly.RDS")
} else {
  est_cs <- readRDS("../data/scratch/est_cs_gas_weekly.RDS")
}

# agg
agg.simple <- aggte(est_cs, type = "simple", na.rm = TRUE, clustervars="id", min_e = -52, bstrap=TRUE, alp = 0.01)
agg.simple$overall.att

# event study style
agg.es <- aggte(est_cs, type = "dynamic", na.rm = TRUE, clustervars="id", min_e = -52,  bstrap=TRUE)

# plot the results
ggdid(agg.es)

# by cohort
agg.grp <- aggte(est_cs, type = "group", na.rm = TRUE, clustervars="id", min_e = -52, bstrap=TRUE)

# plot the results
ggdid(agg.grp)

# by season
agg.cal <- aggte(MP = est_cs, type = "calendar",  na.rm = TRUE, clustervars="id", min_e = -52, bstrap=TRUE)
ggdid(agg.cal)


```

```{r}
# Extract coefficients, standard errors, and event time
coefficients <- agg.es$att.egt  # Convert to daily values
standard_errors <- agg.es$se.egt   # Convert to daily values
event_time <- agg.es$egt

# Create a data frame for plotting
plot_data <- data.frame(
  event_time = event_time,
  coefficient = coefficients,
  lower_ci = coefficients - 1.96 * standard_errors,
  upper_ci = coefficients + 1.96 * standard_errors,
  period = ifelse(event_time < 0, "No", "Yes")
)

# Reverse the color order
plot_data$period <- factor(plot_data$period, levels = c("Yes", "No"))

# Create the ggplot
ggplot(plot_data, aes(x = event_time, y = coefficient, color = period)) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, , alpha = 0.6) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
  scale_color_manual(
    name = "Is HP Installed", 
    labels = c("No" = "No", "Yes" = "Yes"),
    values = c("No" = not_hp_color, "Yes" = hp_color)  # Custom colors
  ) +
  labs(
    x = "Weeks since installation",
    y = "Dynamic ATT for Weekly Gas Consumption (kWh)"
  ) +
  theme_minimal()

ggsave("../graphs/hp_dynamic_att_gas.png")
```

```{r}
# Extract estimates, standard errors, and egt (event time)
estimates <- agg.grp$att.egt   # Convert to daily values
standard_errors <- agg.grp$se.egt   # Convert to daily values
event_time <- agg.grp$egt

# Calculate the week dates based on the start_date
week_dates <- start_date + weeks(event_time)

# Create a data frame for plotting
plot_data <- data.frame(
  event_time = week_dates,
  estimate = estimates,
  lower_ci = estimates - 1.96 * standard_errors,
  upper_ci = estimates + 1.96 * standard_errors
)

# Create the ggplot for group effect
ggplot(plot_data, aes(x = event_time, y = estimate)) +
  geom_point(color = hp_color) +
  geom_line(color = hp_color) +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, color = hp_color, alpha = 0.6) +  # Add transparency
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0+
  labs(
    x = "Weeks of Adoption",
    y = "Group ATT for Weekly Consumption in kWh"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate x-axis labels for better readability

ggsave("../graphs/hp_group_att.png")
```


```{r}
# Extract estimates, standard errors, and egt (event time)
estimates <- agg.cal$att.egt   # Convert to daily values
standard_errors <- agg.cal$se.egt   # Convert to daily values
event_time <- agg.cal$egt

# Calculate the week dates based on the start_date
week_dates <- start_date + weeks(event_time)

# Create a data frame for plotting
plot_data <- data.frame(
  week_date = week_dates,
  estimate = estimates,
  lower_ci = estimates - 1.96 * standard_errors,
  upper_ci = estimates + 1.96 * standard_errors
)


# Create the ggplot for calendar effect
ggplot(plot_data, aes(x = week_date, y = estimate)) +
  geom_point(color = hp_color) +
  geom_line(color = hp_color) +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, color = hp_color, alpha = 0.6) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
  labs(
    x = "Week of Installation",
    y = "Calendar ATT for Weekly Gas Consumption in kWh"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate x-axis labels for better readability

ggsave("../graphs/hp_cal_att.png")
```

## TWFE 

```{r gas-readings}

weather <- fread("../data/input/cosy_-_weather_weekly_2024_06_13.csv") 

cosy_hp_install_gas_consumption <- fread("../data/input/cosy_-_hp_users_gas_2024_06_13.csv") %>%
  group_by(account_id) %>%
  mutate(is_hp_installed = as.numeric(installed_at<=settlement_week),
         treated = max(is_hp_installed),
         min_settlement_week = min(settlement_week)) %>%
  filter(hp_survey_outcome_existing_heat_source=='{GAS_BOILER}', treated==1) %>%
  left_join(weather, by =c("gsp_group_id", "settlement_week" = "week_date"))  %>%
  distinct(account_id, settlement_week, .keep_all = TRUE)

m1_gas <- feols(weekly_consumption ~ i(is_hp_installed) | account_id  + avg_heating_degree + settlement_week, 
                data = cosy_hp_install_gas_consumption, cluster = ~ account_id)

etable(m1_gas,m1_gas, tex=TRUE, title = "HP Installation on Gas Consumption",
       headers = list(list("TWFE" = 1, "CS" = 1)),
       fitstat = ~ N + g + pre_avg + t_obs + r2, file = "../tables/hp_did_gas2.tex", replace = TRUE, label="tab:hp-did-gas-conso")

# Read the generated LaTeX file
file_path <- "../tables/hp_did_gas2.tex"
file_content <- readLines(file_path)

# Find the lines with the pre-treatment average and remove them
pre_avg_line_index <- grep("Pre-Treatment Average", file_content)
pre_avg_lines <- file_content[pre_avg_line_index:(pre_avg_line_index)]
file_content <- file_content[-c(pre_avg_line_index, pre_avg_line_index)]

# Find the position just after the coefficients
coeff_end_index <- grep("Is HP Installed \\$=\\$ 1", file_content) + 2

# Insert the pre-treatment average row after the coefficients
file_content <- append(file_content, pre_avg_lines, after = coeff_end_index)

# Add a \midrule after the pre-treatment average
file_content <- append(file_content, "\\midrule", after = coeff_end_index + length(pre_avg_lines))

# Write the modified content back to the LaTeX file
writeLines(file_content, file_path)

# Initialize variables to store estimates and standard errors
cs_estimate<- agg.simple$overall.att
cs_se <- agg.simple$overall.se
cs_n <- agg.simple$DIDparams$n
cs_nG <- agg.simple$DIDparams$nG
cs_nT <- agg.simple$DIDparams$nT

# Define the file path
file_path <- "../tables/hp_did_gas2.tex"

# Read the generated LaTeX file
file_content <- readLines(file_path)

# Format the estimate and standard error to four decimal places
cs_estimate <- sprintf("%.4f", cs_estimate)
cs_se <- sprintf("%.4f", cs_se)
cs_n <- format(cs_n, big.mark = ",")
cs_nG <- format(cs_nG, big.mark = ",")
cs_nT <- format(cs_nT, big.mark = ",")

# Find the rows that need to be updated
coeff_line <- grep("Is HP Installed \\$=\\$ 1", file_content)
se_line <- coeff_line + 1
obs_line <- grep("Observations", file_content)
sample_line <- grep("Size of the 'effective' sample", file_content)
periods_line <- grep("Number of Time Periods", file_content)
hdd_line <- grep("HDD", file_content)
household_line <- grep("Household", file_content)[1]
day_line <- grep("Week", file_content)[-1]
r2_line <- grep("R", file_content)

# Function to replace the 2nd column in a LaTeX table row
replace_column <- function(line, new_value) {
  parts <- strsplit(line, "&")[[1]]
  if (length(parts) > 1) {
    parts[3] <- str_trim(new_value)
  }
  return(paste(parts, collapse = " & "))
}

# Function to clear the 2nd column in a LaTeX table row
clear_column <- function(line) {
  parts <- strsplit(line, "&")[[1]]
  if (length(parts) > 1) {
    parts[3] <- ""
  }
  return(paste(parts, collapse = " & "))
}

# Ensure each replacement maintains the LaTeX table structure
file_content[coeff_line] <- replace_column(file_content[coeff_line], paste0(cs_estimate, "$^{***}$")) %>% paste0(" \\\\")
file_content[se_line] <- replace_column(file_content[se_line], paste0("(", cs_se, ")")) %>% paste0(" \\\\")
file_content[periods_line] <- replace_column(file_content[periods_line], cs_nT) %>% paste0(" \\\\")
file_content[hdd_line] <- clear_column(file_content[hdd_line]) %>% paste0(" \\\\")
file_content[household_line] <- clear_column(file_content[household_line]) %>% paste0(" \\\\")
file_content[week_line] <- clear_column(file_content[week_line]) %>% paste0(" \\\\")
file_content[r2_line] <- clear_column(file_content[r2_line]) %>% paste0(" \\\\")
file_content[sample_line] <- replace_columns(file_content[sample_line], cs_n) %>% paste0(" \\\\")
file_content[obs_line] <- clear_column(file_content[obs_line]) %>% paste0(" \\\\")

# Update the line with the clustering information
clustering_line_index <- grep("Clustered \\(Household\\)", file_content)
if (length(clustering_line_index) > 0) {
  file_content[clustering_line_index] <- "\\multicolumn{3}{l}{\\emph{Clustered (Household) standard-errors in parentheses for TWFE}}\\\\"
}

# Modify the label for "Size of the 'effective' sample" to "Number of Households"
file_content[sample_line] <- gsub("Size of the 'effective' sample", "Number of Households", file_content[sample_line])

new_row <- "\\multicolumn{3}{l}{\\emph{Clustered cohort (Week of adoption)) standard-errors in parentheses for CS}}\\\\"
file_content <- append(file_content, new_row, after = clustering_line_index)

# Add new row for "Number of cohorts (CS)"
new_row <- paste0("Number of cohorts (CS) & & ", cs_nG, " \\\\")
file_content <- append(file_content, new_row, after = sample_line)

# Write the modified content back to the LaTeX file
writeLines(file_content, file_path)

```



```{r gasdaily}

# 2024-05-27

# add daily weather data
weather <- fread("../data/input/Cosy Analysis Weather Mar 26 daily.csv") %>% 
  rename_with(.cols = starts_with("weekly"), 
              .fn = ~ sub("^weekly", "daily", .)) %>%
  mutate(settlement_date=as.Date(date_day, format = "%Y-%m-%d"))

# import daily gas consumption
daily_gas <- fread("../data/input/cosy_-_hp_gas_consumption_daily_2024_09_10.csv") %>%
  arrange(account_id, settlement_date)%>%
  distinct(account_id, settlement_date, .keep_all = TRUE) %>%
  filter(installed_at < "2024-05-27") %>%
  group_by(account_id) %>%
  mutate(settlement_date = as.Date(settlement_date),
         min_settlement_date = min(settlement_date)) %>%
  ungroup()

# Create a sequence of weeks
min_date <- min(as.Date(daily_gas$settlement_date))
max_date <- max(as.Date(daily_gas$settlement_date))

all_periods <- seq(min_date, max_date, by = "day")

# Create a data frame with all combinations of account_id and settlement_week
all_combinations <- expand.grid(
  account_id = unique(overall_weekly$account_id),
  settlement_date = all_periods
)

# Merge with original data
daily_gas <- all_combinations %>%
  left_join(daily_gas) %>%
  filter(min_settlement_date < settlement_date) %>%
  mutate(
    is_hp_installed = as.numeric(installed_at < settlement_date),
    consumption_chargedcurrent_daily = ifelse(is.na(consumption_chargedcurrent_daily), 
                                              0, consumption_chargedcurrent_daily)) %>%
  group_by(account_id) %>%
  mutate(treated = max(is_hp_installed)) %>%
  filter(treated==1) %>%
  ungroup() %>%
  inner_join(weather) %>%
  mutate(gas_consumption = consumption_chargedcurrent_daily*325.25)


# Round degrees Celsius 
daily_gas <- daily_gas %>% 
  mutate(temp_degree = factor(
    case_when(
      daily_avg_air_temperature_celsius < 0 ~ 0,
      daily_avg_air_temperature_celsius < 25 ~ round(daily_avg_air_temperature_celsius),
      TRUE ~ 25
    )
  ))

# base
m1 <- feols(consumption_chargedcurrent_daily ~ i(is_hp_installed) | 
              account_id + temp_degree + settlement_date, 
            data = daily_gas, cluster = ~ account_id)
m_tempreg <- feols(consumption_chargedcurrent_daily ~ i(is_hp_installed, temp_degree, ref=0) | 
                     account_id + temp_degree + settlement_date, 
                   data = daily_gas, cluster = ~ account_id)
etable(m1, m_tempreg)

library(tibble)

# Remove the overall model if it exists
all_coefs <- coeftable(m_tempreg) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rownames") %>%
  separate(rownames, into = c("is_hp_installed", "remove1", 
                              "daily_avg_air_temperature_celsius"), sep = "::") %>%
  mutate(daily_avg_air_temperature_celsius = as.numeric(daily_avg_air_temperature_celsius),
         lower_ci = Estimate - 1.96 * `Std. Error`,
         upper_ci = Estimate + 1.96 * `Std. Error`)

# Create the ggplot
ggplot(all_coefs, aes(x = daily_avg_air_temperature_celsius, y = Estimate)) +
  geom_point(color = hp_color) +  # Use your desired color
  geom_line(color = hp_color) +   # Use your desired color
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, alpha = 0.6, color = hp_color) +  # Use your desired color
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
  geom_hline(aes(yintercept = m1$coefficients), linetype = "dashed", alpha = 0.6, color = hp_color) +  # Add horizontal line for the average
  scale_y_continuous(
    name = "Estimate (kWh)"  ) +
  labs(
    x = "Average Temperature in Degrees",
  ) +
  theme_minimal() 

# Print the plot
ggsave("../graphs/hp_temperature_gas.png", width = 16, height = 8, units = "cm")

```