---
title: "Heatpump analysis"
author: "Louise Bernard"
date: "2024-06-04"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include=TRUE, warning  = FALSE, fig.pos = "H", out.extra = "")

# Run on a subsample of the data for faster processing
random_subsample <- FALSE

# Function to check if a package is installed, and if not, install it
install_if_needed <- function(package) {
  if (!require(package, character.only = TRUE)) {
    install.packages(package, dependencies = TRUE)
    library(package, character.only = TRUE)
  }
}

# List of packages to load
packages <- c(
  "knitr", "kableExtra", "did", "fixest", "lfe", "data.table", "lubridate", 
  "dplyr", "ggplot2", "RColorBrewer", "tidyr", "scales", "tibble",
  "forcats", "viridis",  "stringr", "stargazer", "panelView", "readxl", "HonestDiD"
)


# Load (and install if needed) each package
lapply(packages, install_if_needed)

# Create folders without warning message
dir.create("../graphs", showWarnings = FALSE)
dir.create("../data", showWarnings = FALSE)
dir.create("../data/scratch", showWarnings = FALSE)
dir.create("../data/output", showWarnings = FALSE)
dir.create("../data/input", showWarnings = FALSE)
dir.create("../tables", showWarnings = FALSE)

# Set graphics colours
hp_color <- "#AD87CA"
not_hp_color <- "#2D354A"

# set dictionary
setFixest_dict(c(consumption_hh = "Consumption in kWh per half hour",
                 total_consumption = "Weekly Energy Consumption in kWh", 
                 daily_consumption = "Consumption in kWh per day",
                 share_consumption = "Share of daily consumption",
                 weekly_consumption = "Weekly Gas Consumption in kWh",
                 is_hp_installed = "OnCosy",
                 daily_avg_heating_degree = "HDD",
                 avg_heating_degree = "HDD",
                 date = "Day", 
                 settlement_week = "Week",
                 account_id = "Household", 
                 corrected_consumption = "Monthly Gas Consumption in kWh",
                 account_closed = "Account Closed",
                 tariff_gsp_group_id = "GSP", 
                 rate_period = "Rate period",
                 is_variable = "Variable Tariff",
                 energy_efficiency = "Energy Efficiency",
                 estimated_annual_consumption = "EAC",
                 eac_mwh = "EAC in mWh",
                 is_hp_installed = "Is HP Installed",
                 predicted_is_installed = "Is HP Installed",
                 elec_consumption = "Weekly Electricity Consumption (kWh)",
                 gas_consumption = "Weekly Gas Consumption (kWh)",
                 month_date = "Month",
                 is_winter = "Winter",
                 previous_is_variable = "Prev Is Variable",
                 epc_letter = "EPC",
                 latest_survey_heat_loss = "Heatloss (W)",
                 urban = "Urban",
                 hp_survey_is_solar_present = "Has Solar PV",
                 floor_area = "Floor area",
                 property_value = "Property value",
                 months_since_hp_rec = "Months Since HP Installation",
                 ev_charging = "EV Charging",
                 has_ev = "EV User"))
```

## Define most used functions

### Add pre-treatment average statistics to tables

```{r define-functions}

CleanPreAverage <- function(file_path) {
  
  # Read the generated LaTeX file
  file_content <- readLines(file_path)
  
  # Find the lines with the pre-treatment average and remove them
  if (length(grep("Yearly Consumption", file_content))==1) {
    pre_avg_line_index <- grep("Yearly Consumption", file_content)
  } else {
    pre_avg_line_index <- grep("Yearly Consumption", file_content)[2]
  }
  
  # Find the lines with the pre-treatment average and remove them
  pre_avg_lines <- file_content[pre_avg_line_index:(pre_avg_line_index)]
  file_content <- file_content[-c(pre_avg_line_index, pre_avg_line_index)]
  
  # Find the position just after the coefficients
  coeff_end_index <- grep("Is HP Installed", file_content)[length(grep("Is HP Installed", file_content))] + 2
  
  # Insert the pre-treatment average row after the coefficients
  file_content <- append(file_content, pre_avg_lines, after = coeff_end_index)
  file_content <- append(file_content, "\\emph{Pre-Treatment Average}\\\\", after = coeff_end_index)
  
  # Add a \midrule after the pre-treatment average
  file_content <- append(file_content, "\\midrule", after = coeff_end_index + length(pre_avg_lines)+1)
  
  # Modify the label for "Size of the 'effective' sample" to "Number of Households"
  sample_line <- grep("Size of the 'effective' sample", file_content)
  file_content[sample_line] <- gsub("Size of the 'effective' sample", "Number of Households", file_content[sample_line])
  
  # Write the modified content back to the LaTeX file
  writeLines(file_content, file_path)
}



# Function to format numbers
format_number <- function(number) {
  return(format(round(number), big.mark = ",", scientific = FALSE))
}

# Function to format numbers with four decimal places
format_decimal <- function(number, digits = 2) {
  return(format(round(number, digits), nsmall = digits, big.mark = ",", scientific = FALSE))
}


# Register the pre-treatment average fit statistic
fitstat_register("pre_avg", function(x) {
  
  # Directly use the model's data
  model_data <- eval(x$call$data, envir = x$call_env)
  
  # Extract the outcome variable from the formula
  outcome_variable <- all.vars(x$fml_all$linear)[1]
  
  # Get the logical vector of observations used in the model
  obs_used <- obs(x)
  
  # Ensure `obs_used` correctly subsets the data
  if (is.logical(obs_used) && length(obs_used) == nrow(model_data)) {
    data_used <- model_data[obs_used, ]
  } else if (is.numeric(obs_used) && all(obs_used <= nrow(model_data))) {
    data_used <- model_data[obs_used, ]
  } else {
    stop("Unable to correctly subset data. Check the obs_used vector.")
  }
  
  # Extract the outcome values
  outcome_values <- data_used[[outcome_variable]]
  
  # Create pre-avg for non-HP installed group
  pre_avg <- mean(outcome_values[data_used$is_hp_installed == 0], na.rm = TRUE)
  
  # Format the pre-avg
  formatted_pre_avg <- format_decimal(pre_avg)
  
  return(formatted_pre_avg)
}, "Yearly Consumption")




# Add number of time periods
fitstat_register("t_obs", function(x) {
  
  # time variable
  t_var <- x$fixef_vars[3]
  
  # nbr of unique val for t var
  t_obs <- x$fixef_sizes[t_var]
  
  return(format_number(t_obs))
}, "Number of Time Periods")


```

# Load data


```{r load-dataset}
# get consumption by period
hp_installed_period <- fread("../data/input/cosy_-_hp_aggregated_up_2024_06_18.csv") %>%
  rename(total_consumption=total_read_value,
         date = settlement_date) %>%
  mutate(consumption_hh = ifelse(rate_period == "Other", 
                                 total_consumption/30, total_consumption/6),
         date = as.Date(date))

# aggreate up to get overall
hp_installed_daily <- hp_installed_period %>%
  group_by(account_id, hashed_mpan, date) %>%
  summarise(total_consumption = sum(total_consumption)) %>%
  mutate(consumption_hh = total_consumption / 48,
         rate_period = factor("Overall")) 

# merge together to make regressions easier
hp_installed <- full_join(hp_installed_period,
                          hp_installed_daily) %>%
  inner_join(fread("../data/input/cosy_-_hp_details_2024_06_25.csv"), by=c("account_id","hashed_mpan"))

# add daily weather data
weather <- fread("../data/input/Cosy Analysis Weather Mar 26 daily.csv") %>% 
  rename_with(.cols = starts_with("weekly"), 
              .fn = ~ sub("^weekly", "daily", .)) %>%
  rename(tariff_gsp_group_id=gsp_group_id) %>%
  mutate(date_day=as.Date(date_day, format = "%Y-%m-%d")) %>%
  rename(date = date_day)

# merge weather
hp_installed <- hp_installed %>%
  left_join(weather)


rm(weather, combined_df, combined_df2, hp_installed_daily, hp_installed_period)

# hp_installed <- hp_installed %>%
#   left_join(readRDS("../data/scratch/ev_mpan.RDS")) %>%
#   mutate(has_ev = ifelse(!is.na(ev_start), as.numeric(date >= ev_start), 0))

# clean up
hp_installed <- hp_installed %>%
  mutate(date = as.Date(date),
         is_hp_installed = as.numeric(installed_at <= date)) %>%
  mutate(rate_period = factor(rate_period, levels = c("Morning Cosy",
                                                      "Afternoon Cosy",
                                                      "Peak Rate",
                                                      "Other", 
                                                      "Overall"))) %>%
  group_by(account_id) %>%
  mutate(treated = max(is_hp_installed)) %>% # identify treated versus not yet treated
  distinct(account_id, date, rate_period, .keep_all = TRUE)

# summary statistics
summary(hp_installed)


# Run on a subsample of the data for faster processing
if (random_subsample) {
  set.seed(123)
  sampled_accounts <- sample(unique(hp_installed$account_id), 1000)
  hp_installed <- hp_installed %>% 
    filter(account_id %in% sampled_accounts)
  gc()
}

```

## Summary statistics {#sec:sumstats}

```{r fig1:weekly-deals-and-installations}
# Prepare the data for installations
weekly_installations <- hp_installed %>%
  group_by(account_id) %>%
  mutate(treated = max(is_hp_installed)) %>%
  filter(treated ==1) %>%
  ungroup() %>%
  select(account_id, installed_at) %>%
  distinct() %>%
  mutate(first_week = as.Date(floor_date(installed_at, "week"))) %>%
  group_by(first_week) %>%
  summarise(installations = n())

# Prepare the data for deals
weekly_deals <- hp_installed %>%
  group_by(account_id) %>%
  mutate(treated = max(is_hp_installed)) %>%
  filter(treated==1) %>%
  ungroup() %>%
  filter(year(deal_created_at)>2000)%>%
  select(account_id, deal_created_at) %>%
  distinct() %>%
  mutate(first_week = as.Date(floor_date(deal_created_at, "week"))) %>%
  group_by(first_week) %>%
  summarise(deals = n())

# Define the date for the announcement
announcement_date <- as.Date("2023-08-31")

# Choose colors from the Brewer palette
color_installations <- hp_color
color_deals <- hp_color

# Create the combined plot
ggplot() +
  # Plot for deals
  geom_line(data = weekly_deals, aes(x = first_week, y = deals, color = "Deals"), linetype = "dashed") +
  geom_vline(xintercept = as.numeric(announcement_date), linetype = "dashed", color = color_deals) +
  # Plot for installations
  geom_line(data = weekly_installations, aes(x = first_week, y = installations, color = "Installations")) +
  geom_point(data = weekly_installations, aes(x = first_week, y = installations, color = "Installations")) +
  annotate("text", x = announcement_date - weeks(1), y = max(weekly_deals$deals) * 0.9,
           label = "Announcement:\nBoiler Upgrade Scheme\nincrease to £7,500", hjust = 1, 
           color = color_deals) +
  labs(
    x = "Week",
    y = "Number of Installations/Deals",
    color = "Metric"
  ) +
  scale_x_date(
    labels = scales::date_format("%b %y"),
    date_breaks = "3 month"
  ) +
  scale_color_manual(values = c("Installations" = color_installations, "Deals" = "grey")) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

# Save the combined plot
ggsave("../graphs/combined_weekly_installations_deals.png", width = 15, height = 10, units = "cm", dpi = 300)
```

```{r installplot}

hp_installed %>%
  distinct(account_id, installed_at) %>%
  mutate(month_installation = month(installed_at, label = TRUE)) %>%
  count(month_installation) %>%
  ggplot(aes(x = month_installation, y = n)) +
  geom_col(fill = hp_color) +
  labs(
    x = "Month of Installation",
    y = "Number of Installations"
  ) +
  theme_minimal()

ggsave("../graphs/monthly_installation.png", width = 12, height = 8, dpi = 300)


```

### Table A.14: External Validity by Area for Heat Pump Installation

```{r pop-weighted-msoas}
# Function to calculate weighted standard deviation
weighted_sd <- function(x, w) {
  sum_w <- sum(w, na.rm = TRUE)
  mean_w <- sum(w * x, na.rm = TRUE) / sum_w
  sqrt(sum(w * (x - mean_w)^2, na.rm = TRUE) / sum_w)
}

# Function to perform weighted t-test
weighted_t_test <- function(x, w, y, v) {
  n_x <- sum(w, na.rm = TRUE)
  n_y <- sum(v, na.rm = TRUE)
  mean_x <- sum(w * x, na.rm = TRUE) / n_x
  mean_y <- sum(v * y, na.rm = TRUE) / n_y
  var_x <- sum(w * (x - mean_x)^2, na.rm = TRUE) / n_x
  var_y <- sum(v * (y - mean_y)^2, na.rm = TRUE) / n_y
  t_stat <- (mean_x - mean_y) / sqrt(var_x / n_x + var_y / n_y)
  df <- (var_x / n_x + var_y / n_y)^2 / ((var_x / n_x)^2 / (n_x - 1) + (var_y / n_y)^2 / (n_y - 1))
  p_value <- 2 * pt(-abs(t_stat), df)
  return(p_value)
}

# Function to summarize and test
summarize_and_test <- function(data, var_name, weight_name) {
  # Calculate weighted means, standard deviations, and non-missing observation counts for each treatment group
  summary_stats <- data %>%
    group_by(treated) %>%
    summarise(
      N = sum(!is.na(.data[[var_name]])), # Count non-missing observations
      Weighted_Mean = weighted.mean(.data[[var_name]], .data[[weight_name]], na.rm = TRUE),
      SD = weighted_sd(.data[[var_name]], .data[[weight_name]]),
      .groups = 'drop'
    ) %>%
    pivot_wider(names_from = treated, values_from = c("N", "Weighted_Mean", "SD"), names_sep = " ")
  
  # Prepare for weighted t-test by separating data and weights
  data1 <- filter(data, treated == 1)[[var_name]]
  weights1 <- filter(data, treated == 1)[[weight_name]]
  data2 <- filter(data, treated == 0)[[var_name]]
  weights2 <- filter(data, treated == 0)[[weight_name]]
  
  # Check if both groups have sufficient data for weighted t-test
  if (length(unique(data1)) > 1 && length(unique(data2)) > 1 && length(data1) > 1 && length(data2) > 1) {
    p_value <- weighted_t_test(data1, weights1, data2, weights2)
  } else {
    p_value <- NA_real_ # Insufficient data or variability
  }
  
  # Combine results
  tibble(Variable = var_name) %>%
    bind_cols(summary_stats) %>%
    mutate(`P Value` = p_value)
}

# Read and process each dataset
population2022 <- read_excel("../data/input/sapemsoasyoatablefinal.xlsx", sheet = "Mid-2022 MSOA 2021", skip = 3)

cosy_hp_details <- fread("../data/input/cosy_-_hp_details_2024_07_03.csv") %>%
  inner_join(hp_installed %>% filter(treated == 1) %>% select(account_id) %>% distinct()) %>%
  select(account_id, postcode) %>%
  distinct() %>%
  group_by(postcode) %>%
  tally() %>%
  filter(!postcode == "")

postcode_msoa <- fread("../data/input/PCD_OA21_LSOA21_MSOA21_LAD_AUG23_UK_LU.csv") %>%
  left_join(cosy_hp_details, by = c("pcds" = "postcode")) %>%
  mutate(n = ifelse(is.na(n), 0, 1)) %>%
  select(msoa21cd, n) %>%
  group_by(msoa21cd) %>%
  summarise(treated = sum(n))

income <- readxl::read_excel("../data/input/saiefy1920finalqaddownload280923.xlsx", sheet = "Total annual income", skip = 4) %>%
  select(`MSOA code`, `Total annual income (£)`) %>%
  distinct() 

net_income <- readxl::read_excel("../data/input/saiefy1920finalqaddownload280923.xlsx", sheet = "Net annual income", skip = 4) %>%
  select(`MSOA code`, `Net annual income (£)`) %>%
  distinct() 

net_housing_income <- readxl::read_excel("../data/input/saiefy1920finalqaddownload280923.xlsx", sheet = "Net income after housing costs", skip = 4) %>%
  select(`MSOA code`, `Net annual income after housing costs (£)`) %>%
  distinct()

# Load and preprocess the property_prices data
property_prices <- read_excel("../data/input/HPSSA Dataset 3 - Mean price paid by MSOA.xls", 
                              sheet = "1a", skip = 4) %>%
  select(`MSOA code`, `Year ending Mar 2023`) %>%
  rename(msoa21cd = `MSOA code`, `Property price (£)` = `Year ending Mar 2023`)

hh_size <- fread("../data/input/custom-filtered-2024-07-03T10_58_30Z.csv") %>%
  group_by(`Middle layer Super Output Areas Code`) %>%
  mutate(sum_obs = sum(Observation), weight = Observation / sum_obs) %>%
  summarise(`Average HH Size` = sum(weight * `Household size (9 categories) Code`))

hh_deprivaton <- fread("../data/input/custom-filtered-2024-07-03T10_43_12Z.csv") %>%
  group_by(`Middle layer Super Output Areas Code`) %>%
  mutate(sum_obs = sum(Observation), `HH Not Deprived in Any Dim. (%)` = 100 * Observation / sum_obs) %>%
  filter(`Household deprivation (6 categories) Code` == 1)

avg_age <- fread("../data/input/custom-filtered-2024-07-03T11_15_15Z.csv") %>%
  group_by(`Middle layer Super Output Areas Code`) %>%
  mutate(sum_obs = sum(Observation), weight = Observation / sum_obs) %>%
  summarise(`Average Age` = sum(weight * `Age (101 categories) Code`))

education <- fread("../data/input/custom-filtered-2024-07-03T11_22_39Z.csv") %>%
  group_by(`Middle layer Super Output Areas Code`) %>%
  mutate(sum_obs = sum(Observation), `Share Level 4 Qualifications (%)` = 100 * Observation / sum_obs) %>%
  filter(`Highest level of qualification (7 categories) Code` == 4)

# Merge all datasets by `MSOA code` or `Middle layer Super Output Areas Code`
merged_data <- postcode_msoa %>%
  inner_join(income, by = c("msoa21cd"="MSOA code")) %>%
  inner_join(property_prices,by = c("msoa21cd"="msoa21cd")) %>%
  inner_join(hh_size, by = c("msoa21cd" = "Middle layer Super Output Areas Code")) %>%
  inner_join(hh_deprivaton, by = c("msoa21cd" = "Middle layer Super Output Areas Code")) %>%
  inner_join(avg_age, by = c("msoa21cd" = "Middle layer Super Output Areas Code")) %>%
  inner_join(education, by = c("msoa21cd" = "Middle layer Super Output Areas Code")) %>%
  inner_join(population2022 %>% select(`MSOA 2021 Code`, Total), by = c("msoa21cd" = "MSOA 2021 Code")) %>%
  mutate(country = substr(msoa21cd, 1, 1),
         treated = as.numeric(treated > 0)) %>%
  filter(!msoa21cd == "", country %in% c("E", "W"))

# List of variables of interest
variables <- c(
  "Total annual income (£)",
  "Property price (£)",
  "Average HH Size",
  "HH Not Deprived in Any Dim. (%)",
  "Average Age",
  "Share Level 4 Qualifications (%)"
)

# Applying the function across all variables
results <- purrr::map_dfr(variables, ~summarize_and_test(merged_data, .x, "Total")) %>%
  as.data.frame()

# Format the counts with thousand separators
results <- results %>%
  mutate(`N 1` = format(`N 1`, big.mark = ",", scientific = FALSE),
         `N 0` = format(`N 0`, big.mark = ",", scientific = FALSE))

# Adjust the format of the table for LaTeX output
formatted_results <- results %>%
  select(Variable, `Weighted_Mean 1`, `SD 1`, `Weighted_Mean 0`, `SD 0`, `P Value`) %>%
  rename(
    `Weighted Mean Treated` = `Weighted_Mean 1`,
    `SD Treated` = `SD 1`,
    `Weighted Mean Others` = `Weighted_Mean 0`,
    `SD Others` = `SD 0`
  ) %>%
  mutate(
    `Weighted Mean Treated` = paste0(format(round(`Weighted Mean Treated`, 2), big.mark = ",", nsmall = 2), " (", format(round(`SD Treated`, 2), big.mark = ",", nsmall = 2), ")"),
    `Weighted Mean Others` = paste0(format(round(`Weighted Mean Others`, 2), big.mark = ",", nsmall = 2), " (", format(round(`SD Others`, 2), big.mark = ",", nsmall = 2), ")"),
    `P Value` = format(round(`P Value`, 2), nsmall = 2)
  ) %>%
  select(Variable, `Weighted Mean Treated`, `Weighted Mean Others`)

# Add the N values to the column names
colnames(formatted_results)[2] <- paste0("MSOAs with HP Installations (N = ", results$`N 1`[1], ")")
colnames(formatted_results)[3] <- paste0("Other MSOAs (N = ", results$`N 0`[1], ")")

# Create the LaTeX table using stargazer
stargazer(formatted_results, type = "latex", summary = FALSE, 
          title = "External Validity by Area for Heat Pump Installations",
          rownames = FALSE,
          digits = 2,
          label = "tab:msoa_stats",
          out = "../tables/balance_table_temp.tex")

# Read the content of the generated LaTeX table
latex_table <- readLines("../tables/balance_table_temp.tex")

# Insert custom headers with multicolumn
header_row <- " & \\multicolumn{2}{c}{Weighted Mean} \\\\"
position <- grep("\\\\begin\\{tabular\\}", latex_table) + 1
latex_table <- append(latex_table, header_row, after = position)

# Replace the first and last instances of \hline \\[-1.8ex] with \hline \hline \\[-1.8ex]
hline_ex_lines <- grep("\\hline" , latex_table)
if (length(hline_ex_lines) >= 2) {
  latex_table[hline_ex_lines[1]] <- gsub("\\hline", "\\hline\\hline", latex_table[hline_ex_lines[1]], fixed = TRUE)
  latex_table[hline_ex_lines[length(hline_ex_lines)]] <- gsub("\\hline", "\\hline\\hline", latex_table[hline_ex_lines[length(hline_ex_lines)]], fixed = TRUE)
}

# Write the modified LaTeX table to a new file
writeLines(latex_table, "../tables/balance_table.tex")
```

## Figure A.11: Impact of Heat Pump Installation by Property Value Decile

```{r}

# Read and process each dataset
population2022 <- read_excel("../data/input/sapemsoasyoatablefinal.xlsx", sheet = "Mid-2022 MSOA 2021", skip = 3)

# Load and preprocess the cosy_hp_details data
cosy_hp_details <- fread("../data/input/cosy_-_cosy_details_2024_07_24.csv") %>%
  inner_join(hp_installed %>% select(hashed_mpan) %>% distinct(), by = "hashed_mpan") %>%
  select(hashed_mpan, postcode, property_value) %>%
  distinct() %>%
  group_by(postcode) %>%
  summarise(property_value = mean(property_value, na.rm = TRUE)) %>%
  filter(postcode != "")

# Load and preprocess the postcode_msoa data
postcode_msoa <- fread("../data/input/PCD_OA21_LSOA21_MSOA21_LAD_AUG23_UK_LU.csv") %>%
  left_join(cosy_hp_details, by = c("pcds" = "postcode")) %>%
  mutate(treated = ifelse(is.na(property_value), 0, 1)) %>%
  select(msoa21cd, treated, property_value)

# Load and preprocess the property_prices data
property_prices <- read_excel("../data/input/HPSSA Dataset 3 - Mean price paid by MSOA.xls", 
                              sheet = "1a", skip = 4) %>%
  select(`MSOA code`, `Year ending Mar 2023`) %>%
  rename(msoa21cd = `MSOA code`, year_ending_mar_2023 = `Year ending Mar 2023`)

# Merge all datasets
merged_data <- postcode_msoa %>%
  inner_join(property_prices, by = "msoa21cd") %>%
  mutate(country = substr(msoa21cd, 1, 1)) %>%
  filter(msoa21cd != "", country %in% c("E", "W"))

# Create combined data frame for plotting
treated_1 <- merged_data %>%
  filter(treated == 1) %>%
  select(property_value = year_ending_mar_2023) %>%
  mutate(group = "MSOAs with Heat Pump Installations")

treated_0 <- merged_data %>%
  filter(treated == 0) %>%
  select(property_value = year_ending_mar_2023) %>%
  mutate(group = "MSOAs without Heat Pump Installations")

property_value_data <- merged_data %>%
  filter(!is.na(property_value)) %>%
  select(property_value) %>%
  mutate(group = "Heat Pump Installations")

combined_data <- bind_rows(
  treated_1,
  treated_0,
  property_value_data
)

# Trim outliers by removing values outside the 1st and 99th percentiles
trimmed_combined_data <- combined_data %>%
  group_by(group) %>%
  filter(property_value > quantile(property_value, 0.01) & property_value < quantile(property_value, 0.99))

# Calculate means for each group
means <- trimmed_combined_data %>%
  group_by(group) %>%
  summarise(mean_value = mean(property_value, na.rm = TRUE))

medians <- trimmed_combined_data %>%
  group_by(group) %>%
  summarise(median_value = median(property_value, na.rm = TRUE))



ggplot(trimmed_combined_data, aes(x = property_value, color = group, fill = group)) +
  geom_density(alpha = 0.5, aes(y = ..scaled..)) +
  geom_vline(data = medians, aes(xintercept = median_value, color = group), linetype = "dashed") +
  scale_color_manual(values = c("skyblue", "lightgreen", "orange")) +
  scale_fill_manual(values = c("skyblue", "lightgreen", "orange")) +
  scale_x_continuous(labels = dollar_format(prefix = "£", suffix = "k", scale = 1e-3, big.mark = ",")) +
  labs(
    title = "Density Plot of Property Prices",
    x = "Property Value",
    y = "Density",
    caption = "Dashed lines represent the medians",
    color = NULL,  # Remove the legend title for color
    fill = NULL    # Remove the legend title for fill
  ) +
  theme_classic() +
  theme(legend.position = "bottom")


ggsave("../graphs/average_property_price.png", width = 12, height = 8, dpi = 300)

```

## Table A.3: HP Installation on Electricity Consumption Controlling for EV Ownership 

```{r ev-detection}

# ev half hours 
# Read the CSV file
ev_charging <- fread("../data/input/cosy_-_ev_detection_2024_07_04.csv") %>%
  mutate(ev_charging = 1,
         date = as.Date(interval_start),
         interval_start = as.POSIXct(interval_start, format="%Y-%m-%d %H:%M:%S"),
         hour = as.integer(format(interval_start, "%H")),
         rate_period = case_when(
           hour >= 4 & hour < 7 ~ "Morning Cosy",
           hour >= 13 & hour < 16 ~ "Afternoon Cosy",
           hour >= 16 & hour < 19 ~ "Peak Rate",
           TRUE ~ "Other"
         )
  )

# Aggregate at the account id, mpan, date and rate period level
ev_charging_agg <- rbind(ev_charging %>%
                           group_by(account_id,  hashed_mpan, date, rate_period) %>%
                           tally(),
                         ev_charging %>%
                           group_by(account_id,  hashed_mpan, date) %>%
                           tally() %>% 
                           mutate(rate_period="Overall")) %>%
  rename(ev_charging=n)

# EV users details
ev_users <- ev_charging %>%
  group_by(account_id) %>%
  summarise(is_ev_detected= min(as.Date(interval_start)))

# Update hp_installed with the new ev_charging values using case_when
hp_installed <- hp_installed %>%
  left_join(ev_charging_agg) %>%
  mutate(ev_charging = ifelse(is.na(ev_charging), 0, ev_charging),
         ev_charging = case_when(
           rate_period == "Overall" ~ ev_charging / 48,
           rate_period == "Other" ~ ev_charging / 30,
           TRUE ~ ev_charging / 6
         )
  ) %>%
  left_join(ev_users) %>%
  mutate(has_ev = as.numeric(is_ev_detected <= date),
         has_ev = ifelse(is.na(has_ev), 0, has_ev))

# Fit the model
m1 <- feols(total_consumption ~ i(is_hp_installed, ref=0)  |
              daily_avg_heating_degree + account_id + date, 
            data = hp_installed %>% 
              filter(treated==1, rate_period %in% c("Overall")) %>% 
              mutate(total_consumption=365.25*total_consumption) %>%
              ungroup(), 
            cluster = ~account_id)

m1c <- feols(total_consumption  ~ i(is_hp_installed, ref=0) + has_ev + i(is_hp_installed, has_ev, ref=0) |
               daily_avg_heating_degree + account_id + date, 
             data = hp_installed %>% 
               filter(treated==1, rate_period %in% c("Overall")) %>% 
               mutate(total_consumption=365.25*total_consumption) %>%
               ungroup(), 
             cluster = ~account_id)

# Generate the initial LaTeX table
etable(m1, m1c, tex = TRUE, title = "HP Installation on Electricity Consumption Controlling for EV Ownership", 
       dict = c("total_consumption" = "Yearly Consumption in kWh"),
       fitstat = ~ N + g + pre_avg + t_obs + r2, 
       file = "../tables/hp_did_ev.tex", replace = TRUE, label = "tab:hp-did-ev")

CleanPreAverage("../tables/hp_did_ev.tex")



```

## Table A.4: HP Installation on Probability of Charging EV by Period


```{r charging-time}

# Identify the period with the highest EV charging for each mpan and date
ev_charging_max <- ev_charging %>%
  group_by(account_id, hashed_mpan, date, rate_period) %>%
  summarise(ev_charging = sum(ev_charging, na.rm = TRUE)) %>%
  group_by(account_id, hashed_mpan, date) %>%
  filter(ev_charging == max(ev_charging)) %>%
  mutate(highest_ev_charging = 1) %>%
  ungroup()

ev_charging_max <- ev_charging_max %>%
  left_join(hp_installed %>% select(account_id, hashed_mpan, date, is_hp_installed) %>% distinct())

# Create dummy variables for rate periods
ev_charging_max <- ev_charging_max %>%
  mutate(
    Morning_Cosy = ifelse(rate_period == "Morning Cosy", 1, 0),
    Afternoon_Cosy = ifelse(rate_period == "Afternoon Cosy", 1, 0),
    Peak_Rate = ifelse(rate_period == "Peak Rate", 1, 0),
    Other = ifelse(rate_period == "Other", 1, 0)
  )

# Run the fixed effects models
m_charging1 <- feols(Morning_Cosy ~ i(is_hp_installed) | account_id + date, data = ev_charging_max, cluster = ~ account_id)
m_charging2 <- feols(Afternoon_Cosy ~ i(is_hp_installed) | account_id + date, data = ev_charging_max, cluster = ~ account_id)
m_charging3 <- feols(Peak_Rate ~ i(is_hp_installed) | account_id + date, data = ev_charging_max, cluster = ~ account_id)
m_charging4 <- feols(Other ~ i(is_hp_installed) | account_id + date, data = ev_charging_max, cluster = ~ account_id)


# Generate the LaTeX table with the dependent variable named "Charging EV"
etable(m_charging1, m_charging2, m_charging3, m_charging4, 
       tex = TRUE, 
       title = "HP Installation on Probability of Charging EV by Period", 
       headers = c("Morning Cosy", "Afternoon Cosy", "Peak Rate", "Other"),
       fitstat = ~ N + g + pre_avg + r2, 
       file = "../tables/hp_ev_charging.tex", 
       replace = TRUE, 
       label = "tab:hp-ev-charging",
       dict = c(Morning_Cosy = "Charging EV", 
                Afternoon_Cosy = "Charging EV", 
                Peak_Rate = "Charging EV", 
                Other = "Charging EV"))

# Read the generated LaTeX file
file_path <- "../tables/hp_ev_charging.tex"

# Read the generated LaTeX file
file_content <- readLines(file_path)

# Find the lines with the pre-treatment average and remove them
if (length(grep("Charging EV", file_content))==1) {F
  pre_avg_line_index <- grep("Charging EV", file_content)
} else {
  pre_avg_line_index <- grep("Charging EV", file_content)[2]
}

# Find the lines with the pre-treatment average and remove them
pre_avg_lines <- file_content[pre_avg_line_index:(pre_avg_line_index)]
file_content <- file_content[-c(pre_avg_line_index, pre_avg_line_index)]

# Find the position just after the coefficients
coeff_end_index <- grep("Is HP Installed", file_content)[length(grep("Is HP Installed", file_content))] + 2

# Insert the pre-treatment average row after the coefficients
file_content <- append(file_content, pre_avg_lines, after = coeff_end_index)
file_content <- append(file_content, "\\emph{Pre-Treatment Average}\\\\", after = coeff_end_index)

# Add a \midrule after the pre-treatment average
file_content <- append(file_content, "\\midrule", after = coeff_end_index + length(pre_avg_lines)+1)

# Modify the label for "Size of the 'effective' sample" to "Number of Households"
sample_line <- grep("Size of the 'effective' sample", file_content)
file_content[sample_line] <- gsub("Size of the 'effective' sample", "Number of Households", file_content[sample_line])

# Write the modified content back to the LaTeX file
writeLines(file_content, file_path)

```


```{r smart-tariff}

Cosy_hp_agreements_data_2024_07_05 <- fread("../data/input/Cosy_-_hp_agreements_data_2024_07_05.csv") %>%
  mutate(time_since_hp = round(as.numeric(difftime(agreement_valid_from, installed_at, units = "week"))/(4.43)),
         time_since_hp = case_when(time_since_hp < -15 ~ -15,
                                   time_since_hp > 15 ~ 15,
                                   TRUE ~ time_since_hp),
         smart_tariff = as.numeric(product_display_name %in% c("Agile Octopus","Intelligent Octopus Go", "Cosy Octopus", "Octopus Go", "Octopus Flux Import", "Intelligent Octopus Flux Import", "Octopus Go Faster")),
         year = year(agreement_valid_from))
table(Cosy_hp_agreements_data_2024_07_05$time_since_hp)

m_tariff <- feols(smart_tariff ~ i(time_since_hp, ref= -1) | account_id + year, data = Cosy_hp_agreements_data_2024_07_05, cluster = ~ account_id)

# Extract coefficients and standard errors
coefs <- coeftable(m_tariff) %>%
  data.frame() %>%
  tibble::rownames_to_column("term") %>%
  separate(term, into = c( "remove1", "time_since_hp"), sep = "::") %>%
  mutate(time_since_hp = as.numeric(time_since_hp), 
         lower_ci = Estimate - 1.96 * `Std..Error`,
         upper_ci = Estimate + 1.96 * `Std..Error`,
         post = (time_since_hp>=0)
  )

# Create the ggplot
ggplot(coefs, aes(x = time_since_hp, y = Estimate, color = post)) +
  geom_point(stat = "identity") +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, alpha=0.5) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(
    x = "Months Since HP Installation",
    y = "Probability of Having a Smart Tariff",
    color = "Is HP Installed"  # Update legend title
  ) +
  scale_color_manual(
    values = c("TRUE" = hp_color, "FALSE" = not_hp_color),  # Set custom colors
    labels = c("No", "Yes")  # Update legend labels
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
  theme_minimal()

ggsave("../graphs/hp_switch_to_smart_tariff.png")
```


## Heterogeneity analysis

### Figure 6: Impact of Heat Pump Installation by Outside Temperature (and Figure A.2 to A.5)

```{r temperature-analysis, eval=TRUE}
rm(m1, m1c, m_solar, ev_charging, ev_users, ev_charging_agg)

# Fit the model
m1 <- feols(consumption_hh ~ i(is_hp_installed) | daily_avg_heating_degree + account_id + date, 
            data = hp_installed %>% filter(treated == 1) %>% ungroup(), 
            cluster = ~account_id, 
            split = ~ rate_period)

# Unique periods 
periods <- unique(hp_installed$rate_period)

# Round degrees Celsius 
hp_installed <- hp_installed %>% mutate(temp_degree = factor(
  case_when(
    daily_avg_air_temperature_celsius < 0 ~ 0,
    daily_avg_air_temperature_celsius < 25 ~ round(daily_avg_air_temperature_celsius),
    TRUE ~ 25
  )
))

# Run the regression model
tempreg <- feols(consumption_hh ~ i(is_hp_installed, temp_degree, ref=0) |
                   account_id + temp_degree  + date,
                 data = hp_installed %>% filter(treated==1),
                 split = ~ rate_period,
                 cluster = ~account_id)
for (i in 1:5) {
  
  # Find model
  val <- tempreg[[i]]$model_info$sample$value
  j <- which(sapply(1:5, function(j) m1[[j]]$model_info$sample$value) == val)
  
  # Extract coefficients and standard errors
  coefs <- coeftable(tempreg[[i]]) %>%
    data.frame() %>%
    tibble::rownames_to_column("term") %>%
    as_tibble() %>%
    separate(term, into = c("is_hp_installed", "remove1", "daily_avg_air_temperature_celsius", "remove2"), sep = "::") %>%
    mutate(daily_avg_air_temperature_celsius = as.numeric(daily_avg_air_temperature_celsius),
           lower_ci = Estimate - 1.96 * `Std..Error`,
           upper_ci = Estimate + 1.96 * `Std..Error`
    ) %>%
    mutate(`/% ATE` = Estimate / m1[[j]]$coefficients * 100,     
           lower_ci_ATE = `/% ATE` - 1.96 * (`Std..Error` / m1[[j]]$coefficients * 100),
           upper_ci_ATE = `/% ATE` + 1.96 * (`Std..Error` / m1[[j]]$coefficients * 100)
    )
  
  # Create the ggplot
  ggplot(coefs, aes(x = daily_avg_air_temperature_celsius, y = Estimate)) +
    geom_point(color = hp_color) +
    geom_line(color = hp_color) +
    geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, alpha = 0.6, color = hp_color) +
    geom_hline(yintercept = m1[[j]]$coefficients, linetype = "dashed", alpha = 0.6, color = hp_color) +  # Add horizontal line at 100% ATE
    scale_y_continuous(
      sec.axis = sec_axis(~ ./m1[[j]]$coefficients, name = "% of ATE", labels = scales::percent_format())
    ) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
    labs(
      x = "Average Temperature in Degrees (°C)",
      y = "Estimate (kWh)"
    ) +
    theme_minimal()
  
  # Print the plot
  ggsave(paste0("../graphs/hp_temperature_", tolower(gsub(" ", "_", val)), ".png"),
         width = 16, height = 8, units = "cm")
}

```

## Installer FE [Not included in the paper]

```{r variance-decomposition}
# =======================
# 1. Data Preparation & Regression
# =======================

# Installer FE
installers <- fread("../data/input/cosy_-_hp_engineers_2025_03_17.csv") %>%
  filter(account_id %in% hp_installed[hp_installed$treated==1,]$account_id) %>%
  filter(hp_engineer != "") %>%
  group_by(hp_engineer) %>%
  mutate(n = n()) %>%
  filter(n > 1) %>%
  select(-n)

# Prepare data: filter, join, engineer features
df <- hp_installed %>%
  filter(treated == 1, rate_period == "Overall") %>%
  distinct(account_id, deal_created_at) %>%
  inner_join(installers) %>%
  filter(hp_engineer != "") %>%
  group_by(hp_engineer) %>%
  tally() %>%
  filter(n > 1) %>%
  rename(num_install = n) %>%
  inner_join(installers) %>%
  inner_join(hp_installed) %>%
  filter(treated == 1, rate_period == "Overall") %>%
  mutate(temperature = round(daily_avg_heating_degree))

# Main model: includes interaction and fixed effects
reg <- feols(
  consumption_hh ~ i(is_hp_installed, ref = 0) +
    i(is_hp_installed, hp_engineer, ref = 0, ref2 = "Steven Wiltshire") |
    account_id + date + temperature,
  cluster = ~account_id,
  data = df
)

etable(reg)
```

```{r out-of-sample-predictions}
# stratified randomisation
set.seed(123)
installers$insample <- randomizr::strata_rs(strata = installers$hp_engineer, 
                                       prob = 0.5)

# Regression in sample
m_insample <- feols(
  consumption_hh ~ i(is_hp_installed, ref = 0) +
    i(is_hp_installed, hp_engineer, ref = 0, ref2 = "Steven Wiltshire") |
    date + temperature,
  cluster = ~account_id,
  data = df %>% filter(hp_engineer %in% installers[installers$insample == 1,]$hp_engineer)
)

# Predict out of sample
df$consumption_hh_pred <- predict(m_insample, 
                                  newdata = df)

# Out of sample regression
m_outsample <- feols(
  consumption_hh ~ consumption_hh_pred |
     account_id,
  cluster = ~account_id,
  data = df %>% filter(hp_engineer %in% installers[installers$insample == 0,]$hp_engineer)
)

# Plot data
plot_data <- df %>%
  inner_join(installers) %>%
  mutate(insample_label = ifelse(insample == 1, "In-sample", "Out-of-sample")) 

ggplot(plot_data, aes(x = consumption_hh_pred, 
                      y = consumption_hh, 
                      color = factor(insample_label),
                      group = factor(insample_label))) +
  geom_point(alpha = 0.3) +
  scale_color_manual(values = c("In-sample" = hp_color, 
                                "Out-of-sample" = "grey")) +
  geom_smooth(method = "lm", se = FALSE) +
  labs(
    x = "Predicted Consumption (kWh)",
    y = "Actual Consumption (kWh)",
    color = "Group",
    title = "Predicted vs. Actual Consumption",
    subtitle = "Linear fit for in-sample and out-of-sample households"
  ) +
  theme_minimal()

# plot engineer FE
ggplot(df, 
       aes(x = consumption_hh_pred, y = consumption_hh, 
           color = factor(insample_label))) +
  geom_point(alpha = 0.3) +
  scale_color_manual(values = c("In-sample" = hp_color, 
                                "Out-of-sample" = "grey")) +
  labs(
    x = "Engineer",
    y = "Consumption (kWh)",
    color = "Group",
    title = "Engineer-Specific Consumption",
    subtitle = "In-sample and out-of-sample households"
  ) +
  theme_minimal()

```

```{r variance-decomposition-2}

# manual decomposition of variance for FE
fes <- fixef(reg)
fe_account <- fes$account_id[as.character(df$account_id)]
fe_date <- fes$date[as.character(df$date)]
fe_temp <- fes$temperature[as.character(df$temperature)]

# decomposition of treatment effects
X <- model.matrix(reg)
interaction_cols <- grep("hp_engineer", colnames(X), value = TRUE)
interaction_pred <- as.numeric(X[, interaction_cols] %*% coef(reg)[interaction_cols])
ate_col <- grep("is_hp_installed::1$", colnames(X), value = TRUE)
ate_pred <- as.numeric(X[, ate_col] * coef(reg)[ate_col])

# total var of outcomes
var_total <- var(df$consumption_hh, na.rm = TRUE)

var_decomp <- data.frame(
  Component = c("Account FE", "Date FE", "HDD FE", "ATE", "Engineer Interaction"),
  Share = c(
    var(fe_account, na.rm = TRUE),
    var(fe_date, na.rm = TRUE),
    var(fe_temp, na.rm = TRUE),
    var(ate_pred, na.rm = TRUE),
    var(interaction_pred, na.rm = TRUE)
  ) / var_total
)

stargazer(var_decomp, 
          summary = FALSE, 
          label = "variance-decomp",
          out = "../tables/variance_decomp.tex",  
          title = "Decomposition of Variance in Consumption Outcomes",
          type = "latex")
```

```{r variance-decomposition-3}

# 3. Bias-Corrected FE Covariance (felm)

df2 <- df %>%
  inner_join(data.frame(date = as.Date(names(fes$date)), time_fe = fes$date)) %>%
  inner_join(data.frame(temperature = as.numeric(names(fes$temperature)), temp_fe = fes$temperature))

df2$consumption_hh_resid <- df2$consumption_hh - df2$time_fe - df2$temp_fe

reg_sub <- felm(
  consumption_hh_resid ~ is_hp_installed + is_hp_installed:hp_engineer | account_id,
  data = df2,
  cmethod = "reghdfe"
)

fe_sub <- getfe(reg_sub, se = TRUE)
covar <- fevcov(reg_sub, fe_sub)
covar_biased <- covar + attr(covar, "bias")
total_var <- var(df2$consumption_hh_resid, na.rm = TRUE)

interaction_cols <- grep("^is_hp_installed:hp_engineer", colnames(model.matrix(reg_sub)))
interact_pred <- model.matrix(reg_sub)[, interaction_cols] %*% coef(reg_sub)[interaction_cols]
main_pred <- model.matrix(reg_sub)[, "is_hp_installed"] * coef(reg_sub)["is_hp_installed"]

var_table <- data.frame(
  Component = c("Account FE", "Main Treatment Effect", "Treatment × Engineer"),
  Variance_Share = c(diag(covar / total_var), var(main_pred) / total_var, var(interact_pred) / total_var)
)

stargazer(var_table, 
          summary = FALSE, 
          label = "bias-coorected-variance-decomp",
          out = "../tables/bias_corrected_decomp.tex",  
          title = "Decomposition of Variance in Consumption Outcomes",
          type = "latex")
```

```{r variance-decomposition-4}
# 4. Covariance: Account FE × Interaction Effect
account_fe_vec <- fe_sub[fe_sub$fe == "account_id", c("idx", "effect")]
colnames(account_fe_vec) <- c("account_id", "account_fe")
account_fe_vec$account_id <- as.character(account_fe_vec$account_id)
df2$account_id <- as.character(df2$account_id)
df2 <- merge(df2, account_fe_vec, by = "account_id")

df2$interaction_pred <- interact_pred
cov_account_interaction <- cov(df2$account_fe, df2$interaction_pred, use = "complete.obs")
cor_account_interaction <- cor(df2$account_fe, df2$interaction_pred, use = "complete.obs")

cat("Covariance:", cov_account_interaction, "\n")
cat("Correlation:", cor_account_interaction, "\n")
```

```{r variance-decomposition-5}
# 5. Plot: Engineer FE vs Avg Household FE

engineer_house_fe <- df2 %>%
  group_by(hp_engineer) %>%
  summarise(avg_account_fe = mean(account_fe.y, na.rm = TRUE))

interaction_coefs <- coef(summary(reg_sub)) %>%
  as.data.frame() %>%
  rownames_to_column("term") %>%
  filter(grepl("^is_hp_installed:hp_engineer", term)) %>%
  mutate(hp_engineer = gsub("is_hp_installed:hp_engineer", "", term),
         hp_engineer = gsub("[()]", "", hp_engineer))

plot_data <- left_join(engineer_house_fe, interaction_coefs, by = "hp_engineer")

ggplot(plot_data, aes(x = avg_account_fe, y = Estimate)) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE, color = "black") +
  labs(
    x = "Average Account Fixed Effect",
    y = "Engineer-Specific Treatment Effect"
  ) +
  theme_minimal() +
  theme(legend.position = "none")

ggsave("../graphs/engineer_vs_household_fe.png", width = 8, height = 6)


# coeftable
coefs <- coeftable(reg) %>%
  data.frame() %>%
  tibble::rownames_to_column("term") %>%
  as_tibble() %>%
  separate(term, into = c("is_hp_installed", "remove1", "remove2", "remove3", "remove44" , "hp_engineer"), sep = ":") %>%
  mutate(lower_ci = Estimate - 1.96 * `Std..Error`,
         upper_ci = Estimate + 1.96 * `Std..Error`
  ) %>% filter(!is.na(remove3))




```

```{r installer-fe, eval=TRUE}
rm(m1, m1c, m_solar, ev_charging, ev_users, ev_charging_agg)

# Installer FE
installers <- fread("../data/input/cosy_-_hp_engineers_2025_03_17.csv") 

# Unique periods 
periods <- unique(hp_installed$rate_period)

# Run the regression model
m1 <- feols(consumption_hh ~ i(is_hp_installed, ref=0) |
              account_id + daily_avg_heating_degree  + date,
            data = hp_installed %>% filter(rate_period == "Overall"),
            cluster = ~account_id) 

# Run the regression model
tempreg <- feols(consumption_hh ~ i(is_hp_installed, hp_engineer, ref=0) |
                   account_id + round(daily_avg_heating_degree)  + date,
                 data = df,
                 cluster = ~account_id) 

coefs <- coeftable(tempreg) %>%
  data.frame() %>%
  tibble::rownames_to_column("term") %>%
  as_tibble() %>%
  separate(term, into = c("is_hp_installed", "remove1", "remove2", "remove3", "remove4" , "hp_engineer"), sep = ":") %>%
  filter(!is.na(hp_engineer)) %>%
  mutate(lower_ci = Estimate - 1.96 * `Std..Error`,
         upper_ci = Estimate + 1.96 * `Std..Error`
  ) %>%
  mutate(`/% ATE` = Estimate / m1$coefficients * 100,     
         lower_ci_ATE = `/% ATE` - 1.96 * (`Std..Error` / m1$coefficients * 100),
         upper_ci_ATE = `/% ATE` + 1.96 * (`Std..Error` / m1$coefficients * 100)
  ) %>%
  arrange(Estimate) %>%
  mutate(hp_engineer = factor(hp_engineer, levels = unique(hp_engineer)))

# plot the yearly impact
yearly_factor <- 365.25*48
ggplot(coefs, aes(x = hp_engineer, y = Estimate * yearly_factor)) +  # Scale Estimate
  geom_point(color = hp_color) +
  geom_line(color = hp_color) +
  geom_errorbar(aes(ymin = lower_ci * yearly_factor, ymax = upper_ci * yearly_factor), 
                width = 0.2, alpha = 0.6, color = hp_color) +  # Scale CI
  geom_hline(yintercept = m1$coefficients * yearly_factor, 
             linetype = "dashed", alpha = 0.6, color = hp_color) +  # Scale ATE line
  scale_y_continuous(
    name = "Estimate (kWh per Year)",  # Update Y-axis label
    labels = label_comma(),  # Format y-axis with comma separator
    sec.axis = sec_axis(~ ./ (m1$coefficients[1] * yearly_factor), 
                        name = "% of ATE", 
                        labels = scales::percent_format())  # Scale % ATE
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Zero line
  labs(
    x = "Is Installed x Engineer"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_blank())

summary(coefs$Estimate)
quantile(coefs$Estimate, 0.75)/quantile(coefs$Estimate, 0.25)

# Print the plot
ggsave(paste0("../graphs/hp_engineer.png"),
       width = 16, height = 8, units = "cm")


```



## Figure A.6: Impact of Heat Pump Installation by EPC Rating 

```{r epc-analysis, eval=TRUE}
rm(tempreg)

m2a <- feols(consumption_hh ~ i(is_hp_installed, epc_letter, ref=0)  | 
               daily_avg_heating_degree + account_id + date,
             data = hp_installed %>%  
               filter(treated==1) %>%
               mutate(epc_letter = case_when(
                 energy_efficiency >= 91 ~ "A",
                 energy_efficiency >= 81 & energy_efficiency <= 90 ~ "B",
                 energy_efficiency >= 69 & energy_efficiency <= 80 ~ "C",
                 energy_efficiency >= 55 & energy_efficiency <= 68 ~ "D",
                 energy_efficiency >= 39 & energy_efficiency <= 54 ~ "E",
                 energy_efficiency >= 21 & energy_efficiency <= 38 ~ "F",
                 energy_efficiency <= 20 ~ "G",
                 TRUE ~ NA_character_
               )), 
             split = ~ rate_period,
             cluster = ~ account_id)

# Define colors to match the Energy Efficiency Rating chart
rating_colors <- c(
  "A" = "#00CC00",  # Green
  "B" = "#66FF33",  # Light Green
  "C" = "#FFFF00",  # Yellow
  "D" = "#FF9900",  # Orange
  "E" = "#FF6600",  # Dark Orange
  "F" = "#FF0000",  # Red
  "G" = "#990000"   # Dark Red
)

for (i in 1:5) {
  # Find model
  val <- m2a[[i]]$model_info$sample$value
  j <- which(sapply(1:5, function(j) m1[[j]]$model_info$sample$value) == val)
  
  # Extract coefficients and standard errors
  coefs <- coeftable(m2a[[i]]) %>%
    data.frame() %>%
    tibble::rownames_to_column("term") %>%
    separate(term, into = c("is_hp_installed", "remove1", "EPC_letter", "remove2"), sep = "::") %>%
    mutate(lower_ci = Estimate - 1.96 * `Std..Error`,
           upper_ci = Estimate + 1.96 * `Std..Error`
    ) %>%
    mutate(`% ATE` = Estimate / m1[[j]]$coefficients * 100,
           lower_ci_ATE = lower_ci / m1[[j]]$coefficients * 100,
           upper_ci_ATE = upper_ci / m1[[j]]$coefficients * 100)
  
  # Assuming coefs is your data frame and rating_colors is your color vector
  coefs <- coefs %>%
    mutate(EPC_label_position = max(`% ATE`) * 0.1)  # Position for EPC labels on the right
  
  # Create the ggplot
  if (mean(coefs$Estimate) > 0) {
    nudge_x <-  0.01
    
  } else {
    nudge_x <- -0.01
  }
  
  ggplot(coefs, aes(y = factor(EPC_letter, levels = rev(unique(EPC_letter))), x = Estimate, fill = factor(EPC_letter))) +
    geom_bar(stat = "identity", show.legend = FALSE) +
    geom_errorbar(aes(xmin = lower_ci, xmax = upper_ci), width = 0.2, color="grey") +
    geom_vline(xintercept = 0, linetype = "dashed", color = "black") +  # Add vertical line at x = 0
    geom_vline(xintercept = m1[[j]]$coefficients, linetype = "dashed", color = hp_color, alpha = 0.6) +  # Add vertical line at 100% ATE
    scale_fill_manual(values = rating_colors, name = "EPC Letter") +  # Use the defined colors
    geom_hline(yintercept = m1[[j]]$coefficients, linetype = "dashed", alpha = 0.6, color = hp_color) +  # Add horizontal line at 100% ATE
    # Add black "shadow" text for border effect
    geom_text(aes(label = EPC_letter, x = Estimate-nudge_x),  
              size = 4,
              color = "black",  # Black shadow
              fontface = "bold") +
    
    # Add white text on top
    geom_text(aes(label = EPC_letter, x = Estimate-nudge_x),  
              size = 4,
              color = "white",  # White text on top
              fontface = "bold") +
    scale_x_continuous(
      sec.axis = sec_axis(~ ./m1[[j]]$coefficients, name = "% of ATE", labels = scales::percent_format())
    ) +
    labs(
      x = "Estimate (kWh)",
      y = "EPC Letter"
    ) +
    theme_minimal() +
    theme(
      axis.text.y = element_blank(),  # Hide original y-axis text
      axis.ticks.y = element_blank(),  # Hide original y-axis ticks
      axis.text.y.right = element_text(hjust = 0.5),  # Center the text on the right-hand side
      axis.title.y.right = element_text(margin = margin(l = 10)),  # Add margin to right y-axis title
      legend.position = "none"  # Remove legend
    )
  
  # Print the plot
  ggsave(paste0("../graphs/hp_epc_", tolower(gsub(" ", "_", val)), ".png"),
         width = 16, height = 8, units = "cm")
}

rm(m2a)
```

## Figure A.10: Impact of Heat Pump Installation by Previous Heat Source

```{r hs-analysis, eval=TRUE}

m_sources <- feols(consumption_hh ~ i(is_hp_installed, hp_survey_outcome_existing_heat_source, ref=0)  | 
                     daily_avg_heating_degree + account_id + date,
                   data = hp_installed %>% filter(treated == 1, !hp_survey_outcome_existing_heat_source==""), 
                   split = ~ rate_period,
                   cluster = ~ account_id)

# Count unique occurrences per 'heat_source'
heat_source_counts <- hp_installed %>%
  filter(treated == 1, !hp_survey_outcome_existing_heat_source=="") %>%
  select(hp_survey_outcome_existing_heat_source, account_id) %>%   
  distinct() %>%
  group_by(hp_survey_outcome_existing_heat_source) %>%
  tally() %>%
  mutate(share = round(100*n/sum(n), digits=2))


for (i in 1:5) {
  # Find model
  val <- m_sources[[i]]$model_info$sample$value
  j <- which(sapply(1:5, function(j) m1[[j]]$model_info$sample$value) == val)
  
  # Assuming m_sources[[i]] is a model object that has already been defined
  coefs <- coeftable(m_sources[[i]]) %>%
    data.frame() %>%
    tibble::rownames_to_column("term") %>%
    separate(term, into = c("is_hp_installed", "remove1", "hp_survey_outcome_existing_heat_source", "remove2"), sep = "::") %>%
    mutate(
      heat_source = str_remove_all(hp_survey_outcome_existing_heat_source, "[{}]"),  # Remove curly braces
      heat_source = str_replace_all(heat_source, "_", " "),  # Replace underscores with spaces
      heat_source = str_to_title(heat_source),  # Capitalize the first letter of each word
      # Special handling for specific terms like 'LPG'
      heat_source = stringr::str_replace_all(heat_source, regex("Lpg", ignore_case = TRUE), "LPG"),
      lower_ci = Estimate - 1.96 * `Std..Error`,
      upper_ci = Estimate + 1.96 * `Std..Error`
    ) %>%
    inner_join(heat_source_counts, by = "hp_survey_outcome_existing_heat_source") %>%
    mutate(`% ATE` = Estimate / m1[[j]]$coefficients * 100,
           lower_ci_ATE = lower_ci / m1[[j]]$coefficients * 100,
           upper_ci_ATE = upper_ci / m1[[j]]$coefficients * 100)
  
  # Ensure that 'heat_source' is a factor ordered by 'Estimate' values
  coefs <- coefs %>%
    mutate(heat_source = factor(heat_source, levels = heat_source[order(Estimate)]))
  
  # Create the ggplot
  yearly_factor <- 365.25*48
  ggplot(coefs, aes(x = hp_engineer, y = Estimate * yearly_factor)) +  # Scale Estimate
    geom_point(color = hp_color) +
    geom_line(color = hp_color) +
    geom_errorbar(aes(ymin = lower_ci * yearly_factor, ymax = upper_ci * yearly_factor), 
                  width = 0.2, alpha = 0.6, color = hp_color) +  # Scale CI
    geom_hline(yintercept = m1$coefficients * yearly_factor, 
               linetype = "dashed", alpha = 0.6, color = hp_color) +  # Scale ATE line
    scale_y_continuous(
      name = "Estimate (kWh per Year)",  
      labels = label_comma(),  # Format y-axis with comma separator
      sec.axis = sec_axis(~ ./ (m1$coefficients[1] * yearly_factor), 
                          name = "% of ATE (Annualized)", 
                          labels = percent_format())  # Secondary y-axis as percentage
    ) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Zero line
    labs(
      x = "Is Installed x Engineer"
    ) +
    theme_minimal() +
    theme(axis.text.x = element_blank())
  
  # Print the plot
  ggsave(paste0("../graphs/hp_hs_", tolower(gsub(" ", "_", val)), ".png"),
         width = 20, height = 12, units = "cm")
}

rm(m_sources)
```

## Figure 7: Impact of Heat Pump Installation by MSOA Income

```{r income}
# Load and preprocess the cosy_hp_details data

cosy_hp_details <- fread("../data/input/cosy_-_hp_details_2024_07_03.csv") %>%
  inner_join(hp_installed %>% filter(treated == 1) %>% select(account_id) %>% distinct()) %>%
  filter(!postcode=="") %>%
  select(account_id, postcode)

postcode_msoa <- fread("../data/input/PCD_OA21_LSOA21_MSOA21_LAD_AUG23_UK_LU.csv") %>%
  left_join(cosy_hp_details, by = c("pcds" = "postcode")) %>%
  select(msoa21cd, pcds) %>%
  distinct(pcds, .keep_all = TRUE)

income <- readxl::read_excel("../data/input/saiefy1920finalqaddownload280923.xlsx", sheet = "Total annual income", skip = 4) %>%
  select(`MSOA code`, `Total annual income (£)`) %>%
  distinct() %>%
  inner_join(postcode_msoa, by=c("MSOA code"="msoa21cd")) %>%
  distinct(pcds, .keep_all = TRUE)


# Create unique breaks for predicted_heatloss_watts
income_dist <- readxl::read_excel("../data/input/saiefy1920finalqaddownload280923.xlsx", sheet = "Total annual income", skip = 4) %>%
  select(`MSOA code`, `Total annual income (£)`) 


breaks <- unique(quantile(income_dist$`Total annual income (£)`/1000, probs = seq(0, 1, by = 0.1)))

# Create pretty labels for the categories
labels <- sapply(1:(length(breaks)-1), function(i) paste0("£", round(breaks[i]), "k-", round(breaks[i+1]), "k"))

hp_installed <- hp_installed %>%
  left_join(cosy_hp_details) %>%
  left_join(income, by=c("postcode"="pcds")) %>%
  mutate(income_category = cut(`Total annual income (£)`/1000, 
                               breaks = breaks, 
                               include.lowest = TRUE,
                               labels = labels))
# income check
m_income <- feols(consumption_hh ~ i(is_hp_installed, income_category, ref =0) 
                  | date +  account_id + daily_avg_heating_degree,
                  data = hp_installed,
                  split = ~ rate_period,
                  cluster = ~account_id)

for (i in 1:5) {
  
  # Find model
  val <- m_income[[i]]$model_info$sample$value
  j <- which(sapply(1:5, function(j) m1[[j]]$model_info$sample$value) == val)
  
  # Extract coefficients and standard errors for total_consumption
  coefs_total <- coeftable(m_income[i]) %>%
    data.frame() %>%
    separate(coefficient, into = c("cosy_contract_active", "remove1", "Income Category", "remove2"), sep = "::") %>%
    mutate(lower_ci = Estimate - 1.96 * `Std..Error`,
           upper_ci = Estimate + 1.96 * `Std..Error`,
           outcome = "Total Consumption") %>%
    mutate(`Income Category` = factor(`Income Category`, levels = labels))
  
  # Define the shades of reds
  red_palette <- c("#FF9999", "#FF8080", "#FF6666", "#FF4D4D", "#FF3333", "#FF1A1A", "#FF0000", "#E60000", "#CC0000", "#B20000")
  
  # Create the ggplot
  ggplot(coefs_total, aes(x = `Income Category`, y = Estimate, fill = `Income Category`)) +
    geom_bar(stat = "identity", show.legend = FALSE) +
    geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, color = "grey") +
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
    geom_hline(yintercept = m1[[j]]$coefficients, linetype = "dashed", color = hp_color, alpha = 0.6) +  # Add horizontal line at ATE
    scale_fill_manual(values = red_palette) +
    labs(
      x = "Income Decile",
      y = "Estimate (kWh)"
    ) +
    scale_y_continuous(
      sec.axis = sec_axis(~ ./(m1[[j]]$coefficients), name = "% of ATE", labels = scales::percent_format())
    ) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),  # Tilt x-axis labels for better readability
      legend.position = "none"  # Remove legend
    )
  
  # Print the plot
  ggsave(paste0("../graphs/hp_income_", val %>% tolower() %>% str_replace(" ", "_"), ".png"),
         width = 16, height = 8, units = "cm")
  
}


# Initialize an empty data frame to store all coefficients
all_coefs <- data.frame()

# Extract coefficients for total consumption
for (i in 1:5) {
  val <- m_income[[i]]$model_info$sample$value
  j <- which(sapply(1:5, function(j) m1[[j]]$model_info$sample$value) == val)
  
  coefs_total <- coeftable(m_income[[i]]) %>%
    data.frame() %>%
    tibble::rownames_to_column("term") %>%
    separate(term, into = c("cosy_contract_active", "remove1", "Income Category", "remove2"), sep = "::") %>%
    mutate(
      lower_ci = Estimate - 1.96 * `Std..Error`,
      upper_ci = Estimate + 1.96 * `Std..Error`,
      `%_ATE` = Estimate / abs(m1[[j]]$coefficients) * 100,
      lower_ci_ATE = lower_ci / abs(m1[[j]]$coefficients) * 100,
      upper_ci_ATE = upper_ci / abs(m1[[j]]$coefficients) * 100,
      outcome = "Total Consumption",
      `Floor_Area` = factor(`Income Category`, levels = labels),
      period = factor(val, levels = c("Morning Cosy",
                                      "Afternoon Cosy",
                                      "Peak Rate",
                                      "Other", 
                                      "Overall")))
  
  all_coefs <- bind_rows(all_coefs, coefs_total)
}


# Define the shades of reds
red_palette <- c("#FF9999", "#FF8080", "#FF6666", "#FF4D4D", "#FF3333", "#FF1A1A", "#FF0000", "#E60000", "#CC0000", "#B20000")


# Create the combined ggplot using facet_wrap
ggplot(all_coefs %>% filter(outcome == "Total Consumption", period != "Overall"), 
       aes(x = `Income Category`, 
           y = Estimate, fill = `Income Category`)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, color = "grey") +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
  scale_fill_manual(values = red_palette) +
  labs(
    x = "Income Category Decile",
    y = "Estimate (kWh)"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Tilt x-axis labels for better readability
    legend.position = "none"  # Remove legend
  ) +
  facet_wrap(~ period)


# Save the combined plot
ggsave("../graphs/hp_income_category_combined.png", device = "png", width = 16, height = 12, units = "cm")
```

## property value

```{r}

# create property value decile
breaks <- hp_installed %>%
  filter(!is.na(property_value)) 
breaks <-
  quantile(breaks$property_value/1000, probs = seq(0, 1, by = 0.1)) %>%
  unique()

# Create pretty labels for the categories
labels <- sapply(1:(length(breaks)-1), function(i) paste0("£", round(breaks[i]), "k-", round(breaks[i+1]), "k"))
labels[10] <- "£742k+"

hp_installed <- hp_installed %>%
  mutate(property_value_category = cut(property_value/1000, 
                                       breaks = breaks, 
                                       include.lowest = TRUE,
                                       labels = labels))
# property_value check
m_property_value <- feols(consumption_hh ~ i(is_hp_installed, property_value_category, ref =0) 
                          | date +  account_id + daily_avg_heating_degree,
                          data = hp_installed,
                          split = ~ rate_period,
                          cluster = ~account_id)

for (i in 1:5) {
  
  # Find model
  val <- m_property_value[[i]]$model_info$sample$value
  j <- which(sapply(1:5, function(j) m1[[j]]$model_info$sample$value) == val)
  
  # Extract coefficients and standard errors for total_consumption
  coefs_total <- coeftable(m_property_value[i]) %>%
    data.frame() %>%
    separate(coefficient, into = c("cosy_contract_active", "remove1", "Property Value Category", "remove2"), sep = "::") %>%
    mutate(lower_ci = Estimate - 1.96 * `Std..Error`,
           upper_ci = Estimate + 1.96 * `Std..Error`,
           outcome = "Total Consumption") %>%
    mutate(`Property Value Category` = factor(`Property Value Category`, levels = labels))
  
  # Define the shades of reds
  red_palette <- c("#FF9999", "#FF8080", "#FF6666", "#FF4D4D", "#FF3333", "#FF1A1A", "#FF0000", "#E60000", "#CC0000", "#B20000")
  
  # Create the ggplot
  ggplot(coefs_total, aes(x = `Property Value Category`, y = Estimate, 
                          fill = `Property Value Category`)) +
    geom_bar(stat = "identity", show.legend = FALSE) +
    geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, color = "grey") +
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
    geom_hline(yintercept = m1[[j]]$coefficients, linetype = "dashed", color = hp_color, alpha = 0.6) +  # Add horizontal line at ATE
    scale_fill_manual(values = red_palette) +
    labs(
      x = "Property Value Decile",
      y = "Estimate (kWh)"
    ) +
    scale_y_continuous(
      sec.axis = sec_axis(~ ./(m1[[j]]$coefficients), name = "% of ATE", labels = scales::percent_format())
    ) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),  # Tilt x-axis labels for better readability
      legend.position = "none"  # Remove legend
    )
  
  # Print the plot
  ggsave(paste0("../graphs/hp_property_value_", val %>% tolower() %>% str_replace(" ", "_"), ".png"),
         width = 16, height = 8, units = "cm")
  
}

```

## Figure A.8: Impact of Heat Pump Installation by Heat Loss Decile


```{r heatloss-analysis, eval=TRUE}

hp_installed <- hp_installed %>%
  left_join(fread("../data/input/cosy_-_hp_details_2024_07_03.csv") %>%
              distinct(account_id, latest_survey_heat_loss) %>% filter(!is.na(latest_survey_heat_loss)))

# Create unique breaks for predicted_heatloss_watts
breaks <- unique(quantile(hp_installed[!is.na(hp_installed$latest_survey_heat_loss),]$latest_survey_heat_loss/1000, probs = seq(0, 1, by = 0.1)))

# Create pretty labels for the categories
labels <- sapply(1:(length(breaks)-1), function(i) paste0(round(breaks[i], 1), " mW to ", round(breaks[i+1], 1), " mW"))

# Create the categories for latest_survey_heat_loss
hp_installed <- hp_installed %>%
  mutate(latest_survey_heat_loss_category = cut(latest_survey_heat_loss/1000, 
                                                breaks = breaks, 
                                                include.lowest = TRUE,
                                                labels = labels))

m_heatloss <- feols(consumption_hh ~ i(is_hp_installed, latest_survey_heat_loss_category, ref =0) 
                    | account_id + daily_avg_heating_degree + date,
                    data = hp_installed %>% filter(!is.na(latest_survey_heat_loss_category)),
                    split = ~ rate_period,
                    cluster = ~account_id)

for (i in 1:5) {
  
  # Find model
  val <- m_heatloss[[i]]$model_info$sample$value
  j <- which(sapply(1:5, function(j) m1[[j]]$model_info$sample$value) == val)
  
  # Extract coefficients and standard errors for total_consumption
  coefs_total <- coeftable(m_heatloss[i]) %>%
    data.frame() %>%
    separate(coefficient, into = c("cosy_contract_active", "remove1", "Heatloss MW Category", "remove2"), sep = "::") %>%
    mutate(lower_ci = Estimate - 1.96 * `Std..Error`,
           upper_ci = Estimate + 1.96 * `Std..Error`,
           outcome = "Total Consumption") %>%
    mutate(`Heatloss MW Category` = factor(`Heatloss MW Category`, levels = labels))
  
  # Define the shades of reds
  red_palette <- c("#FF9999", "#FF8080", "#FF6666", "#FF4D4D", "#FF3333", "#FF1A1A", "#FF0000", "#E60000", "#CC0000", "#B20000")
  
  # Create the ggplot
  ggplot(coefs_total, aes(x = `Heatloss MW Category`, y = Estimate, fill = `Heatloss MW Category`)) +
    geom_bar(stat = "identity", show.legend = FALSE) +
    geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, color="grey") +
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
    geom_hline(yintercept = m1[[j]]$coefficients, linetype = "dashed", color = hp_color, alpha = 0.6) +  # Add horizontal line at ATE
    scale_fill_manual(values = red_palette) +
    labs(
      x = "Heatloss MW Decile",
      y = "Half Hourly Consumption in kWh"
    ) +
    scale_y_continuous(
      sec.axis = sec_axis(~ ./m1[[j]]$coefficients, name = "% of ATE", labels = scales::percent_format())
    ) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),  # Tilt x-axis labels for better readability
      legend.position = "none"  # Remove legend
    )
  
  # Print the plot
  ggsave(paste0("../graphs/hp_heatloss_", val %>% tolower() %>% str_replace(" ", "_"), ".png"),
         width = 16, height = 8, units = "cm")
  
}

```


### Figure A.9: Impact of Heat Pump Installation on Half-Hourly Electricity Consumption by
Region


```{r regions, eval=TRUE}

m_region <- feols(consumption_hh ~ i(is_hp_installed, region, ref =0) | 
                    account_id + daily_avg_heating_degree + date,
                  data = hp_installed %>% filter(!is.na(region), !region=="", rate_period == "Overall"),
                  cluster = ~account_id)


coefs_total <- coeftable(m_region) %>%
  data.frame() %>%
  tibble::rownames_to_column("term") %>%
  separate(term, into = c("is_hp_installed", "remove1", "Region", "remove2"), sep = "::") %>%
  mutate(
    average = m1[[4]]$coefficients,
    lower_ci = Estimate - 1.96 * `Std..Error`,
    upper_ci = Estimate + 1.96 * `Std..Error`,
    `%_ATE` = Estimate / abs(m1[[4]]$coefficients) * 100,
    lower_ci_ATE = lower_ci / abs(m1[[4]]$coefficients) * 100,
    upper_ci_ATE = upper_ci / abs(m1[[4]]$coefficients) * 100)

# Select a color palette from RColorBrewer
region_colors <- brewer.pal(n = length(unique(coefs_total$Region)), name = "Set3")

# Order regions by their estimate size for period == "Morning Cosy"
hp_order <- coefs_total %>%
  arrange(desc(Estimate)) %>%
  pull(Region)

# Reorder the Region factor based on the estimate size in "Morning Cosy"
coefs_total <- coefs_total %>%
  mutate(Region = factor(Region, levels = hp_order))

# Create the ggplot
ggplot(coefs_total, aes(x = Region, y = Estimate, fill = Region)) +
  geom_bar(stat = "identity") +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, color = "grey") +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
  geom_hline(aes(yintercept = m1[[4]]$coefficients), linetype = "dashed", color = hp_color, alpha = 0.6) +  # Add vertical line at average ATE
  scale_fill_manual(values = region_colors) +  # Apply random colors to regions
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Tilt x-axis labels for better readability
    legend.position = "none"  # Remove legend
  ) 

# Save the plot
ggsave("../graphs/hp_region_combined.png", device = "png", width = 16, height = 12, units = "cm")







```

### Figure A.7: Impact of Heat Pump Installation by Floor Area

```{r floor-area, eval=TRUE}

# Create unique breaks for total_floor_area
breaks <- unique(quantile(hp_installed[!is.na(hp_installed$total_floor_area),]$total_floor_area, 
                          probs = seq(0, 1, by = 0.1)))

# Create pretty labels for the categories
labels <- sapply(1:(length(breaks)-1), function(i) paste0(round(breaks[i], 0), " to ", round(breaks[i+1], 0), "m sq."))

# Create the categories for total_floor_area
hp_installed <- hp_installed %>%
  mutate(total_floor_area_category = cut(total_floor_area, 
                                         breaks = breaks, 
                                         include.lowest = TRUE,
                                         labels = labels))


m_floor <- feols(consumption_hh ~ i(is_hp_installed, total_floor_area_category, ref =0) 
                 | date +  account_id + daily_avg_heating_degree,
                 data = hp_installed %>% filter(!is.na(total_floor_area_category), treated==1),
                 split = ~ rate_period,
                 cluster = ~account_id)

for (i in 1:5) {
  
  # Find model
  val <- m_floor[[i]]$model_info$sample$value
  j <- which(sapply(1:5, function(j) m1[[j]]$model_info$sample$value) == val)
  
  # Extract coefficients and standard errors for total_consumption
  coefs_total <- coeftable(m_floor[i]) %>%
    data.frame() %>%
    separate(coefficient, into = c("cosy_contract_active", "remove1", "Floor_Area", "remove2"), sep = "::") %>%
    mutate(lower_ci = Estimate - 1.96 * `Std..Error`,
           upper_ci = Estimate + 1.96 * `Std..Error`,
           outcome = "Total Consumption") %>%
    mutate(`Floor_Area` = factor(`Floor_Area`, levels = labels),
           `% ATE` = Estimate / m1[[j]]$coefficients * 100,
           lower_ci_ATE = lower_ci / m1[[j]]$coefficients * 100,
           upper_ci_ATE = upper_ci / m1[[j]]$coefficients * 100)
  
  # Define the shades of reds
  red_palette <- c("#FF9999", "#FF8080", "#FF6666", "#FF4D4D", "#FF3333", "#FF1A1A", "#FF0000", "#E60000", "#CC0000", "#B20000")
  
  # Create the ggplot
  ggplot(coefs_total, aes(x = `Floor_Area`, y = Estimate, fill = `Floor_Area`)) +
    geom_bar(stat = "identity", show.legend = FALSE) +
    geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, color = "grey") +
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
    geom_hline(yintercept = m1[[j]]$coefficients, linetype = "dashed", color = hp_color, alpha = 0.6) +  # Add horizontal line at 100% ATE
    scale_fill_manual(values = red_palette) +
    scale_y_continuous(
      sec.axis = sec_axis(~ ./(m1[[j]]$coefficients), name = "% of ATE", labels = scales::percent_format())
    ) +
    labs(
      x = "Floor Area Decile",
      y = "Estimate (kWh)"
    ) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),  # Tilt x-axis labels for better readability
      legend.position = "none"  # Remove legend
    )
  
  # Print the plot
  ggsave(paste0("../graphs/hp_floor_area_", tolower(gsub(" ", "_", val)), ".png"),
         width = 16, height = 8, units = "cm")
}



m_floor_share <- feols(share_consumption ~ i(is_hp_installed, total_floor_area_category, ref =0)
                       | date +  account_id + daily_avg_heating_degree,
                       data = hp_installed %>% 
                         filter(!is.na(total_floor_area_category), !rate_period=="Overall", treated==1) %>%
                         group_by(account_id, date) %>%
                         mutate(share_consumption = total_consumption/sum(total_consumption)),
                       split = ~ rate_period,
                       cluster = ~account_id)

m1_share <- feols(share_consumption ~ i(is_hp_installed, ref =0)
                  | date +  account_id + daily_avg_heating_degree,
                  data = hp_installed %>% 
                    filter(!rate_period=="Overall", treated==1) %>%
                    group_by(account_id, date) %>%
                    mutate(share_consumption = total_consumption/sum(total_consumption)),
                  split = ~ rate_period,
                  cluster = ~account_id)

for (i in 1:4) {
  
  # Find model
  val <- m_floor_share[[i]]$model_info$sample$value
  j <- which(sapply(1:4, function(j) m1_share[[j]]$model_info$sample$value) == val)
  
  # Extract coefficients and standard errors for total_consumption
  coefs_total <- coeftable(m_floor_share[i]) %>%
    data.frame() %>%
    separate(coefficient, into = c("cosy_contract_active", "remove1", "Floor_Area", "remove2"), sep = "::") %>%
    mutate(lower_ci = Estimate - 1.96 * `Std..Error`,
           upper_ci = Estimate + 1.96 * `Std..Error`,
           outcome = "Total Consumption") %>%
    mutate(`Floor_Area` = factor(`Floor_Area`, levels = labels),
           `% ATE` = Estimate / m1_share[[j]]$coefficients * 100,
           lower_ci_ATE = lower_ci / m1_share[[j]]$coefficients * 100,
           upper_ci_ATE = upper_ci / m1_share[[j]]$coefficients * 100)
  
  # Define the shades of reds
  red_palette <- c("#FF9999", "#FF8080", "#FF6666", "#FF4D4D", "#FF3333", "#FF1A1A", "#FF0000", "#E60000", "#CC0000", "#B20000")
  
  # Create the ggplot
  ggplot(coefs_total, aes(x = `Floor_Area`, y = Estimate, fill = `Floor_Area`)) +
    geom_bar(stat = "identity", show.legend = FALSE) +
    geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, color = "grey") +
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add horizontal line at y = 0
    geom_hline(yintercept = m1_share[[j]]$coefficients, linetype = "dashed", color = hp_color, alpha = 0.6) +  # Add horizontal line at 100% ATE
    scale_fill_manual(values = red_palette) +
    labs(
      x = "Floor Area Decile",
      y = "Share of Daily Consumption (%)"
    ) +
    scale_y_continuous(
      breaks = seq(0, max(coefs_total$`% ATE`, na.rm = TRUE)),  # Set y-axis to % ATE with breaks at 100% intervals
      labels = function(x) paste0(x, "%")
    ) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),  # Tilt x-axis labels for better readability
      legend.position = "none"  # Remove legend
    )
  
  # Print the plot
  ggsave(paste0("../graphs/hp_share_floor_area_", tolower(gsub(" ", "_", val)), ".png"),
         width = 16, height = 8, units = "cm")
}

```

### Table A.5: HP Installation and Solar PV on Electricity Consumption 

```{r solar}

# Register the pre-treatment average fit statistic
fitstat_register("pre_avg_solar", function(x) {
  
  # Extract the formula
  formula <- x$fml_all$linear
  
  # Extract the outcome variable from the formula
  outcome_variable <- all.vars(formula)[1]
  
  # Extract the call object and evaluate the data argument
  call_object <- x$call
  data_expr <- call_object$data
  data <- eval(data_expr)
  
  # Get the logical vector of observations used in the model
  obs_used <- obs(x)
  
  # Subset the original dataset using this logical vector
  data_used <- data[obs_used, ]
  
  # Ensure the outcome variable is treated as a column name
  outcome_values <- data_used[[outcome_variable]]
  
  # Create pre-avg for non-HP installed group
  pre_avg <- mean(outcome_values[data_used$is_hp_installed == 0 & data_used$hp_survey_is_solar_present == TRUE], na.rm = TRUE)
  
  # Format the pre-avg
  formatted_pre_avg <- format_decimal(pre_avg)
  
  return(formatted_pre_avg)
}, "Yearly Consumption Has Solar PV")



# Register the pre-treatment average fit statistic
fitstat_register("pre_avg_rest", function(x) {
  
  # Extract the formula
  formula <- x$fml_all$linear
  
  # Extract the outcome variable from the formula
  outcome_variable <- all.vars(formula)[1]
  
  # Extract the call object and evaluate the data argument
  call_object <- x$call
  data_expr <- call_object$data
  data <- eval(data_expr)
  
  # Get the logical vector of observations used in the model
  obs_used <- obs(x)
  
  # Subset the original dataset using this logical vector
  data_used <- data[obs_used, ]
  
  # Ensure the outcome variable is treated as a column name
  outcome_values <- data_used[[outcome_variable]]
  
  # Create pre-avg for non-HP installed group
  pre_avg <- mean(outcome_values[data_used$is_hp_installed == 0 & data_used$hp_survey_is_solar_present == FALSE], na.rm = TRUE)
  
  # Format the pre-avg
  formatted_pre_avg <- format_decimal(pre_avg)
  
  return(formatted_pre_avg)
}, "Yearly Consumption No Solar PV")


# Fit the model
m_solar <- feols(total_consumption ~ i(is_hp_installed) + i(is_hp_installed, hp_survey_is_solar_present, ref = 0) | 
                   daily_avg_heating_degree + account_id + date, 
                 data = hp_installed %>% filter(treated == 1) %>% ungroup()  %>% 
                   mutate(total_consumption=365.25*total_consumption,   rate_period = factor(rate_period, levels = c("Morning Cosy",                                                                                                             "Afternoon Cosy","Peak Rate","Other", "Overall"))), 
                 cluster = ~account_id, 
                 split = ~ rate_period)

# Generate the initial LaTeX table
etable(m_solar,  tex = TRUE, title = "HP Installation and Solar PV on Electricity Consumption ", 
       fitstat = ~ N + g + pre_avg_rest + pre_avg_solar +t_obs + r2, 
       dict = c("total_consumption" = "Yearly Consumption in kWh"),
       file = "../tables/hp_did_solar.tex", replace = TRUE, label = "tab:hp-did-solar")

# Read the generated LaTeX file
file_content <- readLines("../tables/hp_did_solar.tex")

# Find the lines with the pre-treatment average and remove them
pre_avg_line_index <- grep("Yearly Consumption No Solar PV", file_content)
pre_avg_line_index2 <- grep("Yearly Consumption Has Solar PV", file_content)
pre_avg_lines <- file_content[pre_avg_line_index:(pre_avg_line_index2)]
file_content <- file_content[-c(pre_avg_line_index, pre_avg_line_index2)]

# Find the position just after the coefficients
coeff_end_index <- grep("Is HP Installed", file_content)[2] + 2
if (length(coeff_end_index) > 1) {
  coeff_end_index <- coeff_end_index[-1]
}

# Insert the pre-treatment average row after the coefficients
file_content <- append(file_content, pre_avg_lines, after = coeff_end_index)
file_content <- append(file_content, "\\emph{Pre-Treatment Average}\\\\", after = coeff_end_index)

# Add a \midrule after the pre-treatment average
file_content <- append(file_content, "\\midrule", after = coeff_end_index + 3)

# Modify the label for "Size of the 'effective' sample" to "Number of Households"
sample_line <- grep("Size of the 'effective' sample", file_content)
file_content[sample_line] <- gsub("Size of the 'effective' sample", "Number of Households", file_content[sample_line])

# Write the modified content back to the LaTeX file
writeLines(file_content, "../tables/hp_did_solar.tex")  

```

## DID checks

## Figure A.1: Smart Meter Data Availability for Heat Pump Customers

```{r panelview, eval=TRUE}

library(panelView)

plot_panel <- panelview(consumption_hh ~ is_hp_installed + daily_avg_heating_degree, 
                        data = hp_installed %>% filter(rate_period=="Overall") %>% select(consumption_hh, account_id, date, is_hp_installed, daily_avg_heating_degree) %>% distinct(), index = c("account_id","date"), 
                        xlab = "Time", 
                        ylab = "MPAN", 
                        by.timing = TRUE, 
                        pre.post = TRUE, 
                        gridOff = TRUE, 
                        axis.lab.gap = c(100),
                        main = "Smart Meter Data Availability",
                        background = "white",
                        color = c("grey", not_hp_color, hp_color, "white"),
                        legend.labs = c("Never Treated (Installation in Future)", 
                                        "Before HP Installation", "After HP Installation", 
                                        "No smart meter data"), collapse.history = "TRUE")

ggsave("../graphs/hp_data_availability.png", 
       width = 16, height = 8, units = "cm")

```



```{r panelviewgas, eval=TRUE}

library(panelView)

cosy_hp_install_gas_consumption <- fread("../data/input/cosy_-_hp_users_gas_2024_06_13.csv") %>%
  group_by(account_id) %>%
  mutate(is_hp_installed = as.numeric(installed_at <= settlement_week),
         treated = max(is_hp_installed),
         min_settlement_week = min(settlement_week)) %>%
  distinct(account_id, settlement_week, .keep_all = TRUE)


plot_panel <- panelview(weekly_consumption ~ is_hp_installed, 
                        data = cosy_hp_install_gas_consumption, index = c("account_id","settlement_week"), 
                        xlab = "Time", ylab = "MPAN", by.timing = TRUE, pre.post = TRUE, gridOff = TRUE,
                        axis.lab.gap = c(40),
                        main = "Gas Data Availability",
                        background = "white",
                        color = c("grey", not_hp_color, hp_color, "white"),
                        legend.labs = c("Never Treated (Installation in Future)", 
                                        "Before HP Installation", "After HP Installation", 
                                        "No smart meter data"), collapse.history = "TRUE")
ggsave("../graphs/hp_gas_data_availability.png", 
       width = 16, height = 8, units = "cm")

```


### CS parallele trends checks

```{r honestdid, eval=FALSE}
# # install from github
# remotes::install_github("asheshrambachan/HonestDiD")
library(HonestDiD)
honest_did <- function(es,
                       e          = 0,
                       type       = c("smoothness", "relative_magnitude"),
                       gridPoints = 100,
                       ...) {
  
  type <- match.arg(type)
  
  # Make sure that user is passing in an event study
  if (es$type != "dynamic") {
    stop("need to pass in an event study")
  }
  
  # Check if used universal base period and warn otherwise
  if (es$DIDparams$base_period != "universal") {
    stop("Use a universal base period for honest_did")
  }
  
  # Recover influence function for event study estimates
  es_inf_func <- es$inf.function$dynamic.inf.func.e
  
  # Recover variance-covariance matrix
  n <- nrow(es_inf_func)
  V <- t(es_inf_func) %*% es_inf_func / n / n
  
  # Check time vector is consecutive with referencePeriod = -1
  referencePeriod <- -1
  consecutivePre  <- !all(diff(es$egt[es$egt <= referencePeriod]) == 1)
  consecutivePost <- !all(diff(es$egt[es$egt >= referencePeriod]) == 1)
  if ( consecutivePre | consecutivePost ) {
    msg <- "honest_did expects a time vector with consecutive time periods;"
    msg <- paste(msg, "please re-code your event study and interpret the results accordingly.", sep="\n")
    stop(msg)
  }
  
  # Remove the coefficient normalized to zero
  hasReference <- any(es$egt == referencePeriod)
  if ( hasReference ) {
    referencePeriodIndex <- which(es$egt == referencePeriod)
    V    <- V[-referencePeriodIndex,-referencePeriodIndex]
    beta <- es$att.egt[-referencePeriodIndex]
  } else {
    beta <- es$att.egt
  }
  
  nperiods <- nrow(V)
  npre     <- sum(1*(es$egt < referencePeriod))
  npost    <- nperiods - npre
  if ( !hasReference & (min(c(npost, npre)) <= 0) ) {
    if ( npost <= 0 ) {
      msg <- "not enough post-periods"
    } else {
      msg <- "not enough pre-periods"
    }
    msg <- paste0(msg, " (check your time vector; note honest_did takes -1 as the reference period)")
    stop(msg)
  }
  
  baseVec1 <- basisVector(index=(e+1),size=npost)
  orig_ci  <- constructOriginalCS(betahat        = beta,
                                  sigma          = V,
                                  numPrePeriods  = npre,
                                  numPostPeriods = npost,
                                  l_vec          = baseVec1)
  
  if (type=="relative_magnitude") {
    robust_ci <- createSensitivityResults_relativeMagnitudes(betahat        = beta,
                                                             sigma          = V,
                                                             numPrePeriods  = npre,
                                                             numPostPeriods = npost,
                                                             l_vec          = baseVec1,
                                                             gridPoints     = gridPoints,
                                                             ...)
    
  } else if (type == "smoothness") {
    robust_ci <- createSensitivityResults(betahat        = beta,
                                          sigma          = V,
                                          numPrePeriods  = npre,
                                          numPostPeriods = npost,
                                          l_vec          = baseVec1,
                                          ...)
  }
  
  return(list(robust_ci=robust_ci, orig_ci=orig_ci, type=type))
}

# start date
start_date <- hp_installed %>% ungroup() %>% select(date) %>% distinct() %>% summarise(date = min(date))
start_date <- start_date$date

# Adjust your existing code to calculate 'week' and 'firstweek' as the number of weeks from the start_date
did_data <- hp_installed %>%
  filter(rate_period == "Overall") %>%
  mutate(
    # Calculate the difference in weeks from the start_date
    week = as.numeric(difftime(date, start_date, units = "weeks")) %/% 1 + 1,
    # Assuming you have a way to determine 'firstweek', adjust similarly if needed
    firstweek = as.numeric(difftime(installed_at, start_date, units = "weeks")) %/% 1 + 1) %>%
  group_by(account_id, firstweek, week) %>%
  summarise(consumption = mean(consumption_hh)) %>%
  mutate(
    firstweek = as.numeric(firstweek),
    week = as.numeric(week),
    firstweek = ifelse(firstweek>=117, 0, firstweek) # not treated needs to be 0 
  ) %>%
  group_by(account_id) %>%
  mutate(id = cur_group_id())  # all variables need to be numeric


did_data_subset <- did_data %>% ungroup()

# cs did estimator
library(did)
est_cs <- att_gt(yname = "consumption",
                 tname = "week",
                 idname = "id",
                 gname = "firstweek",
                 data = did_data_subset,
                 clustervars = "id",
                 control_group=c("notyettreated", "nevertreated"),
                 base_period = "universal",
                 allow_unbalanced_panel = TRUE,
                 print_details = FALSE)

es <- did::aggte(est_cs, type = "dynamic",
                 min_e = -5, max_e = 5, na.rm = TRUE)

#Run sensitivity analysis for relative magnitudes
sensitivity_results <- honest_did(es, e=0,type="relative_magnitude",Mbarvec=seq(from = 0.5, to = 2, by = 0.5))

HonestDiD::createSensitivityPlot_relativeMagnitudes(sensitivity_results$robust_ci,
                                                    sensitivity_results$orig_ci)

ggsave("../graphs/hp_sensitivity_results.png")

```

## Figure A.13: Event Study - Heat Pump Installation on Daily Average of Customers’
Half-Hourly Electricity Consumption

```{r event-study-plot}
# create df
event_study_df <- hp_installed %>%
  mutate(weeks_since_hp = as.numeric(difftime(date, installed_at, units = "weeks")) %/% 1 + 1,
         weeks_since_hp = case_when(
           weeks_since_hp < -52 ~ -52,
           weeks_since_hp > 52 ~ 52,
           TRUE ~ weeks_since_hp)) %>%
  select(account_id, weeks_since_hp, consumption_hh, daily_avg_heating_degree, date, rate_period)

rm(hp_installed)
gc()

m_event_study <- feols(consumption_hh ~ i(weeks_since_hp, ref=-1) | account_id + daily_avg_heating_degree + date, 
                       data = event_study_df %>% filter(rate_period=="Overall") %>% 
                         mutate(),
                       cluster = ~ account_id)

etable(m_event_study)

# plot the coefficients
# Extract coefficients and standard errors
coefs <- coeftable(m_event_study)%>%
  data.frame() %>%
  tibble::rownames_to_column("term")%>%
  as_tibble() %>%
  separate(term, into = c("var",  "weeks_since_hp"), sep = "::") %>%
  mutate(lower_ci = Estimate - 1.96 * `Std..Error`,
         upper_ci = Estimate + 1.96 * `Std..Error`,
         outcome = "Half Hourly Consumption") %>%
  mutate(weeks_since_hp = as.numeric(weeks_since_hp),
         post = (weeks_since_hp >-1))

# Create the plot
ggplot(coefs, aes(x = weeks_since_hp, y = Estimate, color = post)) +
  geom_point(stat = "identity", show.legend = TRUE) +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  labs(
    x = "Weeks Since HP Installation",
    y = "Half Hourly Consumption in kWh",
    color = "Is HP Installed"  # Update legend title
  ) +
  scale_color_manual(
    values = c("TRUE" = hp_color, "FALSE" = not_hp_color),  # Set custom colors
    labels = c("No", "Yes")  # Update legend labels
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Tilt x-axis labels for better readability
    legend.position = "right"  # Show legend
  )


# Print the plot
ggsave(paste0("../graphs/hp_event_study_overall.png"),
       width = 16, height = 8, units = "cm")

rm(m_event_study, hp_installed)


m_event_study <- feols(consumption_hh ~ i(weeks_since_hp, ref=-1) | account_id + daily_avg_heating_degree + date, 
                       data = event_study_df %>% filter(rate_period=="Peak Rate") %>% 
                         mutate(),
                       cluster = ~ account_id)

etable(m_event_study)

# plot the coefficients
# Extract coefficients and standard errors
coefs <- coeftable(m_event_study)%>%
  data.frame() %>%
  tibble::rownames_to_column("term")%>%
  as_tibble() %>%
  separate(term, into = c("var",  "weeks_since_hp"), sep = "::") %>%
  mutate(lower_ci = Estimate - 1.96 * `Std..Error`,
         upper_ci = Estimate + 1.96 * `Std..Error`,
         outcome = "Half Hourly Consumption") %>%
  mutate(weeks_since_hp = as.numeric(weeks_since_hp),
         post = (weeks_since_hp >-1))

# Create the plot
ggplot(coefs, aes(x = weeks_since_hp, y = Estimate, color = post)) +
  geom_point(stat = "identity", show.legend = TRUE) +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  labs(
    x = "Weeks Since HP Installation",
    y = "Half Hourly Consumption in kWh",
    color = "Is HP Installed"  # Update legend title
  ) +
  scale_color_manual(
    values = c("TRUE" = hp_color, "FALSE" = not_hp_color),  # Set custom colors
    labels = c("No", "Yes")  # Update legend labels
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Tilt x-axis labels for better readability
    legend.position = "right"  # Show legend
  )


# Print the plot
ggsave(paste0("../graphs/hp_event_study_peak_rate.png"),
       width = 16, height = 8, units = "cm")


```
